### 2015-10-08 section/0_intro.tex
check into github

\section{Introduction}
\label{sec:intro}
\subsection{Motivation}

Performance bugs\footnote{We also refer performance bugs as performance problems
following previous works in this area~\cite{PerfBug,Alabama,SongOOPSLA2014}} 
are software implementation mistakes that cause unnecessary performance
degradation in software. They widely exist in deployed software due to the 
complexity of modern software and the lack of testing support
~\cite{s2e,PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
They annoy end users and waste energy during production runs, and 
have already caused highly publicized failures~\cite{ACA-health,colorado}.
Tools that can help
developers quickly and accurately diagnose performance problems,
find performance-wasting root causes, and fix performance problems
are sorely desired.

Like general failure diagnosis, 
performance diagnosis starts from studying a problem symptom and hopefully ends
at identifying the root cause and suggesting a fix strategy. 
In the context of performance problems,
the symptom is often
an execution showing severe absolute or
relative slowness \cite{SongOOPSLA2014}; the root cause contains 
information like which code region is inefficient and why
it is inefficient. An effective diagnosis tool can help developers quickly
and correctly figure out a patch to fix the performance problem.

Also like general failure diagnosis, ideal performance diagnosis tools should
satisfy three criteria.
\begin{itemize}
\item Coverage. 
Real-world performance problems are caused by a wide variety of reasons. It 
would be good if the diagnosis tool can cover a good portion of common
root causes of real-world problems.

\item Accuracy. 
The accuracy requirement applies for two aspects of performance diagnosis: (1)
the inefficient code regions need to be accurately located and (2)
the reason a specific region is inefficient needs to be accurately
explained, so that developers can quickly fix the performance problem.

\item Performance. 
Diagnosis often requires collecting run-time information. The lower the overhead
is, the easier for the diagnosis tool to be deployed, especially for 
production-run usage scenarios. 
\end{itemize}

Although progress has been made, no existing tools can satisfy the above
three requirements.

Profiling is the state of practice in performance diagnosis.
It is far from providing the desired \textit{accuracy}, as it is designed to
tell where computation resources are spent, 
but not where and why computation resources are wasted. 
In many cases, the root-cause function of a performance problem may not even
get ranked by a profiler \cite{SongOOPSLA2014}.

Performance bug detection tools use static or dynamic analysis to identify
code regions that match specific inefficiency patterns 
\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616}. 
Unfortunately, these tools are not designed for performance diagnosis.
Consequently, they are not designed to provide \textit{coverage} for a wide
variety of real-world performance problems; they do not target a specific
performance symptom, and hence are at disadvantage in terms of diagnosis
\texttt{accuracy}; dynamic performance-bug detection tools often lead to 
10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
not ideal in terms of \textit{performance}.

Recently, progress has been made on applying statistical debugging to 
performance diagnosis \cite{SongOOPSLA2014}. Given the symptom of 
a performance problem (e.g., two similar inputs leading to very
different execution speed),
statistical debugging, an approach widely used for diagnosing
functional failures \cite{liblit03,liblit05,tarantula1}, can
accurately identify control-flow constructs that are most correlated with
the performance problem by comparing problematic runs and regular runs.
Unfortunately, for loop-related 
performance problems, which contribute to two thirds of
real-world performance problems studied in previous work 
\cite{SongOOPSLA2014,PerfBug}, statistical debugging is not very effective.
Although it can identify the root-cause loop, it does not provide any 
information regarding why the loop is inefficient and hence is not very helpful
in fixing the performance problem.

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC27733.c}}
\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch)}
\label{fig:GCC27733}
\end{figure}

Figure~\ref{fig:GCC27733} shows a real-world performance bug in GCC. 
Function \texttt{synth\_mult} is used to compute the best algorithm for 
multiplying \texttt{t}. It is so time consuming that developers tried 
speeding it up through memoization ---
hash-table
\texttt{alg\_hash} is used to remember which \texttt{t} has been processed
in the past and what is the processing result. 
Unfortunately, a small mistake in the type declaration of hash-table
entry \texttt{alg\_hash\_entry} causes memoization not to work when \texttt{t}
is larger than the maximum value type-\texttt{int} can represent.
As a result, under certain workload, \texttt{synth\_mult} conducts a lot of
redundant computation for same \texttt{t} values recursively, leading to
huge performance problems.  In practice, developers know the problem is inside
\texttt{synth\_mult} very early. However, since this function is 
complicated, it took them several weeks to figure out the root cause. 
If a tool can tell them not only which loop\footnote{Recursive functions are
handled similarly as loops in this paper.}
is the root cause but also why a loop is inefficient (i.e., lot of redundant
computation and the need for better memoization in this example), 
the diagnosis and bug fixing
process would be much easier for developers.

Clearly, more research is needed to improve the state of the art of performance
diagnosis. Diagnosis techniques that can provide better
\textit{coverage} and \textit{accuracy} for common performance problems,
especially loop-related performance problems, with good
performance is well desired.

\subsection{Contributions}
This paper presents a tool, \Tool, that can help effectively diagnose
inefficient loop problems with good coverage, accuracy, and performance.

\Tool targets the most common type of performance problems, inefficient
loops, according to previous
empirical studies \cite{SongOOPSLA2014,PerfBug}.
\Tool also targets a challenging problem. Although
statistical debugging \cite{SongOOPSLA2014}
can help identify suspicious loops that are highly correlated with 
user-perceived performance problems,
it provides no information about why the suspicious loop is inefficient,
not to mention providing fix suggestions. Although various
bug-detection techniques \cite{Cachetor,Alabama,CARAMEL} can help detect
loop-related performance bugs, they all suffer from generality problems,
covering only a specific type of loop problems each; the dynamic
tools \cite{Cachetor,Alabama} also suffer from performance
problem, imposing 10X slowdown or more.

\Tool tackles this challenging problem in three steps.
%}

First, figuring out a taxonomy for the root causes of common inefficient loops.
Such a taxonomy is the prerequisite to developing a general and accurate
diagnosis tool. Guided by a thorough study of 45 real-world inefficient
loop problems, we come up with a hierarchical root-cause taxonomy for
inefficient loops. 
%Specifically, we consider \textit{resultless} and
%\textit{redundancy} as two main categories of root causes for inefficient
%loops, representing loops that spend effort without producing
%any results or producing redundant results. They are further divided into
%sub-categories based on the granularity of the resultless or redundant work. 
Our empirical study shows that our taxonomy is general enough to cover
common inefficient loops, and also specific enough to help developers understand
and fix the performance problem. We will present more details 
in Section \ref{sec:study}.

Second, building a tool(kit) \Tool that can automatically and accurately
identify the fine-grained root-cause type of a suspicious loop, 
together fix-strategy suggestions. 
We achieve this following several principles:

\begin{itemize}
\item Focused checking. 
Different from performance-bug detection tools that blindly checks the whole
software, \Tool focuses on performance symptoms and only check inefficient
loop candidates identified by existing tools, a statistical debugging
tool in our current prototype \cite{SongOOPSLA2014}. 
This focused study is crucial for \Tool to achieve high
accuracy.

\item Root-cause taxonomy guided design. To provide the needed coverage, we follow
the root-cause taxonomy discussed above and design analysis routines for 
every root-cause sub-category. Given a candidate inefficient loop, we will 
apply a series of analysis to it to see if it matches any type of inefficiency.
%We will also put the analysis results from different analysis routines together
%to figure out the most likely root cause category for an inefficient loop.

\item Static-dynamic hybrid analysis to balance performance and accuracy.
As we will see, static analysis alone cannot accurately identify 
inefficiency root causes, especially because some inefficiency problems only
happen under specific workload. However, pure dynamic analysis will 
cause too large 
run-time overhead. Therefore, we take a hybrid approach to achieve both
performance and accuracy goals.
\end{itemize}

Third, using sampling to further lower the run-time overhead of \Tool, without
degrading diagnosis capability. Random sampling is a natural fit for performance
diagnosis due to the repetitive nature of inefficient code, especially
inefficient loops.

We have evaluated \Tool on 18 real-world performance problems. 
Evaluation results show that \Tool can accurately identify the detailed
root cause for all benchmarks and provide correct fix-strategy suggestion for
16 benchmarks. All these are achieved with low run-time overhead.

### 2015-10-08 section/1_under.tex
check into github

\section{Root-Cause Taxonomy}
\label{sec:study}

The first task we are facing is to figure out a root-cause taxonomy for
real-world inefficient loops. 
Our taxonomy design is guided by checking a benchmark suite of real-world
inefficient loops, collected by previous work \cite{SongOOPSLA2014,PerfBug}. 
We also try to satisfy three requirements in our design.
(1) Coverage: covering
a big portion of real-world inefficient loop problems; 
(2) Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
(3) Generality: too application-specific root causes will not work, as we
need to build diagnosis tools to automatically identify these root causes 
without developers' help.
In this section, we will first present our taxonomy, together with real-world
examples, followed by our empirical study about how a suite of real-world 
inefficient
loop problems fall into our root-cause categories.

We should note that we are definitely not the first one who tries to categorize
the root-cause patterns of performance problems. We are also not the first
to identify many of the root-cause categories below. Instead, guided by
previous work and our empirical study, we try to figure out our own taxonomy 
that satisfy the above three requirements and can
work well with the diagnosis tool that we will build later.

\subsection{Taxonomy}
\label{sec:study_tax}
Our taxonomy contains two major root cause categories,
\textit{resultless} and \textit{redundancy}, and several sub-categories, 
as below.

\underline{\textit{\textbf{Resultless}}}
Resultless loops spend a lot of time in computation that does not 
produce any results that will be used after the loop.
Depending on when such resultless computation is conducted, we further
consider four sub-categories.

{\textbf{0*}}: 
This type of loops never produce any results in any iteration.
This type of loops should be rare in mature software systems.
They should simply be deleted from the program.
%Question: dynamic or static?

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
\caption{A resultless 0*1? bug in Mozilla}
\label{fig:Mozilla347306}
\end{figure}

{\textbf{0*1?}}:
This type of loops only produce results in the last iteration, if any. 
They are often related to search: they check a sequence of elements one
by one until the right one is found.
Not all loops of this type are inefficient. If they are, they are often
fixed by data-structure changes.
Figure~\ref{fig:Mozilla347306} shows an example from Mozilla
JavaScript engine. 
The loop searches through an array containing source code information for the input \texttt{pc}. 
In practice, this loop needs to execute more than 10000 iterations for 
many long JavaScript encountered by users, which leads to huge 
performance problems --- web browsers freeze. To fix this problem, 
developers simply replace array with hash table when processing long
JavaScript files.
% This improve the performance by 52.60{\bf X}.

\comment{
This loop searches through xxx for xxx.
When xx, this loop often needs to execute xx iterations, which is very
time consuming.
The developers simply change the data-structure of xx from xx to a hash
table, which eliminates this loop and improving the performance by xxx.}
%Linhai, you have to describe examples using words people can understand
%and you have to provide useful information, such as what is the purpose
% of the loop. What is the loop searching for? What is the bug-triggering
%workload; how bad the performance (throughput or latency) was; how good
%is the fixed version in terms of performance.
\comment{
\textcolor{red}{
MySQL\#27287 is caused by linear backward searching for parent node during XML string parsing. 
In each iteration of the buggy loop, one previous sibling will be skipped, 
and in the last iteration, parent node will be returned. 
The patch applies a stack-like data structure to keep all parent nodes who have unparsed children to avoid the linear backward searching.
} } 
%Linhai, I have no idea what you are talking about here for mysql27287

%TOADD: performance diagnosis is different from bug detection%
%in many cases, there is no absolutely ``bad'' cases. performance problems are
%often a trade-off between code simplicity, performance, xxx.
%treating it like bug detection will inevitably lead to false positives
%we are providing information to developers

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\label{fig:GCC46401}
\end{figure}

{\textbf{[0$|$1]*}}:
Every iteration in this type of loops may or may not produce results.
Under certain workload, the majority of the loop iterations do not produce
any results and lead to performance problems perceived by end users.
The inefficiency problem caused by this type of loops can often be solved
by adding extra conditions to skip the loop under certain contexts.
Figure~\ref{fig:GCC46401} shows such an example from GCC.
%how users perceive this problem
%explain how every iteration may or may not produce any results
%explain the fix
Only when the if branch executed,
one iteration will generate results. 
The bug happens when GCC checks violation of sequence point rule. 
The user notice severe performance degradation when enabling the checking. 
The buggy loop is super-linear inefficient in terms of the number of operands
in one expression. The buggy input contains an expression, which is long and special. 
The loop takes a lot of iterations during bad run, but none of the iterations will 
generate results. 
The patch is to add extra checking before processing each operand. When it also has
the special feature like the bad input, the loop will be skipped.

\comment{
\textcolor{red}{ 
%For example, the patch for GCC\#46401 is to skip the sequence point checking loop when one operand is a constant string.
For example, a long expression inside the bug-triggering input exposes the super-linear 
inefficiency of checking violation of sequence point rule for GCC\#46401. 
Each operand on the expression will be compared with all previous operands on the same expression.
When fixing the bug,
developers notice that each operand on the buggy expression has a special feature which make the violation checking never 
report warning (generate results). 
The patch designed by developers is to add an extra condition checking to skip the violation checking for operands with that feature.    
}
}

{\textbf{[1]*}}:
Loops in this category always generate results in almost all iterations. 
They are inefficient, because the results generated could be useless due to
some high-level semantic reasons.
Understanding and fixing this type of inefficiency problems often require
deep understanding of the program and are difficult to automate.
For example, several Mozilla performance problems are caused by 
loops that contain intensive GUI operations.
Although every iteration of these loops produce side effects, 
the performance problem forced developers to change the program 
and batch/skip some GUI operations.

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
\caption{A cross-loop redundant bug in Mozilla }
\label{fig:Mozilla477564}
\end{figure}

\underline{\textit{\textbf{Redundant}}}
Redundant loops spend a lot of time in repeating computation that is already
conducted.
Depending on the unit of the redundant computation, we further consider 
two sub-categories.

%\begin{figure}[h]
%\centering
%\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
%     morekeywords={+},keepspaces=true}
%  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC1687.c}}
%\caption{A cross-iteration redundant bug in GCC 
% (\texttt{walk\_tree} will call itself recursively inside the loop, 
% and during buggy run, many iterations are doing exactly the same thing.)  }
%\label{fig:GCC1687}
%\end{figure}

\begin{figure}[h]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla490742.js}}
\caption{A cross-iteration redundant bug in Mozilla }
\label{fig:Mozilla490742}
\end{figure}

{\textbf{Cross-iteration Redundancy}}:
Loop iteration is the redundancy unit here:
one iteration repeats
repeating what was already done by an earlier iteration of the same loop.
Here, we consider recursive function calls as a loop, treating one function 
call instance as one loop iteration. 
This type of inefficiency is often fixed by memoization or batching, depending
on whether the redundancy involves I/O operations.
For example, GCC\#27733 shown in Figure~\ref{fig:GCC27733} 
is fixed by better memoization. 
%Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
%This bug is fixed by using a hash table to avoid visiting the same sub-tree twice.
Mozilla\#490742 in Figure~\ref{fig:Mozilla490742} represents a slightly different type of cross-iteration
redundancy. The inefficient loop in this case saves one URL into the ``Favorite
Links'' database in each iteration. One database transaction in each iteration
turns out to be to time consuming, with too much redundant work across
iterations. At the end, developers decide to batch all database updates into 
one big transaction, which speeds up some workload like 
bookmarking 50 tabs 
from popping up timeout windows to not blocking.
%xxx from several minutes
%to a couple of seconds.

{\textbf{Cross-loop Redundancy}}:
A whole loop is the redundancy unit here:
one dynamic instance of a loop spends a big chunk, if not all, of its
computation in repeating the work already done by an
earlier instance of the same loop.
Developers often fix this type of inefficiency problems through memoization:
caching the earlier computation results and skip following redundant loops.
Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
The buggy loop is to count how many previous siblings of the input \texttt{aNode} have the same name and URI. 
There is an outer loop for the buggy one, and the outer loop will update \texttt{aNode} by using its next siblings. 
The bug is fixed by saving the calculated count for each node. 
A new count value is calculated by adding one to the saved count value of the nearest previous sibling with the same name and URI.

\subsection{Empirical study}
\label{sec:tax_study}
Having presented our taxonomy above, we will see how it works for a set of
real-world inefficient loop problems collected by previous work
\cite{SongOOPSLA2014,PerfBug}. Specifically, we want to check the 
coverage and the actionability of our taxonomy presented above:
(1) How common are real-world performance problems caused by the 
patterns discussed above?
(2) How are real-world problems fixed by developers? Can we predict their
fix strategies based on the root-cause pattern?

\subsubsection{Methodology}
\begin{table}[h!]
\centering
\begin{tabular}{@{\hspace{3pt}}l@{\hspace{3pt}}|@{\hspace{3pt}}c@{\hspace{3pt}}}
\hline
Application Suite Description (language) & \# Bugs \\
\hline                            
{\bf Apache Suite} 	 & 11\\
%\cline{1-1}
{HTTPD:	Web Server (C)	}& \\
{TomCat:  Web Application Server (Java)}& \\
{Ant:	Build management utility (Java)}& \\
%\hline
%JMeter	& Load test utility (Java) & \\
\hline                            
{\bf Chromium Suite} Google Chrome browser (C/C++) & 4\\
\hline
%\multicolumn{2}{|l|}
{\bf GCC Suite}  GCC \& G++ Compiler (C/C++)     & 8\\
\hline
{\bf Mozilla Suite}  & 12\\
%\cline{1-1}
{Firefox: Web Browser (C++, JavaScript)}& 	\\
{Thunderbird: Email Client (C++, JavaScript)}& \\
\hline
{\bf MySQL Suite}     & 10	\\
%\cline{1-1}
{Server: Database Server (C/C++)}&  	\\
%\cline{1}
{Connector: DB Client Libraries (C/C++/Java/.Net)} &  	\\
\hline
{\bf Total}	   & 45 \\
\hline
\end{tabular}
\caption{Applications and bugs used in the study}
\label{tab:app_bug}
\end{table}

Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects, as 
shown in Table \ref{tab:app_bug}. Through a mix of random sampling and 
manual inspection, they 
found 65 performance problems that are perceived and reported by users. 
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study 
here\footnote{The definition of ``loop-related'' in this paper is a little
bit broader than earlier paper~\cite{SongOOPSLA2014}, which only considers
43 problems as loop-related. }.
More details can be found in the original papers that collect
these bugs.

\subsubsection{Observations}
\label{sec:study_ob}
\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{|lccccccl|}
\hline
&Apache&Chrome&GCC&Mozilla&MySQL&Total&Fix Strategy\\
\hline
Total \# of loop-related bugs & 11 & 4 & 8 & 12 & 10 & 45 &  \\
\hline
\multicolumn{8}{|c|}{\# of {\textit {Resultless}} bugs}\\
\multicolumn{1}{|l}{ {\bf 0*} }
&0&0&0&0&0&0&\\
\multicolumn{1}{|l}{ {\bf 0*1?} }
&0&0&0&2&3&5&C(4)$|$S(1)\\
\multicolumn{1}{|l}{{\bf [0$|$1]*}}
&0&1&1&1&1&4&S(4)\\
\multicolumn{1}{|l}{{\bf 1*}}
&1&2&3&6&3&15& B(4)$|$S(4)$|$O(7)\\
%&0&2&0&5&0&7&B(4)$|$S(3)\\
%&1&0&3&1&3&8&\\
\hline
\multicolumn{8}{|c|}{ \# of {\textit {Redundant}} bugs}\\
\multicolumn{1}{|l}{Cross-{\bf iteration} redundancy}
&7&1&2&1&1&12&B(4)$|$M(7)$|$O(1)\\
\multicolumn{1}{|l}{ Cross-{\bf loop} redundancy}
&3&0&2&2&2&9&B(4)$|$M(5)\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
%\hline
%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
%\multicolumn{1}{|l}{Not in above categories}
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs in each root-cause category. 
B, M, S, C, and O represent different fix strategies:
B(atching),  
M(emoization), 
S(kipping the loop),
C(hange the data structure), and O(thers). The numbers in the 
parentheses denote the number of problems that are fixed using specific
fix strategies.}
\label{tab:root}
\end{table*}

\underline{Are the root-causes in our taxonomy common?}
The answer is \textit{yes}.
Resultless loops are about as common as redundant loops
(24 vs. 21).
Intuitively, 0* loops, where no iteration produces any results,
are rare in mature software. In fact, no bugs in this
benchmark suite belong to this category.
All other root-cause sub-categories are well represented.

\underline{How are real-world performance bugs fixed?}
Overall, the fix strategies are well aligned with root-cause patterns.
For example, 
all inefficient loops with resultless [0$|$1]* are
fixed by skipping the loop under certain contexts,
and almost all inefficient loops with redundant root causes are fixed either by 
memoization or batching the computation. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a problem.
The only problem is that there are no silver bullets for 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

\paragraph{Implications}
As we can see, resultless loops and redundant loops are both common reasons
that cause user-perceived performance problems in practice. The root-cause
categories discussed above also match with developers' fix strategy well ---
with a little bit amount of extra analysis, one can pretty much predict the fix strategy based on the root-cause pattern.
Consequently, tools that cover these root causes will have high
chances to satisfy the coverage and accuracy requirements of performance 
diagnosis.

%TODO even for the other, there are things we could do ...

\subsubsection{Caveats} 
Just as previous empirical study work, 
our empirical study above needs to be interpreted with our methodology in mind. 
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are still uncovered cases, like distributed systems, 
and scientific computation.

Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
on-line developer/user discussion to judge whether a bug report is about
performance problems and whether 
the performance problem under discussion is noticed and reported by users
or not.
We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
whether the root-cause of a performance problem is related to loops or not.
We do not intentionally ignore any aspect of loop-related performance problems. 
Some loop-related performance problems may never be noticed by end users
or never be fixed by developers, and hence skip our study. However,
there are no conceivable ways to study them.

We believe that the bugs in our study provide a representative sample of the 
well-documented and
fixed performance bugs that are user-perceived and loop-related in the studied 
applications. 
Since we did not set up the root-cause taxonomy to fit particular
bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
framework presented below will go beyond these sampled performance bugs.

### 2015-10-08 section/2_workless.tex
check into github

\section{\Tool design}
\label{sec:design}
\Tool is composed of a series of analysis routines, each designed to 
identify whether a given loop belongs to one specific type of root causes,
as we will present below.

As briefly mentioned in Section \ref{sec:intro}, the design of these analysis routines follows the following principles.
\begin{itemize}
\item Providing diagnosis information, not detecting bugs. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

\item Static-dynamic hybrid analysis. As we will see, static analysis alone
will not be able to provide all the needed information for performance
diagnosis; dynamic analysis alone will incur too much unnecessary overhead.
Therefore, we will use static-dynamic hybrid approach throughout our design.

\item Using sampling to decrease run-time overhead. Loop-related 
performance problems have the unique nature of repetitiveness, which make 
them a natural fit for random sampling. Therefore, we will design different
sampling schemes for different analysis routines.
\end{itemize}

\subsection{Resultless Checker}
\label{sec:workless}

Our resultless checker includes two parts. First, we use static analysis
to figure out which are the side-effect instructions in a loop and hence
decide whether a loop belongs to 0*, 0*1?, [0$|$1]*, or 1*. Second, for
0*1? and [0$|$1]* loops, we use
dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop is indeed
inefficient.

%\begin{figure}[ht]
%\center
%\includegraphics[width=0.7\linewidth]{figures/workless.pdf}
%\caption{Examples for different types of basic blocks inside a loop}
%\label{fig:block_type}
%\end{figure}

\subsubsection{Static Analysis}
\label{sec:s_workless}

We consider side-effect instructions as those instructions that write to
variables defined outside the loop. The analysis to identify side-effect
instructions is straightforward. We consider all functions that are called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
We consider all library functions or function calls through function pointers 
as functions that have side effects, 
unless the library functions are specially marked by us in a white list.

After identifying side-effect instructions, it is straight-forward to
categorize loops into the four types discussed above.
Loop 0* contains no side-effect instructions. 
Loop 1* contains at least one side-effect instruction along every path that
starts from the loop header and ends at the loop header.
The remaining cases are either 
0*1? or [0$|$1]*. 
Differentiating these two cases is also straight-forward.
In short, when the basic block that contains side-effect instructions
is part of the natural loop, the case
belongs to [0$|$1]*; instead, if the side-effect basic block is post-dominated
by one of the loop-exit blocks and is dominated by the loop header, yet is
not part of the natural loop, the case belongs to 0*1?.

Finally, since the 1* pattern contains the least amount of information
about computation \textit{inefficiency}, \Tool will not report a loop's
root-cause type as 1*, if more informative root-cause type is identified 
for this loop (e.g., cross-iteration or cross-loop redundancy).

%TODO Shan will rewrite the next two paragraphs
\subsubsection{Dynamic Monitoring}
\label{sec:d_workless}

Except for 0*, none of the other three type of loops are inefficient for sure.
We need dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop is indeed
the root cause of a user-perceived performance problem and worth fixing.

For a 0*1? loop, since it only generates results in the last iteration, we 
only need to know the total number of iterations (or the average total number 
of iterations when the loop has multiple instances) to figure out the 
\textit{resultless rate} of the loop. The implementation is straightforward
--- we initialize a local counter to be 0 in the pre-header of the loop; we 
increase the counter by 1 in the loop header to count the number of 
iterations; we dump that counter to log when the loop exits.

For [0$|$1]*, we need to count not only the total number of iterations, but
also the exact number of iterations that execute side-effect instructions
at run time. 
To do that, our instrumentation uses a local boolean variable 
\texttt{HasResult} to represent whether one iteration have side effect or not. 
\texttt{HasResult} is set to \texttt{False} in the loop header, and set to
\texttt{True} after each side-effect instruction. It will be used to help
count the number of side-effect iterations. For performance concerns,
before instrumenting side-effect blocks, we check whether there are 
post-domination relation between each pair of side-effect blocks. 
If both block A and block B are side-effect blocks and block A post-dominates 
block B, we only instrument block A to update \texttt{HasResult}.

We could speed up the above counting using sampling. However, since the 
run-time overhead of the above counting is low, as shown in Section 
\ref{sec:experiment}, our current prototype of \Tool does 
not use sampling for this part of run-time analysis.

%\subsubsection{Sampling}
%We calculate the average iteration number 
%and the ratio of working iteration based on a separated 
%process from on-line branch sampling discussed in~\cite{SongOOPSLA2014}.
%We need to instrument the buggy program and re-execute it by using bug-triggering input. 
%In the future, we could design an algorithm to calculate the two resultless metrics 
%based on branch sampling reports to get rid of the extra instrumentation and the extra bad run.

\subsubsection{Limitations}
\label{sec:l_workless}
The technique designed in this section has the following limitations.
First, when callee may have side effect, we will consider it will have side effect in the caller side, 
and do not consider the real execution inside callee. This could bring false negatives, 
because we could miss resultless cases, 
where side effect instructions inside callee do not execute. 
Experiments results in Section~\ref{sec:experiment} show that this is not a big issue, 
since we do not miss any resultless bugs.

Second, our dynamic instrumentation does not consider concurrent execution of the monitored loop, 
because most of buggy loops we study only execute in one single thread. 
When the monitored loop is executed in multi-thread, like loop marked with omp pragma, we need to synchronize updates to global variables.

### 2015-10-08 section/3_redundancy.tex
check into github

\subsection{Redundancy Checker}
\label{sec:redundant}

\subsubsection{Design overview}
To check whether there is redundant computation across different iterations
of one loop instance or across different instances of one static loop, we need
to address several challenges.

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
  \caption{A cross-loop redundant bug in Apache}
  \label{fig:Apache34464}
\end{figure}

\emph{How to judge redundancy between two iterations/loop-instances?}
Given two iterations (or loop-instances) $i_1$ and $i_2$, since they have 
the same source code, 
a naive, yet expensive, solution is to record and compare the return value of
every memory read conducted by $i_1$ and $i_2$. Two better alternative
solutions are to record and compare only the values written or read by the
side-effect instructions, such as 
line 9 in Figure~\ref{fig:Mozilla477564},
or the source instructions\footnote{We define source instructions in a code
region $r$ as a set of memory-read instructions that side-effect
instructions in $r$ depend on and do not depend on any other instructions
inside $r$.}, 
such as source[i] at line 12 of Figure~\ref{fig:Apache34464}.

Among the the above two potential solutions, our design chooses the second one.
The reason is that, if there is indeed
redundancy, repetitive patterns at the side-effect instructions are caused by
repetitive patterns in the source instructions.
For the purpose of performance diagnosis, it is
more informative to track the cause, rather than the effect.

\emph{How to handle partial redundancy?}
In practice, redundant loops may be doing largely the same, instead of exactly
the same, computation across iterations or loop instances. It is also possible
%TODO define loop instance.
that only some, instead of all, iterations in a loop are doing redundant
computation. We will discuss how we handle this issue in Section \ref{sec:cal}.

\emph{How to lower the overhead of record-and-compare?}
Even if we only record and compare the values returned by source instructions,
instead of all instructions in a loop, the run-time overhead and the log size
would still be large. We will use two ways to lower this time and spatial
overhead. First, static analysis can already tell some source instructions
will always return the same value across iterations/loop-instances, and hence
need not be traced at run time. Second, we can leverage the repetitive nature
of performance problems and use random sampling to lower the overhead without
degrading the diagnosis capability. We will discuss details of 
these two optimization in Section \ref{sec:inst} and \ref{sec:perf}.
%TODO static analysis alone is not sufficient, because some redundant is
%workload dependent

\emph{How to provide the most suitable fix-strategy suggestion?}
Finally, as discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
memoization and batching are both common fix strategies for redundant loops.
To pick the right fix strategies to fix a redundant loop, we will conduct 
some extra analysis. We will discuss this in Section \ref{sec:redundant_fix}.

\subsubsection{Identifying source instructions}
\label{sec:dependence}

Informally, we use static analysis to identify a set of 
memory-read instructions that the loop computation depends on. We refer
to these instructions as \textit{source} instructions. The values returned
from them at run-time will be tracked and compared to identify
redundant computation.

Specifically, we first identify side-effect instructions in the loop, as 
discussed in Section \ref{sec:s_workless}; we then conduct static slicing 
from these instructions, considering both control and data
dependency, to identify source instructions.

%TODO How do you handle constant values? I didn't get it.
Our slicing ends when it reaches either a local-variable read conducted
outside the loop or a heap/global-variable read anywhere in the program.
For the latter case, our slicing stops because tracking data-dependency
through heap/global variables is complicated in multi-threaded C/C++
programs. For the former case, 
not including local-variable reads inside the loop can help reduce the
amount of data that needs to be recorded. 
When there are function calls inside the loop,  
we conduct slicing for return values of callees and side-effect instructions
inside callees. 
%In order to reduce the number of memory read we need to record inside callees, 
%we calculate previous writes conducted to the same address for each local-structure read and local-array read. 
%Since local structures and local arrays are mainly used in the declared functions, 
%it is easy to know whether read or write conducted on them are applied to the same address. 
We omit encountered constant values through slicing, because constant values will not influence whether a loop or an iteration is redundant.

%We conduct slicing to for return values of callees and side-effect instructions
%inside callees. In order to reduce the number of memory read we need to record, 
%we design a GEN-KILL based algorithm to analyze previous writes for read from local structures and arrays 
%inside callees.
%TODO Linhai, I have no idea what you are talking about below
%For a memory read inside a callee function, 
%if its source is a structure or an array declared in the same function, 
%we use a GEN-KILL based algorithm to analyze previous writes for these reads. 
%We do not track previous writes for other memory reads, because it is very difficult to do inter-procedural alias analysis.

% function() {
%  struct A;
%  A.a = 10;     // place a,
%  if(...)
%  {
%     A.a = 20;  // place b, value defined in place a will be killed, and this place gen a new value
%     print A.a  // A.a will be 20, because only value defined in place a is live 
%  }
%  return A.a;  // there will be memory read here. 
%  //We will do analysis to track where is the previous write for field a of struct A.
%  //The result will be write in place a, and place b
%  //We then conduct dependence analysis for these two writes.
%  //We only do this for read from structure and array declared in the same function. 
% }

The analysis for cross-iteration and cross-loop redundancy analysis is pretty
much the same. The only difference is that, if a memory read instruction 
$i$ in a loop depends on the value returned by instruction $j$ in an earlier
iteration, we stop tracing the dependence at $i$ and consider $i$ as a
source instruction for cross-iteration redundancy analysis, while we continue
the slicing for cross-loop redundancy analysis. 
For example, 
the instruction defining the value of \texttt{i} is the only side-effect instruction 
for the loop at line 12 of Figure~\ref{fig:Apache34464}. 
The source instructions calculated by cross-loop dependence analysis include 
memory read \texttt{source[i]} inside the loop, 
and three values defined outside the loop, 
which represent the initial value of \texttt{i}, the value of \texttt{max} and \texttt{first} respectively. 
In contrast, 
the source instructions calculated by cross-iteration dependence analysis 
include value \texttt{i} defined in previous iteration, 
memory read \texttt{source[i]}, 
and two values defined outside the loop (\texttt{max} and \texttt{first}).

\comment{
We consider two types of dependence, control dependence and RAW data dependence. 
We build control dependence graph according to the algorithm discussed in~\cite{controldep}. 
If block A is one of ancestors of block B on the control dependence graph, 
we consider all instructions in block B control depend on the branch condition in block A. 
Data dependence is mainly calculated based on instructions' operands. 
We define several types of instrumentation sites. 
The inputs of our dependence analysis are instructions, 
and the output of our dependence analysis is a set of dependent values, 
including instrumentation sites and constant values.

Before calculating dependence inside the monitored loop, 
we conduct inter-procedural dependence analysis for each function directly called by the loop. 
The formal parameters of each direct callee, memory instructions, 
including load, memcpy, and memmove, 
whose source is not from local structures or arrays, 
and return values of library function calls are instrumentation sites. 
During calculating dependence, 
we consider formal parameter data depend on all real parameter, 
the return value of each call site data depend on return inside the callee function, 
and all instructions inside one callee functions inherit control dependence of all its call site.

If a direct callee from the monitored loop does not contain recursive function calls, 
we use a three-stage method to solve the infeasible path problem. 
Assume function A is called inside the monitored loop, function A will call function B, 
and function B will call function C. 
We will have a call tree A $\rightarrow$ B $\rightarrow$ C. 
This call tree does not have recursive function calls, so our three-stage method can apply to this case. 
At the first stage, we conduct intra-procedural dependence analysis for each function.  
We consider return values of all call sites as instrumentation sites. 
For example, we consider both the return value of B in A and the return value of C in B as instrumentation sites. 
At the second stage, we process each function bottom-up on the call tree. 
For each call site inside a function, we calculate 
how the return value depend on real parameters based on dependence information inside the callee.
Back to our example, we will process the three functions in order C, B, and A.
When processing function B, we calculate the dependence for the return value of function C 
based on the dependence information inside C and the real parameters of the call site.
At the last stage, we process each function top-down on call tree, 
and calculate dependence for instruction inside a callee function based on information from all its call site. 
At this stage, we will process the three function in the order A, B, and C. 
We update dependence information inside function B, according to control dependence and real parameters of its call site in A.

We design a Gen-Kill based intra-procedural analysis to 
calculate which previous writes a memory read from local structures and arrays depends on. 
The basic idea is that a memory write will kill all previous writes whose destination address it can cover, 
and the memory write will generate a new write to its destination address. 
Each memory read depends on previous writes whose destination addresses overlap with its source address.

For the monitored loop, we calculate dependent values for all site-effect instructions, 
including side-effect instructions inside the loop and side-effect instructions inside the callees. 
For cross-loop dependence analysis, instrumentation sites include values defined outside the loop, 
memory reads inside the loop, memory reads not from local structure and arrays inside callees, 
and return values of library function calls. 
For cross-iteration dependent analysis, instrumented sites also include value defined in previous iterations. 
For example, the instruction defining the value of \texttt{i} is the only side-effect instruction 
inside the loop at line 12 in Figure~\ref{fig:Apache34464}. 
After running cross-loop dependence analysis, the dependent values include 
memory read \texttt{source[i]} inside the loop, 
and three values defined outside the loop, 
which represent the initial value of \texttt{i}, the value of \texttt{max} and \texttt{first} respectively. 
After running cross-iteration dependence analysis, 
the dependent value include value \texttt{i} defined in previous iteration, 
memory read \texttt{source[i]}, 
and two values defined outside the loop (\texttt{max} and \texttt{first}).

}

\subsubsection{Identifying redundant loops}
\label{sec:cal}

After identifying source instructions, we instrument these source
instructions, so that the values returned by these memory read
instructions can be recorded at run time. Specifically, we will assign
a unique ID for each source instruction, and a pair of $<InstID, Value>$
will be recorded at run time with the execution of a source instruction.
Our trace also includes some delimiters and meta information that allows
trace analysis to differentiate values recorded from different loop
iterations, different loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy.

After collecting values returned by source instructions from every iteration
of one or multiple loop instances, we need to process the trace and decide
whether the loops under study contain cross-iteration redundancy or 
cross-loop redundancy. We will first present our high-level algorithms, followed
by the exact implementation in our prototype.

\paragraph{High-level algorithms}
For cross-iteration redundancy, we need to answer two questions. 
First, how to judge whether
two iterations are doing redundant work --- should the two iterations conduct
exactly the same computation?
Second, is a (dynamic) loop problematic when it contains only few 
iterations that are
redundant with each other?

Our answer to these two questions stick to one principle: there should be
sufficient amount of redundant computation to make a loop likely root-cause
for a user-perceived performance problem and to make itself worthwhile to
get optimized by the developers. Consequently,
for the first question, \Tool takes a strict 
definition --- only iterations that are doing exactly the same computation are
considered redundant. Since one iterating may not contain too much computation,
a weaker definition here may lead to many false positives. For the 
second question, we believe there should be a threshold. In our current 
prototype,
when the number of distinct iterations is less than half of the total iterations, 
we consider the loop is cross-iteration redundant. 
%when the number of distinct iterations is less than half of the total iterations 
%iterations/(distinct iterations) = 2

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache37184.java}}
  \caption{A cross-iteration redundant bug in Apache}
  \label{fig:Apache37184}
\end{figure}

For example, Figure~\ref{fig:Apache37184} shows a loop from Apache-Ant that
contains cross-iteration redundancy.
As we can see, under the problem triggering input, 
only several distinct listeners are contained inside the vector, and most of 
iterations of the loop inside function \texttt{fireMessageLoggedEvent}
are doing exactly the same computation. 
%The problem for this bug is that developers say that the performance 
%loss happens in fireMessageLoggedEvent, but in the code I found, function
%messageLogged does not contain anything, and it is an empty function.
%I guess either developers do not have correct understanding of this bug,
%or I did not find the correct codes.

For cross-loop redundancy, we need to answer similar questions,
especially how to judge whether two loop instances are doing redundant work ---
should they contain exactly the same number of iterations and doing exactly
the same computation in each iteration?
%Second, is a (static) loop problematic when it contains two instances that
%are redundant with each other?

Our answers here are different from our answers above for cross-iteration
redundancy analysis.
We do not require two loop instances to
conduct exactly the same computation to be considered redundant. The rationale
is that a whole loop instance contains a lot of computation, much more than
one iteration in general. Even if only part of its computation
is redundant, it could still be the root-cause of a user-perceived performance
problem and worth developers' attention.

In fact, in practice, we almost have never seen cases where different loop 
instances are doing exactly the same computation.
For example, Figure~\ref{fig:Mozilla477564} demonstrates a cross-loop redundancy
problem in Mozilla. Here, the
latter instances contain more iterations than previous instances. 
Figure~\ref{fig:Apache34464} shows an example in Apache, 
The inner loop, which starts from line 9,  
searches from the beginning of a string \texttt{sb} for a target sub-string 
\texttt{s}. Since the outer loop, which starts on line 36, appends one 
character to \texttt{sb} in every iteration, every inner loop instance is 
doing computation that is similar, but not exactly the same, 
from its previous instance.

\paragraph{Detailed algorithm implementation}

The implementation of checking cross-iteration redundancy is straightforward.
We will record a sequence of $<InstID, Value>$ pair for every monitored
iteration, with each $InstID$ representing a unique source instruction.
We consider two iterations to be redundant, if their sequences are exactly the
same. To make sure a loop contains sufficient redundant computation, 
we calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
the total number of iterations in the loop by the number of distinct iterations.
The smaller the rate is, with 1 being the minimum possible value, 
the less cross-iteration redundancy the loop contains.

The implementation of checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$
--- dividing the number of redundant pairs by $k-1$.
The smaller the rate is, with 0 being the minimum possible value, the
less cross-loop redundancy $L$ contains.
Here we only check redundancy between consecutive loop instances, because  
checking the redundancy between every pairs of loop
instances would be very time consuming.

The key of this implementation is
to judge whether two dynamic loop instances $l_1$ and $l_2$ 
are redundant or not.
The challenge is that $l_1$ and $l_2$ may have executed different number of
iterations; in different iteration, a different set of source instructions
may have executed. Therefore, we cannot simply merge values from different
source instructions and iterations together and compare two big data sequence.
Instead, we decide to check the redundancy for each source instruction across
$l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
all source instructions as the \textit{cross-loop redundancy rate} between
$l_1$ and $l_2$.

We calculate the redundancy for one source instruction $I$ by normalizing the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances. The exact formula is the following:

%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

\[
\Scale[0.8]{
	Redundancy(I) =  \frac{dist(SeqA,SeqB) - (len(SeqA) - len(SeqB))}{len(SeqB)}
}
\]

Here, $SeqA$ and $SeqB$ represent the two value sequences corresponding to $I$
from two loop instances, with $SeqA$ being the longer sequence.
$dist$ means edit distance, and $len$ means the length of a value sequence.
Since the edit distance is at least the length-difference between the
two sequences and at most the length of the longer sequence, we use the 
subtraction and division shown in the formula above to normalize the
redundancy value.

%$r\_dist$ means edit distance after 
%we reverse one sequence.

%TODO
%We define two configurable thresholds to filter out instance pairs which are both too short, 
%or one is too short compared with the other one.

%TODO
%It is also possible that a source instruction is executed outside the loop.
%We divide values defined outside the loop into several cases.
%Firstly, the value defined outside the loop is only used in the first iteration, 
%and all related values used in following iterations have already been recorded, 
%like the initial value of variable \texttt{n} in Figure~\ref{fig:Mozilla477564}. 
%We omit values defined outside the loop like this.
%Secondly, the value defined outside the loop represent the initial value of an induction variable, 
%like the initial value of variable \texttt{i} in Figure~\ref{fig:Apache34464} 
%for the loop at line 12. We deduce the value sequence of the induction variable 
%based on its initial value and stride, and compare the calculated sequences. 
%Thirdly, the value defined outside the loop only influences side-effect instruction through control dependence, 
%and variables it compares with is not calculated from memory read, 
%like variable \texttt{max} in Figure~\ref{fig:Apache34464}. We think that this type of values only influence how many iterations the loop will execute.
%We calculate redundancy for this type of values by dividing the smaller variable value with the larger one. 
%For all other cases, when the values from two compared instances are the same, redundancy is 1, otherwise, redundancy is 0.

\subsubsection{Dynamic performance optimization: sampling}
\label{sec:inst}

%\begin{figure}[ht]
%\center
%\includegraphics[width=0.7\linewidth]{figures/CL-I}
%\caption{Cross-loop Instrumentation}
%\label{fig:CL-I}
%\end{figure}

Recording values returned by every source instructions would lead to 
huge run-time time. To lower the overhead,
we use random sampling to reduce the number of instructions that we
track at run time. Due to the repetitive nature of performance bugs,
we will still be able to recognize redundant 
computation as long as the sampling rate is not too sparse (we will evaluate
this in Section \ref{sec:experiment}). 
Our sampling scheme requires almost no changes to our redundancy 
identification algorithm discussed in Section \ref{sec:cal}.

%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.

%There are two possible reasons for cross-iteration redundancy. 
%The first one is loop-invariant computation, which can be identified statically, 
%and it is the target for traditional compiler optimization. 
%The second one is repetitive processed elements, like GCC\#27733 shown in Figure~\ref{fig:GCC27733}. 
%When processed elements are repetitive, the computation conducted by different iterations is exactly the same. 
%If we compare a pair of iterations, we may fail to observe redundancy. 
%For cross-iteration redundancy, we randomly sample iterations, 
%and compare distinct computation number with the total number of sampled iterations.

\paragraph{Cross-iteration redundancy analysis}
Our high-level sampling strategy is straightforward:
randomly decide at the
beginning of every iteration whether to track the values returned by
source instructions in this iteration.

The implementation is similar with previous sampling work 
\cite{liblit03,liblit05}.
Specifically, we create a clone of the original
loop iteration code, including functions called by the loop directly or
indirectly, and insert value-recording instructions along the
cloned copy. 
We then insert a code snippet that conducts random decision to
the beginning of a loop iteration. 
Two variables \texttt{CurrentID}, which is initialized as 0, 
and \texttt{NextSampleID}, which is initialized by a random integer, 
are maintained
in this code snippet. \texttt{CurrentID} is increased by 1
for each iteration. When it matches \texttt{NextSampleID}, the control
flow jumps to the value-recording clone of the loop iteration and the 
\texttt{NextSampleID} is increased by a random value. Different sampling
sparsity setting will determine the range from which the random value is
generated.

%\begin{figure}
%\center
%\includegraphics[width=0.7\linewidth]{figures/CI-I}
%\caption{Cross-iteration Instrumentation}
%\label{fig:CI-I}
%\end{figure}

\paragraph{Cross-loop redundancy analysis} 
At high level, we randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediately next loop instance too.

The implementation is similar with that for cross-iteration redundancy analysis.
The only difference includes: (1) clone is made for the whole loop and the
sampling control
is done in the pre-header of the loops; (2)
sampling is conducted when \texttt{CurrentID} equals either
\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
increased by a random value in the latter case.

%TODO
%For each monitored memmove or memcpy instruction, 
%we record its ID, the length of accessed memory, 
%and the content of the accessed memory.

\paragraph{Handling recursive functions}
We also conduct sampling to our redundancy analysis for recursive functions.
For a recursive function, we first create an instrumented clone copy of 
the whole function body.
We then add a sampling-control code snippet at the entry point of the function,
where \texttt{CurrentID} and \texttt{NextSampleID} are maintained to decide
whether to execute the original function body or the instrumented 
value-recording clone copy.
We also create clones for all the callee functions of the recursive function
under study, so that the sampling decision can be correctly conducted
throughout the call chain.

\subsubsection{Static analysis for performance optimization}
\label{sec:perf}

We conduct a series of static analysis to reduce the number of instructions we 
need to monitor.

First, we identify and avoid monitoring memory reads whose return values can be 
statically proved to
not change throughout one loop instance (i.e., for cross-iteration
redundancy analysis) or multiple loop instances (i.e., for cross-loop redundancy
analysis). Since we implement \Tool at LLVM byte-code level, a major part of this
analysis is already done by LLVM, which lifts loop-invariant memory
accesses out of loops. The only extra analysis we did is to 
prune memory reads whose reading address is loop invariant, and there are no writes 
inside the loop which are possibly conducted on the same address. 
For example, the read address of \texttt{aNode.localName} and \texttt{aNode.namespaceURI}
in Figure~\ref{fig:Mozilla347306} is loop-invariant, and there are no write conducted 
on the same address. We do not need to record these two memory read. 
%It is easy to lift read from local variable outside the loop. 
%Compiler is conservative to move read, which may cause exception, outside the loop.
%I think this part of analysis is to prune memory read which is invariant, but unsafe to be moved out by compiler. 
%llvm is very conservative to move memory read from array/structure/global variable/heap variable
%outside the loop.
%what we do is if the read address is loop invariant, and there are no other write possibly 
%write to the same place, we will not record the memory read.

%TODO: Linhai, I don't understand your original writing. Pls rephrase, and provide
%an toy example.
%For each monitored memory read, we use loop-invariant analysis to identify 
%whether the read address is loop-invariant. 
%If the address is invariant, and there are no memory writes whose addresses 
%may/must alias to the read address, we will not instrument the memory read.

%ANSWER:
%while(i=lower[j]; a[i]<100 & i<upper[j]; i++); 
%The memory read upper[j] is conducted in each iteration.
%The read address upper+j is loop-invariant. If there is not write to the same
%address, the read is also loop-invariant, and we do not need to record the memory read.
%we conduct alias analysis, and analysis whether there are memory writes, whose
%address may/must alias to the read address.

Second, we identify and avoid monitoring some memory reads whose return values 
can be statically proved to be different throughout one loop instance in 
cross-iteration redundancy analysis.
Specifically, for read on loop induction variable, such as i for loop at line 12 of Figure~\ref{fig:Apache34464}, 
%Specifically, reading of loop induction 
%variables, such as XXX, are always identified as source instructions in % variable i for loop at line 12
%cross-iteration redundancy analysis; 
we also know for sure that their return
values are different in different iterations. 
If source instructions include read on loop induction variables, we know that 
there could not be cross-iteration redundancy. 
We use scalar evolution analysis
provided by LLVM to identify induction variables and avoid tracking their
values.
%induction variables are not alwayes identified as source instructions.
%it could be possible that side-effect instructions do not depend on induction variables.
%for example, side-effect instruction may only depend on array content, and array index 
%will not be source instructions

%TODO: Linhai, I find it hard to believe that consider "there will not be
%cross-iteration redundancy simply because induction variable is in the 
%dependent set. Really? The input workload itself could be repititive, and hence
%could still deserve monitoring, right? 
%

%ANSWER: this is true according to how we calculate cross-iteration redundancy.
%We only consider iteration from the same loop instance.
%induction variable will be changed in each iteration by a fix constant, so
%the value of induction variable will be different from each other in each iteration of the same loop instance. 
%The case you mention is 
%for(i=0; i < 10; i ++) {
%  c = A[i]; 
%   ...   // all other computation only depend on c        
% }
%Our dependence analysis will report the memory read A[i] as dependent value, not i.
%If the content of A is repetitive, we will identify cross-iteration redundancy.

%For cross-iteration instrumentation, we use scalar evolution analysis to identify 
%whether there are induction variables in the dependent value set. 
%A induction variable will be increased or decreased by a fix amount in each loop iteration. 
%If there are induction variable inside the dependent value set, 
%we know that there will not be cross-iteration redundancy.

Third, sometimes we only record the memory-address range of a sequence of memory
read, instead of the value returned by every read, in cross-loop redundancy
analysis. 
The loop at line 12 in Figure~\ref{fig:Apache34464} shows an example.
The content of array \texttt{source} is never modified
throughout the outer-loop, which starts 
at line 12 in the Figure~\ref{fig:Apache34464}.
%We do not have the static analysis to prove the content of array does not change.
%for source[i] for the loop at line 12, we only need to record source, initial value of i and final value of i. 
%TODO
%Do you really do analysis to prove that the source array is not changed?
%ANSWER
%Shan, I do not have invariant analysis to prove the the source array is not changed.
%I remove that part of writing in the last version I sent to you. 
%It is very difficult to implement the invariant analysis.
%I plan to discuss this in limitation part of this section, and say that this could bring false positives.
%There are reasons why I feel it is too difficult to implement the invariant analysis:
%1. it is difficult to find the range (the outer loop) to apply the analysis.
%assume we have loopA, loopB and loopC. loopA contains loopB, and loopB contains loopC. 
%we are analyzing loopC. It could be possible that loopB only execute 1 or 2 iterations, and loopA is the real outer loop
%2. It is very difficult to prove that there is no other loop inside the outer loop which does not write to the same array.
%There could be cases like:
% for(i = 0; i < 10; i++)
%   func(&(A[i]));
% func will write to its parameter.
Therefore, to check whether different inner loop instances read similar
sequence of array data, we only need to record the starting and 
ending array index touched by each inner loop, significantly reduce the 
monitoring overhead. To accomplish this optimization, we again leverage
the scalar evolution analysis provided by LLVM. The scalar evolution analysis
tells us whether the address of a memory read instruction
is a loop induction variable. For example, the address for memory read \texttt{source[i]} is added by one in each loop iteration,
so it is a loop induction variable. 
From the scalar evolution analysis, we know that the starting address is \texttt{source} plus the initial value of \texttt{i}, and the ending address
is source plus the ending value of \texttt{i}.  
%TODO Linhai, I don't understand your original text. The address is 
%source+i; loop induction variable is i. What do you mean by "the read address
%is an induction varaible"? Please rewrite.

%ANSWER
%Shan, both source + i and i are induction variables, becasue both of them 
%will be added by 1 in each iteration. The only difference between these two 
%are their initial values.
%For cross-loop redundant bugs, we also rely on scalar evolution analysis to identify whether the read address
%is an induction variable for each monitored read instruction.

\subsubsection{Fix strategy recommendation}
\label{sec:redundant_fix}
As discussed in Section \ref{sec:tax_study}, extra analysis is needed to
decide whether batching or memoization should be suggested to fix a 
loop that conducts redundant computation.

For cross-iteration redundancy, batching is often used towards
batching I/O related operations, based on our empirical study. 
Therefore, we treat I/O related redundancy separately.
Specifically, when the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, we report this
as I/O related redundancy problem and suggest batching as a potential fix
strategy.

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper to use. \Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is updating 
an sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to help save much computation.

%we xxx
%TODO

%%if side effect of the loop is to define several scalar value used outside the loop, we recommend memoization.
%%if side effect is to write to distinct memory address or conduct system call, 
%%we recommend batch

### 2015-10-08 section/5_exper.tex
check into github

\section{Evaluation}
\label{sec:experiment}

\subsection{Methodology}
\label{sec:result_meth}
%Please discuss the potential usage scenarios of \Tool
%How you will use it together with other tools

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccc}
    \toprule
                         &      	   &                        & {\bf Root}   &          \\
   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf Cause}  & {\bf Fix}\\
   \midrule
   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
   Mozilla490742         & N/A             & JS                     &  C-I         & B       \\
   Mozilla35294          & N/A             & C++                    &  C-L         & B        \\ 
   Mozilla477564         & N/A             & JS                     &  C-L         & M       \\
   \midrule 
   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
   \midrule    
   Apache32546           & N/A             & Java                   &  C-I         & B  \\
   Apache37184           & N/A             & Java                   &  C-I         & M  \\
   Apache29742           & N/A             & Java                   &  C-L         & B \\ 
   Apache34464           & N/A             & Java                   &  C-L         & M  \\
   Apache47223           & N/A             & Java                   &  C-L         & B \\
   \midrule
   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
   GCC1687               & 2099            & C                      &  C-I         & M \\
   GCC27733              & 3217            & C                      &  C-I         & M \\
   GCC8805               & 2538            & C                      &  C-L         & B\\
   GCC21430              & 3844            & C                      &  C-L         & M \\
   GCC12322              & 2341            & C                      &  1*          & S\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Benchmark information.
  (N/A: we skip the size of benchmarks that are extracted from real-world applications.
  Root cause ``C-I'' is short for cross-iteration redundancy.
  Root cause ``C-L'' is short for cross-loop redundancy.
  C, B, M, and S represent different fix strategies, as discussed in
  Table \ref{tab:root}.
  ) 
 }
  \label{tab:benchmarks}
\end{table}

\paragraph{Implementation and Platform}
We implement \Tool in LLVM-3.4.2 \cite{llvm}, and conduct our
%Our implementation consists of 17654 lines of C++ code, 
%with 4748 for instrumenter, 674 for resultless analysis, 
%5802 for redundancy analysis, 
%and the remaining 6430 for common utilities. 
experiments on a i7-960 machine, with Linux 3.11 kernel.

\paragraph{Benchmarks}
We use 18 out of the 45 bugs listed in Table \ref{tab:root} as our 
evaluation benchmarks. Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
The remaining bugs listed in Table \ref{tab:root} are much more difficult to
use as benchmarks, 
either because they depend on special hardware/software environment
or because they involve too complex data structures to extract. 
Overall, these 18 bugs cover a wide variety of performance root causes, as 
shown in Table~\ref{tab:benchmarks}.

\paragraph{Metrics}
Our experiments are designed to evaluate \Tool from three main aspects:
\begin{itemize}
\item Coverage. Given our benchmark suite that covers a wide variety
of real-world root causes, can \Tool identify all those root causes?
\vspace{-0.05in}

\item Accuracy. 
When analyzing non-buggy loops, will \Tool generate any false positives?
\vspace{-0.05in}

\item Performance. 
What is the run-time overhead of \Tool?
\end{itemize}

\paragraph{Evaluation settings}
The imagined usage scenario of \Tool is that one will apply \Tool to identify
detailed root causes and provide fix-strategy suggestion for a small number of
suspicious loops that are most correlated with the specific performance problem.

Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical performance debugging identifies the
real root-cause loop as the top ranked suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcc}
    \toprule
                            	&  {\bf Reported}             &{\bf Fix }                     \\
   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
   \midrule
   Mozilla347306                & \Yes                        & \Yes                                          \\
   Mozilla416628                & \Yes                        & \Yes                                         \\
   Mozilla490742$_a$            & \Yes                        & \Yes                                             \\
   Mozilla35294$_a$             & \Yes                          & \Yes                                              \\ 
   Mozilla477564$_a$            & \Yes                          & \Yes                                            \\
   \midrule 
   MySQL27287                   & \Yes                          & \ding{55}                                         \\
   MySQL15811                   & \Yes                          & \Yes                                      \\ 
   \midrule    
   Apache32546                  & \Yes                          & \Yes                                      \\
   Apache37184$_a$              & \Yes                          & \Yes                                        \\
   Apache29742$_a$              & \Yes                          & \Yes                                       \\ 
   Apache34464                  & \Yes                          & \Yes                                        \\
   Apache47223                  & \Yes                          & \Yes                                       \\
   \midrule
   GCC46401                     & \Yes                     & \Yes                                      \\
   GCC1687                      & \Yes                          & \Yes                                     \\
   GCC27733$_a$                 & \Yes                          & \Yes                                     \\
   GCC8805                      & \Yes                          & \Yes                                  \\
   GCC21430                     & \Yes                          & \Yes                                     \\
   GCC12322                     & \Yes                         & \ding{55}                                   \\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Coverage Results.}
  \label{tab:cover}
\end{table}

To evaluate the coverage, accuracy, and performance of \Tool, we mainly conduct
three sets of evaluation. First, we apply \Tool to the real root-cause loop to
see if \Tool can correctly identify the root-cause category and provide
correct fix-strategy suggestion. Second, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
to see how accurate \Tool is. Third, we evaluate the run-time performance of
applying \Tool to the real root-cause loop.

For all benchmarks we use, real-world
users have provided at least one problem-triggering input in their on-line 
bug bugs. We use these inputs in our run-time analysis.

As discussed in Section \ref{sec:design}, our analysis contains 
several configurable thresholds. In our evaluation,
we use 0.001 as the \textit{resultless rate} threshold for identifying
0*1? loops, 0.01 as the \textit{resultless rate} threshold for identifying 
[0$|$1]* loops, 0.5 as the \textit{cross-loop redundancy rate}, and 
2 as the \textit{cross-iteration redundancy rate} (i.e., 
the number of distinct iterations is less than half of the total iterations).

All the analysis and performance results presented below regarding
cross-loop analysis is obtained using $1/100$ sampling rate; all the
results regarding cross-iteration analysis is obtained using $1/1000$ sampling
rate. We use sparser sampling rate in the latter case, because there tend to
be more loop iterations than loop instances.
All our diagnosis results require only \textbf{one} run under the 
problem-triggering input.

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
the fix strategy that developers used. For MySQL27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
find a new data structure that can eliminate both root causes.
For GCC12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the performance impact of the original loop
to the GCC compilation process.
Providing this type of
fix strategy suggestion goes beyond the capability of \Tool.

\subsection{Accuracy Results}
\label{sec:result_acc}

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool, when applying to top 5 loops reported by 
    statistical performance diagnosis for each benchmark. `-' represents zero false positive.
    Other cells report real false positives and benign false positives, which is in the
    subscript.
}
  \label{tab:top5}
\end{table}

As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
false positive and 14 benign false positives for all the top 5 loops.

Here, benign false positives mean that the \Tool analysis result is true ---
some loops are indeed cross-iteration/loop redundant or indeed producing
results in only a small portion of all the iterations. However, those
problems are \textit{not} fixed by developers in their performance patches.

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 12 out of the
14 benign cases. In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
The remaining two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
For example, 4 benchmarks contain loops that only generate side-effect
in the last iteration among their top 5 suspicious loops. However,
these loops are actually not inefficient because the portion of
resultless iterations is small.

The good accuracy of \Tool can actually help improving the accuracy of
identifying which loop is the root cause loop.
For example, the real root-cause loop of Apache34464 and GCC 46401 both
rank number two by the statistical performance diagnosis tool.
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy. This result can
potentially used to improve the accuracy of identifying root cause loops.

\subsection{Performance}
\label{sec:result_perf}

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop, with and
    without optimizations. 
    Only results from non-extracted benchmarks are shown. 
  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
  /: not applicable. }
  \label{tab:performance}
\end{table}

\comment{
\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
                       & {\bf Resultless} &  \multicolumn{2}{c}{\bf C-L R. } & \multicolumn{2}{c}{\bf C-I R.}\\
      \cmidrule(lr){3-4}    
      \cmidrule(lr){5-6}   
     {\bf BugID}       &                & Not               &  S.+O.            & Not                & S.+O.  \\
     \midrule
     Mozilla347306     & 1.07\%         & 303.37{\bf X}     &  22.40\%       & 467.74{\bf X}         & 10.17\%      \\
     Mozilla416628     & 0.80\%         & 56.51{\bf X}      &  4.10\%        & 84.6{\bf X}           & 2.99\%\\
     \midrule
     MySQL27287        & $\sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
     MySQL15811        &  -             & 226.04{\bf X}     &  0.03\%        & 423.44{\bf X}         & - \\
     \midrule
      GCC46401         & 3.12\%         & 20.07{\bf X}      &  3.80\%        & 37.44{\bf X}          & 5.95\%\\ 
      GCC1687          & -              & /                 &  /             & 141.29{\bf X}         & $\sim$0 \\
      GCC27733         & $\sim$0        & /                 &  /             & 16.41{\bf X}          & 4.73\%         \\
      GCC8805          & -              & 1.22{\bf X}       & $\sim$0        & 2.52{\bf X}           & $\sim$0\\
      GCC21430         & -              & 106.20{\bf X}     & 5.46\%         & 158.89{\bf X}         & 0.69\%\\
      GCC12322         & -              & 20.07{\bf X}      & 1.75\%         & 37.44{\bf X}          & $\sim$0\\
  \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop. 
    Only performance results from non-extracted benchmarks are shown here. 
  Not: not applying the performance optimization in \Tool.
  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
  /: not applicable. }
  \label{tab:performance}
\end{table}
}

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla347306. We believe \Tool is promising for potential production
run usage. Of course, if we apply \Tool to multiple loops simultaneously,
the overhead will be higher. However, the current results are obtained by running the
program only \textbf{once} under the problem-triggering workload. The sampling nature
of \Tool will allow us to keep the overhead low at the exchange of running the program for
a couple of more times, if needed.

As we can also see from the table, our performance optimization discussed in 
Section \ref{sec:inst} and \ref{sec:perf} has contributed
a lot to the good performance of \Tool.

Without sampling, while still applying our static optimization, our redundancy
analysis would lead to over 100X slowdown for five benchmarks.

The buggy loops of MySQL\#27287 and MySQL\#15811 access arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

The side-effect of the buggy loop for MySQL15811 is to calculate the length of a string. 
The variable representing the length is an induction variable. 
The side-effect of the buggy loop for MySQL27287 is to calculate the index of a searched target, 
and the variable representing the index is also an induction variable. 
We can reply on static analysis to figure out that these two loops are not cross-iteration redundant.

We also tried sampling with different sampling rates.
For cross-loop redundancy, we also conduct experiments under sampling rate 1
out of 1000. 
Both run-time overhead and collected sample will be reduced. Mozilla347306 
is still the benchmark with largest overhead, but the overhead is reduced to 0.49\%. For two benchmarks, GCC8805 and GCC12322, we cannot sample 
more than 10 loop instances and hence cannot draw strong conclusion
about their root-cause type. For all other benchmarks, we can 
still have more than 10 loop instances and get exactly the same 
root-cause analysis results presented above.

We also conduct cross-iteration redundant experiment under different sampling rates. When the sampling rate is 1 out of 100, there are two benchmarks, whose runtime overhead is larger than 30\%. The overhead for Mozilla347306 is 59.57\%, 
and the overhead of GCC21430 is 30.65\%. When changing sampling rate to 1
out of 10000, Mozilla347306 has the largest overhead, which is 4.47\%. And mozilla347306 is the only one whose overhead is larger than 2\%. Except for 
GCC12322, all other benchmarks will have more than 100 iterations sampled, under the sample rate is 1 out of 10000. Consequently, the same root-cause
analysis results will be reported for these benchmarks as the ones presented
above.

### 2015-10-08 figures/GCC1687.c

@@ -1,0 +1,42 @@
+// tree-inline.c
+static void
+expand_calls_inline (tp, id)
+{
+-  walk_tree (tp, expand_call_inline, 
+-                            id, NULL);
++  walk_tree (tp, expand_call_inline, 
++                 id, id->tree_pruner);
+}
+
+tree
+walk_tree (tp, func, data, htab_)
+     tree *tp;
+     walk_tree_fn func;
+     void *data;
+     void *htab_;
+{
+  if (htab)
+  {
+    void **slot;
+
+    /* Don't walk the same tree twice, 
+       if the user has requested
+       that we avoid doing so.  */
+    slot = htab_find_slot (htab, *tp, INSERT);
+    if (*slot)
+      return NULL_TREE;
+  }
+  ...
+  /* Walk over all the sub-trees 
+     of this operand.  */
+  len = first_rtl_op (code);
+
+  for (i = 0; i < len; ++i)
+  {
+    result = walk_tree (&(TREE_OPERAND (*tp, i)), 
+                               func, data, htab);
+    if (result)					
+      return result;
+  }
+  ...
+}

### 2015-10-08 figures/GCC27733.c

@@ -1,0 +1,18 @@
+//expmed.c
+struct alg_hash_entry {
+-  unsigned int t;
++  unsigned HOST_WIDE_INT t;
+};
+
+void 
+synth_mult(...unsigned HOST_WIDE_INT t, ...)
+{
+  hash_index = t ...;
+  if (alg_hash[hash_index].t == t ...)
+  {
+    ...
+    //reuse previous results
+  }
+  ...
+  //recursive computation
+}

### 2015-11-05 section/6_related.tex
shrink related work section

\section{Related Works}
\label{sec:related}

\subsection{Performance Diagnosis}
Profilers are the most commonly used tools that help developers understand
performance
\cite{Zaparanuks:2012:AP:2254064.2254074,Coppa:2012:IP:2254064.2254076,
D'Elia:2011:MHC:1993498.1993559, 
Mytkowicz:2010:EAJ:1806596.1806618,
Ravindranath:2012:AMA:2387880.2387891,
Jovic:2011:CMY:2048066.2048081,IntroPerf}.
Different from our work, profiling aims to tell where 
computation resources are spent, 
not where and why computation resources are wasted. 
The root cause code region of a performance problem often is not inside
the top-ranked function in the profiling result \cite{SongOOPSLA2014}.
Even if it is, developers still need to spend a lot of effort to understand
whether and what kind of computation inefficiency exists.

Recently, tools that go beyond profiling and provide more automated analysis
have been proposed.
StackMine~\cite{Han:2012:PDL:2337223.2337241} can
identify slow call-stack patterns inside event handlers. The work by
\citet{TaoAsplos2014} analyzes system traces to understand 
performance impact propagation and 
causality relationship among different system components. 
X-ray~\cite{Attariyan:2012:XAR:2387880.2387910} helps identify inputs
or configuration entries that are most responsible for performance problems.
Although these techniques are all very useful, 
they target different problems from \Tool. \Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.

\Tool is most related to
the recent statistical performance debugging work
\citep{SongOOPSLA2014}, both trying to identify source-code level root causes
for user-perceived performance problems. 
This previous work identifies which loop is most correlated with 
a performance symptom through statistical analysis, 
but cannot answer whether or 
what type of inefficiency this loop contains.
\Tool complements it by
providing detailed root cause information and fix strategy suggestions through
program analysis.

\subsection{Performance Bug Detection}

Many dynamic and static analysis tools have been built to detect different
types of performance problems, such as 
run-time bloat~\cite{Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616}, 
low-utility data structures~\cite{Xu:2010:FLD:1806596.1806617}, 
cacheable data~\cite{Cachetor}, false sharing in
multi-thread programs~\cite{Liu:2011:SPD:2048066.2048070},
inefficient nested loops~\cite{Alabama},
loops with unnecessary iterations~\cite{CARAMEL,IsilDillig.PLDI15},
input-dependent loops~\cite{xiao13:context}, and others. 
%Some static tools \cite{PerfBug} identify performance defects that violate
%specific efficiency rules, often related to API usage.

As discussed in 
Section \ref{sec:intro}, these tools are all useful in improving software
performance, but are not suitable for performance diagnosis.
With different design goals from \Tool, these bug detection tools are not 
guided by any specific
performance symptoms. Consequently, they take different coverage-accuracy
trade-offs from \Tool. \Tool tries to cover a wide variety of root-cause 
categories and is more aggressive in identifying root-cause categories, because
it is only applied to a small number of loops that are known to be highly
correlated with the specific performance symptom under study.
Performance-bug detection tools has to be more conservative and tries hard
to lower false positive rates, because it needs to apply its analysis to the
whole program, instead of just a few loops. This requirement causes bug
detection tools to each focus on a specific root-cause category.
%In fact, most inefficient loops in our study are very difficult to be detected
%by a generic performance bug detectors --- it is very difficult to prove them to
%be inefficient without application-specific domain knowledge.
%For example, only a couple of inefficient loops out of the 45 studied
%in Table \ref{tab:root} can be detected by recent static inefficient
%loop checkers
%\cite{CARAMEL,IsilDillig.PLDI15}.
Performance bug detection tools also do not aim to provide fix suggestions.
For the few that do provide \cite{CARAMEL}, they only focus on very specific
fix patterns, such as adding a break into the loop. 
In addition, dynamic performance bug detectors do not try to achieve any
performance goals. None of them has tried applying sampling to their
bug detection and often leads to 10X slowdowns or more.

\subsection{Other Techniques to Fight Performance Bugs}

There are many test inputs generation techniques that help
performance testing 
\cite{WISE, EventBreak, SpeedGun}.
Some techniques aim to improve the test selection or prioritization during 
performance testing~\cite{Forepost,Huang:2014:PRT:2568225.2568232}.  
All these techniques combat performance bugs from different aspects from performance diagnosis.

### 2015-11-05 section/0_intro.tex
shrinking

@@
 degradation in software. They widely exist in deployed software due to the 
-complexity of modern software and the lack of testing support
+complexity of modern software and the lack of performance testing support
 ~\cite{s2e,PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
@@
 Tools that can help
-developers quickly and accurately diagnose performance problems,
-find performance-wasting root causes, and fix performance problems
+developers quickly and accurately diagnose performance problems
 are sorely desired.
@@
 In the context of performance problems,
-the symptom is often
-an execution showing severe absolute or
-relative slowness \cite{SongOOPSLA2014}; the root cause contains 
-information like which code region is inefficient and why
-it is inefficient. An effective diagnosis tool can help developers quickly
-and correctly figure out a patch to fix the performance problem.
+the symptom is 
+execution 
+slowness \cite{SongOOPSLA2014}; the root cause is about
+which code region is inefficient and why.
+An effective diagnosis tool can help developers quickly
+and correctly figure out a fix to the performance problem.
 
@@
 \item Coverage. 
-Real-world performance problems are caused by a wide variety of reasons. It 
-would be good if the diagnosis tool can cover a good portion of common
-root causes of real-world problems.
+Real-world performance problems are caused by a wide variety of reasons.
+A good diagnosis tool should handle a good portion of them.
 
 \item Accuracy. 
-The accuracy requirement applies for two aspects of performance diagnosis: (1)
-the inefficient code regions need to be accurately located and (2)
-the reason a specific region is inefficient needs to be accurately
-explained, so that developers can quickly fix the performance problem.
+First, the inefficient code regions need to be accurately located.
+Second, the reason a specific region is inefficient needs to be accurately
+explained, so that developers can fix the problem.
 
@@
 is, the easier for the diagnosis tool to be deployed, especially for 
-production-run usage scenarios. 
+production-run usage. 
 \end{itemize}
 
-Although progress has been made, no existing tools can satisfy the above
+No existing tools can satisfy these
 three requirements.
@@
 tell where computation resources are spent, 
-but not where and why computation resources are wasted. 
-In many cases, the root-cause function of a performance problem may not even
-get ranked by a profiler \cite{SongOOPSLA2014}.
+but not where and why resources are wasted. 
+In many cases, the root-cause function may not even
+get ranked by the profiler \cite{SongOOPSLA2014}.
 
@@
 code regions that match specific inefficiency patterns 
-\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616}. 
-Unfortunately, these tools are not designed for performance diagnosis.
-Consequently, they are not designed to provide \textit{coverage} for a wide
-variety of real-world performance problems; they do not target a specific
-performance symptom, and hence are at disadvantage in terms of diagnosis
-\texttt{accuracy}; dynamic performance-bug detection tools often lead to 
+\cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616,IsilDillig.PLDI15}. 
+Unfortunately, these tools are not designed for and are consequently
+unsuitable for performance diagnosis.
+They are not designed to provide \textit{coverage} for a wide
+variety of real-world problems; their analysis is not guided by
+performance failure symptom, and hence are at disadvantage in terms of diagnosis
+\texttt{accuracy}; dynamic detection tools often lead to 
 10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
@@
 
-Recently, progress has been made on applying statistical debugging to 
-performance diagnosis \cite{SongOOPSLA2014}. Given the symptom of 
-a performance problem (e.g., two similar inputs leading to very
-different execution speed),
-statistical debugging, an approach widely used for diagnosing
+Recently, progress has been made on statistical debugging for
+performance diagnosis \cite{SongOOPSLA2014}.
+Statistical debugging, an approach widely used for diagnosing
 functional failures \cite{liblit03,liblit05,tarantula1}, can
 accurately identify control-flow constructs that are most correlated with
-the performance problem by comparing problematic runs and regular runs.
+the performance problem by comparing runs with and without problematic 
+performance.
 Unfortunately, for loop-related 
@@
 user-perceived performance problems,
-it provides no information about why the suspicious loop is inefficient,
+it provides no information about whether and why 
+the suspicious loop is inefficient,
 not to mention providing fix suggestions. Although various
@@
 the root-cause taxonomy discussed above and design analysis routines for 
-every root-cause sub-category. Given a candidate inefficient loop, we will 
+every root-cause sub-category. Given a candidate loop, we will 
 apply a series of analysis to it to see if it matches any type of inefficiency.
@@
 We have evaluated \Tool on 18 real-world performance problems. 
-Evaluation results show that \Tool can accurately identify the detailed
+Evaluation results show that \Tool can accurately identify detailed
 root cause for all benchmarks and provide correct fix-strategy suggestion for
-16 benchmarks. All these are achieved with low run-time overhead.
+16 benchmarks. All of these are achieved with low run-time overhead.

### 2015-11-05 section/1_under.tex
shrinking

@@
 without developers' help.
-In this section, we will first present our taxonomy, together with real-world
-examples, followed by our empirical study about how a suite of real-world 
-inefficient
-loop problems fall into our root-cause categories.
 
-We should note that we are definitely not the first one who tries to categorize
-the root-cause patterns of performance problems. We are also not the first
+Note that we are not the first one who tries to categorize
+the root causes of performance problems. We are also not the first
 to identify many of the root-cause categories below. Instead, guided by

### 2015-11-05 section/2_workless.tex
shrinking

@@
 \label{sec:design}
-\Tool is composed of a series of analysis routines, each designed to 
-identify whether a given loop belongs to one specific type of root causes,
-as we will present below.
-
-As briefly mentioned in Section \ref{sec:intro}, the design of these analysis routines follows the following principles.
+\Tool is composed of a series of analysis routines that
+identify whether a given loop belongs to any root cause type discussed in
+Section \ref{sec:study_tax}.
+Its design
+follows the following principles.
 \begin{itemize}
-\item Providing diagnosis information, not detecting bugs. \Tool will be  
+\item Failure diagnosis, not bug detection. \Tool will be  
 used together with other performance diagnosis tools \cite{SongOOPSLA2014}
@@
 \item Static-dynamic hybrid analysis. As we will see, static analysis alone
-will not be able to provide all the needed information for performance
-diagnosis; dynamic analysis alone will incur too much unnecessary overhead.
-Therefore, we will use static-dynamic hybrid approach throughout our design.
+will not be able to provide all the needed information. However, 
+dynamic analysis alone will incur too much overhead.
+Therefore, we use a hybrid approach throughout our design.
 
-\item Using sampling to decrease run-time overhead. Loop-related 
+\item Sampling. Loop-related 
 performance problems have the unique nature of repetitiveness, which make 
-them a natural fit for random sampling. Therefore, we will design different
-sampling schemes for different analysis routines.
+them a natural fit for random sampling. We will design different
+sampling schemes for different analysis.
 \end{itemize}
@@
 
-We consider side-effect instructions as those instructions that write to
-variables defined outside the loop. The analysis to identify side-effect
-instructions is straightforward. We consider all functions that are called
+\Tool first identifies side-effect instructions that write to
+variables defined outside the loop. 
+\Tool analyzes all functions that are called
 by a loop directly or indirectly --- a function $F$ that updates variables
@@
 
-After identifying side-effect instructions, it is straight-forward to
-categorize loops into the four types discussed above.
+\Tool then categorizes loops into four types.
 Loop 0* contains no side-effect instructions. 
@@
 starts from the loop header and ends at the loop header.
-The remaining cases are either 
-0*1? or [0$|$1]*. 
-Differentiating these two cases is also straight-forward.
-In short, when the basic block that contains side-effect instructions
+For the remaining cases, 
+when the basic block with side-effect instructions
 is part of the natural loop, the case
@@
 We need dynamic analysis to figure out what portion of loop iterations are
-resultless at run time, which will help decide whether the loop is indeed
-the root cause of a user-perceived performance problem and worth fixing.
+resultless at run time, which will help decide whether the loop worths fixing.
 
 For a 0*1? loop, since it only generates results in the last iteration, we 
-only need to know the total number of iterations (or the average total number 
-of iterations when the loop has multiple instances) to figure out the 
+only need to know the total number of loop iterations 
+to figure out the 
 \textit{resultless rate} of the loop. The implementation is straightforward

### 2015-11-05 section/3_redundancy.tex
shrinking

@@
 every memory read conducted by $i_1$ and $i_2$. Two better alternative
-solutions are to record and compare only the values written or read by the
+solutions are to record and compare only the values written by the
 side-effect instructions, such as 
 line 9 in Figure~\ref{fig:Mozilla477564},
-or the source instructions\footnote{We define source instructions in a code
+or read by 
+the source instructions\footnote{We define source instructions in a code
 region $r$ as a set of memory-read instructions that side-effect
@@
 
-Among the the above two potential solutions, our design chooses the second one.
-The reason is that, if there is indeed
-redundancy, repetitive patterns at the side-effect instructions are caused by
-repetitive patterns in the source instructions.
-For the purpose of performance diagnosis, it is
-more informative to track the cause, rather than the effect.
+Among the the above two potential solutions, our design chooses the second one,
+because it is
+more informative for performance diagnosis 
+to track the cause rather than the effect.
 
 \emph{How to handle partial redundancy?}
-In practice, redundant loops may be doing largely the same, instead of exactly
-the same, computation across iterations or loop instances. It is also possible
+In practice, redundant loops may be doing largely the same, but not exactly
+the same, computation across iterations or loop instances. 
+%It is also possible
 %TODO define loop instance.
-that only some, instead of all, iterations in a loop are doing redundant
-computation. We will discuss how we handle this issue in Section \ref{sec:cal}.
+%that only some, instead of all, iterations in a loop are doing redundant
+%computation. 
+We will discuss how we handle this issue in Section \ref{sec:cal}.
 
 \emph{How to lower the overhead of record-and-compare?}
-Even if we only record and compare the values returned by source instructions,
-instead of all instructions in a loop, the run-time overhead and the log size
-would still be large. We will use two ways to lower this time and spatial
-overhead. First, static analysis can already tell some source instructions
-will always return the same value across iterations/loop-instances, and hence
-need not be traced at run time. Second, we can leverage the repetitive nature
-of performance problems and use random sampling to lower the overhead without
-degrading the diagnosis capability. We will discuss details of 
-these two optimization in Section \ref{sec:inst} and \ref{sec:perf}.
+Even if we only record and compare the values returned by source instructions
+the run-time overhead and the log size
+could still be large. We will use static analysis and run-time sampling
+to lower this time and spatial
+overhead 
+(Section \ref{sec:inst} and \ref{sec:perf}).
 %TODO static analysis alone is not sufficient, because some redundant is
@@
 memoization and batching are both common fix strategies for redundant loops.
-To pick the right fix strategies to fix a redundant loop, we will conduct 
-some extra analysis. We will discuss this in Section \ref{sec:redundant_fix}.
+To pick the right fix strategies,
+extra analysis is conducted by \Tool and presented in 
+Section \ref{sec:redundant_fix}.
 
@@
 
-After identifying source instructions, we instrument these source
-instructions, so that the values returned by these memory read
-instructions can be recorded at run time. Specifically, we will assign
-a unique ID for each source instruction, and a pair of $<InstID, Value>$
-will be recorded at run time with the execution of a source instruction.
+After identifying source instructions, we instrument them to record
+what values they read from memory
+at run time.
+%Specifically, we will assign
+%a unique ID for each source instruction, and a pair of $<InstID, Value>$
+%will be recorded at run time with the execution of a source instruction.
 Our trace also includes some delimiters and meta information that allows
-trace analysis to differentiate values recorded from different loop
-iterations, different loop instances, and so on.
+trace analysis to differentiate values recorded from different instructions, 
+loop
+iterations, loop instances, and so on.
 %TODO
@@
 First, how to judge whether
-two iterations are doing redundant work --- should the two iterations conduct
-exactly the same computation?
+two iterations are doing redundant work?
 Second, is a (dynamic) loop problematic when it contains only few 
@@
 definition --- only iterations that are doing exactly the same computation are
-considered redundant. Since one iterating may not contain too much computation,
+considered redundant. Since one iteration may not contain too much computation,
 a weaker definition here may lead to many false positives. For the 
@@
 when the number of distinct iterations is less than half of the total iterations, 
-we consider the loop is cross-iteration redundant. 
+we consider the loop to be cross-iteration redundant. 
 %when the number of distinct iterations is less than half of the total iterations 
@@
 contains cross-iteration redundancy.
-As we can see, under the problem triggering input, 
-only several distinct listeners are contained inside the vector, and most of 
-iterations of the loop inside function \texttt{fireMessageLoggedEvent}
-are doing exactly the same computation. 
+Under the problem triggering input, there are
+only few distinct listeners, and most of the
+loop iterations in \texttt{fireMessageLoggedEvent}
+are doing redundant work. 
 %The problem for this bug is that developers say that the performance 
@@
 checking the redundancy between every pairs of loop
-instances would be very time consuming.
+instances is time consuming.
 
@@
 make sure to sample the immediately next loop instance too.
-
-The implementation is similar with that for cross-iteration redundancy analysis.
-The only difference includes: (1) clone is made for the whole loop and the
-sampling control
-is done in the pre-header of the loops; (2)
-sampling is conducted when \texttt{CurrentID} equals either
-\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
-increased by a random value in the latter case.
+The implementation is straightforward by cloning the whole loop and making
+sampling decisions in the loop pre-headers.
+%; (2)
+%sampling is conducted when \texttt{CurrentID} equals either
+%\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
+%increased by a random value in the latter case.
 
@@
 
-\paragraph{Handling recursive functions}
-We also conduct sampling to our redundancy analysis for recursive functions.
-For a recursive function, we first create an instrumented clone copy of 
-the whole function body.
-We then add a sampling-control code snippet at the entry point of the function,
-where \texttt{CurrentID} and \texttt{NextSampleID} are maintained to decide
-whether to execute the original function body or the instrumented 
-value-recording clone copy.
-We also create clones for all the callee functions of the recursive function
-under study, so that the sampling decision can be correctly conducted
-throughout the call chain.
+%\paragraph{Handling recursive functions}
+%We also conduct sampling to our redundancy analysis for recursive functions.
+%For a recursive function, we first create an instrumented clone copy of 
+%the whole function body.
+%We then add a sampling-control code snippet at the entry point of the function,
+%where \texttt{CurrentID} and \texttt{NextSampleID} are maintained to decide
+%whether to execute the original function body or the instrumented 
+%value-recording clone copy.
+%We also create clones for all the callee functions of the recursive function
+%under study, so that the sampling decision can be correctly conducted
+%throughout the call chain.
 
@@
 values.
-%induction variables are not alwayes identified as source instructions.
+%induction variables are not always identified as source instructions.
 %it could be possible that side-effect instructions do not depend on induction variables.
@@
 %cross-iteration redundancy simply because induction variable is in the 
-%dependent set. Really? The input workload itself could be repititive, and hence
+%dependent set. Really? The input workload itself could be repetitive, and hence
 %could still deserve monitoring, right? 
@@
 %source+i; loop induction variable is i. What do you mean by "the read address
-%is an induction varaible"? Please rewrite.
+%is an induction variable"? Please rewrite.
 
 %ANSWER
-%Shan, both source + i and i are induction variables, becasue both of them 
+%Shan, both source + i and i are induction variables, because both of them 
 %will be added by 1 in each iteration. The only difference between these two 

### 2015-11-05 section/5_exper.tex
test
shrinking

@@
    Mozilla416628         & 105             & C                      &  0*1?        & C     \\
-   Mozilla490742         & N/A             & JS                     &  C-I         & B       \\
-   Mozilla35294          & N/A             & C++                    &  C-L         & B        \\ 
-   Mozilla477564         & N/A             & JS                     &  C-L         & M       \\
+   Mozilla490742         &  -             & JS                     &  C-I         & B       \\
+   Mozilla35294          &  -             & C++                    &  C-L         & B        \\ 
+   Mozilla477564         &  -             & JS                     &  C-L         & M       \\
    \midrule 
@@
    \midrule    
-   Apache32546           & N/A             & Java                   &  C-I         & B  \\
-   Apache37184           & N/A             & Java                   &  C-I         & M  \\
-   Apache29742           & N/A             & Java                   &  C-L         & B \\ 
-   Apache34464           & N/A             & Java                   &  C-L         & M  \\
-   Apache47223           & N/A             & Java                   &  C-L         & B \\
+   Apache32546           &  -             & Java                   &  C-I         & B  \\
+   Apache37184           &  -             & Java                   &  C-I         & M  \\
+   Apache29742           &  -             & Java                   &  C-L         & B \\ 
+   Apache34464           &  -             & Java                   &  C-L         & M  \\
+   Apache47223           &  -             & Java                   &  C-L         & B \\
    \midrule
@@
   \caption{Benchmark information.
-  (N/A: we skip the size of benchmarks that are extracted from real-world applications.
-  Root cause ``C-I'' is short for cross-iteration redundancy.
-  Root cause ``C-L'' is short for cross-loop redundancy.
-  C, B, M, and S represent different fix strategies, as discussed in
+  (-: benchmarks extracted from real-world applications.
+  ``C-I'': cross-iteration redundancy.
+  ``C-L'': cross-loop redundancy.
+  C, B, M, S: fix strategies as discussed in
   Table \ref{tab:root}.
@@
   \caption{False positives of \Tool, when applying to top 5 loops reported by 
-    statistical performance diagnosis for each benchmark. `-' represents zero false positive.
-    Other cells report real false positives and benign false positives, which is in the
-    subscript.
+    statistical performance diagnosis for each benchmark. `-': no false positive. $x_y$: $x$ real false positives and $y$ benign ones.
 }
@@
 resultless iterations is small. 
+%TODO a table 6 was deleted from oopsla submission
 
@@
     \toprule
-	    & \multicolumn{3}{c}{\Tool} & \multicolumn{2}{c}{w/o optimization} \\
+	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
      \cmidrule(lr){2-4}
@@
   %\nocaptionrule
-  \caption{Run-time overhead of applying \Tool to the buggy loop, with and
-    without optimizations. 
-    Only results from non-extracted benchmarks are shown. 
-  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
-  /: not applicable. }
+  \caption{Run-time overhead of applying \Tool to the buggy loop
+    (only non-extracted benchmarks are shown). 
+  -: dynamic analysis is not conducted, as static analysis is sufficient.
+  /: not applicable.}
   \label{tab:performance}

### 2015-11-05 section/6_related.tex
shrinking

@@
 loops with unnecessary iterations~\cite{CARAMEL,IsilDillig.PLDI15},
-input-dependent loops~\cite{xiao13:context}, and others. 
+input-dependent loops~\cite{xiao13:context}. 
 %Some static tools \cite{PerfBug} identify performance defects that violate

### 2015-11-05 section/abstract.tex
shrinking

Writing efficient software is difficult.
Design and implementation defects can easily
lead to severe performance 
degradation in production runs. These problems annoy end users
and waste a huge amount of energy. Techniques that help
diagnose and fix performance problems are desired.

Unfortunately, existing performance diagnosis techniques are still preliminary,
failing to provide the desired diagnosis coverage, accuracy, and performance. 
Existing performance-bug detectors can accurately identify specific type
of inefficient computation, but are not ideal for performance diagnosis
in term of coverage and performance. 
Profiling tools cannot identify
the code regions that \textit{waste} the most resources, not to mention
explain why some resources are wasted, failing
both coverage and accuracy.
Recent work on statistical performance diagnosis can
identify coarse-grained root causes, such as which loop
is the root cause of a performance problem. However, it cannot provide 
fine-grained root cause information, such as why a loop is inefficient and
how developers might fix the problem.

In this paper, we first conduct an empirical study to understand what are
fine-grained performance problem root causes in real world. 
We then design a series of static-dynamic hybrid analysis routines that can
help identify accurate fine-grained performance root cause information.
We further use sampling techniques to lower our diagnosis overhead without
hurting diagnosis accuracy or latency. Evaluation using real-world performance
problems show that our tool can provide better coverage and accuracy than
existing performance diagnosis tools, with small run time overhead.

### 2015-11-10 section/abstract.tex
finish abstract

@@
 lead to severe performance 
-degradation in production runs. These problems annoy end users
-and waste a huge amount of energy. Techniques that help
-diagnose and fix performance problems are desired.
+degradation. Techniques that help
+diagnose performance problems are desired.
+Unfortunately, existing techniques are still preliminary.
+%failing to provide the desired diagnosis coverage, accuracy, and performance. 
+Performance-bug detectors can identify specific type
+of inefficient computation, but are not suitable for accurately diagnosing
+a wide variety of real-world performance problems. 
+Profilers can locate code regions that consume resources, but 
+not the ones that \textit{waste} resources.
+Statistical performance diagnosis can
+identify loops or branches that are most correlated with a performance
+symptom, but cannot decide whether and why a loop is inefficient, and
+how developers might fix it.
 
-Unfortunately, existing performance diagnosis techniques are still preliminary,
-failing to provide the desired diagnosis coverage, accuracy, and performance. 
-Existing performance-bug detectors can accurately identify specific type
-of inefficient computation, but are not ideal for performance diagnosis
-in term of coverage and performance. 
-Profiling tools cannot identify
-the code regions that \textit{waste} the most resources, not to mention
-explain why some resources are wasted, failing
-both coverage and accuracy.
-Recent work on statistical performance diagnosis can
-identify coarse-grained root causes, such as which loop
-is the root cause of a performance problem. However, it cannot provide 
-fine-grained root cause information, such as why a loop is inefficient and
-how developers might fix the problem.
-
-In this paper, we first conduct an empirical study to understand what are
-fine-grained performance problem root causes in real world. 
-We then design a series of static-dynamic hybrid analysis routines that can
-help identify accurate fine-grained performance root cause information.
-We further use sampling techniques to lower our diagnosis overhead without
-hurting diagnosis accuracy or latency. Evaluation using real-world performance
-problems show that our tool can provide better coverage and accuracy than
-existing performance diagnosis tools, with small run time overhead.
+In this paper, we first design a root-cause
+and fix-strategy taxonomy for real-world inefficient loops, 
+one of the most common performance problems in the field.
+We then design a static-dynamic hybrid analysis tool, \Tool, to
+provide accurate performance diagnosis for loops.
+We further use sampling techniques to lower the run-time overhead without
+degrading the accuracy or latency of \Tool diagnosis. 
+Evaluation using real-world performance
+problems shows that \Tool can provide better coverage and accuracy than
+existing techniques, with low overhead.

### 2015-11-17 section/0_intro.tex
finish revising introduction

@@
 performance failure symptom, and hence are at disadvantage in terms of diagnosis
-\texttt{accuracy}; dynamic detection tools often lead to 
+\textit{accuracy}; dynamic detection tools often lead to 
 10X slowdowns or more \cite{Cachetor,Xu:2010:FLD:1806596.1806617,Alabama}, 
@@
 performance diagnosis \cite{SongOOPSLA2014}.
-Statistical debugging, an approach widely used for diagnosing
-functional failures \cite{liblit03,liblit05,tarantula1}, can
-accurately identify control-flow constructs that are most correlated with
-the performance problem by comparing runs with and without problematic 
-performance.
-Unfortunately, for loop-related 
+This approach compares runs with and without problematic performance, and
+accurately identifies control-flow constructs, such as a branch $b$ or 
+a loop $l$, that are most correlated with
+the execution slowness.%, referred to as slowness-predictor.
+Unfortunately, this approach is \textit{not} effective
+for loop-related 
 performance problems, which contribute to two thirds of
 real-world performance problems studied in previous work 
-\cite{SongOOPSLA2014,PerfBug}, statistical debugging is not very effective.
-Although it can identify the root-cause loop, it does not provide any 
-information regarding why the loop is inefficient and hence is not very helpful
-in fixing the performance problem.
+\cite{SongOOPSLA2014,PerfBug}. It cannot
+tell whether and how loop $l$ is inefficient 
+and hence is not very helpful
+in fixing performance problems.
 
@@
 Figure~\ref{fig:GCC27733} shows a real-world performance bug in GCC. 
-Function \texttt{synth\_mult} is used to compute the best algorithm for 
-multiplying \texttt{t}. It is so time consuming that developers tried 
-speeding it up through memoization ---
+Function \texttt{mult\_alg} is used to compute the best algorithm for 
+multiplying \texttt{t}. It is so time consuming that developers used a
 hash-table
-\texttt{alg\_hash} is used to remember which \texttt{t} has been processed
-in the past and what is the processing result. 
-Unfortunately, a small mistake in the type declaration of hash-table
-entry \texttt{alg\_hash\_entry} causes memoization not to work when \texttt{t}
-is larger than the maximum value type-\texttt{int} can represent.
-As a result, under certain workload, \texttt{synth\_mult} conducts a lot of
-redundant computation for same \texttt{t} values recursively, leading to
-huge performance problems.  In practice, developers know the problem is inside
-\texttt{synth\_mult} very early. However, since this function is 
-complicated, it took them several weeks to figure out the root cause. 
-If a tool can tell them not only which loop\footnote{Recursive functions are
-handled similarly as loops in this paper.}
-is the root cause but also why a loop is inefficient (i.e., lot of redundant
-computation and the need for better memoization in this example), 
-the diagnosis and bug fixing
-process would be much easier for developers.
+\texttt{alg\_hash} to remember which \texttt{t} has been processed
+in the past and what is the result. 
+Unfortunately, a mistake in the type declaration of hash-table
+entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t},
+severely hurting performance.
+In reality, developers easily figured out that function
+\texttt{mult\_alg} is most correlated with the execution slowness, but
+spent several weeks to finally figure out \texttt{mult\_alg} is in fact
+inefficient.
+%If a tool can tell them not only which loop\footnote{Recursive functions are
+%handled similarly as loops in this paper.}
+%is the root cause but also why a loop is inefficient (i.e., lot of redundant
+%computation and the need for better memoization in this example), 
+%the diagnosis and bug fixing
+%process would be much easier for developers.
 
 Clearly, more research is needed to improve the state of the art of performance
-diagnosis. Diagnosis techniques that can provide better
-\textit{coverage} and \textit{accuracy} for common performance problems,
-especially loop-related performance problems, with good
-performance is well desired.
+diagnosis --- better diagnosis
+coverage, better diagnosis accuracy, and low run-time
+overhead for common performance problems,
+especially loop-related performance problems.
 
@@
 This paper presents a tool, \Tool, that can help effectively diagnose
-inefficient loop problems with good coverage, accuracy, and performance.
-
-\Tool targets the most common type of performance problems, inefficient
-loops, according to previous
-empirical studies \cite{SongOOPSLA2014,PerfBug}.
-\Tool also targets a challenging problem. Although
-statistical debugging \cite{SongOOPSLA2014}
-can help identify suspicious loops that are highly correlated with 
-user-perceived performance problems,
-it provides no information about whether and why 
-the suspicious loop is inefficient,
-not to mention providing fix suggestions. Although various
-bug-detection techniques \cite{Cachetor,Alabama,CARAMEL} can help detect
-loop-related performance bugs, they all suffer from generality problems,
-covering only a specific type of loop problems each; the dynamic
-tools \cite{Cachetor,Alabama} also suffer from performance
-problem, imposing 10X slowdown or more.
+inefficient loop problems, the most common type of performance problems
+\cite{SongOOPSLA2014,PerfBug}, with good coverage, accuracy, and performance.
 
@@
 
-First, figuring out a taxonomy for the root causes of common inefficient loops.
+First, figuring out a root-cause taxonomy for inefficient loops.
 Such a taxonomy is the prerequisite to developing a general and accurate
@@
 loop problems, we come up with a hierarchical root-cause taxonomy for
-inefficient loops. 
+inefficient loops that are
 %Specifically, we consider \textit{resultless} and
@@
 %sub-categories based on the granularity of the resultless or redundant work. 
-Our empirical study shows that our taxonomy is general enough to cover
+general enough to cover
 common inefficient loops, and also specific enough to help developers understand
-and fix the performance problem. We will present more details 
+and fix performance problems. More details are
 in Section \ref{sec:study}.
@@
 Second, building a tool(kit) \Tool that can automatically and accurately
-identify the fine-grained root-cause type of a suspicious loop, 
-together fix-strategy suggestions. 
+identify whether and how a suspicious loop is inefficient, 
+together with fix-strategy suggestions. 
 We achieve this following several principles:
@@
 \item Focused checking. 
-Different from performance-bug detection tools that blindly checks the whole
-software, \Tool focuses on performance symptoms and only check inefficient
-loop candidates identified by existing tools, a statistical debugging
-tool in our current prototype \cite{SongOOPSLA2014}. 
-This focused study is crucial for \Tool to achieve high
-accuracy.
+Different from performance-bug detectors that blindly checks the whole
+software, \Tool focuses on loops that are
+most correlated with performance symptoms. 
+This focus is crucial for \Tool to achieve both high
+accuracy and high coverage.
 
@@
 
-\item Static-dynamic hybrid analysis to balance performance and accuracy.
+\item Static-dynamic hybrid analysis.
 As we will see, static analysis alone cannot accurately identify 
@@
 
-We have evaluated \Tool on 18 real-world performance problems. 
+We evaluated \Tool on 18 real-world performance problems. 
 Evaluation results show that \Tool can accurately identify detailed

### 2015-11-17 figures/GCC27733.c

@@ -1,18 +1,14 @@
-//expmed.c
-struct alg_hash_entry {
+struct hash_entry {
 -  unsigned int t;
-+  unsigned HOST_WIDE_INT t;
++  HOST_WIDE_UINT t;
 };
 
-void 
-synth_mult(...unsigned HOST_WIDE_INT t, ...)
+void mult_alg(... HOST_WIDE_UINT t, ...)
 {
   hash_index = t ...;
   if (alg_hash[hash_index].t == t ...)
   {
-    ...
     //reuse previous results
   }
-  ...
   //recursive computation
 }

### 2015-11-17 section/1_under.tex
check in correlation table
finish section 2

@@
 
-The first task we are facing is to figure out a root-cause taxonomy for
-real-world inefficient loops. 
-Our taxonomy design is guided by checking a benchmark suite of real-world
-inefficient loops, collected by previous work \cite{SongOOPSLA2014,PerfBug}. 
-We also try to satisfy three requirements in our design.
-(1) Coverage: covering
+Previous work has identified a wide variety of performance root-cause 
+categories. However, no existing taxonomy satisfies all the three 
+requirements below and hence cannot be directly used for our diagnosis tool
+design.
+\begin{enumerate}
+\item Coverage: covering
 a big portion of real-world inefficient loop problems; 
-(2) Actionability: each root-cause category should be informative enough 
+\item Actionability: each root-cause category should be informative enough 
 to help developers
 decide how to fix a performance problem; 
-(3) Generality: too application-specific root causes will not work, as we
-need to build diagnosis tools to automatically identify these root causes 
+\item Generality: application-specific root causes will not work, as we
+hope to build diagnosis tools that can automatically identify root causes 
 without developers' help.
+\end{enumerate}
 
-Note that we are not the first one who tries to categorize
-the root causes of performance problems. We are also not the first
-to identify many of the root-cause categories below. Instead, guided by
-previous work and our empirical study, we try to figure out our own taxonomy 
-that satisfy the above three requirements and can
-work well with the diagnosis tool that we will build later.
+This section first presents the root-cause taxonomy designed by us, 
+and then discusses the coverage, actionability, and generality
+of our taxonomy using a suite of real-world
+inefficient loops collected by previous work \cite{SongOOPSLA2014,PerfBug}.
 
-\subsection{Taxonomy}
+\subsection{Taxonomy Design}
 \label{sec:study_tax}
-Our taxonomy contains two major root cause categories,
-\textit{resultless} and \textit{redundancy}, and several sub-categories, 
-as below.
+We divide all inefficient loops into two root-cause categories:
+\textit{resultless} and \textit{redundancy}.
 
-\underline{\textit{\textbf{Resultless}}}
-Resultless loops spend a lot of time in computation that does not 
-produce any results that will be used after the loop.
-Depending on when such resultless computation is conducted, we further
-consider four sub-categories.
+\subsubsection{Resultless loops}
+A resultless loop spends a lot of time in computation without
+producing any results useful after the loop.
+It is further categorized based on which loop iterations are
+(not) producing useful results.
 
@@
 This type of loops never produce any results in any iteration.
-This type of loops should be rare in mature software systems.
+They are rare in mature software systems.
 They should simply be deleted from the program.
@@
 
-\begin{figure}[h]
-\centering
-\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-     morekeywords={+},keepspaces=true}
-  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
-\caption{A resultless 0*1? bug in Mozilla}
-\label{fig:Mozilla347306}
-\end{figure}
+%\begin{figure}[h]
+%\centering
+%\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+%     morekeywords={+},keepspaces=true}
+%  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
+%\caption{A resultless 0*1? bug in Mozilla}
+%\label{fig:Mozilla347306}
+%\end{figure}
 
@@
 This type of loops only produce results in the last iteration, if any. 
-They are often related to search: they check a sequence of elements one
+They are often related to search: check a sequence of elements one
 by one until the right one is found.
-Not all loops of this type are inefficient. If they are, they are often
+Clearly, whether this type of loops are efficient or not depends on the
+workload. If they are indeed inefficient, they are often
 fixed by data-structure changes.
-Figure~\ref{fig:Mozilla347306} shows an example from Mozilla
-JavaScript engine. 
-The loop searches through an array containing source code information for the input \texttt{pc}. 
-In practice, this loop needs to execute more than 10000 iterations for 
-many long JavaScript encountered by users, which leads to huge 
-performance problems --- web browsers freeze. To fix this problem, 
-developers simply replace array with hash table when processing long
-JavaScript files.
+As an example, Mozilla JavaScript engine used to store the source-code 
+line numbers of all byte-code instructions in a linked list \texttt{script}. 
+Later on, many users complained that Mozilla browser freezed when opening
+some popular websites. It turned out that those websites contained large
+JavaScript files that filled the linked list \texttt{script} with
+tens of thousands of nodes. Linear search on \texttt{script} then caused the
+to freeze. To fix this problem, 
+developers simply replace linked list with hash table
+(Mozilla Bug\#347306).
 % This improve the performance by 52.60{\bf X}.
@@
 {\textbf{[0$|$1]*}}:
-Every iteration in this type of loops may or may not produce results.
-Under certain workload, the majority of the loop iterations do not produce
-any results and lead to performance problems perceived by end users.
-The inefficiency problem caused by this type of loops can often be solved
-by adding extra conditions to skip the loop under certain contexts.
-Figure~\ref{fig:GCC46401} shows such an example from GCC.
+Each iteration in this type of loops may or may not produce results.
+For some workload, the majority of iterations do not produce
+results and lead to performance problems perceived by users.
+These problems are often solved
+by using a simple check to conditionally skip the expensive loop.
+Figure~\ref{fig:GCC46401} shows such an example.
 %how users perceive this problem
@@
 %explain the fix
-Only when the if branch executed,
-one iteration will generate results. 
-The bug happens when GCC checks violation of sequence point rule. 
-The user notice severe performance degradation when enabling the checking. 
-The buggy loop is super-linear inefficient in terms of the number of operands
-in one expression. The buggy input contains an expression, which is long and special. 
-The loop takes a lot of iterations during bad run, but none of the iterations will 
-generate results. 
-The patch is to add extra checking before processing each operand. When it also has
-the special feature like the bad input, the loop will be skipped.
+Users complained that compilation became extremely slow when they 
+enabled the \texttt{-Wsequence-point} checking.
+The slowness was caused
+by the \texttt{for} loop shown in the figure. Since the algorithm
+behind this loop is quadratic in the number of operands in an expression, 
+programs with long expressions suffer severe slow-downs.
+After further diagnosis, developers observed that this loop rarely
+had any side-effects, as the \texttt{if} condition was rarely satisfied.
+At the end, the patch greatly improved performance through a
+simple checking that allows the loop to be
+skipped for most expressions.
 
@@
 Loops in this category always generate results in almost all iterations. 
-They are inefficient, because the results generated could be useless due to
+They are inefficient because their results are useless due to
 some high-level semantic reasons.
@@
 For example, several Mozilla performance problems are caused by 
-loops that contain intensive GUI operations.
-Although every iteration of these loops produce side effects, 
-the performance problem forced developers to change the program 
-and batch/skip some GUI operations.
+loops that contain intensive GUI operations whose graphical outcome may not
+be observed by humans and hence can be optimized.
 
-\begin{figure}[h]
-\centering
-\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-     morekeywords={+},keepspaces=true}
-  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
-\caption{A cross-loop redundant bug in Mozilla }
-\label{fig:Mozilla477564}
-\end{figure}
-
-\underline{\textit{\textbf{Redundant}}}
+\subsubsection{Redundant loops}
 Redundant loops spend a lot of time in repeating computation that is already
-conducted.
-Depending on the unit of the redundant computation, we further consider 
-two sub-categories.
+conducted. They are further categorized below based on their redundancy unit.
 
@@
 
-\begin{figure}[h]
+\comment{
+\begin{figure}
 \centering
@@
 \end{figure}
+}
+
+\begin{figure}
+\centering
+\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+     morekeywords={+},keepspaces=true}
+  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
+\caption{A cross-loop redundant bug in Mozilla }
+\label{fig:Mozilla477564}
+\end{figure}
 
@@
 one iteration repeats
-repeating what was already done by an earlier iteration of the same loop.
-Here, we consider recursive function calls as a loop, treating one function 
-call instance as one loop iteration. 
+what was already done by an earlier iteration of the same loop.
+Here, we consider a recursive function as a loop, treating one function-call
+instance as one loop iteration.
+
 This type of inefficiency is often fixed by memoization or batching, depending
 on whether the redundancy involves I/O operations.
-For example, GCC\#27733 shown in Figure~\ref{fig:GCC27733} 
-is fixed by better memoization. 
+For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
+redundant computation across different invocations of recursive function
+\texttt{mult\_alg}. The patch essentially allows memoization to work.
 %Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
 %This bug is fixed by using a hash table to avoid visiting the same sub-tree twice.
+\comment{
 Mozilla\#490742 in Figure~\ref{fig:Mozilla490742} represents a slightly different type of cross-iteration
@@
 %to a couple of seconds.
+}
 
 {\textbf{Cross-loop Redundancy}}:
-A whole loop is the redundancy unit here:
+A whole loop is the redundancy unit:
 one dynamic instance of a loop spends a big chunk, if not all, of its
@@
 Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
-The buggy loop is to count how many previous siblings of the input \texttt{aNode} have the same name and URI. 
-There is an outer loop for the buggy one, and the outer loop will update \texttt{aNode} by using its next siblings. 
-The bug is fixed by saving the calculated count for each node. 
-A new count value is calculated by adding one to the saved count value of the nearest previous sibling with the same name and URI.
+The buggy loop counts how many previous siblings of the input \texttt{aNode} have the same name and URI. 
+There is an outer loop, not shown in the figure, that repeatedly updates
+\texttt{aNode} to be its next sibling and calls
+\texttt{sss\_xph\_generate} with the new \texttt{aNode}. 
+This bug is fixed by adding an extra field for each node to save the calculated 
+count, so that a new count value can be calculated by simply adding one to the
+saved count value of the nearest previous sibling with the same name and URI.
 
-\subsection{Empirical study}
+\subsection{Taxonomy Assessment}
 \label{sec:tax_study}
-Having presented our taxonomy above, we will see how it works for a set of
+We assess the coverage, actionability, and generality of our taxonomy using
+a set of
 real-world inefficient loop problems collected by previous work
-\cite{SongOOPSLA2014,PerfBug}. Specifically, we want to check the 
-coverage and the actionability of our taxonomy presented above:
-(1) How common are real-world performance problems caused by the 
-patterns discussed above?
-(2) How are real-world problems fixed by developers? Can we predict their
-fix strategies based on the root-cause pattern?
+\cite{SongOOPSLA2014,PerfBug}.
 
@@
 \begin{table}[h!]
+\small{
 \centering
@@
 \end{tabular}
+}
 \caption{Applications and bugs used in the study}
@@
 43 problems as loop-related. }.
-More details can be found in the original papers that collect
+More details can be found in previous papers that collected
 these bugs.
 
-\subsubsection{Observations}
+\subsubsection{Assessment}
 \label{sec:study_ob}
+
 \begin{table*}[tb!]
@@
 {
-\begin{tabular}{|lccccccl|}
+\begin{tabular}{|lcccccc|}
 \hline
-&Apache&Chrome&GCC&Mozilla&MySQL&Total&Fix Strategy\\
+&Apache&Chrome&GCC&Mozilla&MySQL&Total\\
 \hline
-Total \# of loop-related bugs & 11 & 4 & 8 & 12 & 10 & 45 &  \\
+Total \# of loop bugs & 11 & 4 & 8 & 12 & 10 & 45 \\
 \hline
-\multicolumn{8}{|c|}{\# of {\textit {Resultless}} bugs}\\
-\multicolumn{1}{|l}{ {\bf 0*} }
-&0&0&0&0&0&0&\\
-\multicolumn{1}{|l}{ {\bf 0*1?} }
-&0&0&0&2&3&5&C(4)$|$S(1)\\
-\multicolumn{1}{|l}{{\bf [0$|$1]*}}
-&0&1&1&1&1&4&S(4)\\
-\multicolumn{1}{|l}{{\bf 1*}}
-&1&2&3&6&3&15& B(4)$|$S(4)$|$O(7)\\
+\multicolumn{1}{|l}{ {\bf 0*} Resultness}
+&0&0&0&0&0&0\\
+\multicolumn{1}{|l}{ {\bf 0*1?} Resultness}
+&0&0&0&2&3&5\\
+\multicolumn{1}{|l}{{\bf [0$|$1]*} Resultness}
+&0&1&1&1&1&4\\
+\multicolumn{1}{|l}{{\bf 1*} Resultness}
+&1&2&3&6&3&15\\
 %&0&2&0&5&0&7&B(4)$|$S(3)\\
@@
 \hline
-\multicolumn{8}{|c|}{ \# of {\textit {Redundant}} bugs}\\
-\multicolumn{1}{|l}{Cross-{\bf iteration} redundancy}
-&7&1&2&1&1&12&B(4)$|$M(7)$|$O(1)\\
-\multicolumn{1}{|l}{ Cross-{\bf loop} redundancy}
-&3&0&2&2&2&9&B(4)$|$M(5)\\
+\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
+&7&1&2&1&1&12\\
+\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
+&3&0&2&2&2&9\\
   %MySQL15811 is moved from 1* to here; consider it as fixed by M
@@
 \caption{Number of bugs in each root-cause category. 
-B, M, S, C, and O represent different fix strategies:
+}
+\label{tab:root}
+\end{table*}
+
+\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
+%For ranges 0-10, multiply by 10 by adding 0 after #1
+
+\begin{table}[tb!]
+%\begin{adjustwidth}{-.5in}{-.5in}
+\small
+\centering
+{
+\begin{tabular}{lcccccc}
+%\hline
+                                 &{\bf 0*}    & {\bf 0*1?} & {\bf [0$|$1]*}   & {\bf 1*} & {\bf C-I}  & {\bf C-L} \\
+%\hline
+ B                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{4}  & \cca{4}     & \cca{4}   \\
+%\hline
+ M                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{0}  & \cca{7}     & \cca{5}   \\
+ S                               & \cca{0}    & \cca{1}    & \cca{4}          & \cca{4}  & \cca{0}     & \cca{0}   \\
+ C                               & \cca{0}    & \cca{4}    & \cca{0}          & \cca{0}  & \cca{0}     & \cca{0}   \\
+ O                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{7}  & \cca{1}     & \cca{0}   \\
+%\hline
+
+\end{tabular}
+}
+%\end{adjustwidth}
+\caption{Number of bugs fixed by each strategy:
 B(atching),  
@@
 S(kipping the loop),
-C(hange the data structure), and O(thers). The numbers in the 
-parentheses denote the number of problems that are fixed using specific
-fix strategies.}
-\label{tab:root}
-\end{table*}
+C(hange the data structure), and O(thers). 
+``C-I'': cross- iteration redundancy. 
+``C-L'': cross-loop redundancy. 
+}
+\label{tab:correlation}
+\end{table}
 
-\underline{Are the root-causes in our taxonomy common?}
-The answer is \textit{yes}.
+\paragraph{Coverage}
+Our taxonomy does cover all inefficient loops under study. 
 Resultless loops are about as common as redundant loops
@@
 
-\underline{How are real-world performance bugs fixed?}
-Overall, the fix strategies are well aligned with root-cause patterns.
+\paragraph{Actionability}
+As demonstrated in Table \ref{tab:correlation}, 
+the root-cause categories in our taxonomy are highly correlated with
+fix strategies.
+This indicates that our taxonomy is actionable --- once the root cause
+is identified, developers roughly know how to fix the problem.
 For example, 
-all inefficient loops with resultless [0$|$1]* are
-fixed by skipping the loop under certain contexts,
-and almost all inefficient loops with redundant root causes are fixed either by 
-memoization or batching the computation. 
+almost all 0*1? resultness loops are fixed by data-structure changes;
+all [0$|$1]* resultless loops are
+fixed by conditionally skipping the loop;
+almost all redundant loops are fixed either by 
+memoization or batching. 
 In fact, as we will discuss later, simple analysis can tell whether 
-memoization or batching should be used to fix a problem.
-The only problem is that there are no silver bullets for 1* loops.
+memoization or batching should be used to fix a redundant loop.
+The only problem is that there are no silver bullets for fixing 1* loops.
 %all inefficient loops with xx root cause are fixed by xxx.
@@
 
-\paragraph{Implications}
-As we can see, resultless loops and redundant loops are both common reasons
-that cause user-perceived performance problems in practice. The root-cause
-categories discussed above also match with developers' fix strategy well ---
-with a little bit amount of extra analysis, one can pretty much predict the fix strategy based on the root-cause pattern.
-Consequently, tools that cover these root causes will have high
-chances to satisfy the coverage and accuracy requirements of performance 
-diagnosis.
+\paragraph{Generality}
+The root-cause categories in our taxonomy are designed to be 
+generic. Table \ref{tab:root} also shows that these categories 
+each appears in multiple
+application in our study. The only exception is $0^*$-resultless, which
+never appears.
 
+In summary, the study above informally demonstrates that our taxonomy
+is suitable to guide our design of \Tool.
+%chances to satisfy the coverage and accuracy requirements of performance 
+%diagnosis.
+%
 %TODO even for the other, there are things we could do ...
@@
 Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
-on-line developer/user discussion to judge whether a bug report is about
+on-line discussion to judge whether a bug report is about
 performance problems and whether 
@@
 
+\comment{
 We believe that the bugs in our study provide a representative sample of the 
@@
 framework presented below will go beyond these sampled performance bugs. 
+}

### 2015-11-17 figures/GCC46401.c

@@ -1,31 +1,9 @@
-// Bad input contains a long expression:
-// QStringList function_list=QStringList() 
-// <<"abasep" <<"abs" <<"absint" ... 
-
-// c-common.c
-static bool
-candidate_equal_p (const_tree x, const_tree y)
-{
-  return (x == y) || (x && y && 
-                   operand_equal_p (x, y, 0));
-}
-
-// Comments from developers: 
-// "No point tracking CALL_EXPRs that aren't 
-// ECF_CONST (because then operand_equal_p 
-// fails anyway) nor STRING_CSTs (which can't be 
-// written into)"
-static void
-merge_tlist(...)
-{
-  ...
-  for (tmp2 = *to; tmp2; tmp2 = tmp2->next)
-    if (candidate_equal_p (tmp2->expr, add->expr))
++ if(warning_candidate_p(to)) {
+   for (tmp = *to; tmp; tmp = tmp->next)
+    if (candidate_equal_p (tmp->expr, add->expr)
+         && !tmp->writer)
     { 
-      found = 1;
-      if (!tmp2->writer)
-        tmp2->writer = add->writer;
+      ...
+      tmp->writer = add->writer;
     }
-  ...
-}
-
++ }

### 2015-11-17 figures/Mozilla477564.js

@@ -1,13 +1,9 @@
-1  //nsSessionStore.js
-2  generate: function sss_xph_generate(aNode)
-3  {
-4    ...
-5    for (let n = aNode; (n = n.previousSibling); )
-6      if (n.localName == aNode.localName 
-7          && n.namespaceURI == aNode.namespaceURI 
-8          && (!nName || n.name == nName))
-9        count++;
-10   //count will be used to generate a ID 
-11   //for the aNode
-12   ...
-13 }
+void sss_xph_generate(node_t* aNode)
+{
+   ...
+   for (n = aNode; n ; n = aNode->prev)
+     if (n->localName == aNode->localName 
+         && n->namespaceURI == aNode->namespaceURI) 
+         count++;
+     ...
+}//this function is called for every node aNode

### 2015-11-17 section/2_workless.tex
revise through section 3.1

@@
 \label{sec:design}
-\Tool is composed of a series of analysis routines that
-identify whether a given loop belongs to any root cause type discussed in
+\Tool consists of a series of analysis that
+judges whether a given loop belongs to any root cause type discussed in
 Section \ref{sec:study_tax}.
@@
 \item Static-dynamic hybrid analysis. As we will see, static analysis alone
-will not be able to provide all the needed information. However, 
+will not be able to provide all the needed information to judge whether
+a loop is problematic. However, 
 dynamic analysis alone will incur too much overhead.
@@
 to figure out which are the side-effect instructions in a loop and hence
-decide whether a loop belongs to 0*, 0*1?, [0$|$1]*, or 1*. Second, for
-0*1? and [0$|$1]* loops, we use
+decide whether a loop belongs to 0*, 0*1?, [0$|$1]*, or 1*. Second, to
+accurately determine 0*1? and [0$|$1]* loops, we use
 dynamic analysis to figure out what portion of loop iterations are
-resultless at run time, which will help decide whether the loop is indeed
-inefficient.
+resultless at run time.
+%, which will help decide whether the loop is indeed
+%inefficient.
 
@@
 
-Finally, since the 1* pattern contains the least amount of information
+Note that since the 1* pattern contains the least amount of information
 about computation \textit{inefficiency}, \Tool will not report a loop's
@@
 
+\comment{
 We could speed up the above counting using sampling. However, since the 
@@
 not use sampling for this part of run-time analysis.
+}
 
@@
 
+\comment{
 \subsubsection{Limitations}
 \label{sec:l_workless}
-The technique designed in this section has the following limitations.
-First, when callee may have side effect, we will consider it will have side effect in the caller side, 
+When callee may have side effect, we will consider it will have side effect in the caller side, 
 and do not consider the real execution inside callee. This could bring false negatives, 
@@
 When the monitored loop is executed in multi-thread, like loop marked with omp pragma, we need to synchronize updates to global variables. 
+}

### 2015-11-17 section/3_redundancy.tex
revise through section 3.1

@@
 For example, the read address of \texttt{aNode.localName} and \texttt{aNode.namespaceURI}
-in Figure~\ref{fig:Mozilla347306} is loop-invariant, and there are no write conducted 
+in Figure~\ref{fig:Mozilla477564} is loop-invariant, and there are no write conducted 
 on the same address. We do not need to record these two memory read. 

### 2015-11-18 figures/Apache34464.c
remove line number

@@ -1,42 +1,42 @@
-0   //java.lang.String
-1   static int 
-2   indexOf(char[] source, int sourceCount,
-3           char[] target, int targetCount ) 
-4   {
-5     ...
-6     char first  = target[targetOffset];
-7     int max = sourceCount - targetCount;
-8
-9     for (int i = 0; i <= max; i++) {
-10      // Look for first character.
-11      if (source[i] != first) {
-12        while (++i <= max && source[i] != first);
-13      }
-14
-15      // Found first character
-16      //now look at the rest of v2
-17      if (i <= max) {
-18        int j = i + 1;
-19        int end = j + targetCount - 1;
-20        for (int k = 1; j < end && source[j] == 
-21                 target[k]; j++, k++);
-22
-23        if (j == end) {
-24          /* Found whole string. */
-25          return i ;
-26        }
-27      }
-28    }
-29    return -1;
-30  }
-31
-32  //TelnetTask.java
-33  public void waitForString(...)
-34  {
-35 +  int windowIndex = -s.length();
-36 -  while (sb.toString().indexOf(s) == -1) {
-37 +  while (windowIndex++ < 0 || 
-38 +   sb.substring(windowIndex).indexOf(s) == -1){
-39      sb.append((char) is.read());
-40    }
-41  }
+ //java.lang.String
+ static int 
+ indexOf(char[] source, int sourceCount,
+         char[] target, int targetCount ) 
+ {
+   ...
+   char first  = target[targetOffset];
+   int max = sourceCount - targetCount;
+
+   for (int i = 0; i <= max; i++) {
+     // Look for first character.
+     if (source[i] != first) {
+       while (++i <= max && source[i] != first);
+     }
+
+     // Found first character
+     //now look at the rest of v2
+     if (i <= max) {
+       int j = i + 1;
+       int end = j + targetCount - 1;
+       for (int k = 1; j < end && source[j] == 
+                target[k]; j++, k++);
+
+       if (j == end) {
+         /* Found whole string. */
+         return i ;
+       }
+     }
+   }
+   return -1;
+ }
+
+ //TelnetTask.java
+ public void waitForString(...)
+ {
++  int windowIndex = -s.length();
+-  while (sb.toString().indexOf(s) == -1) {
++  while (windowIndex++ < 0 || 
++   sb.substring(windowIndex).indexOf(s) == -1){
+     sb.append((char) is.read());
+   }
+ }

### 2015-11-18 figures/Mozilla477564.js
change mozilla 477564

@@ -1,4 +1,4 @@
-void sss_xph_generate(node_t* aNode)
+char * sss_xph_generate(node_t* aNode)
 {
    ...
    for (n = aNode; n ; n = aNode->prev)

### 2015-11-18 section/1_under.tex
update table 2 and figure 4
revise the heat-map, root-cause table

@@
 fixed by data-structure changes.
-As an example, Mozilla JavaScript engine used to store the source-code 
-line numbers of all byte-code instructions in a linked list \texttt{script}. 
-Later on, many users complained that Mozilla browser freezed when opening
-some popular websites. It turned out that those websites contained large
-JavaScript files that filled the linked list \texttt{script} with
-tens of thousands of nodes. Linear search on \texttt{script} then caused the
-to freeze. To fix this problem, 
+As an example, Mozilla JavaScript engine used to use a linked list 
+\texttt{script}
+to store debugging information
+for every bytecode instruction in a JavaScript file. 
+Later on, people complained that Mozilla browsers were very slow in handling
+large JavaScript files.
+It turned out that those large
+JavaScript files filled the linked list \texttt{script} with
+tens of thousands of nodes. Repeated search through the
+long \texttt{script} list then led to poor performance.
+To fix this problem, 
 developers simply replace linked list with hash table
@@
 
+\comment{
 \begin{table*}[tb!]
@@
 \hline
+\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
+&7&1&2&1&1&12\\
+\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
+&3&0&2&2&2&9\\
 \multicolumn{1}{|l}{ {\bf 0*} Resultness}
@@
 %&1&0&3&1&3&8&\\
-\hline
-\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
-&7&1&2&1&1&12\\
-\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
-&3&0&2&2&2&9\\
   %MySQL15811 is moved from 1* to here; consider it as fixed by M
@@
 \end{table*}
+}
 
 \def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
+
+\begin{table*}[tb!]
+%\begin{adjustwidth}{-.5in}{-.5in}
+\small
+\centering
+{
+\begin{tabular}{lccccccccccccc}
+\hline
+                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
+\cmidrule{2-6}
+\cmidrule{8-12}
+                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
+\hline
+\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
+&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
+\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
+&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
+\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
+&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
+\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
+&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
+\multicolumn{1}{l}{ {\bf 0*} Resultless}
+&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
+\multicolumn{1}{l}{{\bf 1*} Resultless}
+&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
+  %MySQL15811 is moved from 1* to here; consider it as fixed by M
+\hline
+\end{tabular}
+}
+%\end{adjustwidth}
+\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
+(S: conditionally skip the loop; C: change the data structure)
+}
+\label{tab:root}
+\end{table*}
+
+\comment{
+\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
 %For ranges 0-10, multiply by 10 by adding 0 after #1
-
 \begin{table}[tb!]
@@
 \end{table}
+}
 
@@
 For example, 
-almost all 0*1? resultness loops are fixed by data-structure changes;
+almost all 0*1? resultless loops are fixed by data-structure changes;
 all [0$|$1]* resultless loops are

### 2015-11-18 section/1_under.tex
near the end of section 3 revision

@@
 
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 
+\input section/tab_root
+
+\input section/tab_appbug
+
 \subsection{Taxonomy Assessment}
@@
 \subsubsection{Methodology}
-\begin{table}[h!]
-\small{
-\centering
-\begin{tabular}{@{\hspace{3pt}}l@{\hspace{3pt}}|@{\hspace{3pt}}c@{\hspace{3pt}}}
-\hline
-Application Suite Description (language) & \# Bugs \\
-\hline                            
-{\bf Apache Suite} 	 & 11\\
-%\cline{1-1}
-{HTTPD:	Web Server (C)	}& \\
-{TomCat:  Web Application Server (Java)}& \\
-{Ant:	Build management utility (Java)}& \\
-%\hline
-%JMeter	& Load test utility (Java) & \\
-\hline                            
-{\bf Chromium Suite} Google Chrome browser (C/C++) & 4\\
-\hline
-%\multicolumn{2}{|l|}
-{\bf GCC Suite}  GCC \& G++ Compiler (C/C++)     & 8\\
-\hline
-{\bf Mozilla Suite}  & 12\\
-%\cline{1-1}
-{Firefox: Web Browser (C++, JavaScript)}& 	\\
-{Thunderbird: Email Client (C++, JavaScript)}& \\
-\hline
-{\bf MySQL Suite}     & 10	\\
-%\cline{1-1}
-{Server: Database Server (C/C++)}&  	\\
-%\cline{1}
-{Connector: DB Client Libraries (C/C++/Java/.Net)} &  	\\
-\hline
-{\bf Total}	   & 45 \\
-\hline
-\end{tabular}
-}
-\caption{Applications and bugs used in the study}
-\label{tab:app_bug}
-\end{table}
 
@@
 
-\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
-
-\begin{table*}[tb!]
-%\begin{adjustwidth}{-.5in}{-.5in}
-\small
-\centering
-{
-\begin{tabular}{lccccccccccccc}
-\hline
-                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
-\cmidrule{2-6}
-\cmidrule{8-12}
-                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
-\hline
-\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
-&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
-\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
-&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
-\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
-&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
-\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
-&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
-\multicolumn{1}{l}{ {\bf 0*} Resultless}
-&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
-\multicolumn{1}{l}{{\bf 1*} Resultless}
-&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
-  %MySQL15811 is moved from 1* to here; consider it as fixed by M
-\hline
-\end{tabular}
-}
-%\end{adjustwidth}
-\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
-(S: conditionally skip the loop; C: change the data structure)
-}
-\label{tab:root}
-\end{table*}
-
 \comment{
@@
 \paragraph{Coverage}
-Our taxonomy does cover all inefficient loops under study. 
+As shown in Table \ref{tab:root}, 
+our taxonomy does cover all inefficient loops under study. 
 Resultless loops are about as common as redundant loops
@@
 \paragraph{Actionability}
-As demonstrated in Table \ref{tab:correlation}, 
-the root-cause categories in our taxonomy are highly correlated with
+As demonstrated in Table \ref{tab:root}, 
+the root-cause categories in our taxonomy are well correlated with
 fix strategies.

### 2015-11-18 section/3_redundancy.tex
update table 2 and figure 4
near the end of section 3 revision

@@
 \subsubsection{Design overview}
-To check whether there is redundant computation across different iterations
-of one loop instance or across different instances of one static loop, we need
-to address several challenges.
+At high level, we will compare the computation of different iterations
+from one loop instance and that of different loop instances from 
+one static loop, 
+and judge whether there exists redundancy.
+Specifically, our design needs to answer several questions.
 
-\begin{figure}
-  \centering
-  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-     morekeywords={+},keepspaces=true}
-  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
-  \caption{A cross-loop redundant bug in Apache}
-  \label{fig:Apache34464}
-\end{figure}
+\emph{What to compare?}
+Given two loop iterations (or loop instances) $c_1$ and $c_2$, since they 
+originate from the same source code $C$, 
+a naive approach is to record the value read by
+every memory read instruction in $c_1$ and $c_2$. 
+We will know whether $c_1$ and $c_2$ are redundant with each other by comparing
+these values.
+Of course, we could do better by checking fewer instructions, as
+some of these values are determined by values read earlier in $c_1$ and/or 
+$c_2$. Informally speaking, we only need to compare \textit{input}
+values of $c_1$ and $c_2$ to decide whether they are redundant with each other. 
+We will present our formal definition of \textit{input} values, and
+how we identify and record them in
+Section \ref{sec:dependence}.
 
-\emph{How to judge redundancy between two iterations/loop-instances?}
-Given two iterations (or loop-instances) $i_1$ and $i_2$, since they have 
-the same source code, 
-a naive, yet expensive, solution is to record and compare the return value of
-every memory read conducted by $i_1$ and $i_2$. Two better alternative
-solutions are to record and compare only the values written by the
-side-effect instructions, such as 
-line 9 in Figure~\ref{fig:Mozilla477564},
-or read by 
-the source instructions\footnote{We define source instructions in a code
-region $r$ as a set of memory-read instructions that side-effect
-instructions in $r$ depend on and do not depend on any other instructions
-inside $r$.}, 
-such as source[i] at line 12 of Figure~\ref{fig:Apache34464}.
+%TODO
+%Among the the above two potential solutions, our design chooses the second one,
+%because it is
+%more informative for performance diagnosis 
+%to track the cause rather than the effect.
 
-Among the the above two potential solutions, our design chooses the second one,
-because it is
-more informative for performance diagnosis 
-to track the cause rather than the effect.
-
-\emph{How to handle partial redundancy?}
-In practice, redundant loops may be doing largely the same, but not exactly
-the same, computation across iterations or loop instances. 
+\emph{How to compare?}
+Naively, we can judge two iterations or two
+loop instances to be redundant with each other only when they read exactly
+the same data and conduct exactly the same computation. However,
+in practice, redundant loops may be doing largely, but not completely,
+the same computation across iterations or loop instances. 
 %It is also possible
@@
 \emph{How to lower the overhead of record-and-compare?}
-Even if we only record and compare the values returned by source instructions
-the run-time overhead and the log size
-could still be large. We will use static analysis and run-time sampling
-to lower this time and spatial
-overhead 
-(Section \ref{sec:inst} and \ref{sec:perf}).
+We will use both static optimization and dynamic sampling
+to reduce the amount of data that we need to record and compare, lowering
+time and spatial overhead. Details will be presented in 
+Section \ref{sec:inst} and \ref{sec:perf}.
 %TODO static analysis alone is not sufficient, because some redundant is
@@
 
-\emph{How to provide the most suitable fix-strategy suggestion?}
-Finally, as discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
+\emph{How to suggest the most suitable fix strategy?}
+As discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
 memoization and batching are both common fix strategies for redundant loops.
-To pick the right fix strategies,
+To pick the right strategy,
 extra analysis is conducted by \Tool and presented in 
@@
 
-\subsubsection{Identifying source instructions}
+\subsubsection{Identifying and recording \textit{inputs}}
 \label{sec:dependence}
@@
 Informally, we use static analysis to identify a set of 
-memory-read instructions that the loop computation depends on. We refer
-to these instructions as \textit{source} instructions. The values returned
+memory-read instructions that the computation of code $C$
+depends on. We refer
+to these instructions as \textit{input} instructions for $C$. 
+The values returned
 from them at run-time will be tracked and compared to identify
-redundant computation.
+redundant computation among different instances of $C$.
 
-Specifically, we first identify side-effect instructions in the loop, as 
-discussed in Section \ref{sec:s_workless}; we then conduct static slicing 
+Specifically, \Tool first identifies side-effect instructions in $C$.
+%, as 
+%discussed in Section \ref{sec:s_workless}. 
+It then conducts 
+backward static slicing 
 from these instructions, considering both control and data
-dependency, to identify source instructions.
+dependency. For every memory read instruction $r$ 
+(\texttt{read(v)}) that static slicing encounters, \Tool checks whether $r$
+satisfies either one of the following two conditions. 
+If $r$ does, it is marked as
+an \textit{input} instruction; otherwise, \Tool continues growing the
+slice beyond $r$.
+The two conditions are:
+(1) the value of $v$ is defined outside $C$;
+(2) $v$ is a heap or global variable.
+The rationale for the first condition is that slicing outside $C$ is
+unnecessary for redundancy judgement among instances of $C$.
+The rationale for the second condition is that tracking data-dependency
+through heap or global variables is complicated in multi-threaded C/C++
+programs.
 
-%TODO How do you handle constant values? I didn't get it.
-Our slicing ends when it reaches either a local-variable read conducted
-outside the loop or a heap/global-variable read anywhere in the program.
-For the latter case, our slicing stops because tracking data-dependency
-through heap/global variables is complicated in multi-threaded C/C++
-programs. For the former case, 
-not including local-variable reads inside the loop can help reduce the
-amount of data that needs to be recorded. 
-When there are function calls inside the loop,  
-we conduct slicing for return values of callees and side-effect instructions
+The analysis for cross-iteration and cross-loop redundancy analysis is similar
+--- simply replacing $C$ in the above algorithm with one iteration or
+the whole loop body.
+
+%TODO sound or complete
+
+Our analysis considers function calls inside $C$ --- slicing is conducted
+for return values of callees and side-effect instructions
 inside callees. 
@@
 %it is easy to know whether read or write conducted on them are applied to the same address. 
-We omit encountered constant values through slicing, because constant values will not influence whether a loop or an iteration is redundant.
+We omit encountered constant values through slicing, because constant values will not affect the redundancy judgement.
+
+Note that another possible approach is to simply record and compare what
+are written by the side-effect instructions in $C$.
+We did not choose this approach because we believe it is not sufficient
+to judge redundancy. Consider a loop that goes through a character array 
+to check if there exists any special characters in the array
+and returns a boolean
+variable denoting its checking result. Running this loop on 
+different arrays is not redundant, but could easily be judged as redundant
+when only comparing the loop side-effect (e.g., always returning 
+\texttt{FALSE}).
 
@@
 
-The analysis for cross-iteration and cross-loop redundancy analysis is pretty
-much the same. The only difference is that, if a memory read instruction 
-$i$ in a loop depends on the value returned by instruction $j$ in an earlier
-iteration, we stop tracing the dependence at $i$ and consider $i$ as a
-source instruction for cross-iteration redundancy analysis, while we continue
-the slicing for cross-loop redundancy analysis. 
-For example, 
-the instruction defining the value of \texttt{i} is the only side-effect instruction 
-for the loop at line 12 of Figure~\ref{fig:Apache34464}. 
-The source instructions calculated by cross-loop dependence analysis include 
-memory read \texttt{source[i]} inside the loop, 
-and three values defined outside the loop, 
-which represent the initial value of \texttt{i}, the value of \texttt{max} and \texttt{first} respectively. 
-In contrast, 
-the source instructions calculated by cross-iteration dependence analysis 
-include value \texttt{i} defined in previous iteration, 
-memory read \texttt{source[i]}, 
-and two values defined outside the loop (\texttt{max} and \texttt{first}).
+%TODO why not directly judge side-effect values
+
+\paragraph{Example}
+Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache. 
+It contains a cross-loop redundant bug --- 
+the \texttt{for} loop starting on line 7 could be executed for many times,
+applied to many \texttt{source} strings slightly different from each other
+with a lot of
+redundant computation.
+Below, we use it to demonstrate how we identify \texttt{input}s.
+
+\begin{figure}
+  \centering
+  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+     morekeywords={+},keepspaces=true,numbers=left}
+  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
+  \caption{A cross-loop redundant bug in Apache}
+  \label{fig:Apache34464}
+\end{figure}
+
+Take the simple loop at line 10 of Figure~\ref{fig:Apache34464} as an example.
+Its only side-effect is to update \texttt{i}.
+For cross-loop redundancy analysis, we will consider the whole loop and 
+identify these as \textit{input}s:
+every \texttt{source[i]} read inside the loop;
+the initial value of \texttt{i} defined outside the loop;
+\texttt{max} defined outside the loop; 
+and \texttt{first} defined outside the loop.
+For cross-iteration redundancy analysis, the \textit{input}s for each
+iteration is slightly different:
+value \texttt{i} defined in previous iteration, 
+the \texttt{source[i]} read in that iteration, 
+and two values defined outside the loop, \texttt{max} and \texttt{first}.
+
+Take the big loop at line 7 of Figure~\ref{fig:Apache34464} as an example.
+The \textit{input}s for the whole loop include:
+three values defined outside the loop
+(\texttt{max}, \texttt{first}, \texttt{targetLen}) and every
+\texttt{source[.]} and \texttt{target[.]} read inside the loop.
+This set is already smaller than the set of all data read by the loop.
+We will further shrink this set, removing invariant and others, 
+in Section \ref{sec:perf}.
 
@@
 
-After identifying source instructions, we instrument them to record
-what values they read from memory
-at run time.
+After identifying \textit{inputs} using static analysis, 
+\Tool then instruments the program to record \textit{inputs} values at run time.
 %Specifically, we will assign
@@
 %will be recorded at run time with the execution of a source instruction.
-Our trace also includes some delimiters and meta information that allows
+The run-time trace will also include delimiters and meta information that allows
 trace analysis to differentiate values recorded from different instructions, 
@@
 
-After collecting values returned by source instructions from every iteration
-of one or multiple loop instances, we need to process the trace and decide
+Once the trace under problematic workload is collected either during
+off-line debugging or during production runs, 
+\Tool will process the trace and decide
 whether the loops under study contain cross-iteration redundancy or 
@@
 Our answer to these two questions stick to one principle: there should be
-sufficient amount of redundant computation to make a loop likely root-cause
+sufficient amount of redundant computation to make a loop likely culprit
 for a user-perceived performance problem and to make itself worthwhile to
-get optimized by the developers. Consequently,
+get optimized by developers. Consequently,
 for the first question, \Tool takes a strict 
@@
 
+\comment{
 \begin{figure}
@@
 %or I did not find the correct codes. 
+}
 
-For cross-loop redundancy, we need to answer similar questions,
-especially how to judge whether two loop instances are doing redundant work ---
+For cross-loop redundancy, we need to answer similar questions.
+How to judge whether two loop instances are doing redundant work ---
 should they contain exactly the same number of iterations and doing exactly
@@
 
-Our answers here are different from our answers above for cross-iteration
-redundancy analysis.
+Following the same principle discussed above, we have slightly different
+answers here.
 We do not require two loop instances to
@@
 
-In fact, in practice, we almost have never seen cases where different loop 
+In practice, we rarely see cases where different loop 
 instances are doing exactly the same computation.
@@
 The implementation of checking cross-iteration redundancy is straightforward.
+\comment{
 We will record a sequence of $<InstID, Value>$ pair for every monitored
@@
 same. To make sure a loop contains sufficient redundant computation, 
-we calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
+}
+We calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
 the total number of iterations in the loop by the number of distinct iterations.
@@
 are redundant or not.
-The challenge is that $l_1$ and $l_2$ may have executed different number of
-iterations; in different iteration, a different set of source instructions
-may have executed. Therefore, we cannot simply merge values from different
-source instructions and iterations together and compare two big data sequence.
+The challenge is that $l_1$ and $l_2$ may have executed different numbers of
+iterations; in different iterations, different sets of source instructions
+may have executed. Therefore, we cannot simply chain values from different
+input instructions and iterations together and compare two data sequences.
 Instead, we decide to check the redundancy for each source instruction across
@@
 \Scale[0.8]{
-	Redundancy(I) =  \frac{dist(SeqA,SeqB) - (len(SeqA) - len(SeqB))}{len(SeqB)}
+	Redundancy(I) =  \frac{dist(SeqA,SeqB) - (len(SeqA) - len(SeqB))}{len(SeqA)}
 }
@@
 
-\subsubsection{Dynamic performance optimization: sampling}
+\subsubsection{Dynamic optimization (sampling)}
 \label{sec:inst}
@@
 
-Recording values returned by every source instructions would lead to 
-huge run-time time. To lower the overhead,
+Recording values returned by every source instruction would lead to 
+huge run-time overhead. To lower the overhead,
 we use random sampling to reduce the number of instructions that we
@@
 we will still be able to recognize redundant 
-computation as long as the sampling rate is not too sparse (we will evaluate
-this in Section \ref{sec:experiment}). 
+computation as long as the sampling rate is not too sparse, which
+we will evaluate
+in Section \ref{sec:experiment}. 
 Our sampling scheme requires almost no changes to our redundancy 
@@
 \paragraph{Cross-loop redundancy analysis} 
-At high level, we randomly decide at the beginning
+We randomly decide at the beginning
 of every loop instance whether to track values for this instance. 
@@
 instances for redundancy, once we decide to sample one loop instance, we will
-make sure to sample the immediately next loop instance too.
+make sure to sample the immediate next loop instance too.
 The implementation is straightforward by cloning the whole loop and making
@@
 
-\subsubsection{Static analysis for performance optimization}
+\subsubsection{Static optimization}
 \label{sec:perf}
@@
 
-For cross-iteration redundancy, batching is often used towards
-batching I/O related operations, based on our empirical study. 
+For cross-iteration redundancy, batching is often used for
+I/O related operations.
 Therefore, we treat I/O related redundancy separately.
@@
 buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
-we recommend memoization. Instead, if the side effect is updating 
-an sequence of memory locations, with the number of locations increasing
-with the workload, memoization is unlikely to help save much computation.
+we recommend memoization. Instead, if the side effect is to update
+a sequence of memory locations, with the number of locations increasing
+with the workload, memoization is unlikely to help save much computation and
+hence batching is suggested.
 

### 2015-11-18 section/tab_root.tex
near the end of section 3 revision

\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lccccccccccccc}
\hline
                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
\cmidrule{2-6}
\cmidrule{8-12}
                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
\hline
\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
\multicolumn{1}{l}{ {\bf 0*} Resultless}
&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
\multicolumn{1}{l}{{\bf 1*} Resultless}
&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
(S: conditionally skip the loop; C: change the data structure)
}
\label{tab:root}
\end{table*}

### 2015-11-18 figures/Mozilla477564.js

@@ -1,9 +1,9 @@
 char * sss_xph_generate(node_t* aNode)
 {
-   ...
+   int count=0;
    for (n = aNode; n ; n = aNode->prev)
      if (n->localName == aNode->localName 
          && n->namespaceURI == aNode->namespaceURI) 
          count++;
-     ...
-}//this function is called for every node aNode
+   ...
+}//called for every node in a list

### 2015-11-18 section/3_redundancy.tex
finish section 3 roughly

@@
 \paragraph{Example}
-Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache. 
-It contains a cross-loop redundant bug --- 
-the \texttt{for} loop starting on line 7 could be executed for many times,
-applied to many \texttt{source} strings slightly different from each other
-with a lot of
-redundant computation.
-Below, we use it to demonstrate how we identify \texttt{input}s.
+Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache,
+containing a cross-loop redundancy bug. 
+The \texttt{for} loop starting on line 7 
+searches a string \texttt{source} for a target sub-string 
+\texttt{target}. Since the outer loop, which starts on line 2, appends one 
+character to \texttt{source} in every iteration (line 30), 
+every execution of the \texttt{for} loop is working on a similar 
+\texttt{source} string from its previous execution, with a lot of redundancy. 
+%applied to many \texttt{source} strings slightly different from each other
+%with a lot of
+%redundant computation.
+%We use it to demonstrate how we identify \texttt{input}s below.
 
@@
 instances are doing exactly the same computation.
-For example, Figure~\ref{fig:Mozilla477564} demonstrates a cross-loop redundancy
-problem in Mozilla. Here, the
-latter instances contain more iterations than previous instances. 
-Figure~\ref{fig:Apache34464} shows an example in Apache, 
-The inner loop, which starts from line 9,  
-searches from the beginning of a string \texttt{sb} for a target sub-string 
-\texttt{s}. Since the outer loop, which starts on line 36, appends one 
-character to \texttt{sb} in every iteration, every inner loop instance is 
-doing computation that is similar, but not exactly the same, 
-from its previous instance.
+In cross-loop redundancy examples shown in 
+Figure~\ref{fig:Mozilla477564} and
+Figure~\ref{fig:Apache34464}, each loop instance is doing similar, but not
+exactly the same, work from its previous instance.
 
@@
 statically proved to
-not change throughout one loop instance (i.e., for cross-iteration
-redundancy analysis) or multiple loop instances (i.e., for cross-loop redundancy
-analysis). Since we implement \Tool at LLVM byte-code level, a major part of this
+not change throughout one loop instance
+or multiple loop instances. 
+Since we implement \Tool at LLVM byte-code level, the majority of this
 analysis is already done by LLVM, which lifts loop-invariant memory
-accesses out of loops. The only extra analysis we did is to 
-prune memory reads whose reading address is loop invariant, and there are no writes 
-inside the loop which are possibly conducted on the same address. 
-For example, the read address of \texttt{aNode.localName} and \texttt{aNode.namespaceURI}
-in Figure~\ref{fig:Mozilla477564} is loop-invariant, and there are no write conducted 
-on the same address. We do not need to record these two memory read. 
+accesses out of loops. 
+For example, the read of \texttt{max} on line 12 of 
+Figure \ref{fig:Apache34464} is an \textit{input} instruction of the 
+\texttt{while} loop on the same line. LLVM identifies it as a loop invariant
+and lifts the read of \texttt{max}
+out of the loop. Consequently, \Tool only records
+its value once during each loop, not each iteration.
+However, LLVM does not apply its loop-invariant analysis to heap and global
+variables, so \Tool conducts some extra analysis --- it identifies those
+memory reads \texttt{read(v)}, where the address of \texttt{v} 
+is a loop invariant and no instructions 
+inside the loop can possibly write to that address. 
+For example, \Tool can identify that the values of
+\texttt{aNode->localName} and \texttt{aNode->namespaceURI} do not change
+throughout one loop instance
+in Figure~\ref{fig:Mozilla477564}. This analysis is sound but not complete.
+\Tool may miss some loop invariants.
+
+Second, we leverage the scalar evolution analysis in LLVM to remove the 
+monitoring to some loop-induction related variables.
+The scalar evolution analysis can tell which variables are
+loop-induction variables (e.g., \texttt{i} on line 10
+of Figure~\ref{fig:Apache34464}) and what are their strides. 
+We then use this information in two ways. 
+One is for cross-iteration redundancy checking.
+If a loop iteration's \texttt{input} set contains a loop-induction
+variable, we know different iterations' inputs would be different and 
+hence conclude that there is no cross-iteration redundancy without any
+run-time analysis. 
+The other is for cross-loop redundancy checking.
+When the address of a memory read is a loop induction variable, such as
+\texttt{source[i]} on line 10 of Figure~\ref{fig:Apache34464},
+we only record the address range at run time (i.e., the start and the
+end), instead of every value returned by the memory read.
+Of course, this optimization could lead to false positives, reporting
+non-redundant loop computation as redundant.
+This may happen when the corresponding
+memory locations are modified across different loop instances.
+In that case, although different loop instances work on variables read from
+similar memory locations, the values they read are different.
+
+\subsubsection{Fix strategy recommendation}
+\label{sec:redundant_fix}
+As discussed in Section \ref{sec:tax_study}, extra analysis is needed to
+decide whether batching or memoization should be suggested to fix a 
+loop that conducts redundant computation.
+
+For cross-iteration redundancy, batching is often used for
+I/O operations.
+Therefore, we treat I/O related redundancy separately.
+When the only side effect of a loop is I/O operations
+and the same statement(s) is executed in every loop iteration, we report this
+as I/O related redundancy problem and suggest batching as a potential fix
+strategy.
+
+For cross-loop redundancy, whether to use memoization or batching often
+depends on which strategy is cheaper. \Tool uses a simple
+heuristic. If 
+the side effect of each loop instance is to update 
+a constant number of memory locations, like the 
+buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
+we recommend memoization. Instead, if the side effect is to update
+a sequence of memory locations, with the number of locations increasing
+with the workload, memoization is unlikely to save much and
+hence batching is suggested.
+
+%TODO what does batching mean for cross-loop redundancy???
+
+\comment{
+%%if side effect of the loop is to define several scalar value used outside the loop, we recommend memoization.
+%%if side effect is to write to distinct memory address or conduct system call, 
+%%we recommend batch
+
 %It is easy to lift read from local variable outside the loop. 
@@
 %write to the same place, we will not record the memory read.
-
-%TODO: Linhai, I don't understand your original writing. Pls rephrase, and provide
-%an toy example.
-%For each monitored memory read, we use loop-invariant analysis to identify 
-%whether the read address is loop-invariant. 
-%If the address is invariant, and there are no memory writes whose addresses 
-%may/must alias to the read address, we will not instrument the memory read.
 
@@
 
-Second, we identify and avoid monitoring some memory reads whose return values 
-can be statically proved to be different throughout one loop instance in 
-cross-iteration redundancy analysis.
-Specifically, for read on loop induction variable, such as i for loop at line 12 of Figure~\ref{fig:Apache34464}, 
-%Specifically, reading of loop induction 
-%variables, such as XXX, are always identified as source instructions in % variable i for loop at line 12
-%cross-iteration redundancy analysis; 
-we also know for sure that their return
-values are different in different iterations. 
-If source instructions include read on loop induction variables, we know that 
-there could not be cross-iteration redundancy. 
-We use scalar evolution analysis
-provided by LLVM to identify induction variables and avoid tracking their
-values.
 %induction variables are not always identified as source instructions.
@@
 
-Third, sometimes we only record the memory-address range of a sequence of memory
-read, instead of the value returned by every read, in cross-loop redundancy
-analysis. 
-The loop at line 12 in Figure~\ref{fig:Apache34464} shows an example.
-The content of array \texttt{source} is never modified
-throughout the outer-loop, which starts 
-at line 12 in the Figure~\ref{fig:Apache34464}.
-%We do not have the static analysis to prove the content of array does not change.
-%for source[i] for the loop at line 12, we only need to record source, initial value of i and final value of i. 
-%TODO
-%Do you really do analysis to prove that the source array is not changed?
-%ANSWER
-%Shan, I do not have invariant analysis to prove the the source array is not changed.
-%I remove that part of writing in the last version I sent to you. 
-%It is very difficult to implement the invariant analysis.
-%I plan to discuss this in limitation part of this section, and say that this could bring false positives.
-%There are reasons why I feel it is too difficult to implement the invariant analysis:
-%1. it is difficult to find the range (the outer loop) to apply the analysis.
-%assume we have loopA, loopB and loopC. loopA contains loopB, and loopB contains loopC. 
-%we are analyzing loopC. It could be possible that loopB only execute 1 or 2 iterations, and loopA is the real outer loop
-%2. It is very difficult to prove that there is no other loop inside the outer loop which does not write to the same array.
-%There could be cases like:
-% for(i = 0; i < 10; i++)
-%   func(&(A[i]));
-% func will write to its parameter.
-Therefore, to check whether different inner loop instances read similar
-sequence of array data, we only need to record the starting and 
-ending array index touched by each inner loop, significantly reduce the 
-monitoring overhead. To accomplish this optimization, we again leverage
-the scalar evolution analysis provided by LLVM. The scalar evolution analysis
-tells us whether the address of a memory read instruction
-is a loop induction variable. For example, the address for memory read \texttt{source[i]} is added by one in each loop iteration,
-so it is a loop induction variable. 
-From the scalar evolution analysis, we know that the starting address is \texttt{source} plus the initial value of \texttt{i}, and the ending address
-is source plus the ending value of \texttt{i}.  
 %TODO Linhai, I don't understand your original text. The address is 
@@
 
-\subsubsection{Fix strategy recommendation}
-\label{sec:redundant_fix}
-As discussed in Section \ref{sec:tax_study}, extra analysis is needed to
-decide whether batching or memoization should be suggested to fix a 
-loop that conducts redundant computation.
-
-For cross-iteration redundancy, batching is often used for
-I/O related operations.
-Therefore, we treat I/O related redundancy separately.
-Specifically, when the only side effect of a loop is I/O operations
-and the same statement(s) is executed in every loop iteration, we report this
-as I/O related redundancy problem and suggest batching as a potential fix
-strategy.
-
-For cross-loop redundancy, whether to use memoization or batching often
-depends on which strategy is cheaper to use. \Tool uses a simple
-heuristic. If 
-the side effect of each loop instance is to update 
-a constant number of memory locations, like the 
-buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
-we recommend memoization. Instead, if the side effect is to update
-a sequence of memory locations, with the number of locations increasing
-with the workload, memoization is unlikely to help save much computation and
-hence batching is suggested.
-
-%we xxx
-%TODO
-
-%%if side effect of the loop is to define several scalar value used outside the loop, we recommend memoization.
-%%if side effect is to write to distinct memory address or conduct system call, 
-%%we recommend batch
+}

### 2015-11-19 section/0_intro.tex
addressing issues in first 3 sections based on yesterday's discussion

@@
 
-Figure~\ref{fig:GCC27733} shows a real-world performance bug in GCC. 
+Figure~\ref{fig:GCC27733} shows a performance bug in GCC. 
 Function \texttt{mult\_alg} is used to compute the best algorithm for 
@@
 severely hurting performance.
-In reality, developers easily figured out that function
+In reality, developers easily figured out that
 \texttt{mult\_alg} is most correlated with the execution slowness, but
-spent several weeks to finally figure out \texttt{mult\_alg} is in fact
+spent several weeks to finally figure out \texttt{mult\_alg}, 
+containing 400 lines
+of code, is
 inefficient.

### 2015-11-19 section/2_workless.tex
addressing issues in first 3 sections based on yesterday's discussion

@@
 
-\item Static-dynamic hybrid analysis. As we will see, static analysis alone
+\item Static-dynamic hybrid analysis. Static analysis alone
 will not be able to provide all the needed information to judge whether
-a loop is problematic. However, 
+a loop is inefficient. However, 
 dynamic analysis alone will incur too much overhead.
@@
 variables defined outside the loop. 
-\Tool analyzes all functions that are called
+\Tool analyzes all functions called
 by a loop directly or indirectly --- a function $F$ that updates variables
@@
 caller a side-effect instruction.
-We consider all library functions or function calls through function pointers 
-as functions that have side effects, 
+We consider all calls to library functions or through function pointers 
+as having side effects, 
 unless the library functions are specially marked by us in a white list.
@@
 \Tool then categorizes loops into four types.
-Loop 0* contains no side-effect instructions. 
-Loop 1* contains at least one side-effect instruction along every path that
-starts from the loop header and ends at the loop header.
-For the remaining cases, 
-when the basic block with side-effect instructions
-is part of the natural loop, the case
-belongs to [0$|$1]*; instead, if the side-effect basic block is post-dominated
-by one of the loop-exit blocks and is dominated by the loop header, yet is
-not part of the natural loop, the case belongs to 0*1?.
+Given a natural loop $l$, when $l$
+contains at least one side-effect instruction along every path that
+starts from the loop header and ends at the loop header, it is a 1* loop;
+if there exists at least one side-effect instruction inside $l$, but not on
+every path,
+it is a [0$|$1]* loop; if there is no side-effect instructions inside $l$,
+$l$ is either a 0* or a 0*1? loop.
+In the last case, \Tool further checks all the loop exit-blocks. If there 
+exists an exit-block of $l$ that contains a side-effect instruction and is  
+post-dominated by another exit-block of $l$, this is a 0*1? loop.
+For example, line 5 in Figure \ref{fig:Mozilla347306} is such an exit block.
+Otherwise, $l$ is a 0* loop.
 

### 2015-11-19 figures/Apache34464.c

@@ -1,11 +1,8 @@
- //java.lang.String
- static int 
- indexOf(char[] source, int sourceCount,
-         char[] target, int targetCount ) 
- {
-   ...
-   char first  = target[targetOffset];
-   int max = sourceCount - targetCount;
+ int found = -1;
+ while ( found < 0 ) {
+ //Check if string source[] contains target[]
+   char first  = target[0];
+   int max = sourceLen - targetLen;
 
    for (int i = 0; i <= max; i++) {
      // Look for first character.
@@ -14,29 +11,21 @@
      }
 
      // Found first character
-     //now look at the rest of v2
+     // now look at the rest
      if (i <= max) {
        int j = i + 1;
-       int end = j + targetCount - 1;
+       int end = j + targetLen - 1;
        for (int k = 1; j < end && source[j] == 
                 target[k]; j++, k++);
 
        if (j == end) {
-         /* Found whole string. */
-         return i ;
+         /* Found whole string target. */
+         found = i;
+         break;
        }
      }
    }
-   return -1;
- }
 
- //TelnetTask.java
- public void waitForString(...)
- {
-+  int windowIndex = -s.length();
--  while (sb.toString().indexOf(s) == -1) {
-+  while (windowIndex++ < 0 || 
-+   sb.substring(windowIndex).indexOf(s) == -1){
-     sb.append((char) is.read());
-   }
+   //append another character; try again 
+   source[sourceLen++] = getchar();
  }

### 2015-11-19 figures/Mozilla347306.c

@@ -1,13 +1,5 @@
-//jsscript.c
-jssrcnote *
-js_GetSrcNote(JSScript *script, jsbytecode *pc)
-{
-  ...
-  for (sn = SCRIPT_NOTES(script); 
-       !SN_IS_TERMINATOR(sn); sn = SN_NEXT(sn)) {
-    offset += SN_DELTA(sn);
-    if (offset == target && SN_IS_GETTABLE(sn))
+  for (sn=script->start, int offset=0; !sn; sn=sn->next){
+    offset += sn->delta;
+    if (offset == target)
        return sn;
   }
-  return NULL;
-}

### 2015-11-20 section/0_intro.tex
finish a pass of the whole paper

@@
 
-\item Root-cause taxonomy guided design. To provide the needed coverage, we follow
+\item Taxonomy guided design. To provide good coverage, we follow
 the root-cause taxonomy discussed above and design analysis routines for
-every root-cause sub-category. Given a candidate loop, we will 
-apply a series of analysis to it to see if it matches any type of inefficiency.
+every root-cause category. Given a candidate loop, \Tool
+applies a series of analysis to it to see if it matches any type of inefficiency.
 %We will also put the analysis results from different analysis routines together

### 2015-11-20 section/1_under.tex
finish a pass of the whole paper

@@
 A resultless loop spends a lot of time in computation without
-producing any results useful after the loop.
+producing results useful after the loop.
 It is further categorized based on which loop iterations are
@@
 
-%\begin{figure}[h]
-%\centering
-%\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-%     morekeywords={+},keepspaces=true}
-%  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
-%\caption{A resultless 0*1? bug in Mozilla}
-%\label{fig:Mozilla347306}
-%\end{figure}
+\begin{figure}
+\centering
+\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+     morekeywords={+},keepspaces=true,numbers=left}
+  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
+\vspace{-0.05in}
+\caption{A resultless 0*1? bug in Mozilla}
+\label{fig:Mozilla347306}
+\end{figure}
 
@@
 by one until the right one is found.
-Clearly, whether this type of loops are efficient or not depends on the
-workload. If they are indeed inefficient, they are often
+Clearly, whether these loops are efficient or not depends on the
+workload. When indeed inefficient, they are often
 fixed by data-structure changes.
-As an example, Mozilla JavaScript engine used to use a linked list 
-\texttt{script}
-to store debugging information
-for every bytecode instruction in a JavaScript file. 
-Later on, people complained that Mozilla browsers were very slow in handling
-large JavaScript files.
-It turned out that those large
-JavaScript files filled the linked list \texttt{script} with
-tens of thousands of nodes. Repeated search through the
-long \texttt{script} list then led to poor performance.
-To fix this problem, 
-developers simply replace linked list with hash table
-(Mozilla Bug\#347306).
+An example is shown in Figure \ref{fig:Mozilla347306}.
+Large JavaScript files often fill the \texttt{script} list with 
+tens of thousands of nodes and cause poor performance.
+The patch simply replaced the \texttt{script} list with a hash table.
 % This improve the performance by 52.60{\bf X}.
@@
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
+\vspace{-0.05in}
 \caption{A resultless [0$|$1]* bug in GCC }
@@
 For some workload, the majority of iterations do not produce
-results and lead to performance problems perceived by users.
+results and cause performance problems perceived by users.
 These problems are often solved
-by using a simple check to conditionally skip the expensive loop.
+by adding a simple check to conditionally skip the expensive loop.
 Figure~\ref{fig:GCC46401} shows such an example.
@@
 %explain the fix
-Users complained that compilation became extremely slow when they 
-enabled the \texttt{-Wsequence-point} checking.
+Users complained that compilation became extremely slow when
+the \texttt{-Wsequence-point} checking is enabled.
 The slowness was caused
-by the \texttt{for} loop shown in the figure. Since the algorithm
-behind this loop is quadratic in the number of operands in an expression, 
+by the \texttt{for} loop in the figure. As the algorithm
+behind this loop has quadratic complexity in the number of operands in an expression, 
 programs with long expressions suffer severe slow-downs.
@@
 
-{\textbf{[1]*}}:
+{\textbf{1*}}:
 Loops in this category always generate results in almost all iterations. 
@@
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
+\vspace{-0.05in}
 \caption{A cross-loop redundant bug in Mozilla }
@@
 (24 vs. 21).
-Intuitively, 0* loops, where no iteration produces any results,
+Not surprisingly, 0* loops
 are rare in mature software. In fact, no bugs in this

### 2015-11-20 section/2_workless.tex
finish a pass of the whole paper

@@
 
-\Tool first identifies side-effect instructions that write to
-variables defined outside the loop. 
-\Tool analyzes all functions called
+\Tool considers two types of instructions as side-effect instructions:
+(1) write to heap or global variables;
+(2) write to a stack variable, defined outside the loop, and the update value
+may be used after the loop. The second condition is checked through liveness
+analysis.
+\Tool also analyzes all functions called
 by a loop directly or indirectly --- a function $F$ that updates variables
@@
 unless the library functions are specially marked by us in a white list.
+This analysis is complete, but not sound. We may identify side-effect
+instructions that are actually not.
 
@@
 only need to know the total number of loop iterations 
-to figure out the 
-\textit{resultless rate} of the loop. The implementation is straightforward
+to figure out the loop
+\textit{resultful rate}, which we define as the ratio between
+the number of iterations with
+side effects and the total number of iterations. 
+The implementation is straightforward
 --- we initialize a local counter to be 0 in the pre-header of the loop; we 

### 2015-11-20 section/3_redundancy.tex
finish a pass of the whole paper

@@
 
-Specifically, \Tool first identifies side-effect instructions in $C$.
-%, as 
-%discussed in Section \ref{sec:s_workless}. 
+Specifically, \Tool first identifies side-effect instructions in $C$,
+as 
+discussed in Section \ref{sec:s_workless}. 
 It then conducts 
@@
 \texttt{source} string from its previous execution, with a lot of redundancy.
-%applied to many \texttt{source} strings slightly different from each other
-%with a lot of
-%redundant computation.
-%We use it to demonstrate how we identify \texttt{input}s below.
 
@@
 in Section \ref{sec:perf}.
-
-\comment{
-We consider two types of dependence, control dependence and RAW data dependence. 
-We build control dependence graph according to the algorithm discussed in~\cite{controldep}. 
-If block A is one of ancestors of block B on the control dependence graph, 
-we consider all instructions in block B control depend on the branch condition in block A. 
-Data dependence is mainly calculated based on instructions' operands. 
-We define several types of instrumentation sites. 
-The inputs of our dependence analysis are instructions, 
-and the output of our dependence analysis is a set of dependent values, 
-including instrumentation sites and constant values.
-
-Before calculating dependence inside the monitored loop, 
-we conduct inter-procedural dependence analysis for each function directly called by the loop. 
-The formal parameters of each direct callee, memory instructions, 
-including load, memcpy, and memmove, 
-whose source is not from local structures or arrays, 
-and return values of library function calls are instrumentation sites. 
-During calculating dependence, 
-we consider formal parameter data depend on all real parameter, 
-the return value of each call site data depend on return inside the callee function, 
-and all instructions inside one callee functions inherit control dependence of all its call site.
-
-If a direct callee from the monitored loop does not contain recursive function calls, 
-we use a three-stage method to solve the infeasible path problem. 
-Assume function A is called inside the monitored loop, function A will call function B, 
-and function B will call function C. 
-We will have a call tree A $\rightarrow$ B $\rightarrow$ C. 
-This call tree does not have recursive function calls, so our three-stage method can apply to this case. 
-At the first stage, we conduct intra-procedural dependence analysis for each function.  
-We consider return values of all call sites as instrumentation sites. 
-For example, we consider both the return value of B in A and the return value of C in B as instrumentation sites. 
-At the second stage, we process each function bottom-up on the call tree. 
-For each call site inside a function, we calculate 
-how the return value depend on real parameters based on dependence information inside the callee.
-Back to our example, we will process the three functions in order C, B, and A.
-When processing function B, we calculate the dependence for the return value of function C 
-based on the dependence information inside C and the real parameters of the call site.
-At the last stage, we process each function top-down on call tree, 
-and calculate dependence for instruction inside a callee function based on information from all its call site. 
-At this stage, we will process the three function in the order A, B, and C. 
-We update dependence information inside function B, according to control dependence and real parameters of its call site in A.
-
-We design a Gen-Kill based intra-procedural analysis to 
-calculate which previous writes a memory read from local structures and arrays depends on. 
-The basic idea is that a memory write will kill all previous writes whose destination address it can cover, 
-and the memory write will generate a new write to its destination address. 
-Each memory read depends on previous writes whose destination addresses overlap with its source address.
-
-For the monitored loop, we calculate dependent values for all site-effect instructions, 
-including side-effect instructions inside the loop and side-effect instructions inside the callees. 
-For cross-loop dependence analysis, instrumentation sites include values defined outside the loop, 
-memory reads inside the loop, memory reads not from local structure and arrays inside callees, 
-and return values of library function calls. 
-For cross-iteration dependent analysis, instrumented sites also include value defined in previous iterations. 
-For example, the instruction defining the value of \texttt{i} is the only side-effect instruction 
-inside the loop at line 12 in Figure~\ref{fig:Apache34464}. 
-After running cross-loop dependence analysis, the dependent values include 
-memory read \texttt{source[i]} inside the loop, 
-and three values defined outside the loop, 
-which represent the initial value of \texttt{i}, the value of \texttt{max} and \texttt{first} respectively. 
-After running cross-iteration dependence analysis, 
-the dependent value include value \texttt{i} defined in previous iteration, 
-memory read \texttt{source[i]}, 
-and two values defined outside the loop (\texttt{max} and \texttt{first}).
-
-}
 
@@
 beginning of every iteration whether to track the values returned by
-source instructions in this iteration.
+input instructions in this iteration.
 
@@
 
-First, we identify and avoid monitoring memory reads whose return values can be 
-statically proved to
-not change throughout one loop instance
-or multiple loop instances. 
-Since we implement \Tool at LLVM byte-code level, the majority of this
-analysis is already done by LLVM, which lifts loop-invariant memory
-accesses out of loops. 
+First, we avoid tracking multiple read instructions that we can statically 
+prove to return the same value.
+Since we implement \Tool in LLVM, we leverage the SSA construction and the
+\textit{mem2reg} pass in LLVM to avoid unnecessary tracking of
+stack variables.
 For example, the read of \texttt{max} on line 12 of 
@@
 out of the loop. Consequently, \Tool only records
-its value once during each loop, not each iteration.
-However, LLVM does not apply its loop-invariant analysis to heap and global
-variables, so \Tool conducts some extra analysis --- it identifies those
-memory reads \texttt{read(v)}, where the address of \texttt{v} 
-is a loop invariant and no instructions 
-inside the loop can possibly write to that address. 
-For example, \Tool can identify that the values of
+its value once during each loop, instead of each iteration.
+LLVM is conservative in lifting heap/global variables out of
+a loop, for fear of changing the location of potential exceptions, etc.
+\Tool conducts a best-effort
+loop invariant analysis for heap/global variables.
+For example, \Tool identifies that the values of
 \texttt{aNode->localName} and \texttt{aNode->namespaceURI} do not change
 throughout one loop instance
-in Figure~\ref{fig:Mozilla477564}. This analysis is sound but not complete.
-\Tool may miss some loop invariants.
+in Figure~\ref{fig:Mozilla477564}, and hence only traces them once
+outside the loop. This analysis is sound but not complete.
+\Tool may miss some loop invariants. For in-house debugging, since we know
+the problem-triggering inputs do not lead to exceptions, this optimization
+is safe. For production-run usage, users can turn off this heap/global
+variable related optimization.
 
@@
 One is for cross-iteration redundancy checking.
-If a loop iteration's \texttt{input} set contains a loop-induction
+If a loop iteration's input set contains a loop-induction
 variable, we know different iterations' inputs would be different and 
@@
 end), instead of every value returned by the memory read.
-Of course, this optimization could lead to false positives, reporting
-non-redundant loop computation as redundant.
-This may happen when the corresponding
-memory locations are modified across different loop instances.
-In that case, although different loop instances work on variables read from
-similar memory locations, the values they read are different.
+This optimization could lead to false positives ---
+different loop instances may work on variables read from
+similar memory locations but with different values.
+We did not encounter such false positives in our experiments.
 
@@
 
+\comment{
+We consider two types of dependence, control dependence and RAW data dependence. 
+We build control dependence graph according to the algorithm discussed in~\cite{controldep}. 
+If block A is one of ancestors of block B on the control dependence graph, 
+we consider all instructions in block B control depend on the branch condition in block A. 
+Data dependence is mainly calculated based on instructions' operands. 
+We define several types of instrumentation sites. 
+The inputs of our dependence analysis are instructions, 
+and the output of our dependence analysis is a set of dependent values, 
+including instrumentation sites and constant values.
+
+Before calculating dependence inside the monitored loop, 
+we conduct inter-procedural dependence analysis for each function directly called by the loop. 
+The formal parameters of each direct callee, memory instructions, 
+including load, memcpy, and memmove, 
+whose source is not from local structures or arrays, 
+and return values of library function calls are instrumentation sites. 
+During calculating dependence, 
+we consider formal parameter data depend on all real parameter, 
+the return value of each call site data depend on return inside the callee function, 
+and all instructions inside one callee functions inherit control dependence of all its call site.
+
+If a direct callee from the monitored loop does not contain recursive function calls, 
+we use a three-stage method to solve the infeasible path problem. 
+Assume function A is called inside the monitored loop, function A will call function B, 
+and function B will call function C. 
+We will have a call tree A $\rightarrow$ B $\rightarrow$ C. 
+This call tree does not have recursive function calls, so our three-stage method can apply to this case. 
+At the first stage, we conduct intra-procedural dependence analysis for each function.  
+We consider return values of all call sites as instrumentation sites. 
+For example, we consider both the return value of B in A and the return value of C in B as instrumentation sites. 
+At the second stage, we process each function bottom-up on the call tree. 
+For each call site inside a function, we calculate 
+how the return value depend on real parameters based on dependence information inside the callee.
+Back to our example, we will process the three functions in order C, B, and A.
+When processing function B, we calculate the dependence for the return value of function C 
+based on the dependence information inside C and the real parameters of the call site.
+At the last stage, we process each function top-down on call tree, 
+and calculate dependence for instruction inside a callee function based on information from all its call site. 
+At this stage, we will process the three function in the order A, B, and C. 
+We update dependence information inside function B, according to control dependence and real parameters of its call site in A.
+
+We design a Gen-Kill based intra-procedural analysis to 
+calculate which previous writes a memory read from local structures and arrays depends on. 
+The basic idea is that a memory write will kill all previous writes whose destination address it can cover, 
+and the memory write will generate a new write to its destination address. 
+Each memory read depends on previous writes whose destination addresses overlap with its source address.
+
+For the monitored loop, we calculate dependent values for all site-effect instructions, 
+including side-effect instructions inside the loop and side-effect instructions inside the callees. 
+For cross-loop dependence analysis, instrumentation sites include values defined outside the loop, 
+memory reads inside the loop, memory reads not from local structure and arrays inside callees, 
+and return values of library function calls. 
+For cross-iteration dependent analysis, instrumented sites also include value defined in previous iterations. 
+For example, the instruction defining the value of \texttt{i} is the only side-effect instruction 
+inside the loop at line 12 in Figure~\ref{fig:Apache34464}. 
+After running cross-loop dependence analysis, the dependent values include 
+memory read \texttt{source[i]} inside the loop, 
+and three values defined outside the loop, 
+which represent the initial value of \texttt{i}, the value of \texttt{max} and \texttt{first} respectively. 
+After running cross-iteration dependence analysis, 
+the dependent value include value \texttt{i} defined in previous iteration, 
+memory read \texttt{source[i]}, 
+and two values defined outside the loop (\texttt{max} and \texttt{first}).
+
 }
+
+}

### 2015-11-20 section/5_exper.tex
finish a pass of the whole paper

@@
     \toprule
-                         &      	   &                        & {\bf Root}   &          \\
-   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf Cause}  & {\bf Fix}\\
+   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf RootCause}  & {\bf Fix}\\
    \midrule
@@
 Our experiments are designed to evaluate \Tool from three main aspects:
-\begin{itemize}
-\item Coverage. Given our benchmark suite that covers a wide variety
+(1) 
+\textit{Coverage}. Given our benchmark suite that covers a wide variety
 of real-world root causes, can \Tool identify all those root causes?
-\vspace{-0.05in}
-
-\item Accuracy. 
+(2)
+\textit{Accuracy}. 
 When analyzing non-buggy loops, will \Tool generate any false positives?
-\vspace{-0.05in}
-
-\item Performance. 
+(3) 
+\textit{Performance}.
 What is the run-time overhead of \Tool?
-\end{itemize}
 
 \paragraph{Evaluation settings}
-The imagined usage scenario of \Tool is that one will apply \Tool to identify
-detailed root causes and provide fix-strategy suggestion for a small number of
-suspicious loops that are most correlated with the specific performance problem.
-
 Our evaluation uses existing statistical performance diagnosis
@@
 one or a few suspicious loops for \Tool to analyze.
-For 14 out of the 18 benchmarks, statistical performance debugging identifies the
-real root-cause loop as the top ranked suspicious loop. For the remaining
+For 14 out of the 18 benchmarks, statistical debugging identifies the
+real root-cause loop as the most suspicious loop. For the remaining
 benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
@@
 several configurable thresholds. In our evaluation,
-we use 0.001 as the \textit{resultless rate} threshold for identifying
-0*1? loops, 0.01 as the \textit{resultless rate} threshold for identifying 
+we use 0.001 as the \textit{resultful rate} threshold for identifying
+0*1? loops, 0.01 as the \textit{resultful rate} threshold for identifying 
 [0$|$1]* loops, 0.5 as the \textit{cross-loop redundancy rate}, and 
@@
 problem-triggering input.
+
+More discussions about all the parameters/thresholds presented above, including
+how to set them and how sensitive they are, are discussed in Section
+\ref{sec:sensi}.
 
@@
 to be less performance-optimal than before. However, GCC developers feel
-that it is worthwhile considering the performance impact of the original loop
-to the GCC compilation process.
-Providing this type of
-fix strategy suggestion goes beyond the capability of \Tool.
+that it is worthwhile considering the slow-down caused by the original loop.
 
@@
   %\nocaptionrule
-  \caption{False positives of \Tool, when applying to top 5 loops reported by 
-    statistical performance diagnosis for each benchmark. `-': no false positive. $x_y$: $x$ real false positives and $y$ benign ones.
+  \caption{False positives of \Tool for top 5 loops reported by 
+    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
 }
@@
 The accuracy of \Tool benefits from its run-time analysis.
-For example, 4 benchmarks contain loops that only generate side-effect
-in the last iteration among their top 5 suspicious loops. However,
-these loops are actually not inefficient because the portion of
-resultless iterations is small. 
+For example, there are seven benchmarks in total that each contains
+one loop, which generates side effect only
+in its last iteration. Without run-time information, \Tool would judge
+all of them as inefficient (i.e., 0*1? resultless). Fortunately,
+\Tool run-time analysis counts the total number of loop iterations and
+correctly identifies three of them as truly inefficient and severe enough
+to cause the corresponding performance problem.
 %TODO a table 6 was deleted from oopsla submission
 
-The good accuracy of \Tool can actually help improving the accuracy of
+\Tool can also help improve the accuracy of statistical debugging in
 identifying which loop is the root cause loop.
@@
 rank number two by the statistical performance diagnosis tool.
+Fortunately,
 \Tool can tell that the number one loops in both cases do not contain
-any form of inefficiency, resultless or redundancy. This result can
-potentially used to improve the accuracy of identifying root cause loops.
+any form of inefficiency, resultless or redundancy.
 
@@
     (only non-extracted benchmarks are shown). 
-  -: dynamic analysis is not conducted, as static analysis is sufficient.
+  -: dynamic analysis is not needed;
   /: not applicable.}
@@
 except for one benchmark, Mozilla347306. We believe \Tool is promising for potential production
-run usage. Of course, if we apply \Tool to multiple loops simultaneously,
-the overhead will be higher. However, the current results are obtained by running the
-program only \textbf{once} under the problem-triggering workload. The sampling nature
-of \Tool will allow us to keep the overhead low at the exchange of running the program for
-a couple of more times, if needed.
+run usage.
+We can easily further lower the overhead through sparser sampling.
+As we will discuss later, 
+the current diagnosis results are obtained by running the
+program only \textbf{once} under the problem-triggering workload.
+If we use sparser sampling, more failure runs will be needed to obtain good
+diagnosis results.
 
 As we can also see from the table, our performance optimization discussed in 
-Section \ref{sec:inst} and \ref{sec:perf} has contributed
-a lot to the good performance of \Tool.
+Section \ref{sec:inst} and \ref{sec:perf} has helped.
 
-Without sampling, while still applying our static optimization, our redundancy
-analysis would lead to over 100X slowdown for five benchmarks.
+The performance benefit of sampling is huge.
+Without sampling, even with all the static optimization, redundancy
+analysis lead to over 100X slowdown for five benchmarks.
 
-The buggy loops of MySQL\#27287 and MySQL\#15811 access arrays. 
+The benefit of static optimization is also non-trivial. 
+For example, for MySQL15811 and MySQL27287, static analysis alone can
+judge that they do not contain cross-iteration redundancy: the computation of 
+each iteration depends on loop induction variables, which are natually different
+in different iterations. Consequently, run-time overhead is completely
+eliminated for these two benchmarks.
+As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
+arrays. 
 After changing to tracking the initial and ending memory-access addresses
@@
 
-The side-effect of the buggy loop for MySQL15811 is to calculate the length of a string. 
-The variable representing the length is an induction variable. 
-The side-effect of the buggy loop for MySQL27287 is to calculate the index of a searched target, 
-and the variable representing the index is also an induction variable. 
-We can reply on static analysis to figure out that these two loops are not cross-iteration redundant.
+\subsection{Parameter Setting and Sensitivity}
+\label{sec:sensi}
+\paragraph{Sampling rates}
+We have tried different sampling rates for redundancy analysis.
+Intuitively, sparser sampling leads to lower overhead but worse diagnosis
+results. Due to space constraints, we briefly summarize the results below.
 
-We also tried sampling with different sampling rates.
-For cross-loop redundancy, we also conduct experiments under sampling rate 1
-out of 1000. 
-Both run-time overhead and collected sample will be reduced. Mozilla347306 
-is still the benchmark with largest overhead, but the overhead is reduced to 0.49\%. For two benchmarks, GCC8805 and GCC12322, we cannot sample 
-more than 10 loop instances and hence cannot draw strong conclusion
-about their root-cause type. For all other benchmarks, we can 
-still have more than 10 loop instances and get exactly the same 
-root-cause analysis results presented above.
+When we lower the sampling rate from 1/100 to 1/1000 
+in cross-loop redundancy analysis,
+Mozilla347306 still incurs the largest overhead (0.49\%). 
+The diagnosis results remain the same for all but
+GCC8805 and GCC12322, where too few samples are available
+to judge redundancy.
 
-We also conduct cross-iteration redundant experiment under different sampling rates.
-When the sampling rate is 1 out of 100, there are two benchmarks, whose runtime overhead is larger than 30\%.
-The overhead for Mozilla347306 is 59.57\%,
-and the overhead of GCC21430 is 30.65\%. When changing sampling rate to 1
-out of 10000, Mozilla347306 has the largest overhead, which is 4.47\%. And mozilla347306 is the only one whose overhead is larger than 2\%. Except for 
-GCC12322, all other benchmarks will have more than 100 iterations sampled, under the sample rate is 1 out of 10000. Consequently, the same root-cause
-analysis results will be reported for these benchmarks as the ones presented
-above.
+When we lower the sampling rate from 1/1000 to 1/10000
+in cross-iteration redundancy analysis,
+Mozilla347306 has the largest overhead (4.47\%). 
+%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
+The diagnosis results remain 
+the same for all but GCC12322.
+%If we increase the sampling rate to 1/100, we will 
+%have two benchmarks whose overhead is larger than 30\%.
+
+\paragraph{Resultful and redundancy rate}
+Since the severity of resultless and redundant loops depends on
+workload, it is natural that \Tool uses thresholds in its diagnosis.
+Intuitively, changing these thresholds affects the
+false positive and false negative of \Tool. For example, 
+if we change the cross-iteration redundancy rate from the default 2
+to 4, \Tool incurs 1 more false negative and 1 fewer false positive.
+
+Our default setting is obtained based on our experience
+and should work for many problems.
+Developers can adjust these thresholds based on their
+need. They can even get rid of all threshods, and only
+use the raw values of resultful/redundancy rates to understand
+the absolute and relative resultless/redundancy nature of suspicious 
+loops.

### 2015-11-20 section/6_related.tex
finish a pass of the whole paper

@@
 have been proposed.
-StackMine~\cite{Han:2012:PDL:2337223.2337241} can
-identify slow call-stack patterns inside event handlers. The work by
+StackMine~\cite{Han:2012:PDL:2337223.2337241} 
+identifies slow call-stack patterns inside event handlers. The work by
 \citet{TaoAsplos2014} analyzes system traces to understand 
 performance impact propagation and 
-causality relationship among different system components. 
+causality relationship among system components. 
 X-ray~\cite{Attariyan:2012:XAR:2387880.2387910} helps identify inputs
 or configuration entries that are most responsible for performance problems.
+Coz~\cite{coz.sosp15} can estimate the performance impact of any
+potential optimization at any point of a multi-threaded program.
 Although these techniques are all very useful, 
-they target different problems from \Tool. \Tool targets 
+they target different problems from \Tool. 
+\comment{
+\Tool targets 
 inefficient loops, a common
@@
 root cause and provide fix-strategy suggestions.
+}
 
@@
 \Tool complements it by
-providing detailed root cause information and fix strategy suggestions through
-program analysis.
+providing detailed root cause information and fix strategy suggestions.
 
@@
 Performance-bug detection tools has to be more conservative and tries hard
-to lower false positive rates, because it needs to apply its analysis to the
+to lower false positive rates, because it needs to process the
 whole program, instead of just a few loops. This requirement causes bug

### 2015-11-20 figures/GCC27733.c

@@ -3,8 +3,7 @@ struct hash_entry {
 +  HOST_WIDE_UINT t;
 };
 
-void mult_alg(... HOST_WIDE_UINT t, ...)
-{
+void mult_alg(... HOST_WIDE_UINT t, ...) {
   hash_index = t ...;
   if (alg_hash[hash_index].t == t ...)
   {

### 2015-11-20 figures/Mozilla347306.c

@@ -1,5 +1,7 @@
-  for (sn=script->start, int offset=0; !sn; sn=sn->next){
+  for (sn=script->start, offset=0; 
+                      !sn; sn=sn->next){
     offset += sn->delta;
     if (offset == target)
        return sn;
-  }
+  } //script is a linked list with one node for 
+  //each byte-code instruction in a JavaScript file

### 2015-11-20 section/5_exper.tex
check in proofread results

@@
    Mozilla416628                & \Yes                        & \Yes                                         \\
-   Mozilla490742$_a$            & \Yes                        & \Yes                                             \\
-   Mozilla35294$_a$             & \Yes                          & \Yes                                              \\ 
-   Mozilla477564$_a$            & \Yes                          & \Yes                                            \\
+   Mozilla490742                & \Yes                        & \Yes                                             \\
+   Mozilla35294                 & \Yes                          & \Yes                                              \\ 
+   Mozilla477564                & \Yes                          & \Yes                                            \\
    \midrule 
@@
    Apache32546                  & \Yes                          & \Yes                                      \\
-   Apache37184$_a$              & \Yes                          & \Yes                                        \\
-   Apache29742$_a$              & \Yes                          & \Yes                                       \\ 
+   Apache37184                  & \Yes                          & \Yes                                        \\
+   Apache29742                  & \Yes                          & \Yes                                       \\ 
    Apache34464                  & \Yes                          & \Yes                                        \\
@@
    GCC1687                      & \Yes                          & \Yes                                     \\
-   GCC27733$_a$                 & \Yes                          & \Yes                                     \\
+   GCC27733                     & \Yes                          & \Yes                                     \\
    GCC8805                      & \Yes                          & \Yes                                  \\
@@
 for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
-the fix strategy that developers used. For MySQL27287, the root-cause loop
+the fix strategy that developers used. For MySQL\#27287, the root-cause loop
 is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
@@
 find a new data structure that can eliminate both root causes.
-For GCC12322, \Tool correctly tells that the loop under study
+For GCC\#12322, \Tool correctly tells that the loop under study
 does not contain any form of inefficiency and produce results in every 
@@
    Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
-   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
-   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
-   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
+   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
+   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
+   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
    \midrule 
@@
    Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
-   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
-   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
+   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
+   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
    Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
@@
    GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
-   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
+   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
    GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
@@
 identifying which loop is the root cause loop.
-For example, the real root-cause loop of Apache34464 and GCC 46401 both
+For example, the real root-cause loop of Apache\#34464 and GCC\#46401 both
 rank number two by the statistical performance diagnosis tool.
@@
       GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
-      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
+      GCC27733    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
       GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
@@
 the performance of \Tool is good. The overhead is consistently under or around 5\% 
-except for one benchmark, Mozilla347306. We believe \Tool is promising for potential production
+except for one benchmark, Mozilla\#347306. We believe \Tool is promising for potential production
 run usage.
@@
 The benefit of static optimization is also non-trivial. 
-For example, for MySQL15811 and MySQL27287, static analysis alone can
+For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
 judge that they do not contain cross-iteration redundancy: the computation of 
@@
 in cross-loop redundancy analysis,
-Mozilla347306 still incurs the largest overhead (0.49\%). 
+Mozilla\#347306 still incurs the largest overhead (0.49\%). 
 The diagnosis results remain the same for all but
-GCC8805 and GCC12322, where too few samples are available
+GCC\#8805 and GCC\#12322, where too few samples are available
 to judge redundancy.
@@
 in cross-iteration redundancy analysis,
-Mozilla347306 has the largest overhead (4.47\%). 
+Mozilla\#347306 has the largest overhead (4.47\%). 
 %In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
 The diagnosis results remain 
-the same for all but GCC12322.
+the same for all but GCC\#12322.
 %If we increase the sampling rate to 1/100, we will 

### 2015-11-20 figures/GCC46401.c

@@ -1,4 +1,4 @@
-+ if(warning_candidate_p(to)) {
++ if(warning_candidate_p(add->expr)) {
    for (tmp = *to; tmp; tmp = tmp->next)
     if (candidate_equal_p (tmp->expr, add->expr)
          && !tmp->writer)

### 2015-11-20 section/2_workless.tex
address linhai's comments

@@
 \Tool consists of a series of analysis that
-judges whether a given loop belongs to any root cause type discussed in
+judges whether a given loop belongs to any root-cause type discussed in
 Section \ref{sec:study_tax}.
@@
 \end{itemize}
+
+\paragraph{Usage scenario}
+Existing profilers and statistical debugging tool can
+identify suspicious loops that are most correlated with 
+certain performance 
+symptoms \cite{SongOOPSLA2014}. 
+\Tool will analyze
+these suspicious loops, identify which loop(s) is inefficient, why it is
+inefficient, and provide fix suggestions. This analysis could be
+conducted during in-house diagnosis, where failure-triggering inputs
+are available. It could also be conducted during production runs, with
+the run-time analysis component of \Tool running 
+at user sites.
 

### 2015-11-20 section/3_redundancy.tex
slight change to figure 3 explanation

@@
 \subsubsection{Design overview}
-At high level, we will compare the computation of different iterations
+We will compare the computation of different iterations
 from one loop instance and that of different loop instances from 
 one static loop,
-and judge whether there exists redundancy.
-Specifically, our design needs to answer several questions.
+and judge whether there is redundancy.
+Specifically, several questions need to be answered.
 
@@
 \emph{How to lower the overhead of record-and-compare?}
-We will use both static optimization and dynamic sampling
-to reduce the amount of data that we need to record and compare, lowering
-time and spatial overhead. Details will be presented in 
-Section \ref{sec:inst} and \ref{sec:perf}.
+We will use both static optimization 
+(Section \ref{sec:perf})
+and dynamic sampling (Section \ref{sec:inst})
+to reduce the amount of data that is recorded and compared, reducing
+time and spatial overhead.
 %TODO static analysis alone is not sufficient, because some redundant is
@@
 
-For cross-loop redundancy, we need to answer similar questions.
-How to judge whether two loop instances are doing redundant work ---
-should they contain exactly the same number of iterations and doing exactly
-the same computation in each iteration?
+For cross-loop redundancy, we need to answer similar questions:
+how to judge whether two loop instances are doing redundant work?
+%should they contain exactly the same number of iterations and doing exactly
+%the same computation in each iteration?
 %Second, is a (static) loop problematic when it contains two instances that

### 2015-11-20 section/abstract.tex
slight change to figure 3 explanation

@@
 Design and implementation defects can easily
-lead to severe performance 
-degradation. Techniques that help
-diagnose performance problems are desired.
-Unfortunately, existing techniques are still preliminary.
+cause severe performance 
+degradation. 
+Unfortunately, existing performance diagnosis techniques are still preliminary.
 %failing to provide the desired diagnosis coverage, accuracy, and performance. 

### 2015-11-20 section/5_exper.tex
slight change to figure 3 explanation
change threshold, over limit now

@@
 we use 0.001 as the \textit{resultful rate} threshold for identifying
-0*1? loops, 0.01 as the \textit{resultful rate} threshold for identifying 
-[0$|$1]* loops, 0.5 as the \textit{cross-loop redundancy rate}, and 
-2 as the \textit{cross-iteration redundancy rate} (i.e., 
-the number of distinct iterations is less than half of the total iterations).
+0*1? 
+%loops, 0.01 as the \textit{resultful rate} threshold for identifying 
+and [0$|$1]* resultless loops; we use 
+0.5 as the \textit{redundancy rate} threshold for identifying redundant loops.
+%, and 
+%2 as the \textit{cross-iteration redundancy rate} (i.e., 
+%the number of distinct iterations is less than half of the total iterations).
 
@@
    GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
-   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
+   GCC8805               &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
    GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
@@
 The main reason is that they are not the main contributor to the 
-performance problem perceived by the users. This happens to 12 out of the
-14 benign cases. In fact, this is not really a problem for \Tool in 
+performance problem perceived by the users. This happens to 11 out of the
+13 benign cases. In fact, this is not really a problem for \Tool in 
 real usage scenarios, because statistical debugging can accurately
@@
 to cause the corresponding performance problem.
-%TODO a table 6 was deleted from oopsla submission
 
 \Tool can also help improve the accuracy of statistical debugging in
-identifying which loop is the root cause loop.
+identifying which loop is the root-cause loop.
 For example, the real root-cause loop of Apache\#34464 and GCC\#46401 both
@@
 Since the severity of resultless and redundant loops depends on
-workload, it is natural that \Tool uses thresholds in its diagnosis.
-Intuitively, changing these thresholds affects the
-false positive and false negative of \Tool. For example, 
-if we change the cross-iteration redundancy rate from the default 2
-to 4, \Tool incurs 1 more false negative and 1 fewer false positive.
+workload, it is natural that \Tool uses two thresholds in its diagnosis.
+In fact, the diagnosis results are largely insensitive to the threshold
+setting. For example, the results would remain the same when
+changing the redundancy rate threshold from 0.5 to any value between about
+0.1 and 0.66. We will have 1 more false negative and 1 fewer benign report, 
+when the rate is 0.75. The trend is similar for resultless
+loop checking.
 
-Our default setting is obtained based on our experience
-and should work for many problems.
-Developers can adjust these thresholds based on their
-need. They can even get rid of all threshods, and only
+Our default setting %is obtained based on our experience
+should work for many problems.
+Developers can adjust these thresholds. 
+They can even get rid of threshods, and only
 use the raw values of resultful/redundancy rates to understand
-the absolute and relative resultless/redundancy nature of suspicious 
-loops.
+the absolute and relative (in)efficiency nature of suspicious 
+loops. Based on our experiments, the difference between efficient and inefficient
+loops is usually obvious, based on these rates.

### 2015-11-20 section/3_redundancy.tex
shrink back to 11 pages

@@
 }
-We calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
-the total number of iterations in the loop by the number of distinct iterations.
-The smaller the rate is, with 1 being the minimum possible value, 
-the less cross-iteration redundancy the loop contains.
+We calculate a loop's \textit{cross-iteration redundancy rate} based on
+the number of (distinct) iterations in a loop:
+Rate$_\text{C.I.}$ = $1 - \frac{\text{\# of distinct iterations}}{\text{\# of iterations}}$.
+This rate ranges between 0 and 1, the smaller it is
+the less redundancy the loop contains.
 
-The implementation of checking cross-loop redundancy goes through several
+Checking cross-loop redundancy goes through several
 steps. First, for $k$ dynamic instances of a static loop $L$ that appear
@@
 $l_2$ and $l_3$, and so on. Second, we compute a 
-\textit{cross-loop redundancy rate} for $L$
---- dividing the number of redundant pairs by $k-1$.
-The smaller the rate is, with 0 being the minimum possible value, the
-less cross-loop redundancy $L$ contains.
-Here we only check redundancy between consecutive loop instances, because  
-checking the redundancy between every pairs of loop
+\textit{cross-loop redundancy rate} for $L$:
+Rate$_\text{C.L.}$ = $\frac{\text{\# of redundant pairs}}{\text{\# of pairs}}$
+(In this example, $\text{\# of pairs}$ is $k-1$).
+This rate ranges between 0 and 1, the smaller it is the less redundancy
+$L$ contains.
+We only check redundancy between consecutive loop instances, because  
+checking that between every pairs of loop
 instances is time consuming.

### 2015-11-20 section/5_exper.tex
shrink back to 11 pages

@@
   %\nocaptionrule
+\vspace{-0.1in}
   \caption{False positives of \Tool for top 5 loops reported by 
@@
 The accuracy of \Tool benefits from its run-time analysis.
-For example, there are seven benchmarks in total that each contains
-one loop, which generates side effect only
+For example, there are 7 benchmarks in total that each contains
+a loop that generates side effect only
 in its last iteration. Without run-time information, \Tool would judge
-all of them as inefficient (i.e., 0*1? resultless). Fortunately,
-\Tool run-time analysis counts the total number of loop iterations and
-correctly identifies three of them as truly inefficient and severe enough
+all of them as inefficient (0*1? resultless). Fortunately,
+\Tool run-time counts the total number of iterations and
+correctly identifies 3 of them as truly inefficient and severe enough
 to cause the corresponding performance problem.
@@
 judge that they do not contain cross-iteration redundancy: the computation of 
-each iteration depends on loop induction variables, which are natually different
+each iteration depends on loop induction variables, which are naturally different
 in different iterations. Consequently, run-time overhead is completely
@@
 changing the redundancy rate threshold from 0.5 to any value between about
-0.1 and 0.66. We will have 1 more false negative and 1 fewer benign report, 
+0.1 and 0.7. We will have 1 more false negative and 1 fewer benign false positive, 
 when the rate is 0.75. The trend is similar for resultless
@@
 Developers can adjust these thresholds. 
-They can even get rid of threshods, and only
+They can even get rid of thresholds, and only
 use the raw values of resultful/redundancy rates to understand

### 2015-11-20 section/5_exper.tex
fix ~0

@@
     \midrule
-     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
+     MySQL27287   & $<$0.01\%           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
      MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
@@
       GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
-      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
-      GCC27733    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
-      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
+      GCC1687     & -              & /                 &  $<$0.01\%       &   /           & 142.29{\bf X} \\
+      GCC27733    & $<$0.01\%        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
+      GCC8805     & -              & $<$0.01\%           & $<$0.01\%        & 2.22{\bf X}   &  3.52{\bf X}\\
       GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
-      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
+      GCC12322    & -              & 1.75\%            &  $<$0.01\%       & 21.07{\bf X}  & 38.44{\bf X} \\
    \bottomrule
@@
      \midrule
-     MySQL27287        & $\sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
+     MySQL27287        & $sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
      MySQL15811        &  -             & 226.04{\bf X}     &  0.03\%        & 423.44{\bf X}         & - \\

### 2015-11-20 section/3_redundancy.tex
test

@@
 %we do not record values defined outside the loop for cross-iteration redundancy. 
-
 Once the trace under problematic workload is collected either during
-off-line debugging or during production runs, 
+off-line debugging or production runs, 
 \Tool will process the trace and decide
-whether the loops under study contain cross-iteration redundancy or 
+whether the loops under study contain cross-iteration or 
 cross-loop redundancy. We will first present our high-level algorithms, followed
@@
 The challenge is that $l_1$ and $l_2$ may have executed different numbers of
-iterations; in different iterations, different sets of source instructions
+iterations; in different iterations, different sets of input instructions
 may have executed. Therefore, we cannot simply chain values from different
 input instructions and iterations together and compare two data sequences.
-Instead, we decide to check the redundancy for each source instruction across
+Instead, we decide to check the redundancy for each input instruction across
 $l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
-all source instructions as the \textit{cross-loop redundancy rate} between
+all input instructions as the \textit{cross-loop redundancy rate} between
 $l_1$ and $l_2$.
 
-We calculate the redundancy for one source instruction $I$ by normalizing the
+We calculate the redundancy for one input instruction $I$ by normalizing the
 edit-distance between the two sequences of values returned by $I$ in the two
@@
 
-Recording values returned by every source instruction would lead to 
-huge run-time overhead. To lower the overhead,
-we use random sampling to reduce the number of instructions that we
-track at run time. Due to the repetitive nature of performance bugs,
-we will still be able to recognize redundant 
-computation as long as the sampling rate is not too sparse, which
-we will evaluate
-in Section \ref{sec:experiment}. 
-Our sampling scheme requires almost no changes to our redundancy 
+Recording values returned by every input instruction would lead to 
+huge run-time overhead.
+\Tool uses random sampling to reduce this overhead, which 
+requires almost no changes to our redundancy 
 identification algorithm discussed in Section \ref{sec:cal}.
 
+Note that, \Tool leverages sampling to gain performance with \textbf{no}
+sacrifice to diagnosis latency or quality, which is
+\textbf{different} from traditional sampling techniques
+for diagnosing correctness failures \cite{liblit03,liblit05}, where
+many more failure runs and hence longer diagnosis latency
+are needed to compensate for the performance gain.
+Performance bugs have a unique repetitive nature:
+a loop can cause a severe performance problem only when it 
+contains many redundant iterations/instances.
+Therefore, we can still recognize redundant behavior in just
+\textbf{one} failure run, 
+as long as the sampling is not insanely sparse
+(Section \ref{sec:experiment}). 
 %Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 

### 2015-11-20 section/3_redundancy.tex
emphasize sampling does not hurt quality

@@
 
-Note that, \Tool leverages sampling to gain performance with \textbf{no}
+Note that, \Tool leverages sampling to gain performance with almost \textbf{no}
 sacrifice to diagnosis latency or quality, which is
@@
 are needed to compensate for the performance gain.
-Performance bugs have a unique repetitive nature:
+The reason is that performance bugs have a unique repetitive nature:
 a loop can cause a severe performance problem only when it 

### 2015-11-20 section/5_exper.tex
emphasize sampling does not hurt quality

@@
   %\nocaptionrule
+\vspace{-0.1in}
   \caption{Coverage Results.}
+\vspace{-0.1in}
   \label{tab:cover}
@@
 The diagnosis results remain the same for all but
-GCC\#8805 and GCC\#12322, where too few samples are available
+GCC\#12322, where too few samples are available
 to judge redundancy.
@@
 changing the redundancy rate threshold from 0.5 to any value between about
-0.1 and 0.7. We will have 1 more false negative and 1 fewer benign false positive, 
-when the rate is 0.75. The trend is similar for resultless
+0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
+when the rate is 0.7. The trend is similar for resultless
 loop checking.

### 2015-11-20 section/3_redundancy.tex
polish

@@
 
-Note that, \Tool leverages sampling to gain performance with almost \textbf{no}
-sacrifice to diagnosis latency or quality, which is
+Note that, although \Tool uses sampling, its diagnosis is still conducted
+in just \textbf{one} run, with almost \textbf{no}
+sacrifice to diagnosis latency or quality. This is
 \textbf{different} from traditional sampling techniques
-for diagnosing correctness failures \cite{liblit03,liblit05}, where
-many more failure runs and hence longer diagnosis latency
-are needed to compensate for the performance gain.
+for correctness diagnosis \cite{liblit03,liblit05}, where
+many more failure runs and hence longer latency
+are needed once sampling is enabled.
 The reason is that performance bugs have a unique repetitive nature:

### 2015-11-20 section/3_redundancy.tex
all edits for pldi'16 submission

@@
 depends on. We refer
-to these instructions as \textit{input} instructions for $C$. 
+to these instructions as \textit{input instructions} for $C$. 
 The values returned
-from them at run-time will be tracked and compared to identify
+from them at run-time, referred to as \textit{inputs}, 
+will be tracked and compared to identify
 redundant computation among different instances of $C$.
@@
 Specifically, \Tool first identifies side-effect instructions in $C$,
-as 
-discussed in Section \ref{sec:s_workless}. 
+similar with that in Section \ref{sec:s_workless}. 
 It then conducts 
@@
 stack variables.
-For example, the read of \texttt{max} on line 12 of 
+For example, the read of \texttt{max} on line 10 of 
 Figure \ref{fig:Apache34464} is an \textit{input} instruction of the 

### 2016-03-16 section/0_intro.tex
finish revising explanation to figure 1

@@
 Figure~\ref{fig:GCC27733} shows a performance bug in GCC. 
-Function \texttt{mult\_alg} is used to compute the best algorithm for 
-multiplying \texttt{t}. It is so time consuming that developers used a
+Function \texttt{mult\_alg} is a recursive function 
+that computes the best algorithm for 
+multiplying \texttt{t}, a time-consuming computation. 
+At run time, \texttt{mult\_alg} is often invoked for many times, and often
+with the same parameter partly due to its recursive nature.
+To avoid redundant computation across different instances of
+\texttt{mult\_alg} with the same parameter, developers used a
 hash-table
-\texttt{alg\_hash} to remember which \texttt{t} has been processed
+\texttt{alg\_hash} to remember which parameter \texttt{t} has been processed
 in the past and what is the result. 
 Unfortunately, a mistake in the type declaration of hash-table
-entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t},
-severely hurting performance.
-In reality, developers easily figured out that
-\texttt{mult\_alg} is most correlated with the execution slowness, but
-spent several weeks to finally figure out \texttt{mult\_alg}, 
-containing 400 lines
-of code, is
-inefficient.
-%If a tool can tell them not only which loop\footnote{Recursive functions are
-%handled similarly as loops in this paper.}
-%is the root cause but also why a loop is inefficient (i.e., lot of redundant
-%computation and the need for better memoization in this example), 
-%the diagnosis and bug fixing
-%process would be much easier for developers.
+entry \texttt{hash\_entry} makes the memoization useless for large \texttt{t}.
+In many cases, a slow path is taken, when the fast path should have been taken.
+This mistake does not affect software correctness, but it causes a large amount
+of redundant computation\footnote{This problem will be considered as 
+cross-loop redundancy later in this paper, as we consider
+recursive functions as a special case of loops.} 
+and hurts GCC performance severely,
+causing hundreds of times slow down for GCC test cases.
+
+Debugging this performance bug is challenging. According to 
+the discussion forum of GCC, developers identified
+\texttt{mult\_alg} as the most time-consuming function
+through profilers early on. However, developers did not figure out 
+whether \texttt{mult\_alg} is inefficient, which part of it is 
+inefficient (\texttt{mult\_alg} is a large function with about 400 lines of 
+code), and how it is inefficient, until several weeks later.
+
+If a tool can tell developers not only \emph{which} loop or function is
+responsible for execution slowness, but also \emph{why} and \emph{how}
+the loop/function is inefficient, 
+the diagnosis and bug fixing
+process would be much easier.
 

### 2016-03-16 section/0_intro.tex
split study section. the benchmark study does not guide study, but evaluate study

@@
 This mistake does not affect software correctness, but it causes a large amount
-of redundant computation\footnote{This problem will be considered as 
-cross-loop redundancy later in this paper, as we consider
+of redundant computation\footnote{This will be considered as a
+loop-redundancy problem later in this paper, as we consider
 recursive functions as a special case of loops.} 
@@
 First, figuring out a root-cause taxonomy for inefficient loops.
-Such a taxonomy is the prerequisite to developing a general and accurate
-diagnosis tool. Guided by a thorough study of 45 real-world inefficient
-loop problems, we come up with a hierarchical root-cause taxonomy for
-inefficient loops that are
 %Specifically, we consider \textit{resultless} and
@@
 %sub-categories based on the granularity of the resultless or redundant work. 
-general enough to cover
-common inefficient loops, and also specific enough to help developers understand
+Our taxonomy categorizes all inefficient loops into two main categories:
+\emph{resultless}, when a large amount of computation produces
+no side effect, and \emph{redundancy}, when a large amount of 
+computation produces already-available results.
+Each main category is then further divided to sub-categories.
+We have strived to make our taxonomy both general enough to cover
+common inefficient loops, and also specific enough to guide the failure
+diagnosis of \Tool, and eventually
+help developers understand
 and fix performance problems. More details are
@@
 
-We evaluated \Tool on 18 real-world performance problems. 
+We evaluated \Tool on \allbugs real-world performance problems,
+coming from two representative benchmark suites 
+\cite{SongOOPSLA2014,Alabama}. 
 Evaluation results show that \Tool can accurately identify detailed
 root cause for all benchmarks and provide correct fix-strategy suggestion for
-16 benchmarks. All of these are achieved with low run-time overhead.
+most benchmarks. All of these are achieved with low run-time overhead.

### 2016-03-16 section/1_under.tex
check in proofread results
slight change to figure 3 explanation
all edits for pldi'16 submission
split study section. the benchmark study does not guide study, but evaluate study

@@
 
-This section first presents the root-cause taxonomy designed by us, 
-and then discusses the coverage, actionability, and generality
-of our taxonomy using a suite of real-world
-inefficient loops collected by previous work \cite{SongOOPSLA2014,PerfBug}.
+We divide all inefficient loops into two main root-cause categories,
+\textit{resultless} and \textit{redundancy}, and many sub-categories under
+these two.
+The details of these categories will be presented below.
 
-\subsection{Taxonomy Design}
-\label{sec:study_tax}
-We divide all inefficient loops into two root-cause categories:
-\textit{resultless} and \textit{redundancy}.
+Our discussion below will qualitatively show that 
+our taxonomy is general, not application-specific, and
+cover common loop inefficiency problems.
+We will quantitatively measure the coverage, actionability, and 
+generality of our taxonomy
+using real-world performance-bug suite in Section \ref{sec:eval_taxonomy}.
 
-\subsubsection{Resultless loops}
+\subsection{Resultless loops}
+\label{sec:study_resultless}
 A resultless loop spends a lot of time in computation without
@@
 simple checking that allows the loop to be
-skipped for most expressions.
+skipped in most cases.
 
@@
 
-\subsubsection{Redundant loops}
+\subsection{Redundant loops}
+\label{sec:study_redundant}
+
 Redundant loops spend a lot of time in repeating computation that is already
@@
 saved count value of the nearest previous sibling with the same name and URI.
-
-\input section/tab_root
-
-\input section/tab_appbug
-
-\subsection{Taxonomy Assessment}
-\label{sec:tax_study}
-We assess the coverage, actionability, and generality of our taxonomy using
-a set of
-real-world inefficient loop problems collected by previous work
-\cite{SongOOPSLA2014,PerfBug}.
-
-\subsubsection{Methodology}
-
-Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
-databases of five representative open-source software projects, as 
-shown in Table \ref{tab:app_bug}. Through a mix of random sampling and 
-manual inspection, they 
-found 65 performance problems that are perceived and reported by users. 
-Among these 65 problems, 45 problems are related to inefficient loops and 
-hence are the target of the study 
-here\footnote{The definition of ``loop-related'' in this paper is a little
-bit broader than earlier paper~\cite{SongOOPSLA2014}, which only considers
-43 problems as loop-related. }.
-More details can be found in previous papers that collected
-these bugs.
-
-\subsubsection{Assessment}
-\label{sec:study_ob}
-
-\comment{
-\begin{table*}[tb!]
-%\begin{adjustwidth}{-.5in}{-.5in}
-\small
-\centering
-{
-\begin{tabular}{|lcccccc|}
-\hline
-&Apache&Chrome&GCC&Mozilla&MySQL&Total\\
-\hline
-Total \# of loop bugs & 11 & 4 & 8 & 12 & 10 & 45 \\
-\hline
-\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
-&7&1&2&1&1&12\\
-\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
-&3&0&2&2&2&9\\
-\multicolumn{1}{|l}{ {\bf 0*} Resultness}
-&0&0&0&0&0&0\\
-\multicolumn{1}{|l}{ {\bf 0*1?} Resultness}
-&0&0&0&2&3&5\\
-\multicolumn{1}{|l}{{\bf [0$|$1]*} Resultness}
-&0&1&1&1&1&4\\
-\multicolumn{1}{|l}{{\bf 1*} Resultness}
-&1&2&3&6&3&15\\
-%&0&2&0&5&0&7&B(4)$|$S(3)\\
-%&1&0&3&1&3&8&\\
-  %MySQL15811 is moved from 1* to here; consider it as fixed by M
-%\hline
-%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
-%\multicolumn{1}{|l}{Not in above categories}
-\hline
-\end{tabular}
-}
-%\end{adjustwidth}
-\caption{Number of bugs in each root-cause category. 
-}
-\label{tab:root}
-\end{table*}
-}
-
-\comment{
-\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
-%For ranges 0-10, multiply by 10 by adding 0 after #1
-\begin{table}[tb!]
-%\begin{adjustwidth}{-.5in}{-.5in}
-\small
-\centering
-{
-\begin{tabular}{lcccccc}
-%\hline
-                                 &{\bf 0*}    & {\bf 0*1?} & {\bf [0$|$1]*}   & {\bf 1*} & {\bf C-I}  & {\bf C-L} \\
-%\hline
- B                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{4}  & \cca{4}     & \cca{4}   \\
-%\hline
- M                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{0}  & \cca{7}     & \cca{5}   \\
- S                               & \cca{0}    & \cca{1}    & \cca{4}          & \cca{4}  & \cca{0}     & \cca{0}   \\
- C                               & \cca{0}    & \cca{4}    & \cca{0}          & \cca{0}  & \cca{0}     & \cca{0}   \\
- O                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{7}  & \cca{1}     & \cca{0}   \\
-%\hline
-
-\end{tabular}
-}
-%\end{adjustwidth}
-\caption{Number of bugs fixed by each strategy:
-B(atching),  
-M(emoization), 
-S(kipping the loop),
-C(hange the data structure), and O(thers). 
-``C-I'': cross- iteration redundancy. 
-``C-L'': cross-loop redundancy. 
-}
-\label{tab:correlation}
-\end{table}
-}
-
-\paragraph{Coverage}
-As shown in Table \ref{tab:root}, 
-our taxonomy does cover all inefficient loops under study. 
-Resultless loops are about as common as redundant loops
-(24 vs. 21).
-Not surprisingly, 0* loops
-are rare in mature software. In fact, no bugs in this
-benchmark suite belong to this category.
-All other root-cause sub-categories are well represented.
-
-\paragraph{Actionability}
-As demonstrated in Table \ref{tab:root}, 
-the root-cause categories in our taxonomy are well correlated with
-fix strategies.
-This indicates that our taxonomy is actionable --- once the root cause
-is identified, developers roughly know how to fix the problem.
-For example, 
-almost all 0*1? resultless loops are fixed by data-structure changes;
-all [0$|$1]* resultless loops are
-fixed by conditionally skipping the loop;
-almost all redundant loops are fixed either by 
-memoization or batching. 
-In fact, as we will discuss later, simple analysis can tell whether 
-memoization or batching should be used to fix a redundant loop.
-The only problem is that there are no silver bullets for fixing 1* loops.
-%all inefficient loops with xx root cause are fixed by xxx.
-%xxx
-
-\paragraph{Generality}
-The root-cause categories in our taxonomy are designed to be 
-generic. Table \ref{tab:root} also shows that these categories 
-each appears in multiple
-application in our study. The only exception is $0^*$-resultless, which
-never appears.
-
-In summary, the study above informally demonstrates that our taxonomy
-is suitable to guide our design of \Tool.
-%chances to satisfy the coverage and accuracy requirements of performance 
-%diagnosis.
-%
-%TODO even for the other, there are things we could do ...
-
-\subsubsection{Caveats} 
-Just as previous empirical study work, 
-our empirical study above needs to be interpreted with our methodology in mind. 
-The performance bugs examined above cover a variety of applications, workload, 
-development environments and programming languages. 
-However, there are still uncovered cases, like distributed systems, 
-and scientific computation.
-
-Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
-on-line discussion to judge whether a bug report is about
-performance problems and whether 
-the performance problem under discussion is noticed and reported by users
-or not.
-We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
-whether the root-cause of a performance problem is related to loops or not.
-We do not intentionally ignore any aspect of loop-related performance problems. 
-Some loop-related performance problems may never be noticed by end users
-or never be fixed by developers, and hence skip our study. However,
-there are no conceivable ways to study them.
-
-\comment{
-We believe that the bugs in our study provide a representative sample of the 
-well-documented and
-fixed performance bugs that are user-perceived and loop-related in the studied 
-applications. 
-Since we did not set up the root-cause taxonomy to fit particular
-bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
-framework presented below will go beyond these sampled performance bugs. 
-}

### 2016-03-16 section/evaltax.tex
split study section. the benchmark study does not guide study, but evaluate study

\section{Evaluation of Taxonomy}
\label{sec:eval_taxonomy}

\input section/tab_root

\input section/tab_appbug

We quantitatively 
assess the coverage, actionability, and generality of our taxonomy presented
in Section \ref{sec:study} using
a set of
real-world inefficient loop problems collected by previous work
\cite{SongOOPSLA2014,PerfBug}.

\subsection{Methodology}

Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects, as 
shown in Table \ref{tab:app_bug}. Through a mix of random sampling and 
manual inspection, they 
found 65 performance problems that are perceived and reported by users. 
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study 
here\footnote{The definition of ``loop-related'' in this paper is a little
bit broader than earlier paper~\cite{SongOOPSLA2014}, which only considers
43 problems as loop-related. }.
More details can be found in previous papers that collected
these bugs.

\subsection{Assessment}
\label{sec:study_ob}

\comment{
\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{|lcccccc|}
\hline
&Apache&Chrome&GCC&Mozilla&MySQL&Total\\
\hline
Total \# of loop bugs & 11 & 4 & 8 & 12 & 10 & 45 \\
\hline
\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&12\\
\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&9\\
\multicolumn{1}{|l}{ {\bf 0*} Resultless}
&0&0&0&0&0&0\\
\multicolumn{1}{|l}{ {\bf 0*1?} Resultless}
&0&0&0&2&3&5\\
\multicolumn{1}{|l}{{\bf [0$|$1]*} Resultless}
&0&1&1&1&1&4\\
\multicolumn{1}{|l}{{\bf 1*} Resultless}
&1&2&3&6&3&15\\
%&0&2&0&5&0&7&B(4)$|$S(3)\\
%&1&0&3&1&3&8&\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
%\hline
%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
%\multicolumn{1}{|l}{Not in above categories}
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs in each root-cause category. 
}
\label{tab:root}
\end{table*}
}

\comment{
\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
%For ranges 0-10, multiply by 10 by adding 0 after #1
\begin{table}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lcccccc}
%\hline
                                 &{\bf 0*}    & {\bf 0*1?} & {\bf [0$|$1]*}   & {\bf 1*} & {\bf C-I}  & {\bf C-L} \\
%\hline
 B                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{4}  & \cca{4}     & \cca{4}   \\
%\hline
 M                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{0}  & \cca{7}     & \cca{5}   \\
 S                               & \cca{0}    & \cca{1}    & \cca{4}          & \cca{4}  & \cca{0}     & \cca{0}   \\
 C                               & \cca{0}    & \cca{4}    & \cca{0}          & \cca{0}  & \cca{0}     & \cca{0}   \\
 O                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{7}  & \cca{1}     & \cca{0}   \\
%\hline

\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs fixed by each strategy:
B(atching),  
M(emoization), 
S(kipping the loop),
C(hange the data structure), and O(thers). 
``C-I'': cross- iteration redundancy. 
``C-L'': cross-loop redundancy. 
}
\label{tab:correlation}
\end{table}
}

\paragraph{Coverage}
As shown in Table \ref{tab:root}, 
our taxonomy does cover all inefficient loops under study. 
Resultless loops are about as common as redundant loops
(24 vs. 21).
Not surprisingly, 0* loops
are rare in mature software. In fact, no bugs in this
benchmark suite belong to this category.
All other root-cause sub-categories are well represented.

\paragraph{Actionability}
As demonstrated in Table \ref{tab:root}, 
the root-cause categories in our taxonomy are well correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultless loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

\paragraph{Generality}
The root-cause categories in our taxonomy are designed to be 
generic. Table \ref{tab:root} also shows that these categories 
each appears in multiple
application in our study. The only exception is $0^*$-resultless, which
never appears.

In summary, the study above informally demonstrates that our taxonomy
is suitable to guide our design of \Tool.
%chances to satisfy the coverage and accuracy requirements of performance 
%diagnosis.
%
%TODO even for the other, there are things we could do ...

\subsection{Caveats} 
Just as previous empirical study work, 
our empirical study above needs to be interpreted with our methodology in mind. 
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are still uncovered cases, like distributed systems, 
and scientific computation.

Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
on-line discussion to judge whether a bug report is about
performance problems and whether 
the performance problem under discussion is noticed and reported by users
or not.
We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
whether the root-cause of a performance problem is related to loops or not.
We do not intentionally ignore any aspect of loop-related performance problems. 
Some loop-related performance problems may never be noticed by end users
or never be fixed by developers, and hence skip our study. However,
there are no conceivable ways to study them.

\comment{
We believe that the bugs in our study provide a representative sample of the 
well-documented and
fixed performance bugs that are user-perceived and loop-related in the studied 
applications. 
Since we did not set up the root-cause taxonomy to fit particular
bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
framework presented below will go beyond these sampled performance bugs. 
}

### 2016-03-17 section/1_under.tex
trying to make taxonomy presentation natural

@@
 \label{sec:study_resultless}
-A resultless loop spends a lot of time in computation without
-producing results useful after the loop.
-It is further categorized based on which loop iterations are
-(not) producing useful results.
+Resultless loops spend a lot of time in computation that does not
+produce results useful after the loop (i.e., computation without side effects).
+They can be further categorized to four sub-types 
+based on which part of the loop is
+(not) producing useful results. We explain these four sub-types below, 
+as well as
+how they can be fixed.
 
@@
 They are rare in mature software systems.
-They should simply be deleted from the program.
+
+{\textit{How to fix?}} This type of loops should simply be deleted from the program.
 %Question: dynamic or static?
@@
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
-\vspace{-0.05in}
 \caption{A resultless 0*1? bug in Mozilla}
@@
 tens of thousands of nodes and cause poor performance.
-The patch simply replaced the \texttt{script} list with a hash table.
+
+{\textit{How to fix?}}
+To make a linear search more efficient, it usually requires a data
+structure change. For example, 
+the patch for the bug in Figure \ref{fig:Mozilla347306}
+simply replaced the \texttt{script} list with a hash table.
 % This improve the performance by 52.60{\bf X}.
@@
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
-\vspace{-0.05in}
 \caption{A resultless [0$|$1]* bug in GCC }
@@
 
+{\textit{How to fix?}}
+The patch shown in Figure \ref{fig:GCC46401} reflects the typical fix
+strategy for this type of inefficient loops. The developers should 
+think about what exactly is the condition for the loop to produce
+results, and use that condition to skip the whole loop
+whenever possible.
+
 \comment{
@@
 
+{\textit{How to fix?}}
+As we can see, a deep understanding of software semantics is required
+to understand the inefficiency root cause of these loops.
+Similarly, the fix strategies for these loops would vary from case to case.
+%At high level, the patch often involves skip some computation that produces
+%side effects that are useless due to semantic reasons.
+
 \subsection{Redundant loops}
@@
 Redundant loops spend a lot of time in repeating computation that is already
-conducted. They are further categorized below based on their redundancy unit.
+conducted. They can be further categorized to two sub-types
+based on which part of the loop is the unit of redundancy.
 
@@
 
-\begin{figure}
-\centering
-\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-     morekeywords={+},keepspaces=true}
-  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
-\vspace{-0.05in}
-\caption{A cross-loop redundant bug in Mozilla }
-\label{fig:Mozilla477564}
-\end{figure}
-
 {\textbf{Cross-iteration Redundancy}}:
@@
 
-This type of inefficiency is often fixed by memoization or batching, depending
-on whether the redundancy involves I/O operations.
+{\textit{How to fix?}}
+Intuitively, most redundancy problems can be fixed through memoization or
+batching --- either caching the earlier computation results and skip
+some of the following iterations; or combining multiple iterations' work
+together.
+
 For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
@@
 earlier instance of the same loop.
-Developers often fix this type of inefficiency problems through memoization:
-caching the earlier computation results and skip following redundant loops.
+
+{\textit{How to fix?}}
+Just like that in cross-iteration redundancy, memoization and batching
+are the typical fix strategies for this type of redundancy problems ---
+caching the earlier computation results and skip following redundant loops;
+or combining multiple loop instances together to avoid or alleviate redundancy.
+
 Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
@@
 saved count value of the nearest previous sibling with the same name and URI.
+
+\begin{figure}
+\centering
+\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+     morekeywords={+},keepspaces=true}
+  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
+\caption{A cross-loop redundant bug in Mozilla }
+\label{fig:Mozilla477564}
+\end{figure}
+
+\subsection{Discussion}
+Coverage, actionability, and generality are the principles behind our taxonomy
+design. Intuitively, the categories above cover a lot of common inefficient
+loop problems; each sub-category is concrete enough to guide the design of a
+failure diagnosis tool; none of the categories above involve any application
+specific knowledges or heuristics. We will further assess our taxonomy
+through the design of \Tool (Section \ref{sec:design}) and 
+real-world bug study (Section \ref{sec:eval_taxonomy}).
+
+Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.
+For example, some loops may be vulnerable to false sharing problems or lock
+contention problems, which are out of the scope of our taxonomy.

### 2016-03-17 section/3_redundancy.tex
trying to make taxonomy presentation natural

@@
 \label{sec:redundant_fix}
+It is difficult to directly produce patches with correctness guarantee for
+all inefficient loops.
+What \Tool aims to do is to provide fix-strategy suggestion to developers.
+This process is straightforward following our taxonomy discussion in 
+Section \ref{sec:study}, as there is often one or two natural fix strategies for
+each sub-category of root causes.
+
+xxxTODOxxx
+
 As discussed in Section \ref{sec:tax_study}, extra analysis is needed to

### 2016-03-17 section/3_redundancy.tex
finish revision before section 5

--- 2015-11-20 section/3_redundancy.tex
@@
 \label{sec:redundant_fix}
-As discussed in Section \ref{sec:tax_study}, extra analysis is needed to
-decide whether batching or memoization should be suggested to fix a 
-loop that conducts redundant computation.
+\Tool suggests how to fix an inefficient loop to developers.
+This process is straightforward following our taxonomy discussion in 
+Section \ref{sec:study}, as there is often only one or two natural fix 
+strategies for each sub-category of root causes.
 
-For cross-iteration redundancy, batching is often used for
-I/O operations.
-Therefore, we treat I/O related redundancy separately.
-When the only side effect of a loop is I/O operations
-and the same statement(s) is executed in every loop iteration, we report this
-as I/O related redundancy problem and suggest batching as a potential fix
-strategy.
+Once a loop is identified as \emph{resultless}, \Tool will suggest
+the loop to be completely deleted, in case of 0$^*$ resultless, or
+conditionally skipped, in case of [0$|$1]*; \Tool will suggest a 
+data-structure change in case of 0*1? loops.
+
+When a loop is identified as \emph{redundant}, \Tool conducts
+extra analysis to
+decide whether batching or memoization should be suggested to fix the
+redundancy problem.
+
+For cross-iteration redundancy, \Tool suggests batching if the
+redundancy is related to I/O operations and suggests memoization otherwise.
+Specifically, 
+when the only side effect of a loop is I/O operations
+and the same statement(s) is executed in every loop iteration, \Tool reports 
+this
+as an I/O related redundancy problem and suggests batching as a potential fix
+strategy. Otherwise, \Tool suggests memoization.
 
 For cross-loop redundancy, whether to use memoization or batching often
-depends on which strategy is cheaper. \Tool uses a simple
+depends on which strategy is cheaper.
+\Tool uses a simple
 heuristic. If 
@@
 hence batching is suggested.
+
+In addition to the above high-level fix strategies, \Tool can also provide some 
+detailed information to help developers design the patch.
+For example, in case of memoization fix strategy,
+since \Tool knows what exactly are the memory reads that return the same values
+again and again, it can help decide what to memoize; in case of
+I/O-related batching, \Tool points out the exact I/O operations that should
+be considered batching; and so on. 
+Generating the exact patch is out of the scope of \Tool.
 

### 2016-03-17 section/evaltax.tex
trying to make taxonomy presentation natural
finish revision before section 5

@@
 
+\input section/tab_appbug
 \input section/tab_root
 
-\input section/tab_appbug
-
-We quantitatively 
-assess the coverage, actionability, and generality of our taxonomy presented
-in Section \ref{sec:study} using
+The root-cause taxonomy presented in Section \ref{sec:study} is the foundation
+of \Tool. In this section,
+we quantitatively 
+assess the coverage, actionability, and generality of our taxonomy using
 a set of
@@
 memoization or batching. 
-In fact, as we will discuss later, simple analysis can tell whether 
-memoization or batching should be used to fix a redundant loop.
 The only problem is that there are no silver bullets for fixing 1* loops.
@@
 \subsection{Caveats} 
-Just as previous empirical study work, 
-our empirical study above needs to be interpreted with our methodology in mind. 
+We do not intend to overly generalize the evaluation results above.
 The performance bugs examined above cover a variety of applications, workload, 

### 2016-03-18 section/5_exper.tex
linhai, pls fill XXX

@@
-\section{Evaluation}
+\section{Evaluation of \Tool}
 \label{sec:experiment}
@@
 
-\begin{table}
-  \centering
-  \small
-  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
-  \newcommand{\No}[0]{-}
-  \begin{tabular}{lcccc}
-    \toprule
-   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf RootCause}  & {\bf Fix}\\
-   \midrule
-   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
-   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
-   Mozilla490742         &  -             & JS                     &  C-I         & B       \\
-   Mozilla35294          &  -             & C++                    &  C-L         & B        \\ 
-   Mozilla477564         &  -             & JS                     &  C-L         & M       \\
-   \midrule 
-   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
-   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
-   \midrule    
-   Apache32546           &  -             & Java                   &  C-I         & B  \\
-   Apache37184           &  -             & Java                   &  C-I         & M  \\
-   Apache29742           &  -             & Java                   &  C-L         & B \\ 
-   Apache34464           &  -             & Java                   &  C-L         & M  \\
-   Apache47223           &  -             & Java                   &  C-L         & B \\
-   \midrule
-   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
-   GCC1687               & 2099            & C                      &  C-I         & M \\
-   GCC27733              & 3217            & C                      &  C-I         & M \\
-   GCC8805               & 2538            & C                      &  C-L         & B\\
-   GCC21430              & 3844            & C                      &  C-L         & M \\
-   GCC12322              & 2341            & C                      &  1*          & S\\
-\bottomrule
-   \end{tabular}
-  %\nocaptionrule
-  \caption{Benchmark information.
-  (-: benchmarks extracted from real-world applications.
-  ``C-I'': cross-iteration redundancy.
-  ``C-L'': cross-loop redundancy.
-  C, B, M, S: fix strategies as discussed in
-  Table \ref{tab:root}.
-  ) 
- }
-  \label{tab:benchmarks}
-\end{table}
+\input section/tab_benchmarks
 
@@
 \paragraph{Benchmarks}
-We use 18 out of the 45 bugs listed in Table \ref{tab:root} as our 
-evaluation benchmarks. Among these 18, seven are extracted from Java or JavaScript
+Note that \Tool is a tool that helps diagnose performance problems that
+have already manifested, not a detection tool that can help predict not-yet-manifested
+problems. Consequently, our benchmarks are performance problems that have already
+happened in real world, and we will reproduce these problems to evaluate \Tool.
+To conduct a thorough evaluation, we use
+benchmarks from two sources.
+
+First, we evaluate \Tool on 18 out of the 45 bugs listed in Table \ref{tab:root}. 
+Among these 18, seven are extracted from Java or JavaScript
 programs and re-implemented in C++, as \Tool currently only handles C/C++
@@
 %statistical performance debugging work~\cite{SongOOPSLA2014}.
-The remaining bugs listed in Table \ref{tab:root} are much more difficult to
-use as benchmarks, 
+The extraction is conducted by XXX.
+We did not use the remaining 27 bugs listed in Table \ref{tab:root}
+as benchmarks, 
 either because they depend on special hardware/software environment
-or because they involve too complex data structures to extract. 
-Overall, these 18 bugs cover a wide variety of performance root causes, as 
+or because they involve too complex data structures to extract XXX. 
+Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
 shown in Table~\ref{tab:benchmarks}.
+
+Second, we evaluate \Tool on 21 out of the xx bugs in the benchmark
+suite of Toddler \cite{Alabama}.
+All of these bugs come from Java programs. We extract XXX (how did you
+extract exactly?) and re-implement in C++. Each extracted benchmark 
+contains 4--5 loops (how come you always have 4--5 loops??XXX). 
+Note that, Toddler focuses on inefficient nested loops, and its
+benchmark bugs only cover two types of inefficiency root causes,
+as shown in Table \ref{tab:benchmarks}.
+We use Toddler benchmark suite because it provides a larget set of
+repeatable inefficient loop problems.
 
@@
 %of suspicious loops.
+XXX (what can we say about Toddler benchmark set here?)
 
-\begin{table}
-  \centering
-  \small
-  \newcommand{\Yes}[0]{\checkmark}
-  \newcommand{\No}[0]{-}
-  \begin{tabular}{lcc}
-    \toprule
-                            	&  {\bf Reported}             &{\bf Fix }                     \\
-   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
-   \midrule
-   Mozilla347306                & \Yes                        & \Yes                                          \\
-   Mozilla416628                & \Yes                        & \Yes                                         \\
-   Mozilla490742                & \Yes                        & \Yes                                             \\
-   Mozilla35294                 & \Yes                          & \Yes                                              \\ 
-   Mozilla477564                & \Yes                          & \Yes                                            \\
-   \midrule 
-   MySQL27287                   & \Yes                          & \ding{55}                                         \\
-   MySQL15811                   & \Yes                          & \Yes                                      \\ 
-   \midrule    
-   Apache32546                  & \Yes                          & \Yes                                      \\
-   Apache37184                  & \Yes                          & \Yes                                        \\
-   Apache29742                  & \Yes                          & \Yes                                       \\ 
-   Apache34464                  & \Yes                          & \Yes                                        \\
-   Apache47223                  & \Yes                          & \Yes                                       \\
-   \midrule
-   GCC46401                     & \Yes                     & \Yes                                      \\
-   GCC1687                      & \Yes                          & \Yes                                     \\
-   GCC27733                     & \Yes                          & \Yes                                     \\
-   GCC8805                      & \Yes                          & \Yes                                  \\
-   GCC21430                     & \Yes                          & \Yes                                     \\
-   GCC12322                     & \Yes                         & \ding{55}                                   \\
-\bottomrule
-   \end{tabular}
-  %\nocaptionrule
-\vspace{-0.1in}
-  \caption{Coverage Results.}
-\vspace{-0.1in}
-  \label{tab:cover}
-\end{table}
+\input section/tab_cover
 
@@
 Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
-\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
+\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
 suggests fix strategies that exactly match what developers took in practice
-for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
-the fix strategy that developers used. For MySQL\#27287, the root-cause loop
+for 33 out of \allbugs cases.
+
+The six cases where the fix strategy suggested by \Tool does not match that of 
+developers fall into three categories.
+First, the fix strategy taken by developers is a subset of what suggested by 
+\Tool.
+For MySQL\#27287 and Apache\#53622, the root-cause loop
 is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
 data structures and memoization as fix strategies. In practice, the developers
-find a new data structure that can eliminate both root causes.
+only changed the data structure, which eliminated both types of inefficiency,
+in case of MySQL\#27287, or the main type of inefficiency, in case of Apache\#53622.
+
+Second, the fix strategy taken by developers is a superset of what suggested by
+\Tool.
+In Collections bugs \#407, \#408, and \#425, XXX.
+
+Third, \Tool cannot suggest fix strategy for 1* loops.
 For GCC\#12322, \Tool correctly tells that the loop under study
@@
 
-\begin{table}
-  \centering
-  \small
-  \newcommand{\Yes}[0]{\checkmark}
-  \newcommand{\No}[0]{-}
-  \begin{tabular}{lcccccc}
-    \toprule
-   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
-   \midrule
-   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
-   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
-   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
-   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
-   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
-   \midrule 
-   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
-   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
-   \midrule    
-   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
-   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
-   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
-   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
-   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
-   \midrule
-   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
-   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
-   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
-   GCC8805               &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
-   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
-   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
-\bottomrule
-   \end{tabular}
-  %\nocaptionrule
-\vspace{-0.1in}
-  \caption{False positives of \Tool for top 5 loops reported by 
-    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
-}
-  \label{tab:top5}
-\end{table}
+\input section/tab_top5
 
 As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
-false positive and 14 benign false positives for all the top 5 loops.
+false positive and 23 benign false positives for all the top 5 loops
+of the \allbugs benchmarks.
 
@@
 performance problem perceived by the users. This happens to 11 out of the
-13 benign cases. In fact, this is not really a problem for \Tool in 
+13 benign cases (XXX subject to change XXX). 
+In fact, this is not really a problem for \Tool in 
 real usage scenarios, because statistical debugging can accurately
@@
 problems.
-The remaining two cases happen when fixing the 
+Two cases happen when fixing the 
 identified redundant/resultless problems
 are very difficult and hence developers decide not to fix them.
+The remaining cases XXX.
 
 The accuracy of \Tool benefits from its run-time analysis.
-For example, there are 7 benchmarks in total that each contains
+For example, there are 7 (XXX to change XXX) benchmarks in total that each contains
 a loop that generates side effect only
@@
 \Tool run-time counts the total number of iterations and
-correctly identifies 3 of them as truly inefficient and severe enough
+correctly identifies 3 (XXX to change XXX) of them as truly inefficient and severe enough
 to cause the corresponding performance problem.
@@
 
-\comment{
-\begin{table}
-  \centering
-  \scriptsize
-  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
-  \newcommand{\No}[0]{-}
-  \begin{tabular}{lccccc}
-    \toprule
-                       & {\bf Resultless} &  \multicolumn{2}{c}{\bf C-L R. } & \multicolumn{2}{c}{\bf C-I R.}\\
-      \cmidrule(lr){3-4}    
-      \cmidrule(lr){5-6}   
-     {\bf BugID}       &                & Not               &  S.+O.            & Not                & S.+O.  \\
-     \midrule
-     Mozilla347306     & 1.07\%         & 303.37{\bf X}     &  22.40\%       & 467.74{\bf X}         & 10.17\%      \\
-     Mozilla416628     & 0.80\%         & 56.51{\bf X}      &  4.10\%        & 84.6{\bf X}           & 2.99\%\\
-     \midrule
-     MySQL27287        & $sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
-     MySQL15811        &  -             & 226.04{\bf X}     &  0.03\%        & 423.44{\bf X}         & - \\
-     \midrule
-      GCC46401         & 3.12\%         & 20.07{\bf X}      &  3.80\%        & 37.44{\bf X}          & 5.95\%\\ 
-      GCC1687          & -              & /                 &  /             & 141.29{\bf X}         & $\sim$0 \\
-      GCC27733         & $\sim$0        & /                 &  /             & 16.41{\bf X}          & 4.73\%         \\
-      GCC8805          & -              & 1.22{\bf X}       & $\sim$0        & 2.52{\bf X}           & $\sim$0\\
-      GCC21430         & -              & 106.20{\bf X}     & 5.46\%         & 158.89{\bf X}         & 0.69\%\\
-      GCC12322         & -              & 20.07{\bf X}      & 1.75\%         & 37.44{\bf X}          & $\sim$0\\
-  \bottomrule
-   \end{tabular}
-  %\nocaptionrule
-  \caption{Run-time overhead of applying \Tool to the buggy loop. 
-    Only performance results from non-extracted benchmarks are shown here. 
-  Not: not applying the performance optimization in \Tool.
-  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
-  /: not applicable. }
-  \label{tab:performance}
-\end{table}
-}
-
 As shown in Table \ref{tab:performance}, 
@@
 in cross-loop redundancy analysis,
+among all the benchmarks in Table \ref{tab:performance},
 Mozilla\#347306 still incurs the largest overhead (0.49\%). 
@@
 in cross-iteration redundancy analysis,
+among all the benchmarks in Table \ref{tab:performance},
 Mozilla\#347306 has the largest overhead (4.47\%). 
@@
 loop checking. 
+XXX
 
@@
 loops is usually obvious, based on these rates.
+
+\subsection{Comparison with other tools}
+XXXXXX

### 2016-03-19 section/5_exper.tex
check in template changing and some content in experiments

@@
 %statistical performance debugging work~\cite{SongOOPSLA2014}.
-The extraction is conducted by XXX.
+%The extraction is conducted by XXX.
+We extract the original data structures and caller-callees, 
+and translate them into C++ programs, following the original data flow and control flow dependence. 
+We design unit test inputs based on inputs in bug reports and our understanding to run our re-implemented codes.  
 We did not use the remaining 27 bugs listed in Table \ref{tab:root}
@@
 either because they depend on special hardware/software environment
-or because they involve too complex data structures to extract XXX. 
+or because they involve too complex data structures to extract. 
+For example, some bugs can only be triggered on Windows, and some bugs depend on .Net libraries. 
+For example, we have bugs related to GUI widgets, and it is too complex to re-implement these GUI widgets. 
+We also have bugs, in which buggy loops traverse graphs. 
+Without repeating these bugs, it is too difficult to figure out graph structures just through code reading.  
 Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
@@
 
-Second, we evaluate \Tool on 21 out of the xx bugs in the benchmark
-suite of Toddler \cite{Alabama}.
-All of these bugs come from Java programs. We extract XXX (how did you
-extract exactly?) and re-implement in C++. Each extracted benchmark 
-contains 4--5 loops (how come you always have 4--5 loops??XXX). 
+Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama}.
+We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
+All of these bugs come from Java programs. 
+%We extract XXX (how did you
+%extract exactly?) and re-implement in C++. Each extracted benchmark 
+%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
+All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
+We re-implement these basic data structures following the recent version of openjdk. 
+We re-implement the buggy codes and test inputs in the bug reports, 
+following the original data flow and control flow dependence. 
+For two benchmarks, there are only 4 loops in our re-implemented versions. For all other benchmarks, there are no less than 5 loops. 
 Note that, Toddler focuses on inefficient nested loops, and its
@@
 as shown in Table \ref{tab:benchmarks}.
-We use Toddler benchmark suite because it provides a larget set of
+We use Toddler benchmark suite because it provides a large set of
 repeatable inefficient loop problems.
@@
 %of suspicious loops.
-XXX (what can we say about Toddler benchmark set here?)
+%XXX (what can we say about Toddler benchmark set here?)
+For all benchmarks from Toddler project, 
+statistical debugging ranks the real root-cause loop as Top 1 or Top 2 (for cases where there are two root-cause loops). 
+During our accuracy experiments, we will apply LDoctor to top 5 loops identified by statistical debugging. 
+For some re-implemented bugs, there may be less than 5 loops returned by statistical debugging. 
+The number of loops we analyze for the first benchmark set is 64, and the number of loops we analyze for Toddler benchmark set is 103.
 
@@
 \Tool.
-For MySQL\#27287 and Apache\#53622, the root-cause loop
+For MySQL\#27287, the root-cause loop
 is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
@@
 only changed the data structure, which eliminated both types of inefficiency,
-in case of MySQL\#27287, or the main type of inefficiency, in case of Apache\#53622.
+in case of MySQL\#27287. 
+For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? Inefficient. 
+\Tool suggests batching and changing data structure respectively. 
+In practice, developers only fix the main root cause loop, by using changing data structure.
 

### 2016-03-19 section/5_exper.tex
finish section 5.2

--- 2016-03-18 section/5_exper.tex
@@
 %statistical performance debugging work~\cite{SongOOPSLA2014}.
-The extraction is conducted by XXX.
+%The extraction is conducted by XXX.
+{\color{red} We extract the original data structures and caller-callees, 
+and translate them into C++ programs, following the original data flow and control flow dependence. 
+We design unit test inputs based on inputs in bug reports and our understanding to run our re-implemented codes.}  
 We did not use the remaining 27 bugs listed in Table \ref{tab:root}
@@
 either because they depend on special hardware/software environment
-or because they involve too complex data structures to extract XXX. 
+or because they involve too complex data structures to extract. 
+{\color{red} For example, some bugs can only be triggered on Windows, and some bugs depend on .Net libraries. 
+For example, we have bugs related to GUI widgets, and it is too complex to re-implement these GUI widgets. 
+And we also have bugs, in which buggy loops traverse graphs. 
+Without repeating these bugs, it is too difficult to figure out graph structures just through reading codes. }  
 Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
@@
 
-Second, we evaluate \Tool on 21 out of the xx bugs in the benchmark
-suite of Toddler \cite{Alabama}.
-All of these bugs come from Java programs. We extract XXX (how did you
-extract exactly?) and re-implement in C++. Each extracted benchmark 
-contains 4--5 loops (how come you always have 4--5 loops??XXX). 
+Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
+{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
+All of these bugs come from Java programs. 
+%We extract XXX (how did you
+%extract exactly?) and re-implement in C++. Each extracted benchmark 
+%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
+All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
+We re-implement these basic data structures following one recent version of openjdk. 
+We re-implement the buggy codes and test inputs in the bug reports, 
+following the original data flow and control flow dependence. 
+For two benchmarks, there are only 4 loops in our re-implemented versions. 
+For all other benchmarks, there are no less than 5 loops.} 
 Note that, Toddler focuses on inefficient nested loops, and its
@@
 one or a few suspicious loops for \Tool to analyze.
-For 14 out of the 18 benchmarks, statistical debugging identifies the
+For 14 out of the 18 benchmarks {\color{red} in the first benchmark set}, statistical debugging identifies the
 real root-cause loop as the most suspicious loop. For the remaining
@@
 %of suspicious loops.
-XXX (what can we say about Toddler benchmark set here?)
+%XXX (what can we say about Toddler benchmark set here?)
+{\color{red} For all benchmarks from Toddler project, 
+statistical debugging ranks the real root-cause loop as the most suspicious loop, 
+or the two most suspicious loops (for cases where there are two root-cause loops). }
 
@@
 \Tool.
-For MySQL\#27287 and Apache\#53622, the root-cause loop
+{\color{red} For MySQL\#27287, the root-cause loop
 is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
 data structures and memoization as fix strategies. In practice, the developers
-only changed the data structure, which eliminated both types of inefficiency,
-in case of MySQL\#27287, or the main type of inefficiency, in case of Apache\#53622.
+only changed the data structure, which eliminated both types of inefficiency. 
+For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? inefficient. 
+\Tool suggests batching and changing data structure, respectively. 
+In practice, developers only fix the main root cause loop, by using changing data structure.}
 
@@
 \Tool.
-In Collections bugs \#407, \#408, and \#425, XXX.
+{\color{red} In Collections bugs \#407, \#408, and \#425, there is a HashSet and ArrayList containing the same set of data. 
+The buggy codes keep trying to remove elements from the HashSet and the ArrayList. 
+The buggy loops search elements to be deleted on the ArrayList, which are 0*1? inefficient in buggy runs. 
+Under buggy inputs, all elements to be deleted are not contained in the HashSet and ArrayList. 
+The return value of removing elements from HashSet can indicate whether elements are really removed. 
+In the patch, an extra check is added to use the return value of removing elements from HashSet 
+to decide whether to skip removing elements from ArrayList. 
+We think in the patch developers change the usage of HashSet to skip removing elements from ArrayList. }
 

### 2016-03-20 section/5_exper.tex
check in comparison with other techniques and explanation why we only use 21 bugs from Toddler

@@
 
-Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
-{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
-All of these bugs come from Java programs. 
+%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
+%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
+%All of these bugs come from Java programs. 
 %We extract XXX (how did you
@@
 %contains 4--5 loops (how come you always have 4--5 loops??XXX). 
+{\color{red}
+Second, we evaluate \Tool on bugs from Toddler~\cite{Alabama, toddlerbuglist} project.
+Toddler project provides the bug-triggering inputs and detailed explanation
+for 21 performance bugs that have been fixed by developers. We evaluate \Tool on all these 21 bugs.
+All of these bugs come from Java programs.
 All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
@@
 For two benchmarks, there are only 4 loops in our re-implemented versions. 
-For all other benchmarks, there are no less than 5 loops.} 
+For all other benchmarks, there are no less than 5 loops.
 Note that, Toddler focuses on inefficient nested loops, and its
@@
 repeatable inefficient loop problems. 
+}
 
@@
 As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
-false positive and 23 benign false positives for all the top 5 loops
+false positive and 22 benign false positives for all the top 5 loops
 of the \allbugs benchmarks.
@@
 The main reason is that they are not the main contributor to the 
-performance problem perceived by the users. This happens to 11 out of the
-13 benign cases (XXX subject to change XXX). 
+performance problem perceived by the users. {\color{red} This happens to 20 out of the
+22 benign cases.} % 11 out of 13 in the first benchmark set 
 In fact, this is not really a problem for \Tool in 
@@
 are very difficult and hence developers decide not to fix them.
-The remaining cases XXX.
 
 The accuracy of \Tool benefits from its run-time analysis.
-For example, there are 7 (XXX to change XXX) benchmarks in total that each contains
+{\color{red} For example, there are 26 % 7 in the first benchmark set
+benchmarks in total that each contains
 a loop that generates side effect only
@@
 \Tool run-time counts the total number of iterations and
-correctly identifies 3 (XXX to change XXX) of them as truly inefficient and severe enough
+correctly identifies 21 %3 in the first benchmark set 
+of them as truly inefficient and severe enough
 to cause the corresponding performance problem.
+}
 
@@
 loop checking. 
-XXX
+%XXX
 
@@
 \subsection{Comparison with other tools}
-XXXXXX
+
+{\color{red}
+\cite{Alabama, CARAMEL, IsilDillig.PLDI15} are most recent performance bug detection techniques. 
+These techniques aim to find previously unknown performance bugs inside programs. 
+Compared with diagnosis techniques, they do not consider real-world workload, 
+and they are likely to report performance bugs without user-perceived symptoms.
+
+Toddler~\cite{Alabama} tries to identify redundant computation through monitoring repetitive memory access patterns. 
+21 out of 45 bugs in our benchmark set can be detected by Toddler, 
+and 12 out of 18 bugs used in our evaluation can be detected by Toddler. 
+All these bugs contain a loop traversing the same data structure many times, 
+including all cross-loop redundant bugs and part of resultless bugs. 
+Except for cross-loop redundant bugs, Toddler does not provide more information than fault localization. 
+Compared with LDoctor, Toddler will incur a large runtime overhead, 
+because it monitors all memory read instructions, 
+and Toddler will report more false positives, because our cross-loop redundancy algorithm is more strict.
+
+Caramel~\cite{CARAMEL} can statically detect loops with Cond-Break Fix. 
+Caramel cannot detect any bug in our benchmark set, 
+and Caramel cannot detect any bugs from Toddler benchmark set either. 
+Depending on the dynamic workload, bugs detected by caramel can be identified as resultless loops or missed by LDoctor.
+
+CLARITY~\cite{IsilDillig.PLDI15} can statically detect redundant traversal bugs. 
+Compared with Toddler, the traversed data structures are not changed across different instances of the buggy loop. 
+CLARITY can detect 6 out of 45 bugs in benchmark set, and can detect 5 out of 18 bugs evaluated in our experiment. 
+CLARITY can detect 14 out of 21 bugs in TODDLER benchmark set used in our experiment, 
+and all these bugs belong to RetainAll and ContainAll cases discussed in~\cite{IsilDillig.PLDI15}.
+}

### 2016-03-22 section/5_exper.tex
rough pass of results

--- 2016-03-19 section/5_exper.tex
@@
 
-First, we evaluate \Tool on 18 out of the 45 bugs listed in Table \ref{tab:root}. 
+First, we evaluate \Tool on all bugs, 18 in total, that we can reproduce 
+among the 45 bugs listed in Table \ref{tab:root}. 
 Among these 18, seven are extracted from Java or JavaScript
 programs and re-implemented in C++, as \Tool currently only handles C/C++
-programs; one is extracted from a very old version of Mozilla.
+programs; one is extracted from a very old version of Mozilla that can no longer be
+compiled as it is.
 %These 18 bugs include all the benchmarks used in the recent
@@
 %The extraction is conducted by XXX.
-We extract the original data structures and caller-callees, 
-and translate them into C++ programs, following the original data flow and control flow dependence. 
-We design unit test inputs based on inputs in bug reports and our understanding to run our re-implemented codes.  
-We did not use the remaining 27 bugs listed in Table \ref{tab:root}
-as benchmarks, 
-either because they depend on special hardware/software environment
-or because they involve too complex data structures to extract. 
-For example, some bugs can only be triggered on Windows, and some bugs depend on .Net libraries. 
-For example, we have bugs related to GUI widgets, and it is too complex to re-implement these GUI widgets. 
-We also have bugs, in which buggy loops traverse graphs. 
-Without repeating these bugs, it is too difficult to figure out graph structures just through code reading.  
+When we extract code, we try our best to keep all bug-related data structures,
+caller functions, and callee functions intact, and re-implement them in C++, 
+following the original data flow and control flow. For these extracted benchmarks, 
+we design bug-triggering inputs for them based on the bug-triggering inputs in 
+the original bug reports and our understanding about how original program inputs
+map to the inputs of our re-implemented programs.
 Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
 shown in Table~\ref{tab:benchmarks}. 
+We will refer to this set of bugs as our \emph{general} benchmark suite.
 
-Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama}.
-We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
-All of these bugs come from Java programs. 
+Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
+listed in Table \ref{tab:root}, but they are too difficult to be reproduced
+on our machines.
+First, they all depend on 
+special hardware/software environment that our machine is not equipped with.
+For example, some bugs can only be triggered on Windows, and some bugs depend on 
+.Net libraries. 
+Furthermore, the bug-related code for these 27 cases
+cannot be easily extracted or reimplemented, as we did for the eight 
+benchmarks mentioned above. 
+For example, some bugs are related to GUI widgets, which are too complicated to 
+re-implement or emulate. As another example, some bugs' inefficient 
+loops traverse big graphs. Although we can extract the buggy code regions, it is 
+too difficult to figure out the bug-triggering inputs
+(i.e., the graphs) without reproducing the original bugs.
+
+%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
+%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
+%All of these bugs come from Java programs. 
 %We extract XXX (how did you
@@
 %contains 4--5 loops (how come you always have 4--5 loops??XXX). 
-All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
-We re-implement these basic data structures following the recent version of openjdk. 
-We re-implement the buggy codes and test inputs in the bug reports, 
-following the original data flow and control flow dependence. 
-For two benchmarks, there are only 4 loops in our re-implemented versions. For all other benchmarks, there are no less than 5 loops. 
-Note that, Toddler focuses on inefficient nested loops, and its
+Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
+Toddler project provides the bug-triggering inputs and detailed explanation
+for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
+we evaluate \Tool on \emph{all} of these 21 bugs.
+Due to the focus of Toddler, all of these bugs 
+are related to misusing basic data structures in Java, like ArrayList, HashSet, 
+HashMap, and LinkedList. We extract these bugs and re-implemented them in 
+C/C++, following the procedure discussed above. In doing so,
+we also re-implement basic Java data structures following a recent version of 
+\texttt{openjdk}. At the end, each extracted benchmark contains at least five
+loops, except for two cases where only 4 loops exist in the extracted version. 
+Note that, Toddler focuses on inefficient nested loops, and hence its
 benchmark bugs only cover two types of inefficiency root causes,
 as shown in Table \ref{tab:benchmarks}.
-We use Toddler benchmark suite because it provides a large set of
-repeatable inefficient loop problems.
+
+We use Toddler benchmark suite for two reasons.
+First, it was set up for completely different reasons and methodology from our
+\emph{general} benchmark suite,
+and hence can well complement the latter suite.
+Second, it provides the largest set of 
+repeatable inefficient loop problems that we can find.
 
@@
 one or a few suspicious loops for \Tool to analyze.
-For 14 out of the 18 benchmarks, statistical debugging identifies the
-real root-cause loop as the most suspicious loop. For the remaining
-benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
+For all but four benchmarks, statistical debugging identifies the
+real root-cause loop as the most suspicious loop. For the remaining four
+benchmarks, which all come from Table \ref{tab:root},
+the real root-cause loops are ranked number 2, 2, 4, and 10.
 %Overall, we believe future tools can accurately identify the most one or a couple
@@
 %XXX (what can we say about Toddler benchmark set here?)
-For all benchmarks from Toddler project, 
-statistical debugging ranks the real root-cause loop as Top 1 or Top 2 (for cases where there are two root-cause loops). 
-During our accuracy experiments, we will apply LDoctor to top 5 loops identified by statistical debugging. 
-For some re-implemented bugs, there may be less than 5 loops returned by statistical debugging. 
-The number of loops we analyze for the first benchmark set is 64, and the number of loops we analyze for Toddler benchmark set is 103.
 
@@
 \Tool.
-For MySQL\#27287, the root-cause loop
-is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
+For MySQL\#27287 and Apache\#53622, the root-cause loops contain both
+cross-loop redundancy and 0*1? inefficiency. \Tool suggests both changing
 data structures and memoization as fix strategies. In practice, the developers
-only changed the data structure, which eliminated both types of inefficiency,
-in case of MySQL\#27287. 
-For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? Inefficient. 
-\Tool suggests batching and changing data structure respectively. 
-In practice, developers only fix the main root cause loop, by using changing data structure.
+acknowledge both types of inefficiencies, but the patches
+only changed the data structures, which eliminated both types of inefficiencies 
+in case of MySQL\#27287 and left the cross-loop redundancy unsolved in
+Apache\#53622. 
+%For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? inefficient. 
+%\Tool suggests batching and changing data structure, respectively. 
+%In practice, developers only fix the main root cause loop, by using changing data structure.}
 
-Second, the fix strategy taken by developers is a superset of what suggested by
-\Tool.
-In Collections bugs \#407, \#408, and \#425, XXX.
+Second, the fix strategy taken by developers is related but not exactly the same as
+what suggested by \Tool.
+The root-cause loops in 
+Collections bugs \#407, \#408, and \#425 all conduct frequent linear searches in arrays.
+\Tool suggests data-structure changes for these three cases. Developers' patches 
+still keep the original data structure and the original buggy loop, but they
+did use hash-sets, which contain the same content as the arrays do,
+to help conditionally skip the loops.
 
@@
 The main reason is that they are not the main contributor to the 
-performance problem perceived by the users. This happens to 11 out of the
-13 benign cases (XXX subject to change XXX). 
+performance problem perceived by the users. This happens to 20 out of the
+22 benign cases. % 11 out of 13 in the first benchmark set 
 In fact, this is not really a problem for \Tool in 
@@
 are very difficult and hence developers decide not to fix them.
-The remaining cases XXX.
 
 The accuracy of \Tool benefits from its run-time analysis.
-For example, there are 7 (XXX to change XXX) benchmarks in total that each contains
-a loop that generates side effect only
-in its last iteration. Without run-time information, \Tool would judge
+%{\color{red} For example, there are 26 
+For example, our run-time analysis has correctly pruned out 24 false positives
+in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
+top-5 suspicious loops in one of our benchmarks; it only generates side effect
+in its last iteration, and hence is identified as by \Tool static analysis. 
+Without run-time information, \Tool would judge
 all of them as inefficient (0*1? resultless). Fortunately,
 \Tool run-time counts the total number of iterations and
-correctly identifies 3 (XXX to change XXX) of them as truly inefficient and severe enough
-to cause the corresponding performance problem.
+correctly identifies them as false positives. Similarly, \Tool run-time analysis
+helps prune out 19 false positives for [0$|$1]* loop identification.
 
@@
 \subsection{Comparison with other tools}
-XXXXXX
+
+Automated tools have been developed to detect inefficient loop bugs
+\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
+As discussed in Section \ref{sec:intro}, although these tools are very
+useful, they are not suitable for failure diagnosis. 
+For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
+hence can only cover about half of the bugs in our \emph{general} benchmark suite.
+Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
+expensive than \Tool. 
+Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
+by adding conditional-breaks. Very few bugs in Table \ref{tab:} are like this.
+CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 
+We expect it to automatically detect a sub-set of the cross-loop redundancy
+loops in our benchmark set, but not for other types of inefficient
+loops. In summary, \Tool aims to explain performance problems that have 
+already manifested,
+yet bug detection tools aim to predict problems that may not have manifested.
+\Tool achieves higher generality and accuracy at the cost of the prediction
+capability.
+
+Comparing with existing profiling and performance
+statistical debugging technique \cite{SongOOPSLA2014}, \Tool provides much
+more detailed root-cause information. Instead of just identifying loops that
+are highly correlated-with/responsible-for the execution slowness, \Tool
+can accurately point out whether these suspicious loops are efficient or not,
+and which type of inefficiency a loop contains, if any, and make fix suggestions.

### 2016-03-22 section/5_exper.tex
merge tables

@@
 
-\input section/tab_cover
+%\input section/tab_cover
 
@@
 \label{sec:coverage}
-Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
+Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:benchmarks}. 
 \Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
@@
 
-\input section/tab_top5
+%\input section/tab_top5
 
-As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
+As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
 false positive and 22 benign false positives for all the top 5 loops
@@
 Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
-by adding conditional-breaks. Very few bugs in Table \ref{tab:} are like this.
+by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
 CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 

### 2016-03-23 section/0_intro.tex
submitted version

@@
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC27733.c}}
-\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch)}
+\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch; variable and 
+function names are simplified for demonstration purposes)}
 \label{fig:GCC27733}
@@
 \item Focused checking. 
-Different from performance-bug detectors that blindly checks the whole
+Different from performance-bug detectors that blindly check the whole
 software, \Tool focuses on loops that are

### 2016-03-23 section/1_under.tex
submitted version

@@
 Previous work has identified a wide variety of performance root-cause 
-categories. However, no existing taxonomy satisfies all the three 
-requirements below and hence cannot be directly used for our diagnosis tool
+categories. However, existing taxonomies do not satisfy all the three 
+requirements below and hence cannot be directly used to guide our 
+diagnosis-tool
 design.
@@
 
-\begin{figure}
-\centering
-\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-     morekeywords={+},keepspaces=true}
-  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
-\caption{A resultless [0$|$1]* bug in GCC }
-\label{fig:GCC46401}
-\end{figure}
-
 {\textbf{[0$|$1]*}}:
@@
 results and cause performance problems perceived by users.
-These problems are often solved
-by adding a simple check to conditionally skip the expensive loop.
+%These problems are often solved
+%by adding a simple check to conditionally skip the expensive loop.
 Figure~\ref{fig:GCC46401} shows such an example.
@@
 skipped in most cases.
+
+\begin{figure}[t!]
+\centering
+\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+     morekeywords={+},keepspaces=true}
+  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
+\caption{A resultless [0$|$1]* bug in GCC }
+\label{fig:GCC46401}
+\end{figure}
 
@@
 {\textit{How to fix?}}
-As we can see, a deep understanding of software semantics is required
-to understand the inefficiency root cause of these loops.
-Similarly, the fix strategies for these loops would vary from case to case.
+Since a deep understanding of software semantics is required
+to understand the inefficiency of these loops,
+the fix strategies for these loops will likely vary from case to case.
 %At high level, the patch often involves skip some computation that produces
@@
 together.
-
 For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
 redundant computation across different invocations of recursive function
-\texttt{mult\_alg}. The patch essentially allows memoization to work.
+\texttt{mult\_alg}. The patch essentially enables memoization.
 %Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
@@
 or combining multiple loop instances together to avoid or alleviate redundancy.
-
 Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
@@
 through the design of \Tool (Section \ref{sec:design}) and 
-real-world bug study (Section \ref{sec:eval_taxonomy}).
+a real-world bug study (Section \ref{sec:eval_taxonomy}).
 

### 2016-03-23 section/2_workless.tex
split study section. the benchmark study does not guide study, but evaluate study
submitted version

@@
 judges whether a given loop belongs to any root-cause type discussed in
-Section \ref{sec:study_tax}.
+Section \ref{sec:study}.
 Its design
-follows the following principles.
+follows three principles.
 \begin{itemize}
@@
 used together with other performance diagnosis tools \cite{SongOOPSLA2014}
+or profilers,
 and focus on a small
 number of loops that are most correlated with a specific performance symptom,
-instead of being applied to the whole program. Therefore, we will have different
+instead of the whole program. Therefore, we will have different
 design trade-offs in terms of coverage and accuracy, comparing with 
@@
 
-\subsubsection{Static Analysis}
+\subsubsection{Static analysis}
 \label{sec:s_workless}
@@
 %TODO Shan will rewrite the next two paragraphs
-\subsubsection{Dynamic Monitoring}
+\subsubsection{Dynamic monitoring}
 \label{sec:d_workless}
 
-Except for 0*, none of the other three type of loops are inefficient for sure.
+Except for 0*, none of the other three types of loops are inefficient for sure.
 We need dynamic analysis to figure out what portion of loop iterations are
@@
 For a 0*1? loop, since it only generates results in the last iteration, we 
-only need to know the total number of loop iterations 
+only need to know the total number of loop iterations of each loop instance
 to figure out the loop

### 2016-03-23 section/3_redundancy.tex
submitted version

@@
 %workload dependent
-
-\emph{How to suggest the most suitable fix strategy?}
-As discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
-memoization and batching are both common fix strategies for redundant loops.
-To pick the right strategy,
-extra analysis is conducted by \Tool and presented in 
-Section \ref{sec:redundant_fix}.
 
@@
 
-\subsubsection{Fix strategy recommendation}
+\subsection{Fix Strategy Recommendation}
 \label{sec:redundant_fix}
@@
 Specifically, 
-when the only side effect of a loop is I/O operations
+when the only side effect of a loop is from I/O operations
 and the same statement(s) is executed in every loop iteration, \Tool reports 
@@
 be considered batching; and so on. 
-Generating the exact patch is out of the scope of \Tool.
+Generating complete patches is out of the scope of \Tool.
 

### 2016-03-23 section/5_exper.tex
submitted version

@@
 \paragraph{Benchmarks}
-Note that \Tool is a tool that helps diagnose performance problems that
-have already manifested, not a detection tool that can help predict not-yet-manifested
+Note that \Tool is a tool that helps diagnose already-manifested performance problems,
+not a detection tool that can help predict not-yet-manifested
 problems. Consequently, our benchmarks are performance problems that have already
@@
 To conduct a thorough evaluation, we use
-benchmarks from two sources.
+benchmarks from two different sources.
 
@@
 we design bug-triggering inputs for them based on the bug-triggering inputs in 
-the original bug reports and our understanding about how original program inputs
-map to the inputs of our re-implemented programs.
+the original bug reports and the mapping relationship between inputs of original programs 
+and re-implemented programs.
 Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
@@
 Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
-listed in Table \ref{tab:root}, but they are too difficult to be reproduced
-on our machines.
+listed in Table \ref{tab:root}, but they are too difficult to be reproduced.
 First, they all depend on 
-special hardware/software environment that our machine is not equipped with.
-For example, some bugs can only be triggered on Windows, and some bugs depend on 
+special hardware/software environment that our machines are not equipped with.
+For example, some bugs can only be triggered on Windows, and some depend on 
 .Net libraries. 
@@
 \texttt{openjdk}. At the end, each extracted benchmark contains at least five
-loops, except for two cases where only 4 loops exist in the extracted version. 
-Note that, Toddler focuses on inefficient nested loops, and hence its
+loops, except for two cases where only four loops exist in the extracted version.
+
+We use Toddler benchmark suite for two reasons.
+First, it provides a large set of 
+repeatable inefficient loop problems that we can access. 
+Second, it was set up for a completely different reason and with a different 
+methodology from our
+\emph{general} benchmark suite,
+and hence can well complement the \emph{general} suite.
+We should also note that, Toddler focuses on inefficient nested loops, and hence its
 benchmark bugs only cover two types of inefficiency root causes,
 as shown in Table \ref{tab:benchmarks}.
-
-We use Toddler benchmark suite for two reasons.
-First, it was set up for completely different reasons and methodology from our
-\emph{general} benchmark suite,
-and hence can well complement the latter suite.
-Second, it provides the largest set of 
-repeatable inefficient loop problems that we can find.
 
@@
 users have provided at least one problem-triggering input in their on-line 
-bug bugs. We use these inputs in our run-time analysis.
+bug reports. We use these inputs in our run-time analysis.
 
@@
 \label{sec:coverage}
-Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:benchmarks}. 
+Overall, \Tool provides good diagnosis coverage, as shown by the check-marks in Table~\ref{tab:benchmarks}
+(the ``Did \Tool Identify ..?'' columns). 
 \Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
@@
 For MySQL\#27287 and Apache\#53622, the root-cause loops contain both
-cross-loop redundancy and 0*1? inefficiency. \Tool suggests both changing
-data structures and memoization as fix strategies. In practice, the developers
+cross-loop redundancy and 0*1? inefficiency. Consequently, \Tool suggests two
+corresponding fix strategies. In practice, the developers
 acknowledge both types of inefficiencies, but the patches
@@
 
-Second, the fix strategy taken by developers is related but not exactly the same as
+Second, the fix strategy taken by developers is related to but not exactly the same as
 what suggested by \Tool.
@@
 \Tool suggests data-structure changes for these three cases. Developers' patches 
-still keep the original data structure and the original buggy loop, but they
+still keep the original data structures and the original buggy loops, but they
 did use hash-sets, which contain the same content as the arrays do,
@@
 As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
-false positive and 22 benign false positives for all the top 5 loops
+false positive and 22 benign false positives in total for all the top five loops
 of the \allbugs benchmarks.
 
-Here, benign false positives mean that the \Tool analysis result is true ---
+Here, benign false positives mean that \Tool analysis result is true ---
 some loops are indeed cross-iteration/loop redundant or indeed producing
-results in only a small portion of all the iterations. However, those
+results in only a tiny portion of all the iterations. However, those
 problems are \textit{not} fixed by developers in their performance patches.
@@
 In fact, this is not really a problem for \Tool in 
-real usage scenarios, because statistical debugging can accurately
+real usage scenarios, because statistical debugging or profiling can often
 tell that these loops are not top contributors to the performance
@@
 in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
-top-5 suspicious loops in one of our benchmarks; it only generates side effect
-in its last iteration, and hence is identified as by \Tool static analysis. 
+top-5 suspicious loops in one of our benchmarks; it only generates side effects
+in its last iteration, and hence is identified as 0*1? by static analysis. 
 Without run-time information, \Tool would judge
 all of them as inefficient (0*1? resultless). Fortunately,
-\Tool run-time counts the total number of iterations and
+\Tool run-time counts the number of iterations of each loop instance and
 correctly identifies them as false positives. Similarly, \Tool run-time analysis
@@
 among all the benchmarks in Table \ref{tab:performance},
-Mozilla\#347306 still incurs the largest overhead (0.49\%). 
+Mozilla\#347306 still incurs the largest overhead (merely 0.49\%). 
 The diagnosis results remain the same for all but
@@
 among all the benchmarks in Table \ref{tab:performance},
-Mozilla\#347306 has the largest overhead (4.47\%). 
+Mozilla\#347306 has the largest overhead (merely 4.47\%). 
 %In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
@@
 workload, it is natural that \Tool uses two thresholds in its diagnosis.
-In fact, the diagnosis results are largely insensitive to the threshold
+In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
 setting. For example, the results would remain the same when
@@
 As discussed in Section \ref{sec:intro}, although these tools are very
-useful, they are not suitable for failure diagnosis. 
+useful, they are not designed for failure diagnosis. 
 For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
@@
 by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
-CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 
-We expect it to automatically detect a sub-set of the cross-loop redundancy
-loops in our benchmark set, but not for other types of inefficient
-loops. In summary, \Tool aims to explain performance problems that have 
+CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs, 
+which arise if a program fragment repeatedly iterates over a data structure, such as an array or list, that has not been modified between successive traversals of the data structure.
+Like Toddler, it targets nested loops.
+We expect it to detect a sub-set of the cross-loop redundancy
+loops and a sub-set of 0*1? resultless loops in our benchmark set.
+In summary, \Tool aims to explain performance problems that have 
 already manifested,
 yet bug detection tools aim to predict problems that may not have manifested.
-\Tool achieves higher generality and accuracy at the cost of the prediction
-capability.
+They are suitable for different usage scenarios.
 

### 2016-03-23 section/evaltax.tex
submitted version

@@
-\section{Evaluation of Taxonomy}
+\section{Assessment of Root-Cause Taxonomy}
 \label{sec:eval_taxonomy}
@@
 \subsection{Caveats} 
-We do not intend to overly generalize the evaluation results above.
+What presented above reflects our best effort in assessing our root-cause
+taxonomy using a non-biased set of real-world inefficient loop problems that
+have been perceived by users and fixed by developers.
+
+The numbers presented above should be interpreted together with our methodology
+and should not be overly generalized.
 The performance bugs examined above cover a variety of applications, workload, 
 development environments and programming languages. 
-However, there are still uncovered cases, like distributed systems, 
-and scientific computation.
+However, there are definitely uncovered cases, like problems in distributed systems
+and scientific computing systems, and others.
 

### 2016-03-23 figures/GCC27733.c

@@ -4,10 +4,13 @@ struct hash_entry {
 };
 
 void mult_alg(... HOST_WIDE_UINT t, ...) {
-  hash_index = t ...;
-  if (alg_hash[hash_index].t == t ...)
+  hash_index = hash (t); 
+  if (alg_hash[hash_index].t == t) 
   {
-    //reuse previous results
+    //fast path: reuse previous results
+  }else{
+    //slow path: expensive recursive computation
+    ...
+    mult_alg (...);
   }
-  //recursive computation
 }

### 2016-06-01 oopsla16_reviews_rebuttal.txt
check in review and rebuttal

===========================================================================
                         OOPSLA 2016 Review #108A
---------------------------------------------------------------------------
          Paper #108: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: X. I am an expert in this area
                Reviewer confidence: 3. High
                      Overall merit: 2. Some merit, significant objections

                         ===== Paper summary =====

This paper addresses the problem of automatically finding performance bugs that are caused by inefficient loops. Towards this goal, the paper first presents a taxonomy of inefficiencies in loops: The two main classes are so-called "resultless" loops which perform computation with no observable side effects. The second main class of inefficiency arises from "redundant" loops which perform redundant computation. The paper further categorizes these inefficiencies into subclasses, such as (0|1)* loops, 0*1 loops, cross-iteration redundant loops etc. Based on this taxonomy, the paper proposes a tool called LDoctor for finding inefficient loops. The tool employs a hybrid (static + dynamic) analysis approach: The static analysis is used to identify possible inefficiencies while the dynamic analysis is used to assess the existence/severity of the inefficiency. The paper performs two kinds of evaluations: First, it assesses the generality of the proposed taxonomy on performance proble
 ms from Apache, Chrome, GCC, Mozilla, and MySQL. Second, it evaluates the usefulness of the LDoctor tool on the benchmarks from Toddler as well as a subset of the benchmarks used for evaluating the taxonomy.

                      ===== Comments for author =====

On the positive side, the paper addresses an important problem, and tools for finding performance issues in software are likely to be quite useful. However, as detailed below, the paper has a number of weaknesses with respect to novelty, writing, evaluation etc.

* Novelty/contributions: One of the main selling points of the paper is the root-cause taxonomy, but I did not find this taxonomy to be particularly useful/insightful. For instance, consider "resultless" loops: Out of the four classes, 0* loops basically never seem to arise, and 1* loops do not seem to indicate a root cause. The techniques underlying the LDoctor tool also do not seem particularly novel -- from what I could tell, it seems to use basic and standard static analysis techniques.

* Evaluation: The overall experimental results are not very convincing for two reasons: 1) The authors picked 65 performance problems from an existing bug database but only 18 of them are used to evaluate LDoctor. 2) Although additional Java benchmarks from previous papers are included, LDoctor can only analyze C++ code, so the authors seem to have manually translated Java to C++. The evaluation would be significantly more convincing if the authors show that LDoctor finds previously unknown performance issues in real programs. I was also not convinced that the "fix strategies" suggested by LDoctor are very insightful/useful.

* Writing: The writing seems quite imprecise, and the paper generally lacks a formal treatment of the concepts that are introduced. The paper could also really benefit from a running example that puts everything together.

* Usefelness:  In order to generate a useful report, LDoctor relies on the existence of inputs that trigger the performance problem. However, such inputs may be hard to obtain in practice, so the usefulness of LDoctor for detecting performance problems is a bit questionable. Also, even though the paper claims that LDoctor provides accurate diagnosis for inefficient loops, its "fix strategy" mainly relies on some global, predefined templates which are well-known (e.g., batching, memoization.).

* Comparison with other tools: Section 5.6 seems completely out of place -- this discussion belongs in Related Work, not in Evaluation. You should either do a quantitative comparison with these tools or not include this discussion in Evaluation.

===========================================================================
                         OOPSLA 2016 Review #108B
                     Updated 26 May 2016 8:27:45am EDT
---------------------------------------------------------------------------
          Paper #108: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: Y. I am knowledgeable in this area,
                                        but not an expert
                Reviewer confidence: 2. Medium
                      Overall merit: 4. Significant merit, some objections

                      ===== Comments for author =====

This paper introduces the LDoctor tool, which uses static analysis to identify
possibly ill-performing loops and dynamic sampling to confirm whether the loops
really do perform badly when a program is run. This is not an area of
performance I was previously familiar with, so I can't validate LDoctor's
novelty. However, I really liked the core idea in this paper, and can imagine
using something like this to help improve the performance of real programs. [I
quite often see, for example, people writing loops which are accidentally
quadratic, when they could easily be linear.]

In many ways, the paper is fairly easy to read, possibly in part because I found
the basic concepts easy to understand. However, the writing is often more vague
and confusing than it needs to be. A few major examples follow.

1) The introduction spends a lot of effort explaining why existing tools aren't
good enough, but this is rather confusing, because (until Section 1.2) there is
no hint given as to the approach the authors are proposing. This is a problem
because the reader can't tell if the authors are simply putting up strawmen
arguments or not. For example, the paragraph on p1 with the sentence
"Unfortunately, these tools are not designed for and are consequently unsuitable
for performance diagnosis" makes no sense to the reader at that point in the
paper, as the reader has no idea what the difference between a "performance
bug" and "performance diagnosis" might be? An easy fix might be to put the
paper's solutions into the abstract, so that the reader has some idea of what
those solutions are when reading the introduction.

2) The authors sensibly consider arbitrary library functions to be side-effecting
(unless they're part of a manually maintained whitelist). However, I'm unclear
as to how this effects the calculation of input recording. For example, if I
have an expression "if getchar() == 32" (and assuming getchar is an external
function), is that considered to be equivalent to a memory read? It's clearly
something that can vary in each iteration of the loop, but Section 3.2.2 doesn't
seem to explain this (in Figure 5, the output of getchar() is stored into
memory, which bypasses the issue I'm raising). [p8 suggests that LDoctor
considers IO as a special thing, but that's the only mention I can find.]

3) Something that puzzled me whilst reading the paper is what languages LDoctor can
work on. Some of the examples appear to be given in JavaScript (though this is
vague), and it is only on p9 that we discover that "Among these 18 [benchmarks],
seven are extracted from Java or JavaScript programs and re-implemented in C++,
as LDoctor currently only handles C/C++ programs". I don't know why the paper is
so vague about this, because, in my mind, this is not a negative point: I would
have been astonished if LDoctor could handle multiple languages!

Unfortunately, I didn't find the evaluation section hugely convincing. The
authors seem only to to focus on showing that LDoctor can find bugs and fixes
that other people have already discovered (in some cases, I think, on rather
ancient software). As one technique for evaluating LDoctor this is fine, but I
really wanted to see LDoctor applied to modern systems. Can LDoctor find
performance bugs in Firefox or Chrome, for example? I'd like to think it can
and, if so, I'd almost certainly find that really convincing.

As a technical benchmarking comment, as I understand things, Table 4's
performance figures result from a single run of a program. This is not an
appropriate way of benchmarking, as program performance frequently varies
significantly from run to run -- 5% performance differences can easily vanish
when a program is rerun. It is therefore important that benchmarks are run
multiple times and confidence intervals reported.

So, in summary, this paper has a really interesting idea, just about explains it
well enough, and misses some opportunities to convince readers in the
evaluation. That makes it a little hard to give a verdict, but I like the core
idea here enough to score it fairly highly. In a revision of this paper, I would
encourage the authors to first rethink the evaluation section somewhat, and then
to tighten the paper's general explanation of the ideas herein.

  Minor comments

p3, Figure 2: I've stared at this for a while and, based on the information
in the figure, I can't work out why is resultless. Can offset never equal
target (the latter var isn't defined, so I have no idea what possible value(s)
it may contain). [The additional information in the prose below helps a bit,
but I still don't fully get the example.]

p3: What are the "+" figures in Figure 3 for? Output from diff maybe? <Reads
further> Aha, the prose below makes it clear that this is both a performance
bottleneck *and* the patch that fixes the bug. So I was right that it's diff
output. The caption could, then, be much clearer.

p3: "0*1" and "[0|1]*" are easily misread as being the same. There again, I
couldn't come up with better names myself, so perhaps they should just stay as
they are!

p4: What's a "natural" loop?

p5: "Except for 0*, none of the other three types of loops are inefficient for
sure." might better be something like "Although 0* loops are obviously
inefficient, all we can say statically about the other three loop types is that
they may be inefficient."

p5: "For a 0*1? loop, since it only generates results in the last iteration, we
only need to know the total number of loop iterations of each loop instance to f
i gure out the loop resultful rate, which we define as the ratio between the
number of iterations with side effects and the total number of iterations."
Isn't this ratio always "1/num_iterations"? Is the point of the description to
show that the same idea can be used for [0|1]* loops, where the ratio will be
"M/N" for arbitrary integers(where M<=N)?

p6, Figure 5: I found the figure a little hard to understand, partly because
what it's doing seems to be really silly. Maybe it would help to explain why the
loop is doing what it's doing (i.e. what's the context of the function).

p7: The change of gears into talking about LLVM feels a little out of place. I
wonder if Section 3.2.4 should be a new section (rather than a subsubsection).

p8: "LDoctor will suggest a data-structure change in case of 0*1? loops." I'd
like to see an example of the output in this case.

p8, Table 1: I think it would be better not to call these "bugs", as that is
much more commonly used to mean "semantic flaw" rather than "non-functional
property flaw".

p8: "Generating complete patches is out of the scope of LDoctor." Presumably
this is impossible for the tool to guess, in general? Or is it just "this
might be possible, but it's too hard given the current scope of LDoctor"?

p8, Table 1: This table must include software version numbers, otherwise there's
no way that the study can be replicated.

p9, Table 2: I don't know how to interpret this table (what do the shaded boxes
mean?).

p12, Table 4: This table is a little easier to interpret, but I still had to
read the prose in the main body of text to work out what the important numbers
were (what are the other numbers in the table telling me? I'm not really sure).
[As a minor nit, the acronym "C-L R." was just "C-L" in Table 3.]

==============================

Comments after PC meeting

Whilst I still like the basic idea in this paper, I admit that my confidence in the paper has been slightly chipped away at over time. This meant that I ended up being unable to champion it, hence its rejection.

What the Programme Committee largely (though not wholly) agree is that there are good ideas in this paper.

The major problem that ultimately the PC agreed on is that the evaluation is not good enough for a conference like OOPSLA. The authors really need to evaluate more systems and, preferably, to find performance bugs in real systems. It would also help a great deal if performance numbers were then presented of the performance before and afterheads (with timings given as means and confidence intervals).

A lesser (though not insignificant) problem is that the paper's presentation needs improving: there are plenty of comments in the reviews above to help the authors in this regard.

                 ===== Questions for Author Response =====

None

===========================================================================
                         OOPSLA 2016 Review #108C
                     Updated 28 May 2016 7:59:51pm EDT
---------------------------------------------------------------------------
          Paper #108: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: Y. I am knowledgeable in this area,
                                        but not an expert
                Reviewer confidence: 2. Medium
                      Overall merit: 3. Some merit, weak objections

                         ===== Paper summary =====

This paper presents a tool, called LDoctor, focused on identifying root causes of performance problems caused by inefficient loops. LDoctor assumes a set of loops that seem to be correlated with performance problems as input; the goal is to use LDoctor in conjunction with other performance diagnostic tools. LDoctor checks for two types of issues: resultless loops (where some iterations do not produce results) and redundant loops (where some/all iterations of the loop are identical to previous iterations), using a combination of dynamic and static analysis focused on the specific loop types.

                      ===== Comments for author =====

I enjoyed reading this paper. I particularly liked the taxonomy of loop-related performance problems, and I can see the appeal of a tool like LDoctor when solving real issues. However, there were a few issues with the evaluation/implementation.

I was excited to read that LDoctor provides fixes for loop-related performance issues. From the motivating examples, it seems clear that just pinpointing a loop that has performance problems is not enough information to debug the issue. However, it was not clear that the provided fixes would be useful enough to fix the problem. From the description in section 3.3, it sounds like the fixes only point to which area in the taxonomy the loop problem falls, without providing specific guidance. Is this actually enough information to help developers fix the problem?

Secondly, I had some serious concerns about the effectiveness of LDoctor after reading the evaluation section. It seems that LDoctor is only applicable on 18/45 loop bugs. The remaining bugs are "too difficult to be reproduced". Since the goal is to help identify and fix real-world performance bugs, does this mean LDoctor is often not effective in practice because performance bugs are difficult to reproduce? Since the implementation of LDoctor is essentially heuristic-based, how could the tool be expanded to deal with these other 27 cases?

I am also concerned that several benchmarks were reimplemented in C++ in order to run LDoctor. It fact, it seems LDoctor was able to run directly on only 11/39 benchmarks.

The paper also had a number of typos and could use a proofreading pass. e.g.:
"loop worths fixing" ==> loop is worth fixing
"one iteration have side effects" ==> one iteration has side effects
"We will compare the computation" ==> we compare the computation

ADDED AFTER AUTHOR RESPONSE

Thank you for the response. Although there are several things I like about this paper, I still have some confusion.

* The "diagnosis not detection" distinction is still not totally clear when reading the paper. How exactly does LDoctor fit in the workflow of a developer who is concerned about performance? How much time does it take to act based on the tool output, and what other tasks are required? Including some actual examples of LDoctor output would be helpful.

* The evaluation is still giving me pause. Reimplementing benchmarks and not being able to fix most performance issues highlighted as possible benchmarks both give me pause. Also, how much did the benchmarks speed up after making the suggested fixes?

* You say you "picked" a taxonomy. How was this choice validated?

                 ===== Questions for Author Response =====

1) Can you provide some examples of fixes? Would LDoctor typically just output "conditionally skip this loop" or "use batching"?

2) Sometimes LDoctor "can" provide some detailed information to help with the patch. When is LDoctor able to do this? What does the detailed information look like (i.e. a few specific output examples)?

3) How was the taxonomy developed?

===========================================================================
                 Response by Shan Lu <shanlu@uchicago.edu>
          Paper #108: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

We thank the reviewers’ feedback. We will take the reviewers’ insightful suggestion about writing and evaluation in the next version of this paper.

Review#A

Question: LDoctor didn’t find previously unknown performance issues? Are the inputs hard to obtain for performance diagnosis?

Answer: As emphasized in Section-5.1, “LDoctor is a tool that helps diagnose already-manifested performance problems, not a detection tool that can help predict not-yet-manifested problems.”

Inputs are easy to obtain in the context of diagnosing already-manifested performance problems. Previous study found that almost all performance bug reports contain detailed input information [32].

Review#B

Question: How to treat getchar()-like library functions?

Answer: Indeed, we treat them like memory reads and record their return values. We will clarify this in the next version of paper.

Question: Apply LDoctor to modern systems?

Answer: Good suggestion. In fact, many of our benchmarks, including all the 21 bugs from Toddler suite, are from code released within last 5 years. Most of our Mozilla bugs are indeed from the Firefox component.

Question: Did you run each benchmark multiple times for performance measurement?

Answer: Sorry that our writing led to the confusion. To compute each overhead number, we always run 10 times and use the average execution time. For each version of a benchmark that requires sampling, we use the same random seed in different performance-measurement runs. The run-time difference across these 10 runs is always less than 5%.

Review#C

Question 1) and 2): How does LDoctor help patching?

Answer: For every inefficient loop, LDoctor suggests a fix strategy and provides related information for carrying out that strategy.

For example, when suggesting iteration-memoization for a cross-iteration redundant loop, LDoctor reports the run-time iteration-redundancy ratio, the memory-read instructions M that each iteration’s side-effect instructions S depend on, and run-time values read by M. If developers decide to take the fix suggestion, they simply need to refactor the loop to cache S results indexed by values returned by M.

When suggesting conditional-skip for a [0|1]* loop, LDoctor identifies the side effect instructions S in the loop and reports what percentage of loop iterations have executed each such instruction. If developers decide to take the fix suggestion, they simply need to refactor the loop, lifting the path condition of S outside the loop.

Overall, LDoctor provides information to help developers decide whether and how to fix.

Question 3): How was the taxonomy developed?

Answer: Based on our understanding of real-world performance problems, we tried several taxonomies and finally picked the one that best fit the three principles listed in Section 2 --- coverage, actionability, and generality.

Question: Is LDoctor only applicable on 18/45 loop bugs?

Answer: No. These 27 bugs have all been reliably reproduced by users and developers when they were reported. Table-2 shows that developers should be able to apply LDoctor (or its Java/JavaScript-version) to these bugs and obtain good diagnosis results. We couldn’t reproduce these bugs because either (1) we do not have the machine settings that developers had a few years ago or (2) some reproducing information may be omitted by developers in on-line discussion.
HotCRP

### 2016-06-01 pldi16_reviews_rebuttal.txt
check in review and rebuttal

===========================================================================
                           PLDI '16 Review #141A
                     Updated 14 Jan 2016 7:53:07am EST
---------------------------------------------------------------------------
          Paper #141: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: Y. Knowledgeable
                      Overall merit: B. OK paper, but I will not champion
                                        it

                         ===== Paper summary =====

This work focuses on diagnosing loop related performance problems which contribute to a significant proportion of the real world performance issues (based on [11]). Existing approaches based on statistical performance diagnosis report suspicious control flows/loops which cause execution slowness. This paper extends this further to identify the root cause of the slowness and suggests fixes.

The paper divides the problematic loops into multiple categories and illustrates the problems well with examples from real codebases. Subsequently, a mix of static and dynamic analysis is applied to associate the suspicious loops with one of the categories. This can be useful to developers as identifying the root cause can be a manually intensive task. 18 of the 45 bugs from another paper is studied to investigate the effectiveness of LDoctor (tool based on the proposed approach). The results are favorable.

                      ===== Comments for author =====

The paper is well written and articulates the various issues pertaining to the inefficiencies with loops well. Using examples from real code bases is a big positive because it shows that these problems happen in practice. From the perspective of a developer, detecting these problems can be very useful. Experimental evaluation is performed on bugs reported by [31]. Positives from this evaluation include the low overhead of LDoctor and its ability to identify root causes effectively.

However, it is quite surprising that the paper does not discuss some related efforts in more detail [24,25,26]. My understanding is that [24] and [26] are dynamic and static analysis approaches to detect problems with nested loops. It seems that some aspects of [24] can be directly applied to LDoctor. While the current paper is not restricted to nested loops, the discussion with these papers should have been more elaborate. In the rebuttal, can you clearly explain how this effort is different from these approaches (24,25,26)? How many issues found in your experimental results can be detected by these tools?

There are a few concerns regarding the experiments. First, what were the performance gains obtained by performing the fixes proposed by LDoctor? Second, out of 45 bugs, only 18 bugs are analyzed and the other bugs are not considered because they correspond to complicated data structures or hardware/software issues. What is the complication with these data structures that causes LDoctor to fail? Knowing this can also help future efforts in addressing the problem. What are the environment issues? Can it not be simulated? Can you clarify this in the rebuttal? Third, the experimental setup to modify programs from other languages (Java/JS) to C/C++ is a bit unsatisfying. Is it the case that these problems occur more often in other languages rather in C/C++? If not, why not find other benchmarks from C/C++? Fourth, the experiments are performed on bugs found in [31]. Is the approach extensible to loops identified by generic profilers?

While the presentation is good, there are some gaps that need to be filled. Despite multiple reads, there are many outstanding questions. The input to LDoctor is not clearly specified. Do you analyze the entire benchmark, or just the function that contains the loop? If it is the function, what are the inputs and how do you setup the heap? Also, how is coverage guaranteed? Also, were there any interesting design/implementation challenges? 
 Is data from [31] used or tests automatically generated? What happens to the benchmarks that are transformed from other languages to C/C++? What are the inputs there? Can you clarify the relation between coverage and overall precision? It will help if experimental results are provided to support this. In general, the informal nature of the presentation helps in readability. But, it will be better if an algorithm is given in Section 3 to provide a comprehensive picture.

Minor issues:

1) 0* does not add much value to the discussion.

2) The performance problem in Figure 1 is never explained. What happens due to the change from unsigned int to HOST_WIDE_UINT? What are the gains?

3) The background material on [31] should be discussed more elaborately (may be after Section 1).

4) Section 3.2.6 discusses only memoization and branching strategies. More discussion on other fix strategies mentioned in Table 1 will complete the section.

5) page 2, "16 benchmarks" should be 16 performance bugs.

6) page 9, "For all benchmarks ... bug bugs" -- unclear. Will poor coverage not lead to FPs?

Overall, a well written paper addressing performance inefficiencies due to loops. Its incremental nature (not restricted to reliance on [31]), the experimental setup, and the absence of detailed comparison with other related efforts are sources of concern.

ADDED AFTER AUTHOR RESPONSE:

Thanks for the elaborate response. It appears that 9 out of the 18 bugs could not be detected by either [24] or [26] (calculated from the response and table3). However, my concerns regarding why only 18 bugs were studied were not addressed completely. For instance, instead of picking old software that does not compile, it would have helped if the experiments were performed on latest versions.

Overall, I think there is a good idea here. I encourage the authors to strengthen the paper by addressing the concerns raised in these reviews (including addressing the concern related to overfitting).

===========================================================================
                           PLDI '16 Review #141B
                     Updated 13 Jan 2016 8:34:19pm EST
---------------------------------------------------------------------------
          Paper #141: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: X. Expert
                      Overall merit: C. Weak paper, though I will not fight
                                        strongly against it

                         ===== Paper summary =====

This paper presents a tool, called LDoctor, for finding root causes of performance problems and suggesting an appropriate fix. The proposed approach focuses specifically on "inefficient" loops, that are pinpointed using an existing tool for statistical performance debugging. The design of the tool is guided by an empirical study of real-world performance problems, in which they categorize performance bugs in a taxonomy. The two main categories of performance problems are "resultless loops", which waste computational resources without producing useful results, and "redundant loops", which recompute values that shouldn't be recomputed. Guided by this empirical study, the paper goes on describe a combination of static and dynamic analyses for addressing each subclass of performance problems. The paper evaluates LDoctor on a subset (18) of the 45 performance problems considered in the empirical study for classification. The tool seems to have a low false positive rate and low run
 time overhead.

                      ===== Comments for author =====

I agree with the authors that performance bugs are an important and often overlooked aspect of software development, and program analysis tools for finding performance problems are certainly useful. I also appreciate that the authors performed a thorough case study of real-world performance bugs and identified common root causes of performance problems in mature software.

However, in its current form, I believe the paper has a number of flaws that make it unsuitable for publication at PLDI. In particular, my main criticisms are as follows:

* It is not clear if the paper has a significant technical contribution beyond introducing a taxonomy of performance bugs. In particular, it seems that the overwhelming majority of the program analysis  techniques used for identifying performance problems in this paper are already well known (e.g., die effect analysis, slicing, sampling...), so it wasn't entirely clear what the contributions are. Also, from a presentation perspective, the paper reads a little bit like a laundry list of different techniques, one for each subclass of performance problems. Can the authors perhaps clarify the novel and reusable program analysis idea that would be of interest to the PLDI community? From a presentation perspective, it might be a good idea to focus on one key aspect of the analysis and elaborate on it a bit more.

* I think it's great that this paper makes a step towards suggesting fixes for performance bugs, but it seems like the suggested fixes are too coarse and not program-specific. Based on my understanding, LDoctor only suggests global, high-level fixes, such as "can be fixed using memoization/batching". However, the tool does not suggest what to memoize, for example. Is my understanding correct? I would have found it much more interesting if the tool could automatically repair the performance problem and ask the user to accept/reject the repair.

* While the results in the evaluation seem pretty good, the choice of the benchmarks themselves seem rather biased. In particular, since these are the same 18 benchmarks that were already part of the earlier empirical taxonomy evaluation, it's not surprising that the tool works fairly well on these benchmarks. It would seem more impressive if the authors had applied LDoctor to a different set of benchmarks than the ones they had developed the tool for. In fact, using the "training set" (over which you build your model) as your "test set" (to verify its effectiveness) is considered a methodological sin in many disciples (e.g., machine learning), and it seems to me that the methodology used in this paper can be viewed as using the training set also as the test set.

* Also regarding the evaluation, the paper mentions that the remaining 27 bugs were unsuitable for the evaluation due to "dependence on special hardware/software" or "involving complex data structures". I found this a bit worrisome, particularly since the paper seems to be motivated by very pragmatic goals and does not make a deep technical contribution. After all, it seems that LDoctor cannot analyze more than half the performance problems that serve as its motivation.

Minor comments:
* It would be helpful to elaborate on the performance problem from Figure 1. It was not entirely clear to me.
* In Section 2.1.1, it would be useful to give an example of a 1* loop.
* Section 3.1.2, typo at the end of last paragraph: "worths" => "is worth"
* I found the discussion in Section 3.2.2 before the example a bit cryptic.
* In Section 3.2.2, it seems odd to defer to instructions as "inputs" -- maybe consider a different term?
* I would have liked to learn more about the fix strategy recommendation, but this section is very brief.

UPDATE AFTER AUTHOR RESPONSE:
----------------------------
Thanks for the clarification regarding training data vs. testing set. However, my main concern still stands: Beyond the taxonomy, I don't see what the paper's key technical contributions are.

===========================================================================
                           PLDI '16 Review #141C
                    Updated 16 Jan 2016 10:47:31pm EST
---------------------------------------------------------------------------
          Paper #141: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: Y. Knowledgeable
                      Overall merit: B. OK paper, but I will not champion
                                        it

                         ===== Paper summary =====

This paper presents a tool (LDoctor) to identify and help fix performance bugs specifically caused by inefficient loops. The tool is based on a taxonomy of loop inefficiencies developed via an empirical study of 45 real-world performance bugs caused by inefficient loops. The two top-level types of loop inefficiencies are loops where some (or all) iterations do not produce results, and loops with redundant computations. LDoctor detects "resultless" loops by using static analysis to identify side-effecting instructions, refined by dynamic analysis to figure out how often loop iterations do not produce results. LDoctor detects "redundant" loops by identifying loop iterations with the same inputs -- first loop inputs are identified via static analysis and then a dynamic analysis (leveraging random sampling) is used to pinpoint the values of those inputs on various loop iterations.

      ===== Comments for author =====

I enjoyed reading this paper, particularly the section describing the taxonomy of loop inefficiencies. Diagnosing and fixing performance problems automatically remains a difficult problem, and the taxonomy guided design is a compelling approach to address this. I also like how the approach provides fixes.

However, this paper did have some issues. The design and implementation of LDoctor read like a collection of heuristics merged into one "tool". There was not a cohesive, unique analysis. Perhaps this follows from a taxonomy-based approach though.

I also had some questions about the evaluation section. 18 of the 45 empirically studied bugs were used as evaluation benchmarks. It looks like LDoctor would not work on the remaining bugs? How difficult would it be to address this limitation in LDoctor? Also, how were these benchmarks "extracted"? Do they consist of a test case provided in the bug report that exercises an inefficient loop? What if an inefficient loop call is difficult to reproduce?

Although I was initially very excited to see the tool provides fixes, it is not clear how useful these fixes are. Are they just a general hint as to where in the taxonomy a performance issue falls (e.g. "use memoization")? What exactly to the provided fixes look like? How easy is it to apply them? How much effort is entailed for going from fix to patch?

I found the discussion of "benign" false positives confusing. The phrase "benign performance problems" is used. Are these still performance problems, just not as severe as other existing problems? Or would fixing them not actually improve program performance? How exactly were these reports validated as benign? Since the benchmarks were also the subjects used to develop the taxonomy, would LDoctor have more false positives when run on other benchmarks?

Actually, this is a major issue with the paper. The fact that the same benchmarks were used to both develop the analysis and evaluate it throws the results into question. How do you guard against overfitting?

Small notes:
* Figures 3 & 4 do not have line numbers (and figure 3 has "+" symbols on two lines).
* Section 2.2.2, Generality: "each appears" ==> "each appear"
* 3.2.3: "inputs values" ==> input values
* 4.1, evaluation settings: "bug bugs"
* inconsistent tenses in section 4.2
* Section 5 title should be "Related Work"

UPDATED AFTER AUTHOR RESPONSE

Thank you for your detailed response. However, it still sounds like the taxonomy was developed using a suite of programs, then an analysis was developed from that taxonomy, then the analysis was tested on the same suite of programs used when developing the taxonomy. If this is inaccurate, it should be clarified in the paper.

===========================================================================
                           PLDI '16 Review #141D
                     Updated 17 Jan 2016 4:42:50pm EST
---------------------------------------------------------------------------
          Paper #141: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: Y. Knowledgeable
                      Overall merit: D. Reject

                         ===== Paper summary =====

The goal of this paper is to build a tool that helps programmers
identify performance problems and fix them. The work focuses on loops.
The input to the tool is loops that appear to have performance
problems (e.g., identified using profiling).

The tool uses simple static analysis to classify each loop as either a
possibly dead code or a possibly redundant code.

For redundant code, the paper considers two cases:
1) iterations of the same loop instance are redundant if their
observable effect is the same given the same input, and 
2) loop instances are redundant if their observable effect is *almost*
the same given the same input.

For each of these classes and cases, a metric is defined that compares
the number of inefficient instances of the relevant granularity to the
total number of instances of that granularity in any given program
execution.

The tool collects some static information that helps instrument the
program to measure the metrics. Then, program executions are monitored
and results reported to the user.

The fixes proposed to the programmer for each case are also predefined.

The tool is implemented on top of LLVM.
The paper reports on analysing 18 benchmarks and finding known
performance problems in them.

 ===== Comments for author =====

ADDED AFTER AUTHOR RESPONSE

I have read the author response in full. 
It clarifies some of the issues that were raised, but fails to address the main concern of overfitting. Moreover, it confirms that the evaluation is inadequate.

My original review follows.

----

The work is motivated by practical and real need in software
developement to identifying and fixing performance problems. This paper tries to identify
opportunities for loop optimization by observing performance problems
during execution.  In general, it is not possible to guarantee soundness of such optimizations
in a compiler. The programmer needs to find them and manually rewrite the code.

There are very few tools that help with it especially in production
code. The existing tools from research use static and dynamic analysis
to help in certain situations.  This paper claims to provide a more
general approach but in fact it can tackle limited cases of dead and
redundant code in loops and provides no guarantees.

Static and dynamic analysis are quite straightforward. They are
described with enough detail to understand the ideas, although some
details that would be needed to implement these analysis are left
unspecified.

There is no formal definition of what it means to "produce any
results" or have "side effects". The paper informally says that it
means global variables in the relevant code and local variables used
outside the relevant code.  The relevant code seems to include
interprocedurally all reachable callees. It is not clear how output
operations (such as printing) are treated. It is not clear how
indirect calls are resolved. Presumably the standard LLVM machinery is
used (as hinted in sec 3.2.5).

The main contribution of this paper seems to be experimental but the
evaluation is not sufficient.

The classification of performance problems considered in this paper is
based on experiemental results reported and studied in previous work
[11,31].  That previous study included 65 benchmarks, out of them 45
were chosen by the current work to be related to loops and guide the
design. Out of these 18 were used in the experiements.

In fact, these 18 benchmarks consist of several different versions of
4 different large programs: gcc, mysql, mozilla, apache. Not clear
exactly what components of the last 2 are used, but that is described
in [31].

If the classification is a contribution, it should be attributed to
the previous study [31] and the fact that [31] didn't do a good
analysis of its findings. This analysis is perhaps valuable but 
very incremental over [31].  Moreover, the classification is
straightforward and provides no insight.

It is not surprising and in fact expected that a tool motivated by
this analysis can deal well with a subset of its training set, that is
the benchmarks the analysis is based upon. The tool should have been
evaluated on different benchmarks to show that "coverage, precision,
and performance" is transferrable.

Moreover, some of the benchmarks were manually translated from Java or
JS to C++.  First, it is compeletely uclear why this translation
preserves "usability".  Second, I wonder if using an LLVM frontend for
Java or some more direct means of handing java bytecode to LLVM would
also extend applicability of LDoctor.

Not all 45 training set benchmarks are handled and the stated reason
for it is that their translation to C would be too hard.

Sec 3.2.2 mentiones multithreaded C/C++ programs but no treatment of
multithreading is done anywhere else in the paper. Moreovere,
redundancy of computation can be a benefit in the presence of
concurrency as it reduces sharing.

If the analysis in sec 3.2.5 that identifies values that do not change
throughout the loop is sound as stated why not just adding it to LLVM?
It would be useful for optimizations in general.

The motivating example fig 1 in sec 1 is questionable.

Which gcc version are is this? I cannot find any method
named mult_alg and has never been any such method as far as I know.
Is this example talking about synth_mult in gcc/expmed.c?  The
hash_entry unsigned_int bug is not performance bug, it's functionality
bug.  The type of the hash entry is simply wrong in the original code
introduced in Nov 2004.  The bug was reported in May 2006 and fixed in
June 2006.

I don't see any indication in the PR that Paolo Bonzini spent all his
time since the bug was filed to figure out what was causing the
inefficiency. I doubt it, unless Paolo himself says so.

https://gcc.gnu.org/bugzilla/show_bug.cgi?id=27733
https://gcc.gnu.org/ml/gcc-patches/2004-11/msg01420.html

There has been quite a bit of progress in software
development tools since 2006. I am not convinced that this bug would
not have been easier to detect in 2006 than 2004, even
without this paper's contribution.

I therefore don't understand how this example supports the conclusion
that follows it: "Clearly, more research is neeeded to improve the
state of the art of performance diagnosis"

* reference 26 title: shouldn't it be [A]?

References
==========

[A] Oswaldo Olivo, Isil Dillig, Calvin Lin: Static detection of
asymptotic performance bugs in collection traversals. PLDI 2015:
369-378

===========================================================================
                           PLDI '16 Review #141E
                     Updated 15 Jan 2016 2:07:09pm EST
---------------------------------------------------------------------------
          Paper #141: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------

                 Reviewer expertise: X. Expert
                      Overall merit: B. OK paper, but I will not champion
                                        it

                         ===== Paper summary =====

This paper is an empirical investigation of performance bugs in real
systems. The paper (i) generates a taxonomy of performance issues in loops and
then (ii) provides root-cause strategies to deal with each issue in the
taxonomy, and then (iii) demonstrates how to automatically find and suggest such
a mapping from issue to potential fix to a user.  The paper's taxonomy deals
with loops which a) only do useful work at the last iterate, b) may or may not
do work in the last iterate, or c) always generate results in every iterate.
Furthermore, the taxonomy also includes loops which do redundant work, either
within the same loop but across loop iterations, or across loops.  The paper
maps each of these items in the taxonomy to actions to fix such issues and then
demonstrates that this system in concert can help pin-point and root cause
common types of performance problems on a wide variety of real systems which
have real performance bugs.

===== Comments for author =====

I like the spirit of this work; I often spend many hours a day fixing
performance bugs in large and complex software and I welcome anything that helps
automate this process!  The paper is well-written and the evaluation seems
reasonable.  With a bit more work this could be a really awesome paper (and a
really useful tool).  Please see my comments below that I hope help make the
paper stronger in future versions.

The paper states:

"Unfortunately, existing performance diagnosis techniques are still
preliminary. Performance-bug detectors can identify specific type of inefficient
computation, but are not suitable for accurately diagnosing a wide variety of
real-world performance problems..."

This is a strong statement and really jumps out at the reader as at this point
in the text there is little motivation or reason to believe such a statement.
Please consider re-phrasing to something akin to "This paper argues existing
performance diagnosis techniques are still preliminary" as I get by solving
performance bugs at my day-to-day job with the existing techniques (albeit, as
the paper correctly argues, with more burden on my brain and less on automated
tooling).

The notion that "accuracy" includes root-cause reasons in addition to pointing
out hot loops seems a bit stringent. A profiler can be accurate with one and not
the other (indeed even making a profiler accurate with respect to finding hot
loops can be challenging). I would consider breaking out causal analysis on its
own as it is an important and often overlooked part of performance bugs.
Further, since a large part of the paper is on finding root causes correlated
with a taxonomy, calling this part out strengthens the contribution in addition
to differentiates this work from prior art.

Figure 1 and the corresponding text could use more explanation. What is
"severely hurting performance" in terms of numbers?  Why is such a change
associated with a loop as the prior paragraph points out is where prior work in
this space is deficient? I see no loop in the code nor is it clear why fixing
this bug is difficult. The details here do not come out till 2.1.2.

I like the taxonomy in 2.1.1: clear and obvious why such a view of the world is
useful in diagnosing performance problems.

Does memoization/batching ever cause a performance regression? Memoization, for
example, can add memory overheads which adversely impact performance.

I was excited to read the abstract/intro as this part of the paper makes it
sound like LDoctor is something I can use today.  Then, I read the evaluation
and saw that the paper only uses 18 of the 45 benchmarks.  Being an empirical
paper, the results live and die by how usable LDoctor is on real programs.  Can
you please elaborate as to why over half of the programs in Table 1 do not work
with LDoctor?  The current explanation is not really sufficient.

Why does the evaluation of accuracy only look at false-positives? Why not
false-negatives?  This is particularly important given the earlier definition of
accuracy---knowing that the root causes are in the set described by the paper is
paramount to knowing if I can use the tool.

The root-cause and taxonomy were built from looking at these programs /
bugs. How do we know the taxonomy is sufficient to find interesting bugs in
programs NOT in this set. [31] it seems to have almost the same set of bugs
(i.e., table 1 in this paper vs table 7 of 31) and that paper finds the
redundant loops manually.  What would make this paper stronger is a set of
programs which have redundant/resultless loops but are not drawn from the same
set of programs which were used to come up with this taxonomy.  In other words,
how general is the set of fixes the paper provides? If I were to download the
tool today, would the fix strategies in table 1 solve all of my performance
issues?  I find this unlikely (e.g., blocking is an important optimization in
matrix-multiplication and does not seem to fit into the taxonomy/fix
strategies), so the question is, by looking at this set of programs, how general
is LDoctor?  Do the authors feel their evaluation answers this question?

The paper states that its approach is actionable.  And, I agree that it
is. However, the actions require of the programmer may not be as trivial as it
appears in these examples. For example, I may be able to twist a blocking
optimization into one that batches memory reads --- however, implementing such
an optimization is nontrivial! In this instance, the important part the
performance tool is to point me to the location of a potential issue (i.e., poor
memory locality) rather than suggesting the fix.  And, pointing me to a
problematic loop is already done by standard profilers. Do the authors feel such
a problem exists and if so how does LDoctor help a user here?

ADDED AFTER AUTHOR RESPONSE: Thank you for the detailed rebuttal. I agree with other reviewers and worry about the selection of benchmarks both used to generate the taxonomy in addition to evaluating whether LDoctor can find and fix bugs according to that taxonomy.

===========================================================================
                 Response by Shan Lu <shanlu@uchicago.edu>
          Paper #141: Performance Diagnosis for Inefficient Loops
---------------------------------------------------------------------------
We thank the reviewers for their valuable comments.

* Comparing with [24,25,26] (#A)

[24] detects redundant nested loops. It helps diagnose cross-loop redundancies, but not
 other types. Being a dynamic tool, it incurs 10X or more slowdowns; it has more false 
positives than LDoctor, without focusing on suspicious loops.

[25] detects loops with conditional-break fixes, which does not match any bugs
in our benchmark.

[26] statically detects a sub-set of cross-loop redundancies, not other types.

* Explain Figure-1 Example (#A,#B,#D,#E)

It is from GCC bug-database (https://gcc.gnu.org/bugzilla/show_bug.cgi?id=27733). 
We changed the function-name from synth_mult to mult_alg for illustration purpose.
The bug makes memoization not always work, but not affecting correctness.
GCC developers tagged it as ``compile-time-hog''. 
The patch achieves hundreds-of-times speedup for GCC test cases.
There is no loop in Figure-1, but mult_alg is a recursive function.
Discussion on the GCC forum shows that the problematic function was identified
through profiling early on, but the root-cause and patch were not figured
out until rounds of discussion/testing later. We wanted to demonstrate 
the need for performance diagnosis tools beyond profilers.

* Why only 18 bugs (out of 45) are evaluated (#A,#B,#C,#D,#E)

There is no fundamental challenges in applying LDoctor to the remaining 27
cases. We didn't try them due to a mix of:
(1) difficult to repeat (e.g., the buggy software only runs on Windows machines;
the buggy software is too old to compile);
(2) programs written in non-C/C++ languages, although there are no reasons 
why similar bugs cannot appear in C/C++ programs;
(3) programs difficult to extract (e.g., containing a lot of GUI actions or
complicated data structures). Note that complicated data structures making
code extracting difficult, but does not affect LDoctor's diagnosis in these cases.

* Apply LDoctor beyond the 45 bugs (#B,#C,#D)

We do not believe that we are committing the sin of using the training set as test set.
LDoctor is designed following the taxonomy presented in Section 2.
Our taxonomy is designed in a general way, as mentioned by several reviewers.
The 45 bugs is a test set, *not* a training set, for the taxonomy or LDoctor design.
The taxonomy and LDoctor design simply share common tests.
There is no over-fitting in LDoctor. For parameters used in LDoctor, our paper reported
 how results change with parameter changes.

Similar methodology has been shared by many previous work, where a common
benchmark suite is used to evaluate many tools.

We agree with reviewers that more benchmarks can make the evaluation stronger.

The challenge is that LDoctor is a failure-diagnosis tool, *not* a bug-detection tool. 
That is, we cannot feed LDoctor with a random program and expect LDoctor to 
report performance problems. Instead, like performance diagnosis in practice, 
LDoctor needs to be provided with a performance-slowdown/problem symptom 
that is already observed, together with triggering inputs.
This severely limits the benchmarks we can use. [31] provides the 
best performance-debugging benchmarks, and hence we use it.

* Can LDoctor suggest what to memoize? (#B)

Good suggestion! Since LDoctor knows what exactly are the memory reads that 
return the same values again and again, it can help decide what to memoize. 
Generating a concrete patch goes beyond the scope of LDoctor.

* Are output-operations considered having side-effect? (#D)
Yes

* What are false negatives of LDoctor? (#E)
Discussed in Section-4.1 (Coverage Results).

* How is a benchmark extracted? (#C,#D)

We extract the buggy code and its related code (callers, callees, etc.) and translates
them to C/C++. We keep all related data structures and control/data flows unchanged.
We design unit tests for the re-implemented code based on inputs in bug reports 
and our understanding of the bug.

* Is LDoctor extensible to loop identified by generic profilers (#A)?
Yes

* What is the input to LDoctor? (#A)

We run the whole applications using the inputs suggested by bug
reports. The analysis only focuses on top-ranked suspicious loops.

* There is no new program-analysis techniques in LDoctor (#B)

We don't invent new program-analysis techniques. Instead, we aim to solve
an important problem, performance diagnosis, using program analysis.

### 2016-06-01 section/7_con.tex
check in the technical report

\section{Conclusion}
\label{sec:con}
Performance diagnosis is time consuming and also critical for 
complicated modern software. \Tool tries to automatically 
pin-point the root cause of
the most common type of real-world performance problems, inefficient loops,
and provide fix-strategy suggestions to developers. It achieves the 
coverage, accuracy, and performance goal of performance diagnosis by leveraging
(1) a comprehensive root-cause taxonomy; (2) a hybrid static-dynamic program
analysis approach; and (3) customized random sampling that is a natural fit for 
performance diagnosis.
Our evaluation shows that \Tool can accurately identify detailed root causes
of real-world inefficient loop problems and provide fix-strategy suggestions. 
Future work can further improve \Tool by providing more detailed fix
suggestions and providing more information to help diagnose and fix
1* loops.

\acks
This work is supported in part by NSF grants IIS-1546543, CNS-1514256, CCF-1439091, and CCF-1514189; 
and Alfred P. Sloan Research Fellowship.

### 2016-08-17 section/5_exper.tex
check in overhead number

@@
 %and the remaining 6430 for common utilities. 
-experiments on a i7-960 machine, with Linux 3.11 kernel.
+experiments on a i5-3330S machine, with Linux 3.19 kernel.
 
@@
   \centering
-  \scriptsize
+  %\scriptsize
+  \tiny
   \newcommand{\Yes}[1]{\checkmark{}$_#1$}
@@
     \midrule
-    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
-    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
+    Mozilla347306 &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\ 
+    Mozilla416628 &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$        &  $2.41\%\pm1.58\%$   & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
     \midrule
-     MySQL27287   & $<$0.01\%           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
-     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
+     MySQL27287   &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$        &   -                  & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
+     MySQL15811   &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
     \midrule
-      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
-      GCC1687     & -              & /                 &  $<$0.01\%       &   /           & 142.29{\bf X} \\
-      GCC27733    & $<$0.01\%        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
-      GCC8805     & -              & $<$0.01\%           & $<$0.01\%        & 2.22{\bf X}   &  3.52{\bf X}\\
-      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
-      GCC12322    & -              & 1.75\%            &  $<$0.01\%       & 21.07{\bf X}  & 38.44{\bf X} \\
+      GCC46401    &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\ 
+      GCC1687     & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
+      GCC27733    & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
+      GCC8805     & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
+      GCC21430    & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
+      GCC12322    & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
    \bottomrule
@@
 The performance benefit of sampling is huge.
-Without sampling, even with all the static optimization, redundancy
-analysis lead to over 100X slowdown for five benchmarks.
+Without sampling, redundancy
+analysis lead to over 100X slowdown for six benchmarks.
 
@@
 of the array, instead of the content of the whole array accesses,
-the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
-and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
+the overhead is reduced from 12.18\% to 0.20\% for MySQL\#27287, 
+and from 20.53\% to 0.35\% for MySQL\#15811 respectively 
 (sampling is conducted consistently here).
@@
 among all the benchmarks in Table \ref{tab:performance},
-Mozilla\#347306 still incurs the largest overhead (merely 0.49\%). 
+Mozilla\#416628 incurs the largest overhead (merely 4.51\%). 
 The diagnosis results remain the same for all but
@@
 among all the benchmarks in Table \ref{tab:performance},
-Mozilla\#347306 has the largest overhead (merely 4.47\%). 
+Mozilla\#347306 has the largest overhead (merely 7.38\%). 
 %In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 

### 2016-08-23 section/0_intro.tex
check in Linhai's updates

@@
 \cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616,IsilDillig.PLDI15}. 
-Unfortunately, these tools are not designed for and are consequently
+Unfortunately, these tools are not designed %for
+{\color{red} to identify code regions for a specific execution slowness}  
+and are consequently
 unsuitable for performance diagnosis.
@@
 \cite{SongOOPSLA2014,PerfBug}, with good coverage, accuracy, and performance.
+{\color{red} \Tool does not target identifying previously unknown performance bugs, 
+but aims to provide root causes for execution slowness caused by inefficient loops.}
 

### 2016-08-23 section/3_redundancy.tex
check in Linhai's updates

@@
 \label{sec:redundant_fix}
-\Tool suggests how to fix an inefficient loop to developers.
+
+\Tool suggests how to fix an inefficient loop 
+{\color{red} and provides related information for carrying out that fix} 
+to developers.
 This process is straightforward following our taxonomy discussion in 
@@
 data-structure change in case of 0*1? loops.
+{\color{red}Besides these fix strategies, \Tool also reports side-effect instructions 
+and what percentage of loop iterations executing each such instruction. 
+These information can help developers refactor the loop or change data structures processed by the loop. }
 
@@
 this
-as an I/O related redundancy problem and suggests batching as a potential fix
-strategy. Otherwise, \Tool suggests memoization.
+as an I/O related redundancy problem, 
+{\color{red}pointing out I/O instructions,} 
+and suggests batching as a potential fix
+strategy. Otherwise, \Tool suggests memoization, 
+{\color{red}and provides information for input instructions and redundancy rate.}
 
@@
 hence batching is suggested.
+{\color{red} \Tool will also provide information for input instructions and side-effect instructions to developers. }
 
+{\color{red} [redundant]
 In addition to the above high-level fix strategies, \Tool can also provide some 
@@
 Generating complete patches is out of the scope of \Tool.
+}
 

### 2016-08-23 section/5_exper.tex
check in Linhai's updates

@@
 
-\begin{table}
+\begin{table*}[tb!]
   \centering
-  %\scriptsize
-  \tiny
+  \scriptsize
   \newcommand{\Yes}[1]{\checkmark{}$_#1$}
   \newcommand{\No}[0]{-}
-  \begin{tabular}{lccccc}
+  \begin{tabular}{lccccccc}
     \toprule
-	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
-     \cmidrule(lr){2-4}
-     \cmidrule(lr){5-6}
-     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
+	    & \multicolumn{2}{c}{execution time} & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
+     \cmidrule(lr){2-3}
+     \cmidrule(lr){4-6}
+     \cmidrule(lr){7-8}
+     {\bf BugID}  & {\bf Buggy}  & {\bf Patched} & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
     \midrule
-    Mozilla347306 &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\ 
-    Mozilla416628 &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$        &  $2.41\%\pm1.58\%$   & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
+    Mozilla347306 &  $1.52\pm1.80*10^{-2}$ & $5.37*10^{-2}\pm3.77*10^{-3}$  &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\
+    Mozilla416628 &  $4.29*10^{-1}\pm6.70*10^{-3}$  & $1.15*10^{-1}\pm4.64*10^{-3}$  &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$ &  $2.41\%\pm1.58\%$ & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
     \midrule
-     MySQL27287   &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$        &   -                  & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
-     MySQL15811   &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
+     MySQL27287   & $1.21\pm1.77*10^{-2}$& $2.03*10^{-2}\pm3.45*10^{-4}$ &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$  &   - & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
+     MySQL15811   & $1.65\pm1.67*10^{-2}$& $8.39*10^{-2}\pm6.64*10^{-3}$          &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
     \midrule
-      GCC46401    &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\ 
-      GCC1687     & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
-      GCC27733    & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
-      GCC8805     & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
-      GCC21430    & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
-      GCC12322    & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
+      GCC46401    & $3.21\pm7.92*10^{-3}$ & $6.56*10^{-2}\pm3.68*10^{-3}$          &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\
+      GCC1687     & $2.99\pm7.78*10^{-3}$ & $0.68*10^{-2}\pm8.12*10^{-4}$          & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
+      GCC27733    &  $10.50\pm1.20*10^{-2}$ & $0.80\pm1.99*10^{-2}$           & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
+      GCC8805     & $2.40\pm2.36*10^{-2}$  & $0.28\pm1.73*10^{-2}$          & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
+      GCC21430    & $3.27\pm2.02*10^{-2}$             & $0.66\pm1.06*10^{-2}$          & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
+      GCC12322    & $47.68\pm1.01$       & $3.06\pm8.67*10^{-3}$          & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
    \bottomrule
@@
   -: dynamic analysis is not needed;
-  /: not applicable.}
+  /: not applicable;
+  execution time is measured in seconds;
+  $95\%$ confidence interval is calculated by running each benchmark 10 times.}
   \label{tab:performance}
-\end{table}
+\end{table*}
 

### 2016-08-25 section/0_intro.tex
finish ab and intro

--- 2016-03-23 section/0_intro.tex
@@
 degradation in software. They widely exist in deployed software due to the 
-complexity of modern software and the lack of performance testing support
-~\cite{s2e,PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
+complexity of modern software
+~\cite{PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
 They annoy end users and waste energy during production runs, and 
@@
 
-Like general failure diagnosis, 
-performance diagnosis starts from studying a problem symptom and hopefully ends
-at identifying the root cause and suggesting a fix strategy. 
-In the context of performance problems,
-the symptom is 
-execution 
+Performance diagnosis is different from performance testing or
+bug detection: it does \textit{not} aim to expose previously unknown performance
+anomalies. 
+Instead, it is similar with general failure diagnosis: 
+it is applied \textit{after} an unexpected software behavior (i.e., symptom)
+is observed, hoping to identify the root cause of this symptom and suggest
+strategies to eliminate this symptom.
+In the context of performance problems, the symptom is execution 
 slowness \cite{SongOOPSLA2014}; the root cause is about
 which code region is inefficient and why.
-An effective diagnosis tool can help developers quickly
-and correctly figure out a fix to the performance problem.
+An effective diagnosis tool can help developers quickly and correctly understand 
+and fix already-exposed performance symptoms.
 
@@
 \item Accuracy. 
-First, the inefficient code regions need to be accurately located.
-Second, the reason a specific region is inefficient needs to be accurately
-explained, so that developers can fix the problem.
+Which code regions are inefficient and why they are inefficient
+need to be accurately identified.
 
@@
 Diagnosis often requires collecting run-time information. The lower the overhead
-is, the easier for the diagnosis tool to be deployed, especially for 
+is, the easier for the tool to deploy, especially for 
 production-run usage. 
@@
 
-Performance bug detection tools use static or dynamic analysis to identify
+Performance bug detection tools use program analysis to identify
 code regions that match specific inefficiency patterns 
 \cite{Alabama,CARAMEL, Cachetor,Xu:2010:FLD:1806596.1806617,Dufour:2008:STC:1453101.1453111, Xu:2009:GFP:1542476.1542523, Xu:2010:DIC:1806596.1806616,IsilDillig.PLDI15}. 
-Unfortunately, these tools are not designed for and are consequently
-unsuitable for performance diagnosis.
-They are not designed to provide \textit{coverage} for a wide
-variety of real-world problems; their analysis is not guided by
-performance failure symptom, and hence are at disadvantage in terms of diagnosis
+Unfortunately, these tools are not designed and hence are unsuitable
+to identify code regions that contribute to a specific slowness symptom.
+They do not provide \textit{coverage} for a wide
+variety of real-world problems; they are not guided by
+performance failure symptoms, and hence are at disadvantage in terms of diagnosis
 \textit{accuracy}; dynamic detection tools often lead to 
@@
 This approach compares runs with and without problematic performance, and
-accurately identifies control-flow constructs, such as a branch $b$ or 
+identifies control-flow constructs, such as a branch $b$ or 
 a loop $l$, that are most correlated with
-the execution slowness.%, referred to as slowness-predictor.
+the execution slowness.
 Unfortunately, this approach is \textit{not} effective
@@
 tell whether and how loop $l$ is inefficient 
-and hence is not very helpful
-in fixing performance problems.
+and hence is limited in its diagnosis \textit{coverage} and \textit{accuracy}.
 
@@
 
-Figure~\ref{fig:GCC27733} shows a performance bug in GCC. 
-Function \texttt{mult\_alg} is a recursive function 
-that computes the best algorithm for 
+Figure~\ref{fig:GCC27733} shows a performance problem in GCC. 
+Recursive function \texttt{mult\_alg} computes the best algorithm for 
 multiplying \texttt{t}, a time-consuming computation. 
@@
 To avoid redundant computation across different instances of
-\texttt{mult\_alg} with the same parameter, developers used a
+\texttt{mult\_alg}, developers used a
 hash-table
@@
 In many cases, a slow path is taken, when the fast path should have been taken.
-This mistake does not affect software correctness, but it causes a large amount
+This mistake does not affect software correctness, but causes a large amount
 of redundant computation\footnote{This will be considered as a
@@
 
-Debugging this performance bug is challenging. According to 
+Debugging this performance problem is challenging. According to 
 the discussion forum of GCC, developers identified
 \texttt{mult\_alg} as the most time-consuming function
-through profilers early on. However, developers did not figure out 
+through profilers early on. However, they did not figure out 
 whether \texttt{mult\_alg} is inefficient, which part of it is 
@@
 responsible for execution slowness, but also \emph{why} and \emph{how}
-the loop/function is inefficient, 
-the diagnosis and bug fixing
-process would be much easier.
+it is inefficient, 
+diagnosis and fixing
+would be much easier.
 
+\iffalse
+%to save space
 Clearly, more research is needed to improve the state of the art of performance
@@
 especially loop-related performance problems.
+\fi
 
 \subsection{Contributions}
-This paper presents a tool, \Tool, that can help effectively diagnose
+This paper presents a tool \Tool that can help effectively diagnose
 inefficient loop problems, the most common type of performance problems
 \cite{SongOOPSLA2014,PerfBug}, with good coverage, accuracy, and performance.
+After users or developers observe a performance failure symptom, \Tool can 
+automatically judge whether the symptom is caused by inefficient loops and
+provide detailed root-cause information that helps understand and fix 
+inefficient loops.
 
@@
 \emph{resultless}, when a large amount of computation produces
-no side effect, and \emph{redundancy}, when a large amount of 
+no side effects, and \emph{redundancy}, when a large amount of 
 computation produces already-available results.
-Each main category is then further divided to sub-categories.
-We have strived to make our taxonomy both general enough to cover
-common inefficient loops, and also specific enough to guide the failure
-diagnosis of \Tool, and eventually
-help developers understand
-and fix performance problems. More details are
-in Section \ref{sec:study}.
+Each main category is further divided to sub-categories.
+We strive to make the taxonomy both general enough to cover
+common inefficient loops, and specific enough to guide the design
+of \Tool and eventually help developers understand
+and fix performance problems
+(Section \ref{sec:study}).
 
@@
 identify whether and how a suspicious loop is inefficient, 
-together with fix-strategy suggestions. 
-We achieve this following several principles:
+following these principles (Section \ref{sec:design}):
 
@@
 every root-cause category. Given a candidate loop, \Tool
-applies a series of analysis to it to see if it matches any type of inefficiency.
+applies a series of analysis to see if it matches any type of inefficiency.
 %We will also put the analysis results from different analysis routines together
@@
 \item Static-dynamic hybrid analysis.
-As we will see, static analysis alone cannot accurately identify 
-inefficiency root causes, especially because some inefficiency problems only
-happen under specific workload. However, pure dynamic analysis will 
+Static analysis alone cannot accurately identify 
+inefficiency root causes, because some inefficiency problems only
+happen or matter under specific workload. However, pure dynamic analysis will 
 cause too large 
-run-time overhead. Therefore, we take a hybrid approach to achieve both
+run-time overhead. Therefore, we use a hybrid approach to achieve both
 performance and accuracy goals.
@@
 degrading diagnosis capability. Random sampling is a natural fit for performance
-diagnosis due to the repetitive nature of inefficient code, especially
-inefficient loops.
+diagnosis due to the repetitive nature of inefficient loops (Section \ref{sec:inst}).
 

### 2016-08-25 section/abstract.tex
finish ab and intro

@@
 Writing efficient software is difficult.
-Design and implementation defects can easily
+Design and implementation defects can
 cause severe performance 
 degradation. 
-Unfortunately, existing performance diagnosis techniques are still preliminary.
+Unfortunately, existing performance diagnosis techniques like profilers are still preliminary.
 %failing to provide the desired diagnosis coverage, accuracy, and performance. 
-Performance-bug detectors can identify specific type
-of inefficient computation, but are not suitable for accurately diagnosing
-a wide variety of real-world performance problems. 
-Profilers can locate code regions that consume resources, but 
+%Performance-bug detectors can identify specific type
+%of inefficient computation, but are not suitable for accurately diagnosing
+%a wide variety of real-world performance problems. 
+They can locate code regions that consume resources, but 
 not the ones that \textit{waste} resources.
-Statistical performance diagnosis can
-identify loops or branches that are most correlated with a performance
-symptom, but cannot decide whether and why a loop is inefficient, and
-how developers might fix it.
+%Statistical performance diagnosis can
+%identify loops or branches that are most correlated with a performance
+%symptom, but cannot decide whether and why a loop is inefficient, and
+%how developers might fix it.
 
 In this paper, we first design a root-cause
-and fix-strategy taxonomy for real-world inefficient loops, 
+and fix-strategy taxonomy for inefficient loops, 
 one of the most common performance problems in the field.

### 2016-08-25 section/1_under.tex
finish sec 2

@@
 
-Previous work has identified a wide variety of performance root-cause 
-categories. However, existing taxonomies do not satisfy all the three 
-requirements below and hence cannot be directly used to guide our 
-diagnosis-tool
-design.
-\begin{enumerate}
-\item Coverage: covering
+To guide the design of automated diagnosis tools, we need a
+taxonomy for inefficient loops that satisfies three requirements:
+(1) \textit{Coverage}, covering
 a big portion of real-world inefficient loop problems; 
-\item Actionability: each root-cause category should be informative enough 
-to help developers
-decide how to fix a performance problem; 
-\item Generality: application-specific root causes will not work, as we
-hope to build diagnosis tools that can automatically identify root causes 
-without developers' help.
-\end{enumerate}
+(2) \textit{Actionability}, each root-cause category being informative enough 
+to help developers fix a performance problem; 
+(3) \textit{Generality}, allowing automated diagnosis to be applied to many
+applications.
 
-We divide all inefficient loops into two main root-cause categories,
-\textit{resultless} and \textit{redundancy}, and many sub-categories under
-these two.
-The details of these categories will be presented below.
-
-Our discussion below will qualitatively show that 
-our taxonomy is general, not application-specific, and
-cover common loop inefficiency problems.
-We will quantitatively measure the coverage, actionability, and 
-generality of our taxonomy
+Previous work identified a wide variety of performance root-cause 
+categories. However, existing taxonomies do not satisfy all these 
+requirements and hence cannot be directly used by us.
+Therefore, we have designed our own taxonomy,
+as presented below.
+We will discuss how our taxonomy meets these three requirements
+qualitatively in this section and quantitatively 
 using real-world performance-bug suite in Section \ref{sec:eval_taxonomy}.
@@
 Resultless loops spend a lot of time in computation that does not
-produce results useful after the loop (i.e., computation without side effects).
+produce results useful after the loop (i.e., no side effects).
 They can be further categorized to four sub-types 
 based on which part of the loop is
-(not) producing useful results. We explain these four sub-types below, 
-as well as
-how they can be fixed.
+(not) producing useful results.
 
-{\textbf{0*}}: 
-This type of loops never produce any results in any iteration.
+{\textbf{0*}} loops
+never produce any results in any iteration.
 They are rare in mature software systems.
 
-{\textit{How to fix?}} This type of loops should simply be deleted from the program.
+{\textit{How to fix?}} They should be deleted from software.
 %Question: dynamic or static?
@@
 
-{\textbf{0*1?}}:
-This type of loops only produce results in the last iteration, if any. 
+{\textbf{0*1?}} loops only produce results in the last iteration, if any. 
 They are often related to search: check a sequence of elements one
 by one until the right one is found.
-Clearly, whether these loops are efficient or not depends on the
-workload. When indeed inefficient, they are often
-fixed by data-structure changes.
+Whether these loops are efficient or not depends on the
+workload. 
 An example is shown in Figure \ref{fig:Mozilla347306}.
@@
 {\textit{How to fix?}}
-To make a linear search more efficient, it usually requires a data
-structure change. For example, 
-the patch for the bug in Figure \ref{fig:Mozilla347306}
+They are often fixed by data-structure changes.
+For example, the patch for the bug in Figure \ref{fig:Mozilla347306}
 simply replaced the \texttt{script} list with a hash table.
@@
 
-{\textbf{[0$|$1]*}}:
-Each iteration in this type of loops may or may not produce results.
+{\textbf{[0$|$1]*}} loops may or may not produce results in each
+iteration.
 For some workload, the majority of iterations do not produce
@@
 had any side-effects, as the \texttt{if} condition was rarely satisfied.
-At the end, the patch greatly improved performance through a
-simple checking that allows the loop to be
-skipped in most cases.
+%At the end, the patch greatly improved performance through a
+%simple checking that allows the loop to be skipped in most cases.
 
@@
 
-{\textbf{1*}}:
-Loops in this category always generate results in almost all iterations. 
-They are inefficient because their results are useless due to
-some high-level semantic reasons.
-Understanding and fixing this type of inefficiency problems often require
-deep understanding of the program and are difficult to automate.
+{\textbf{1*}} loops in this category always generate results in almost all iterations. 
+They are inefficient because their results are useless due to high-level semantic reasons.
+%Understanding and fixing this type of inefficiency problems often require
+%deep understanding of the program and are difficult to automate.
 For example, several Mozilla performance problems are caused by 
@@
 to understand the inefficiency of these loops,
-the fix strategies for these loops will likely vary from case to case.
+the fix strategies for these loops likely vary from case to case
+and are difficult to automate.
 %At high level, the patch often involves skip some computation that produces
@@
 {\textbf{Cross-iteration Redundancy}}:
-Loop iteration is the redundancy unit here:
 one iteration repeats
@@
 batching --- either caching the earlier computation results and skip
-some of the following iterations; or combining multiple iterations' work
+some following iterations; or combining multiple iterations' work
 together.
-For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
+For example, the bug shown in Figure~\ref{fig:GCC27733} is caused by
 redundant computation across different invocations of recursive function
@@
 {\textbf{Cross-loop Redundancy}}:
-A whole loop is the redundancy unit:
 one dynamic instance of a loop spends a big chunk, if not all, of its
@@
 Just like that in cross-iteration redundancy, memoization and batching
-are the typical fix strategies for this type of redundancy problems ---
-caching the earlier computation results and skip following redundant loops;
-or combining multiple loop instances together to avoid or alleviate redundancy.
-Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
+are the typical fix strategies for this type of loops.
+Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example. 
 The buggy loop counts how many previous siblings of the input \texttt{aNode} have the same name and URI. 
@@
 
-\subsection{Discussion}
-Coverage, actionability, and generality are the principles behind our taxonomy
-design. Intuitively, the categories above cover a lot of common inefficient
+\noindent\textbf{Threats to Validity}
+Intuitively, the categories above cover a lot of common inefficient
 loop problems; each sub-category is concrete enough to guide the design of a
 failure diagnosis tool; none of the categories above involve any application
-specific knowledges or heuristics. We will further assess our taxonomy
-through the design of \Tool (Section \ref{sec:design}) and 
-a real-world bug study (Section \ref{sec:eval_taxonomy}).
-
+specific knowledges or heuristics.
 Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.

### 2016-08-25 section/2_workless.tex
shrink through section 3 and 4

--- 2015-11-20 section/2_workless.tex
@@
 \label{sec:design}
-\Tool consists of a series of analysis that
-judges whether a given loop belongs to any root cause type discussed in
-Section \ref{sec:study_tax}.
-Its design
-follows the following principles.
-\begin{itemize}
-\item Failure diagnosis, not bug detection. \Tool will be  
+The design of \Tool follows three principles.
+First, \textit{symptom oriented}. \Tool will be  
 used together with other performance diagnosis tools \cite{SongOOPSLA2014}
+or profilers,
 and focus on a small
-number of loops that are most correlated with a specific performance symptom,
-instead of being applied to the whole program. Therefore, we will have different
+number of loops that are most correlated with a specific already-observed 
+performance symptom,
+instead of the whole program. Therefore, we will have different
 design trade-offs in terms of coverage and accuracy, comparing with 
 bug detection tools.
-
-\item Static-dynamic hybrid analysis. Static analysis alone
-will not be able to provide all the needed information to judge whether
+Second, \textit{static--dynamic hybrid}. Static analysis alone
+cannot provide all the needed information to judge whether
 a loop is inefficient. However, 
@@
 Therefore, we use a hybrid approach throughout our design.
-
-\item Sampling. Loop-related 
+Third, \textit{sampling}. Loop-related 
 performance problems have the unique nature of repetitiveness, which make 
@@
 sampling schemes for different analysis.
-\end{itemize}
+
+We envision \Tool to be used in the following way.
+Existing profilers and statistical debugging tool first
+identify suspicious loops that are most correlated with 
+certain performance 
+symptoms \cite{SongOOPSLA2014}. 
+\Tool will then apply a series of analysis to judge whether a given
+loop belongs to any root-cause type discussed in Section \ref{sec:study}
+and recommend corresponding fix strategy. This series of analysis could be
+conducted during either in-house diagnosis, where failure-triggering inputs
+are available, or production runs, with
+the run-time analysis component of \Tool running at user sites.
 
@@
 to figure out which are the side-effect instructions in a loop and hence
-decide whether a loop belongs to 0*, 0*1?, [0$|$1]*, or 1*. Second, to
-accurately determine 0*1? and [0$|$1]* loops, we use
+decide whether a loop might belong to 0*, 0*1?, [0$|$1]*, or 1*. Second, to
+determine whether 0*1? and [0$|$1]* loops are indeed inefficient
+under specific workload, we use
 dynamic analysis to figure out what portion of loop iterations are
@@
 caller a side-effect instruction.
+\comment{
 We consider all calls to library functions or through function pointers 
@@
 unless the library functions are specially marked by us in a white list.
+}
 This analysis is complete, but not sound. We may identify side-effect
-instructions that are actually not.
+instructions that are actually not. %to be moved to threats to validity
 
@@
 it is a [0$|$1]* loop; if there is no side-effect instructions inside $l$,
-$l$ is either a 0* or a 0*1? loop.
-In the last case, \Tool further checks all the loop exit-blocks. If there 
-exists an exit-block of $l$ that contains a side-effect instruction and is  
-post-dominated by another exit-block of $l$, this is a 0*1? loop.
-For example, line 5 in Figure \ref{fig:Mozilla347306} is such an exit block.
-Otherwise, $l$ is a 0* loop.
+$l$ is either a 0* or a 0*1? loop, which will be differentiated by checking
+all the loop exit-blocks.
+%If there 
+%exists an exit-block of $l$ that contains a side-effect instruction and is  
+%post-dominated by another exit-block of $l$, this is a 0*1? loop.
+For example, the loop in Figure \ref{fig:Mozilla347306} is 0*1?, because 
+its exit block on Line 5 contains side effects.
 
+\comment{
 Note that since the 1* pattern contains the least amount of information
@@
 for this loop (e.g., cross-iteration or cross-loop redundancy).
+}
 
-%TODO Shan will rewrite the next two paragraphs
-\subsubsection{Dynamic Monitoring}
+\subsubsection{Dynamic monitoring}
 \label{sec:d_workless}
 
-Except for 0*, none of the other three type of loops are inefficient for sure.
-We need dynamic analysis to figure out what portion of loop iterations are
-resultless at run time, which will help decide whether the loop worths fixing.
+Further checking is conducted to determine whether 0*1? and [0$|$1]* 
+loops are inefficient.
 
 For a 0*1? loop, since it only generates results in the last iteration, we 
-only need to know the total number of loop iterations 
+only need to know the total number of loop iterations of each loop instance
 to figure out the loop
@@
 \texttt{True} after each side-effect instruction. It will be used to help
-count the number of side-effect iterations. For performance concerns,
+count the number of side-effect iterations. 
+\comment{
+For performance concerns,
 before instrumenting side-effect blocks, we check whether there are 
@@
 block B, we only instrument block A to update \texttt{HasResult}. 
+}
 

### 2016-08-25 section/3_redundancy.tex
shrink through section 3 and 4

--- 2016-03-23 section/3_redundancy.tex
@@
 
-\subsubsection{Design overview}
 We will compare the computation of different iterations
@@
 originate from the same source code $C$, 
-a naive approach is to record the value read by
+a naive approach is to record and compare the value read by
 every memory read instruction in $c_1$ and $c_2$. 
-We will know whether $c_1$ and $c_2$ are redundant with each other by comparing
-these values.
-Of course, we could do better by checking fewer instructions, as
-some of these values are determined by values read earlier in $c_1$ and/or 
+%We will know whether $c_1$ and $c_2$ are redundant with each other by comparing
+%these values.
+We could do better by checking fewer instructions, as
+some of these values are determined by values read earlier in $c_1$ and
 $c_2$. Informally speaking, we only need to compare \textit{input}
 values of $c_1$ and $c_2$ to decide whether they are redundant with each other. 
-We will present our formal definition of \textit{input} values, and
-how we identify and record them in
-Section \ref{sec:dependence}.
+We will present formal definition of \textit{input} and the detailed algorithms
+in Section \ref{sec:dependence}.
 
@@
 backward static slicing 
-from these instructions, considering both control and data
-dependency. For every memory read instruction $r$ 
+from these instructions, considering control and data
+dependency. For every memory read $r$ 
 (\texttt{read(v)}) that static slicing encounters, \Tool checks whether $r$
@@
 programs.
-
 The analysis for cross-iteration and cross-loop redundancy analysis is similar
@@
 %it is easy to know whether read or write conducted on them are applied to the same address. 
-We omit encountered constant values through slicing, because constant values will not affect the redundancy judgement.
+We omit encountered constant values through slicing, as they do not affect redundancy judgement.
 
+\comment{
 Note that another possible approach is to simply record and compare what
@@
 \texttt{FALSE}).
+}
 
@@
 
-%TODO why not directly judge side-effect values
-
-\paragraph{Example}
-Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache,
-containing a cross-loop redundancy bug. 
-The \texttt{for} loop starting on line 7 
-searches a string \texttt{source} for a target sub-string 
-\texttt{target}. Since the outer loop, which starts on line 2, appends one 
-character to \texttt{source} in every iteration (line 30), 
-every execution of the \texttt{for} loop is working on a similar 
-\texttt{source} string from its previous execution, with a lot of redundancy.
-
 \begin{figure}
@@
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
-  \caption{A cross-loop redundant bug in Apache}
+  \caption{A cross-loop redundant bug in Apache (The \texttt{for} loop on line 7 
+searches a string \texttt{source} for a target sub-string 
+\texttt{target}. Since the outer loop on line 2 appends one 
+character to \texttt{source} in every iteration (line 30), 
+the \texttt{for} loop is always working on a similar 
+\texttt{source} from its previous execution, with a lot of redundancy.) 
+}
   \label{fig:Apache34464}
@@
 
+\comment{
 Take the simple loop at line 10 of Figure~\ref{fig:Apache34464} as an example.
@@
 in Section \ref{sec:perf}.
+}
 
@@
 After identifying \textit{inputs} using static analysis, 
-\Tool then instruments the program to record \textit{inputs} values at run time.
+\Tool instruments the program to record \textit{inputs} values at run time.
 %Specifically, we will assign
@@
 %will be recorded at run time with the execution of a source instruction.
-The run-time trace will also include delimiters and meta information that allows
-trace analysis to differentiate values recorded from different instructions, 
-loop
-iterations, loop instances, and so on.
+The run-time trace also includes information that
+differentiate values recorded from different instructions, loop
+iterations, loop instances, etc.
 %TODO
@@
 whether the loops under study contain cross-iteration or 
-cross-loop redundancy. We will first present our high-level algorithms, followed
-by the exact implementation in our prototype.
+cross-loop redundancy. 
+%We will first present our high-level algorithms, followed
+%by the exact implementation.
 
 \paragraph{High-level algorithms}
-For cross-iteration redundancy, we need to answer two questions. 
-First, how to judge whether
-two iterations are doing redundant work?
-Second, is a (dynamic) loop problematic when it contains only few 
-iterations that are
-redundant with each other?
-
-Our answer to these two questions stick to one principle: there should be
+We need to answer two questions:
+how to judge whether
+two iterations or loop-instances are doing redundant work, and
+how to judge whether a loop contains sufficient redundant
+computation to be inefficient.
+Our answer stick to one principle: there should be
 sufficient amount of redundant computation to make a loop likely culprit
 for a user-perceived performance problem and to make itself worthwhile to
-get optimized by developers. Consequently,
-for the first question, \Tool takes a strict 
-definition --- only iterations that are doing exactly the same computation are
-considered redundant. Since one iteration may not contain too much computation,
-a weaker definition here may lead to many false positives. For the 
-second question, we believe there should be a threshold. In our current 
+get optimized by developers.
+
+For the first question, \Tool takes a strict 
+definition for cross-iteration redundancy and a looser definition for
+cross-loop redundancy checking. Specifically,
+two iterations that conduct exactly the same computation are
+considered redundant; two loop instances that conduct largely
+the same computation are considered redundant.
+The rationale is that 
+a whole loop instance contains a lot of computation, much more than
+one iteration in general. Even if only part of its computation
+is redundant, it could still be the root-cause of a user-perceived performance
+problem and worth developers' attention. 
+In practice, we rarely see different loop 
+instances doing exactly the same computation.
+In cross-loop redundancy examples shown in 
+Figure~\ref{fig:Mozilla477564} and
+Figure~\ref{fig:Apache34464}, each loop instance is doing similar, but not
+exactly the same, work from its previous instance.
+For the second question, we believe there should be a threshold. 
+A loop will be considered inefficient if its \textit{redundancy rate} goes
+beyond the threshold.
+
+\comment{
+In our current 
 prototype,
@@
 we consider the loop to be cross-iteration redundant. 
+}
 %when the number of distinct iterations is less than half of the total iterations 
@@
 are doing redundant work. 
+}
 %The problem for this bug is that developers say that the performance 
@@
 %or I did not find the correct codes.
-}
 
-For cross-loop redundancy, we need to answer similar questions:
-how to judge whether two loop instances are doing redundant work?
 %should they contain exactly the same number of iterations and doing exactly
@@
 %are redundant with each other?
-
-Following the same principle discussed above, we have slightly different
-answers here.
-We do not require two loop instances to
-conduct exactly the same computation to be considered redundant. The rationale
-is that a whole loop instance contains a lot of computation, much more than
-one iteration in general. Even if only part of its computation
-is redundant, it could still be the root-cause of a user-perceived performance
-problem and worth developers' attention.
-
-In practice, we rarely see cases where different loop 
-instances are doing exactly the same computation.
-In cross-loop redundancy examples shown in 
-Figure~\ref{fig:Mozilla477564} and
-Figure~\ref{fig:Apache34464}, each loop instance is doing similar, but not
-exactly the same, work from its previous instance.
 
@@
 $l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
-all input instructions as the \textit{cross-loop redundancy rate} between
+all input instructions as the \textit{redundancy rate} between
 $l_1$ and $l_2$.
@@
 edit-distance between the two sequences of values returned by $I$ in the two
-loop instances. The exact formula is the following:
+loop instances, denoted by $SeqA$ and $SeqB$. 
+The exact formula is the following:
 
@@
 
+\vspace{-0.1in}
 \[
 \Scale[0.8]{
-	Redundancy(I) =  \frac{dist(SeqA,SeqB) - (len(SeqA) - len(SeqB))}{len(SeqA)}
+	Redundancy(I) =  \frac{EditDistance(SeqA, SeqB) - |Length(SeqA) - Length(SeqB)|}{max(Length(SeqA), Length(SeqB))}
 }
@@
 
+\comment{
 Here, $SeqA$ and $SeqB$ represent the two value sequences corresponding to $I$
@@
 redundancy value.
+}
 
@@
 
-\paragraph{Cross-iteration redundancy analysis}
-Our high-level sampling strategy is straightforward:
-randomly decide at the
+For cross-iteration redundancy analysis,
+we randomly decide at the
 beginning of every iteration whether to track the values returned by
 input instructions in this iteration.
-
 The implementation is similar with previous sampling work 
@@
 Specifically, we create a clone of the original
-loop iteration code, including functions called by the loop directly or
-indirectly, and insert value-recording instructions along the
+loop iteration code, 
+%including functions called by the loop directly or indirectly, 
+and insert value-recording instructions along the
 cloned copy. 
-We then insert a code snippet that conducts random decision to
-the beginning of a loop iteration. 
+We then insert a code snippet that randomly decides to execute the
+cloned copy or the original copy at the beginning of a loop iteration. 
+\comment{
 Two variables \texttt{CurrentID}, which is initialized as 0, 
@@
 generated.
+}
 
@@
 
-\paragraph{Cross-loop redundancy analysis} 
+For cross-loop redundancy analysis,
 We randomly decide at the beginning
@@
 
-First, we avoid tracking multiple read instructions that we can statically 
+First, we avoid tracking multiple reads that we can statically 
 prove to return the same value.
@@
 LLVM is conservative in lifting heap/global variables out of
-a loop, for fear of changing the location of potential exceptions, etc.
+a loop.
+%, for fear of changing the location of potential exceptions.
 \Tool conducts a best-effort
@@
 in Figure~\ref{fig:Mozilla477564}, and hence only traces them once
-outside the loop. This analysis is sound but not complete.
+outside the loop. 
+\comment{
+This analysis is sound but not complete.
 \Tool may miss some loop invariants. For in-house debugging, since we know
@@
 variable related optimization.
+}
 
-Second, we leverage the scalar evolution analysis in LLVM to remove the 
+Second, we leverage the scalar evolution (SE) analysis in LLVM to remove the 
 monitoring to some loop-induction related variables.
-The scalar evolution analysis can tell which variables are
+SE analysis can tell which variables are
 loop-induction variables (e.g., \texttt{i} on line 10
 of Figure~\ref{fig:Apache34464}) and what are their strides. 
-We then use this information in two ways. 
-One is for cross-iteration redundancy checking.
-If a loop iteration's input set contains a loop-induction
+In cross-iteration redundancy checking,
+if a loop iteration's input set contains a loop-induction
 variable, we know different iterations' inputs would be different and 
-hence conclude that there is no cross-iteration redundancy without any
+hence conclude that there is no redundancy without
 run-time analysis.
-The other is for cross-loop redundancy checking.
-When the address of a memory read is a loop induction variable, such as
+In cross-loop redundancy checking,
+when the address of a read is a loop induction variable, such as
 \texttt{source[i]} on line 10 of Figure~\ref{fig:Apache34464},
-we only record the address range at run time (i.e., the start and the
-end), instead of every value returned by the memory read.
+we only record the address range at run time,
+instead of every value returned by the memory read.
 This optimization could lead to false positives ---
@@
 \label{sec:redundant_fix}
-\Tool suggests how to fix an inefficient loop to developers.
+
+\Tool suggests a fix strategy for each inefficient loop 
+and provides related information for carrying out that strategy.
 This process is straightforward following our taxonomy discussion in 
@@
 Once a loop is identified as \emph{resultless}, \Tool will suggest
-the loop to be completely deleted, in case of 0$^*$ resultless, or
-conditionally skipped, in case of [0$|$1]*; \Tool will suggest a 
-data-structure change in case of 0*1? loops.
+the loop to be deleted in case of 0$^*$,
+conditionally skipped in case of [0$|$1]*, or a
+data-structure change in case of 0*1?.
+\Tool also reports side-effect instructions 
+and what percentage of loop iterations executes each such instruction,
+helping developers refactor the loop or change data structures.
 
@@
 extra analysis to
-decide whether batching or memoization should be suggested to fix the
-redundancy problem.
-
+decide whether batching or memoization should be used. 
 For cross-iteration redundancy, \Tool suggests batching if the
 redundancy is related to I/O operations and suggests memoization otherwise.
-Specifically, 
-when the only side effect of a loop is from I/O operations
-and the same statement(s) is executed in every loop iteration, \Tool reports 
-this
-as an I/O related redundancy problem and suggests batching as a potential fix
-strategy. Otherwise, \Tool suggests memoization.
+Specifically, when the only side effect of a loop is from I/O operations
+and the same statement(s) is executed in every iteration, \Tool suggests
+batching the specific I/O operations.
+Otherwise, \Tool suggests memoization, and reports
+input instructions that lead to redundant computation and redundancy rate.
 
@@
 buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
-we recommend memoization. Instead, if the side effect is to update
+we recommend memoization. If the side effect is to update
 a sequence of memory locations, with the number of locations increasing
@@
 hence batching is suggested.
-
-In addition to the above high-level fix strategies, \Tool can also provide some 
-detailed information to help developers design the patch.
-For example, in case of memoization fix strategy,
-since \Tool knows what exactly are the memory reads that return the same values
-again and again, it can help decide what to memoize; in case of
-I/O-related batching, \Tool points out the exact I/O operations that should
-be considered batching; and so on. 
-Generating complete patches is out of the scope of \Tool.
-
-%TODO what does batching mean for cross-loop redundancy???
+\Tool will also report
+the memory reads that return the same values
+again and again, which can help decide what to memoize.
 

### 2016-08-25 section/evaltax.tex
shrink through section 3 and 4

@@
 
-\input section/tab_appbug
+%\input section/tab_appbug
 \input section/tab_root
-
-The root-cause taxonomy presented in Section \ref{sec:study} is the foundation
-of \Tool. In this section,
-we quantitatively 
-assess the coverage, actionability, and generality of our taxonomy using
-a set of
-real-world inefficient loop problems collected by previous work
-\cite{SongOOPSLA2014,PerfBug}.
 
@@
 Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
-databases of five representative open-source software projects, as 
-shown in Table \ref{tab:app_bug}. Through a mix of random sampling and 
+databases of five representative open-source software projects:
+(1) Apache suite, including HTTPD web server written in C/C++,
+TomCat server written in Java, and Ant build management tool in Java;
+(2) Chromium Google Chrome browser in C/C++;
+(3) GCC compiler suite in C/C++;
+(4) Mozilla suite, including Firefox web browser and Thunderbird
+Email client in C/C++ and JavaScript; 
+(5) MySQL database server in C/C++.
+Through a mix of random sampling and 
 manual inspection, they 
@@
 hence are the target of the study 
-here\footnote{The definition of ``loop-related'' in this paper is a little
+here.
+\comment{
+\footnote{The definition of ``loop-related'' in this paper is a little
 bit broader than earlier paper~\cite{SongOOPSLA2014}, which only considers
@@
 these bugs. 
+}
 
@@
 
-\paragraph{Coverage}
+\textit{Coverage:}
 As shown in Table \ref{tab:root}, 
@@
 Not surprisingly, 0* loops
-are rare in mature software. In fact, no bugs in this
-benchmark suite belong to this category.
+are rare in mature software. 
+%In fact, no bugs in this
+%benchmark suite belong to this category.
 All other root-cause sub-categories are well represented.
 
-\paragraph{Actionability}
-As demonstrated in Table \ref{tab:root}, 
+\textit{Actionability:}
+As shown in Table \ref{tab:root}, 
 the root-cause categories in our taxonomy are well correlated with
@@
 This indicates that our taxonomy is actionable --- once the root cause
-is identified, developers roughly know how to fix the problem.
+is identified, developers roughly know how to fix.
 For example, 
@@
 
-\paragraph{Generality}
+\textit{Generality:}
 The root-cause categories in our taxonomy are designed to be 
@@
 
-\subsection{Caveats} 
+\subsection{Threats to Validity} 
 What presented above reflects our best effort in assessing our root-cause
@@
 or not.
-We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
-whether the root-cause of a performance problem is related to loops or not.
+%We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
+%whether the root-cause of a performance problem is related to loops or not.
 We do not intentionally ignore any aspect of loop-related performance problems. 

### 2016-08-25 section/5_exper.tex
extract table

--- 2016-08-17 section/5_exper.tex
@@
 
-\begin{table}
-  \centering
-  %\scriptsize
-  \tiny
-  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
-  \newcommand{\No}[0]{-}
-  \begin{tabular}{lccccc}
-    \toprule
-	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
-     \cmidrule(lr){2-4}
-     \cmidrule(lr){5-6}
-     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
-    \midrule
-    Mozilla347306 &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\ 
-    Mozilla416628 &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$        &  $2.41\%\pm1.58\%$   & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
-    \midrule
-     MySQL27287   &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$        &   -                  & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
-     MySQL15811   &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
-    \midrule
-      GCC46401    &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\ 
-      GCC1687     & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
-      GCC27733    & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
-      GCC8805     & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
-      GCC21430    & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
-      GCC12322    & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
-   \bottomrule
-   \end{tabular}
-  %\nocaptionrule
-  \caption{Run-time overhead of applying \Tool to the buggy loop
-    (only non-extracted benchmarks are shown). 
-  -: dynamic analysis is not needed;
-  /: not applicable.}
-  \label{tab:performance}
-\end{table}
+\input section/overhead_tab.tex
 

### 2016-08-25 section/5_exper.tex
finish shrinking

@@
 
-\paragraph{Implementation and Platform}
+\noindent\textbf{Implementation and Platform}
 We implement \Tool in LLVM-3.4.2 \cite{llvm}, and conduct our
@@
 
-\paragraph{Benchmarks}
-Note that \Tool is a tool that helps diagnose already-manifested performance problems,
-not a detection tool that can help predict not-yet-manifested
+\noindent\textbf{Benchmarks}
+\Tool is a diagnosis tool that helps understand and fix 
+already-manifested performance problems,
+not a detection tool that help predict not-yet-manifested
 problems. Consequently, our benchmarks are performance problems that have already
-happened in real world, and we will reproduce these problems to evaluate \Tool.
-To conduct a thorough evaluation, we use
+happened in real world, and we will reproduce them to evaluate \Tool.
+For a thorough evaluation, we use
 benchmarks from two different sources.
 
-First, we evaluate \Tool on all bugs, 18 in total, that we can reproduce 
-among the 45 bugs listed in Table \ref{tab:root}. 
-Among these 18, seven are extracted from Java or JavaScript
-programs and re-implemented in C++, as \Tool currently only handles C/C++
-programs; one is extracted from a very old version of Mozilla that can no longer be
-compiled as it is.
+First, \emph{general} benchmark suite.
+We evaluate \Tool on all bugs, 18 in total, that we can reproduce 
+among the 45 bugs discussed in Section \ref{sec:eval_taxonomy}. 
+These 18 bugs cover a wide variety of inefficiency root causes, as 
+shown in Table~\ref{tab:benchmarks}. 
+We use the problem-triggering inputs reported by real-world
+users in \Tool run-time analysis.
+Among these 18, seven are extracted from Java/JavaScript
+programs.
+%, as \Tool currently only handles C/C++
+%programs; one is extracted from a very old version of Mozilla that can no longer be
+%compiled as it is.
 %These 18 bugs include all the benchmarks used in the recent
@@
 %The extraction is conducted by XXX.
-When we extract code, we try our best to keep all bug-related data structures,
-caller functions, and callee functions intact, and re-implement them in C++, 
-following the original data flow and control flow. For these extracted benchmarks, 
-we design bug-triggering inputs for them based on the bug-triggering inputs in 
-the original bug reports and the mapping relationship between inputs of original programs 
-and re-implemented programs.
-Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
-shown in Table~\ref{tab:benchmarks}. 
-We will refer to this set of bugs as our \emph{general} benchmark suite.
+For these benchmarks, we did our best to keep all bug-related data structures
+and caller/callee functions intact, and re-implement them in C++
+following the original data and control flow. 
+%Their
+%bug-triggering inputs are produced based on the bug-triggering inputs in 
+%the original bug reports.
 
-Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
-listed in Table \ref{tab:root}, but they are too difficult to be reproduced.
-First, they all depend on 
-special hardware/software environment that our machines are not equipped with.
-For example, some bugs can only be triggered on Windows, and some depend on 
-.Net libraries. 
-Furthermore, the bug-related code for these 27 cases
-cannot be easily extracted or reimplemented, as we did for the eight 
-benchmarks mentioned above. 
+Note that, we expect \Tool to also work for most, if not all, of 
+the remaining 27 bugs listed in Table \ref{tab:root}.
+However, these 27 bugs are too difficult to be reproduced, as they 
+depend on special hardware/software environment (e.g., Windows OS and 
+.Net libraries) and cannot be easily extracted or reimplemented. 
 For example, some bugs are related to GUI widgets, which are too complicated to 
-re-implement or emulate. As another example, some bugs' inefficient 
-loops traverse big graphs. Although we can extract the buggy code regions, it is 
-too difficult to figure out the bug-triggering inputs
-(i.e., the graphs) without reproducing the original bugs.
+re-implement. Some bugs' inefficient 
+loops traverse big graphs, whose bug-triggering inputs
+(i.e., the graphs) are difficult to figure out 
+without reproducing the original bugs.
 
@@
 for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
-we evaluate \Tool on \emph{all} of these 21 bugs.
-Due to the focus of Toddler, all of these bugs 
-are related to misusing basic data structures in Java, like ArrayList, HashSet, 
-HashMap, and LinkedList. We extract these bugs and re-implemented them in 
-C/C++, following the procedure discussed above. In doing so,
+we evaluate \Tool on \emph{all} of them.
+Due to the focus of Toddler, all of these bugs are caused by inefficient
+\textit{nested} loops and only cover two types of inefficiency root causes,
+as shown in Table \ref{tab:benchmarks}.
+We extract these bugs and re-implemented them in 
+C/C++;
 we also re-implement basic Java data structures following a recent version of 
-\texttt{openjdk}. At the end, each extracted benchmark contains at least five
-loops, except for two cases where only four loops exist in the extracted version.
+\texttt{openjdk}. Each extracted benchmark contains at least five
+loops, except for two that contain four loops each.
 
-We use Toddler benchmark suite for two reasons.
-First, it provides a large set of 
-repeatable inefficient loop problems that we can access. 
-Second, it was set up for a completely different reason and with a different 
-methodology from our
-\emph{general} benchmark suite,
-and hence can well complement the \emph{general} suite.
-We should also note that, Toddler focuses on inefficient nested loops, and hence its
-benchmark bugs only cover two types of inefficiency root causes,
-as shown in Table \ref{tab:benchmarks}.
+The general benchmark suite and Toddler benchmark suite both provide
+a large set of repeatable inefficient loop problems that we can access. 
+At the same time, they were initially set up for different reasons and
+methodologies,
+and hence well complement each other.
+All the benchmarks led to severe performance problems.
+After developers fixed these problems, the performance of each benchmark improves
+4X -- 500X under the user-reported workload in our experiments.
 
-\paragraph{Metrics}
-Our experiments are designed to evaluate \Tool from three main aspects:
-(1) 
-\textit{Coverage}. Given our benchmark suite that covers a wide variety
-of real-world root causes, can \Tool identify all those root causes?
-(2)
-\textit{Accuracy}. 
-When analyzing non-buggy loops, will \Tool generate any false positives?
-(3) 
-\textit{Performance}.
-What is the run-time overhead of \Tool?
-
-\paragraph{Evaluation settings}
+\noindent\textbf{Evaluation settings}
 Our evaluation uses existing statistical performance diagnosis
@@
 
-For all benchmarks we use, real-world
-users have provided at least one problem-triggering input in their on-line 
-bug reports. We use these inputs in our run-time analysis.
-
-As discussed in Section \ref{sec:design}, our analysis contains 
-several configurable thresholds. In our evaluation,
-we use 0.001 as the \textit{resultful rate} threshold for identifying
+We use 0.001 as the default \textit{resultful rate} threshold for identifying
 0*1? 
@@
 and [0$|$1]* resultless loops; we use 
-0.5 as the \textit{redundancy rate} threshold for identifying redundant loops.
+0.5 as the default \textit{redundancy rate} threshold for identifying redundant loops.
 %, and 
@@
 %the number of distinct iterations is less than half of the total iterations).
-
-All the analysis and performance results presented below regarding
-cross-loop analysis is obtained using $1/100$ sampling rate; all the
-results regarding cross-iteration analysis is obtained using $1/1000$ sampling
-rate. We use sparser sampling rate in the latter case, because there tend to
-be more loop iterations than loop instances.
+We use $1/100$ sampling rate for cross-loop redundancy analysis and 
+$1/1000$ sampling rate for cross-iteration redundancy analysis
+(there tend to be more loop iterations than loop instances).
 All our diagnosis results require only \textbf{one} run under the 
 problem-triggering input.
+All our performance results are obtained by taking average of \textbf{ten} runs, 
+with the variation among different runs always less than 5\%.
 
-More discussions about all the parameters/thresholds presented above, including
-how to set them and how sensitive they are, are discussed in Section
-\ref{sec:sensi}.
+%More discussions about all the parameters/thresholds presented above, including
+%how to set them and how sensitive they are, are discussed in Section
+%\ref{sec:sensi}.
 
@@
 \Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
-suggests fix strategies that exactly match what developers took in practice
+suggests fix strategies that match what developers took in practice
 for 33 out of \allbugs cases.
@@
 
-Second, the fix strategy taken by developers is related to but not exactly the same as
+Second, the fix strategy taken by developers is related to
 what suggested by \Tool.
@@
 GCC
-to be less performance-optimal than before. However, GCC developers feel
-that it is worthwhile considering the slow-down caused by the original loop.
+to be less performance-optimal than before. 
+%However, GCC developers feel
+%that it is worthwhile considering the slow-down caused by the original loop.
 
@@
 the performance of \Tool is good. The overhead is consistently under or around 5\% 
-except for one benchmark, Mozilla\#347306. We believe \Tool is promising for potential production
+except for one benchmark, Mozilla\#347306. 
+We believe \Tool is promising for potential production
 run usage.
 We can easily further lower the overhead through sparser sampling.
-As we will discuss later, 
-the current diagnosis results are obtained by running the
-program only \textbf{once} under the problem-triggering workload.
-If we use sparser sampling, more failure runs will be needed to obtain good
-diagnosis results.
+%the current diagnosis results are obtained by running the
+%program only \textbf{once} under the problem-triggering workload.
+%If we use sparser sampling, more failure runs will be needed to obtain good
+%diagnosis results.
 
@@
 analysis lead to over 100X slowdown for six benchmarks.
-
 The benefit of static optimization is also non-trivial. 
-For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
+For example, for MySQL\#15811 and MySQL\#27287, static analysis alone
+(i.e., no run-time overhead) can
 judge that they do not contain cross-iteration redundancy: the computation of 
 each iteration depends on loop induction variables, which are naturally different
-in different iterations. Consequently, run-time overhead is completely
-eliminated for these two benchmarks.
+in different iterations. 
 As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
@@
 \label{sec:sensi}
-\paragraph{Sampling rates}
+\noindent\textbf{Sampling rates}
 We have tried different sampling rates for redundancy analysis.
@@
 Mozilla\#416628 incurs the largest overhead (merely 4.51\%). 
-The diagnosis results remain the same for all but
-GCC\#12322, where too few samples are available
-to judge redundancy.
-
 When we lower the sampling rate from 1/1000 to 1/10000
@@
 %In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
-The diagnosis results remain 
-the same for all but GCC\#12322.
+In both cases,
+the diagnosis results remain 
+the same for all but GCC\#12322, where too few samples are available
+to judge redundancy.
 %If we increase the sampling rate to 1/100, we will 
@@
 
-\paragraph{Resultful and redundancy rate}
-Since the severity of resultless and redundant loops depends on
-workload, it is natural that \Tool uses two thresholds in its diagnosis.
+\noindent\textbf{Resultful and redundancy rate}
+Our default setting should work in most cases.
 In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
@@
 0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
-when the rate is 0.7. The trend is similar for resultless
-loop checking. 
-%XXX
-
-Our default setting %is obtained based on our experience
-should work for many problems.
+when the rate is 0.7. The trend is similar for resultless loop checking. 
 Developers can adjust these thresholds. 
@@
 loops. Based on our experiments, the difference between efficient and inefficient
-loops is usually obvious, based on these rates.
-
-\subsection{Comparison with other tools}
-
-Automated tools have been developed to detect inefficient loop bugs
-\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
-As discussed in Section \ref{sec:intro}, although these tools are very
-useful, they are not designed for failure diagnosis. 
-For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
-hence can only cover about half of the bugs in our \emph{general} benchmark suite.
-Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
-expensive than \Tool. 
-Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
-by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
-CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs, 
-which arise if a program fragment repeatedly iterates over a data structure, such as an array or list, that has not been modified between successive traversals of the data structure.
-Like Toddler, it targets nested loops.
-We expect it to detect a sub-set of the cross-loop redundancy
-loops and a sub-set of 0*1? resultless loops in our benchmark set.
-In summary, \Tool aims to explain performance problems that have 
-already manifested,
-yet bug detection tools aim to predict problems that may not have manifested.
-They are suitable for different usage scenarios.
-
-Comparing with existing profiling and performance
-statistical debugging technique \cite{SongOOPSLA2014}, \Tool provides much
-more detailed root-cause information. Instead of just identifying loops that
-are highly correlated-with/responsible-for the execution slowness, \Tool
-can accurately point out whether these suspicious loops are efficient or not,
-and which type of inefficiency a loop contains, if any, and make fix suggestions.
+loops is obvious based on these rates.

### 2016-08-25 section/6_related.tex
slight change to figure 3 explanation
finish shrinking

--- 2015-11-05 section/6_related.tex
@@
 
-\subsection{Performance Diagnosis}
 Profilers are the most commonly used tools that help developers understand
@@
 Jovic:2011:CMY:2048066.2048081,IntroPerf}.
-Different from our work, profiling aims to tell where 
+They aim to tell where 
 computation resources are spent, 
 not where and why computation resources are wasted. 
-The root cause code region of a performance problem often is not inside
+The root-cause code region of a performance problem often is not inside
 the top-ranked function in the profiling result \cite{SongOOPSLA2014}.
@@
 
-Recently, tools that go beyond profiling and provide more automated analysis
-have been proposed.
-StackMine~\cite{Han:2012:PDL:2337223.2337241} can
-identify slow call-stack patterns inside event handlers. The work by
-\citet{TaoAsplos2014} analyzes system traces to understand 
-performance impact propagation and 
-causality relationship among different system components. 
-X-ray~\cite{Attariyan:2012:XAR:2387880.2387910} helps identify inputs
-or configuration entries that are most responsible for performance problems.
-Although these techniques are all very useful, 
-they target different problems from \Tool. \Tool targets 
+Recently proposed tools go beyond profiling and provide more automated analysis.
+They can identify slow call-stack patterns inside event handlers
+\cite{Han:2012:PDL:2337223.2337241}, help understand performance causality
+relationship among system components
+\citet{TaoAsplos2014}, identify inputs 
+or configuration entries that are most responsible for performance problems
+\cite{Attariyan:2012:XAR:2387880.2387910},
+and estimate the performance impact of any
+potential optimization at any point of a multi-threaded program
+\cite{coz.sosp15}. 
+They all target different problems from \Tool. 
+\comment{
+\Tool targets 
 inefficient loops, a common
@@
 \Tool complements it by
-providing detailed root cause information and fix strategy suggestions through
-program analysis.
-
-\subsection{Performance Bug Detection}
+accurately pointing out whether the suspicious loop is inefficient,
+which type of inefficiency a loop contains if any, and 
+what is the best fix strategy.
 
@@
 As discussed in 
-Section \ref{sec:intro}, these tools are all useful in improving software
-performance, but are not suitable for performance diagnosis.
-With different design goals from \Tool, these bug detection tools are not 
-guided by any specific
+Section \ref{sec:intro}, these tools are all useful, 
+but are not suitable for performance diagnosis.
+Bug detectors are not guided by any specific
 performance symptoms. Consequently, they take different coverage-accuracy
@@
 categories and is more aggressive in identifying root-cause categories, because
-it is only applied to a small number of loops that are known to be highly
-correlated with the specific performance symptom under study.
-Performance-bug detection tools has to be more conservative and tries hard
-to lower false positive rates, because it needs to apply its analysis to the
+it is only applied to a few loops known to be highly
+correlated with a specific performance symptom.
+Performance-bug detection tools are more conservative and try hard
+to lower false positive rates, because they need to process the
 whole program, instead of just a few loops. This requirement causes bug
-detection tools to each focus on a specific root-cause category.
+detectors to each focus on a specific root-cause category.
 %In fact, most inefficient loops in our study are very difficult to be detected
@@
 %\cite{CARAMEL,IsilDillig.PLDI15}.
-Performance bug detection tools also do not aim to provide fix suggestions.
+Bug detectors also do not aim to provide fix suggestions.
 For the few that do provide \cite{CARAMEL}, they only focus on very specific
 fix patterns, such as adding a break into the loop. 
-In addition, dynamic performance bug detectors do not try to achieve any
-performance goals. None of them has tried applying sampling to their
-bug detection and often leads to 10X slowdowns or more.
+In addition, dynamic performance bug detectors often lead to 10X slowdowns or 
+more, and never tried sampling.
 
-\subsection{Other Techniques to Fight Performance Bugs}
+Automated tools have been developed to detect inefficient loop bugs
+\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
+As discussed above, these tools are good detection tools but not suitable for 
+diagnosis. 
+For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
+hence can only cover about half of the bugs in our \emph{general} benchmark suite.
+Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
+expensive than \Tool. 
+Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
+by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
+CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs, 
+which arise if a program fragment repeatedly iterates over a data structure, such as an array or list, that has not been modified between successive traversals of the data structure.
+Like Toddler, it targets nested loops.
+We expect it to detect a sub-set of the cross-loop redundancy
+loops and a sub-set of 0*1? resultless loops in our benchmark set.
 

### 2016-08-25 section/7_con.tex
check to icse format
finish shrinking

@@
 the most common type of real-world performance problems, inefficient loops,
-and provide fix-strategy suggestions to developers. It achieves the 
-coverage, accuracy, and performance goal of performance diagnosis by leveraging
-(1) a comprehensive root-cause taxonomy; (2) a hybrid static-dynamic program
+and suggest fix strategies to developers. It achieves the 
+coverage, accuracy, and performance goal by leveraging
+(1) a comprehensive root-cause taxonomy; (2) a hybrid program
 analysis approach; and (3) customized random sampling that is a natural fit for 
@@
 Our evaluation shows that \Tool can accurately identify detailed root causes
-of real-world inefficient loop problems and provide fix-strategy suggestions. 
-Future work can further improve \Tool by providing more detailed fix
-suggestions and providing more information to help diagnose and fix
+of real-world inefficient loops and suggest fix strategies.
+Future work can improve \Tool by providing more detailed fix
+suggestions and more information to diagnose and fix
 1* loops.
 
-\acks
-This work is supported in part by NSF grants IIS-1546543, CNS-1514256, CCF-1439091, and CCF-1514189; 
-and Alfred P. Sloan Research Fellowship.
+%\acks
+%This work is supported in part by NSF grants IIS-1546543, CNS-1514256, CCF-1439091, and CCF-1514189; 
+%and Alfred P. Sloan Research Fellowship.

### 2016-08-25 section/tab_root.tex
check in Linhai's updates
finish shrinking

@@
 \cmidrule{8-12}
-                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
+\# of Bugs            & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
 \hline
@@
 %\end{adjustwidth}
-\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
-(S: conditionally skip the loop; C: change the data structure)
+\caption{Distribution among different applications and fix strategies for bugs with each root-cause category.
+\footnotesize{
+(C: change data structure; S: conditionally skip loop; darker background means more correlation between root causes and fixes)
+}
 }

### 2016-08-26 section/1_under.tex
address linhai comments

@@
 qualitatively in this section and quantitatively 
-using real-world performance-bug suite in Section \ref{sec:eval_taxonomy}.
+using real-world performance bugs in Section \ref{sec:eval_taxonomy}.
 

### 2016-08-26 section/5_exper.tex
address linhai comments

@@
 in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
-top-5 suspicious loops in one of our benchmarks; it only generates side effects
+top-5 suspicious loop in one of our benchmarks; it only generates side effects
 in its last iteration, and hence is identified as 0*1? by static analysis. 

### 2016-08-26 section/1_under.tex
in the middle of moving threats to validity

@@
 
-\noindent\textbf{Threats to Validity}
-Intuitively, the categories above cover a lot of common inefficient
+Intuitively, the above categories above cover many common inefficient
 loop problems; each sub-category is concrete enough to guide the design of a
-failure diagnosis tool; none of the categories above involve any application
+diagnosis tool; none of these (sub-)categories involve application
 specific knowledges or heuristics.
-Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.
-For example, some loops may be vulnerable to false sharing problems or lock
-contention problems, which are out of the scope of our taxonomy.

### 2016-08-26 section/2_workless.tex
in the middle of moving threats to validity

@@
 \Tool considers two types of instructions as side-effect instructions:
-(1) write to heap or global variables;
-(2) write to a stack variable, defined outside the loop, and the update value
-may be used after the loop. The second condition is checked through liveness
-analysis.
+(1) writes to heap or global variables;
+(2) writes to a stack variable defined outside the loop and
+may be used after the loop.
+The second condition is checked through liveness analysis.
 \Tool also analyzes all functions called
@@
 }
-This analysis is complete, but not sound. We may identify side-effect
-instructions that are actually not. %to be moved to threats to validity
+ %to be moved to threats to validity
 

### 2016-08-26 section/evaltax.tex
in the middle of moving threats to validity

@@
 %TODO even for the other, there are things we could do ...
-
-\subsection{Threats to Validity} 
-What presented above reflects our best effort in assessing our root-cause
-taxonomy using a non-biased set of real-world inefficient loop problems that
-have been perceived by users and fixed by developers.
-
-The numbers presented above should be interpreted together with our methodology
-and should not be overly generalized.
-The performance bugs examined above cover a variety of applications, workload, 
-development environments and programming languages. 
-However, there are definitely uncovered cases, like problems in distributed systems
-and scientific computing systems, and others.
-
-Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
-on-line discussion to judge whether a bug report is about
-performance problems and whether 
-the performance problem under discussion is noticed and reported by users
-or not.
-%We follow the methodology used in previous work~\cite{SongOOPSLA2014} to judge 
-%whether the root-cause of a performance problem is related to loops or not.
-We do not intentionally ignore any aspect of loop-related performance problems. 
-Some loop-related performance problems may never be noticed by end users
-or never be fixed by developers, and hence skip our study. However,
-there are no conceivable ways to study them.
-
-\comment{
-We believe that the bugs in our study provide a representative sample of the 
-well-documented and
-fixed performance bugs that are user-perceived and loop-related in the studied 
-applications. 
-Since we did not set up the root-cause taxonomy to fit particular
-bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
-framework presented below will go beyond these sampled performance bugs. 
-}

### 2016-08-26 section/threats.tex
in the middle of moving threats to validity

\section{Threats to Validity}
\label{sec:threats}

Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.
For example, some loops may be vulnerable to false sharing problems or lock
contention problems, which are out of the scope of our taxonomy.

The static program analysis and optimization.
This analysis is complete, but not sound. We may identify side-effect
instructions that are actually not (Section \ref{sec:s_workless}).
The optimization discussed in Section \ref{sec:perf}.

The resuleless and redundancy rate thresholds could lead to false positives
and false negatives.

Our evaluation.
What presented above reflects our best effort in assessing our root-cause
taxonomy using a non-biased set of real-world inefficient loop problems that
have been perceived by users and fixed by developers.

The numbers presented above should be interpreted together with our methodology
and should not be overly generalized.
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are definitely uncovered cases, like problems in distributed systems
and scientific computing systems, and others.

Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
on-line discussion to judge whether a bug report is about
performance problems and whether 
the performance problem under discussion is noticed and reported by users
or not.
We do not intentionally ignore any aspect of loop-related performance problems. 
Some loop-related performance problems may never be noticed by end users
or never be fixed by developers, and hence skip our study. However,
there are no conceivable ways to study them.

\comment{
We believe that the bugs in our study provide a representative sample of the 
well-documented and
fixed performance bugs that are user-perceived and loop-related in the studied 
applications. 
Since we did not set up the root-cause taxonomy to fit particular
bugs in this bug benchmark suite, we believe our taxonomy and diagnosis
framework presented below will go beyond these sampled performance bugs. 
}

### 2016-08-26 section/0_intro.tex
shrink back to 10 pages. will work on threats to validity later

@@
 Static analysis alone cannot accurately identify 
-inefficiency root causes, because some inefficiency problems only
-happen or matter under specific workload. However, pure dynamic analysis will 
+inefficiency root causes, as some inefficiency only
+happens or matters under specific workload; dynamic analysis alone will 
 cause too large 

### 2016-08-26 section/1_under.tex
shrink back to 10 pages. will work on threats to validity later

@@
 \caption{A resultless 0*1? bug in Mozilla}
+\vspace{-0.05in}
 \label{fig:Mozilla347306}
@@
 \caption{A resultless [0$|$1]* bug in GCC }
+\vspace{-0.05in}
 \label{fig:GCC46401}
@@
 \caption{A cross-loop redundant bug in Mozilla }
+\vspace{-0.05in}
 \label{fig:Mozilla477564}
@@
 
-Intuitively, the above categories above cover many common inefficient
-loop problems; each sub-category is concrete enough to guide the design of a
+Intuitively, the above categories cover many common inefficient
+loop problems; each sub-category is concrete to guide the design of a
 diagnosis tool; none of these (sub-)categories involve application

### 2016-08-26 section/2_workless.tex
shrink back to 10 pages. will work on threats to validity later

@@
 (1) writes to heap or global variables;
-(2) writes to a stack variable defined outside the loop and
-may be used after the loop.
-The second condition is checked through liveness analysis.
+(2) writes to stack variables defined outside the loop and
+may be used after the loop (checked through liveness analysis).
 \Tool also analyzes all functions called

### 2016-08-26 section/6_related.tex
address linhai comments
finish threats to validity

@@
 
-Recently proposed tools go beyond profiling and provide more automated analysis.
+Recently proposed tools go beyond profiling.
 They can identify slow call-stack patterns inside event handlers
@@
 relationship among system components
-\citet{TaoAsplos2014}, identify inputs 
+\cite{TaoAsplos2014}, identify inputs 
 or configuration entries that are most responsible for performance problems

### 2016-08-26 section/threats.tex
finish threats to validity

@@
 
-Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.
-For example, some loops may be vulnerable to false sharing problems or lock
-contention problems, which are out of the scope of our taxonomy.
+\Tool does not cover all loop inefficiency problems.
+For example, it does not handle performance problems caused by
+cache-line false sharing in multi-core machines or lock
+contention issues. It also cannot provide useful fixing 
+suggestions for 1* inefficient loops, as discussed in 
+Section \ref{sec:coverage}.
 
-The static program analysis and optimization.
-This analysis is complete, but not sound. We may identify side-effect
-instructions that are actually not (Section \ref{sec:s_workless}).
-The optimization discussed in Section \ref{sec:perf}.
+The static analysis in \Tool could occasionally lead to inaccurate diagnosis.
+Specifically, \Tool static analysis could conservatively identify some
+non-side-effect instructions, such as a write to a heap variable that
+is not used after the loop, as having side effects 
+(Section \ref{sec:s_workless}). 
+The SE-based optimization discussed in Section \ref{sec:perf} could cause
+false positives in cross-loop redundancy diagnosis.
+These cases are all rare in practice and not encountered in our experiments.
 
-The resuleless and redundancy rate thresholds could lead to false positives
-and false negatives.
+Our default settings of resultless and redundancy rate thresholds 
+work well in our evaluation. However, they could potentially lead to false 
+positives and false negatives, as discussed in Section \ref{sec:sensi}.
 
-Our evaluation.
-What presented above reflects our best effort in assessing our root-cause
-taxonomy using a non-biased set of real-world inefficient loop problems that
-have been perceived by users and fixed by developers.
-
-The numbers presented above should be interpreted together with our methodology
-and should not be overly generalized.
-The performance bugs examined above cover a variety of applications, workload, 
+The results presented in Section \ref{sec:eval_taxonomy}
+and Section \ref{sec:experiment}
+should be interpreted together with corresponding methodologies
+and not be overly generalized.
+They reflect our best effort in evaluating our root-cause
+taxonomy and \Tool using a non-biased set of real-world inefficient loop 
+problems that have been perceived by users and fixed by developers.
+The benchmark suite covers a variety of applications, workload, 
 development environments and programming languages. 
@@
 and scientific computing systems, and others. 
-
-Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
-on-line discussion to judge whether a bug report is about
-performance problems and whether 
-the performance problem under discussion is noticed and reported by users
-or not.
-We do not intentionally ignore any aspect of loop-related performance problems. 
-Some loop-related performance problems may never be noticed by end users
-or never be fixed by developers, and hence skip our study. However,
-there are no conceivable ways to study them.
+Furthermore, although
+we did not intentionally ignore any aspect of loop-related performance problems,
+some loop-related problems may never be noticed by end users
+or never be fixed by developers, and hence may skip our evaluation. However,
+there are no conceivable ways to study them, particularly considering that 
+\Tool is designed to diagnose already-manifested performance problems not to
+predict not-yet-observed problems.
 

### 2016-08-26 section/0_intro.tex
minor changes, submitted

@@
 Performance bugs\footnote{We also refer performance bugs as performance problems
-following previous works in this area~\cite{PerfBug,Alabama,SongOOPSLA2014}} 
+following previous works in this area~\cite{PerfBug,Alabama,SongOOPSLA2014}.} 
 are software implementation mistakes that cause unnecessary performance
@@
 
-\begin{figure}
-\centering
-\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
-     morekeywords={+},keepspaces=true}
-  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC27733.c}}
-\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch; variable and 
-function names are simplified for demonstration purposes)}
-\label{fig:GCC27733}
-\end{figure}
-
 Figure~\ref{fig:GCC27733} shows a performance problem in GCC. 
@@
 code), and how it is inefficient, until several weeks later.
+
+\begin{figure}
+\centering
+\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+     morekeywords={+},keepspaces=true}
+  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC27733.c}}
+\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch; variable and 
+function names are simplified for demonstration purposes)}
+\vspace{-0.1in}
+\label{fig:GCC27733}
+\end{figure}
 

### 2016-08-26 section/5_exper.tex
minor changes. done

@@
 %and the remaining 6430 for common utilities. 
-experiments on a i5-3330S machine, with Linux 3.19 kernel.
+experiments on an i5-3330S machine, with Linux 3.19 kernel.
 
@@
 These 18 bugs cover a wide variety of inefficiency root causes, as 
-shown in Table~\ref{tab:benchmarks}. 
+shown in the upper half of Table~\ref{tab:benchmarks}. 
 We use the problem-triggering inputs reported by real-world
@@
 the remaining 27 bugs listed in Table \ref{tab:root}.
-However, these 27 bugs are too difficult to be reproduced, as they 
+However, these 27 bugs are too difficult to reproduce, as they 
 depend on special hardware/software environment (e.g., Windows OS and 
@@
 %contains 4--5 loops (how come you always have 4--5 loops??XXX). 
-Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
+Second, we evaluate \Tool on Toddler benchmark suite~\cite{Alabama, toddlerbuglist}.
 Toddler project provides the bug-triggering inputs and detailed explanation
@@
 \textit{nested} loops and only cover two types of inefficiency root causes,
-as shown in Table \ref{tab:benchmarks}.
+as shown in the bottom half of Table \ref{tab:benchmarks}.
 We extract these bugs and re-implemented them in 
 C/C++;
-we also re-implement basic Java data structures following a recent version of 
+we re-implement basic Java data structures following a recent version of 
 \texttt{openjdk}. Each extracted benchmark contains at least five
-loops, except for two that contain four loops each.
+loops, except for two cases with four loops each.
 
@@
 three sets of evaluation. First, we apply \Tool to the real root-cause loop to
-see if \Tool can correctly identify the root-cause category and provide
-correct fix-strategy suggestion. Second, we apply
+see if \Tool can correctly identify the root-cause category and suggest
+a fix strategy. Second, we apply
 statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
@@
 
-The six cases where the fix strategy suggested by \Tool does not match that of 
-developers fall into three categories.
+The six cases where \Tool and developers suggest/take different fix strategies
+fall into three categories.
 First, the fix strategy taken by developers is a subset of what suggested by 
@@
 cross-loop redundancy and 0*1? inefficiency. Consequently, \Tool suggests two
-corresponding fix strategies. In practice, the developers
+fix strategies. In practice, the developers
 acknowledge both types of inefficiencies, but the patches
@@
 \Tool suggests data-structure changes for these three cases. Developers' patches 
-still keep the original data structures and the original buggy loops, but they
-did use hash-sets, which contain the same content as the arrays do,
+still keep the original data structures, but they
+did use hash-sets, which contain the same content as the arrays,
 to help conditionally skip the loops.
@@
 some loops are indeed cross-iteration/loop redundant or indeed producing
-results in only a tiny portion of all the iterations. However, those
+results in only a tiny portion of loop iterations. However, those
 problems are \textit{not} fixed by developers in their performance patches.
@@
 22 benign cases. % 11 out of 13 in the first benchmark set 
-In fact, this is not really a problem for \Tool in 
+In fact, this is not a problem for \Tool in 
 real usage scenarios, because statistical debugging or profiling can often
@@
 The benefit of static optimization is also non-trivial. 
-For example, for MySQL\#15811 and MySQL\#27287, static analysis alone
-(i.e., no run-time overhead) can
-judge that they do not contain cross-iteration redundancy: the computation of 
+For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
+judge that they do not contain cross-iteration redundancy (i.e., no run-time 
+overhead): the computation of 
 each iteration depends on loop induction variables, which are naturally different
@@
 the overhead is reduced from 12.18\% to 0.20\% for MySQL\#27287, 
-and from 20.53\% to 0.35\% for MySQL\#15811 respectively 
-(sampling is conducted consistently here).
+and from 20.53\% to 0.35\% for MySQL\#15811 respectively. 
+%(sampling is conducted consistently here).
 

### 2017-01-23 section/3_redundancy.tex
address linhai comments
fix some small issues

@@
 After identifying \textit{inputs} using static analysis, 
-\Tool instruments the program to record \textit{inputs} values at run time.
+\Tool instruments the program to record \textit{input} values at run time.
 %Specifically, we will assign
@@
 computation to be inefficient.
-Our answer stick to one principle: there should be
+Our answer sticks to one principle: there should be
 sufficient amount of redundant computation to make a loop likely culprit
@@
 $L$ contains.
-We only check redundancy between consecutive loop instances, because  
-checking that between every pairs of loop
-instances is time consuming.
+%We only check redundancy between consecutive loop instances, because  
+%checking that between every pairs of loop
+%instances is time consuming.
+{\color{red} We only check redundancy between consecutive loop instances.
+This could bring false negatives, but checking redundancy between every pairs of loop instances is time consuming.}
 
@@
 
-We calculate the redundancy for one input instruction $I$ by normalizing the
+{\color{red} We calculate the redundancy for one input instruction $I$ by using 1 to subtract the normalized
 edit-distance between the two sequences of values returned by $I$ in the two
@@
 The exact formula is the following:
-
+}
 %\[
@@
 \Scale[0.8]{
-	Redundancy(I) =  \frac{EditDistance(SeqA, SeqB) - |Length(SeqA) - Length(SeqB)|}{max(Length(SeqA), Length(SeqB))}
+	Redundancy(I) = 1 - \frac{EditDistance(SeqA, SeqB) - |Length(SeqA) - Length(SeqB)|}{min(Length(SeqA), Length(SeqB))}
 }
@@
 For cross-loop redundancy analysis,
-We randomly decide at the beginning
+we randomly decide at the beginning
 of every loop instance whether to track values for this instance. 
@@
 This process is straightforward following our taxonomy discussion in 
-Section \ref{sec:study}, as there is often only one or two natural fix 
+Section \ref{sec:study}, as there are often only one or two natural fix 
 strategies for each sub-category of root causes.

### 2017-01-25 section/evaltax.tex
address review-1

@@
 
+\comment{
 Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
@@
 here.
+}
+
+{\color{red} Our previous} work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
+databases of five representative open-source software projects:
+(1) Apache suite, including HTTPD web server written in C/C++,
+TomCat server written in Java, and Ant build management tool in Java;
+(2) Chromium Google Chrome browser in C/C++;
+(3) GCC compiler suite in C/C++;
+(4) Mozilla suite, including Firefox web browser and Thunderbird
+Email client in C/C++ and JavaScript; 
+(5) MySQL database server in C/C++.
+{\color{red} We manually inspected randomly sampled bug reports and identified 
+65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.}  
+Among these 65 problems, 45 problems are related to inefficient loops and 
+hence are the target of the study 
+here.
+
 \comment{

### 2017-02-01 section/3_redundancy.tex
address review-1
roll back some of my updates

@@
 $L$ contains.
-%We only check redundancy between consecutive loop instances, because  
-%checking that between every pairs of loop
-%instances is time consuming.
-{\color{red} We only check redundancy between consecutive loop instances.
-This could bring false negatives, but checking redundancy between every pairs of loop instances is time consuming.}
+We only check redundancy between consecutive loop instances, because  
+checking that between every pairs of loop
+instances is time consuming.
 
@@
 outside the loop.
+
 \comment{

### 2017-02-12 section/3_redundancy.tex
address reviewer concerns

@@
 
-{\color{red} We calculate the redundancy for one input instruction $I$ by using 1 to subtract the normalized
+{\color{red}
+We calculate the redundancy for an input instruction $I$ based on the
 edit-distance between the two sequences of values returned by $I$ in the two
-loop instances, denoted by $SeqA$ and $SeqB$. 
+loop instances
+and the lengths of the two sequences, denoted by $SeqA$ and $SeqB$. 
+The intuition is that the redundancy rate should be 1 if one sequence is the 
+sub-sequence of the other; and, the redundancy rate should be 0 if these two
+sequences are completely different.
+}
 The exact formula is the following:
-}
 %\[

### 2017-02-12 section/5_exper.tex
address review-1
roll back some of my updates
address reviewer concerns

@@
 loops, except for two cases with four loops each.
+%{\color{red} All re-implemented benchmarks used in our experiments are released on github~\cite{re-implemented}.}
 
@@
 
-To evaluate the coverage, accuracy, and performance of \Tool, we mainly conduct
-three sets of evaluation. First, we apply \Tool to the real root-cause loop to
-see if \Tool can correctly identify the root-cause category and suggest
-a fix strategy. Second, we apply
-statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
-and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
-have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
-to see how accurate \Tool is. Third, we evaluate the run-time performance of
-applying \Tool to the real root-cause loop.
-
 We use 0.001 as the default \textit{resultful rate} threshold for identifying
@@
 
+{\color{red}
+\noindent\textbf{Research questions to answer}
+We mainly conduct three sets of evaluation to answer three key research 
+questions regarding the coverage, accuracy, and performance of \Tool,
+
+\textbf{RQ1}.
+Can \Tool correctly identify inefficiency categories and suggest fix 
+strategies for many real-world loops? (Sec.\ref{sec:coverage})
+
+\textbf{RQ2}.
+Might \Tool report many false positives and hence waste developers' diagnosis
+effort? (Sec.\ref{sec:result_acc})
+
+\textbf{RQ3}.
+What is the run-time overhead of \Tool? (Sec.\ref{sec:result_perf})
+}
+
 \subsection{Coverage Results}
 \label{sec:coverage}
-Overall, \Tool provides good diagnosis coverage, as shown by the check-marks in Table~\ref{tab:benchmarks}
-(the ``Did \Tool Identify ..?'' columns). 
+{\color{red}
+To answer \textbf{RQ1}, we apply \Tool to real root-cause loops to see if 
+it can accurately identify inefficiency categories.
+As shown by the check-marks in Table~\ref{tab:benchmarks}
+(the ``Did \Tool Identify ..?'' columns), 
+\Tool does provide good diagnosis coverage.
+}
 \Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
@@
 %\input section/tab_top5
-
-As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
-false positive and 22 benign false positives in total for all the top five loops
+{\color{red}
+To answer \textbf{RQ2}, we apply
+statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
+and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
+have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
+to see how accurate \Tool is. 
+}
+{\color{red}
+As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 2 real
+false positive and 20 benign false positives in total for all the top five loops
 of the \allbugs benchmarks.
 
-Here, benign false positives mean that \Tool analysis result is true ---
-some loops are indeed cross-iteration/loop redundant or indeed producing
-results in only a tiny portion of loop iterations. However, those
-problems are \textit{not} fixed by developers in their performance patches.
+%TODO for Linhai: 
+%1. check the accuracy of the next two paragraphs
+%2. fill in the XXX and XXX in the next paragraph
+%3. change the false positive numbers in Table
+%4. change the true false positive and benign false positive numbers in other part of the paper
 
-There are several reasons for these benign performance problems. 
-The main reason is that they are not the main contributor to the 
-performance problem perceived by the users. This happens to 20 out of the
-22 benign cases. % 11 out of 13 in the first benchmark set 
-In fact, this is not a problem for \Tool in 
-real usage scenarios, because statistical debugging or profiling can often
-tell that these loops are not top contributors to the performance
-problems.
-Two cases happen when fixing the 
-identified redundant/resultless problems
-are very difficult and hence developers decide not to fix them.
+The two real false positives happen for benchmarks XXX and XXX.
+These two loops are identified as
+redundant and resultless by \Tool. However, they
+are very difficult to fix and hence are not changed in the patches.
+Since these two loops are ranked higher than the true positive loops by
+statistical debugging, they could cost (waste) \Tool users some effort during 
+performance diagnosis. Future work could try to prune these false positives
+by estimating the fix difficulty.
+
+\Tool also reports 20 benign false positives.
+In these cases, \Tool correctly identified truly inefficient loops.
+However, these loops are not the main contributors to the 
+performance problems perceived by the users, and hence are not
+fixed in patches. 
+Different from the two false positives discussed above, these 20 loops are
+ranked {\bf lower} than the true positive loops by statistical debugging, as
+well as by profillers,
+because of their low contributions to the perceived performance problems.
+Consequently, they will not cause extra diagnosis effort for \Tool users.
+}
 
@@
 
+{\color{red}
+To answer \textbf{RQ3}, we evaluate the run-time performance of
+applying \Tool to the real root-cause loop. 
+}
 As shown in Table \ref{tab:performance}, 

### 2017-02-12 section/evaltax.tex
address reviewer concerns

@@
 
-{\color{red} Our previous} work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
+Our previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
 databases of five representative open-source software projects:
@@
 (5) MySQL database server in C/C++.
-{\color{red} We manually inspected randomly sampled bug reports and identified 
+{\color{red} By manually inspecting a set of randomly sampled bug reports,
+previous work identified 
 65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.}  

### 2017-02-13 section/5_exper.tex
fix comments from Shan

@@
 {\color{red}
-As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 2 real
-false positive and 20 benign false positives in total for all the top five loops
+As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having five real
+false positives and 17 benign false positives in total for all the top five loops
 of the \allbugs benchmarks.
@@
 
-The two real false positives happen for benchmarks XXX and XXX.
-These two loops are identified as
+The five real false positives happen for benchmarks GCC\#8805 and GCC\#12322.
+These five loops are identified as
 redundant and resultless by \Tool. However, they
 are very difficult to fix and hence are not changed in the patches.
-Since these two loops are ranked higher than the true positive loops by
+Since these five loops are ranked higher than the true positive loops by
 statistical debugging, they could cost (waste) \Tool users some effort during 
@@
 
-\Tool also reports 20 benign false positives.
+\Tool also reports 17 benign false positives.
 In these cases, \Tool correctly identified truly inefficient loops.
@@
 fixed in patches. 
-Different from the two false positives discussed above, these 20 loops are
+Different from the five false positives discussed above, these 17 loops are
 ranked {\bf lower} than the true positive loops by statistical debugging, as
@@
 changing the redundancy rate threshold from 0.5 to any value between about
-0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
+0.1 and 0.66. We will have 1 more false negative and 1 fewer true false positive, 
 when the rate is 0.7. The trend is similar for resultless loop checking. 

### 2017-02-13 section/7_con.tex
fix comments from Shan

@@
 
+\section*{Acknowledgment}
+We thank the anonymous reviewers, Darko Marinov, and Ben Liblit for their comments.
+Our research has been supported by NSF (CNS-1563956, IIS-1546543, CNS-1514256, CCF-1514189, CCF-1439091), 
+and generous supports from Alfred P. Sloan Foundation and CERES Center for Unstoppable Computing.
+
 %\acks

### 2017-02-13 section/3_redundancy.tex
fix comments from Shan
revise linhai's recent revise

@@
 The intuition is that the redundancy rate should be 1 if one sequence is the 
-sub-sequence of the other; and, the redundancy rate should be 0 if these two
+sub-sequence of the other, and be 0 if these two
 sequences are completely different.
@@
 
+{\color{red}
+\Tool suggests a fix strategy for each inefficient loop based on the
+inefficiency category. Making this suggestion is straightforward for
+most categories, and requires a small amount of extra
+analysis occasionally. \Tool also
+provides related information for carrying out the suggested fix strategy. 
+}
+
+\comment{
 \Tool suggests a fix strategy for each inefficient loop 
@@
 strategies for each sub-category of root causes.
+}
 

### 2017-02-13 section/5_exper.tex
revise linhai's recent revise

@@
 \textbf{RQ1}.
-Can \Tool correctly identify inefficiency categories and suggest fix 
+Can \Tool correctly identify inefficiency categories and fix 
 strategies for many real-world loops? (Sec.\ref{sec:coverage})
@@
 To answer \textbf{RQ2}, we apply
-statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
-and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
-have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
-to see how accurate \Tool is. 
+statistical performance debugging \cite{SongOOPSLA2014} to all benchmarks
+and then apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
+have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}.
 }
 {\color{red}
-As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having five real
+Table \ref{tab:benchmarks} shows that \Tool is accurate, having five real
 false positives and 17 benign false positives in total for all the top five loops
@@
 redundant and resultless by \Tool. However, they
-are very difficult to fix and hence are not changed in the patches.
+are very difficult to fix and hence are not patched.
 Since these five loops are ranked higher than the true positive loops by
@@
 
-\Tool also reports 17 benign false positives.
-In these cases, \Tool correctly identified truly inefficient loops.
-However, these loops are not the main contributors to the 
-performance problems perceived by the users, and hence are not
+\Tool also reports 17 benign false positives. These are 
+correctly identified inefficient loops.
+However, they are not the main contributors to the perceived
+performance problems, and hence are not
 fixed in patches. 

### 2017-02-13 section/3_redundancy.tex
shrink to 10 pages

@@
   \centering
-  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+  \lstset{basicstyle=\ttfamily\fontsize{7}{8}\selectfont,
      morekeywords={+},keepspaces=true,numbers=left}
   \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
-  \caption{A cross-loop redundant bug in Apache (The \texttt{for} loop on line 7 
+  \caption{A cross-loop redundant bug in Apache 
+{\footnotesize{(The \texttt{for} loop on line 7 
 searches a string \texttt{source} for a target sub-string 
@@
 the \texttt{for} loop is always working on a similar 
-\texttt{source} from its previous execution, with a lot of redundancy.) 
+\texttt{source} from its previous execution, with a lot of redundancy.}}) 
 }
@@
 
-{\color{red}
 \Tool suggests a fix strategy for each inefficient loop based on the
@@
 provides related information for carrying out the suggested fix strategy.
-}
-
-\comment{
-\Tool suggests a fix strategy for each inefficient loop 
-and provides related information for carrying out that strategy.
-This process is straightforward following our taxonomy discussion in 
-Section \ref{sec:study}, as there are often only one or two natural fix 
-strategies for each sub-category of root causes.
-}
 
@@
 decide whether batching or memoization should be used. 
-For cross-iteration redundancy, \Tool suggests batching if the
-redundancy is related to I/O operations and suggests memoization otherwise.
-Specifically, when the only side effect of a loop is from I/O operations
-and the same statement(s) is executed in every iteration, \Tool suggests
-batching the specific I/O operations.
+For cross-iteration redundancy, \Tool suggests batching 
+I/O operations.
+when the only side effect of a loop is from I/O operations
+and the same statement(s) is executed in every iteration.
 Otherwise, \Tool suggests memoization, and reports

### 2017-02-13 section/5_exper.tex
shrink to 10 pages

@@
 \Tool is a diagnosis tool that helps understand and fix 
-already-manifested performance problems,
-not a detection tool that help predict not-yet-manifested
-problems. Consequently, our benchmarks are performance problems that have already
-happened in real world, and we will reproduce them to evaluate \Tool.
+already-manifested performance problems.
+Consequently, our benchmarks are performance problems that have already
+happened in real world.
 For a thorough evaluation, we use
@@
 %the original bug reports.
-
-Note that, we expect \Tool to also work for most, if not all, of 
-the remaining 27 bugs listed in Table \ref{tab:root}.
+We expect \Tool to also work for most of 
+the remaining 27 bugs in Table \ref{tab:root}.
 However, these 27 bugs are too difficult to reproduce, as they 
-depend on special hardware/software environment (e.g., Windows OS and 
+depend on special environment (e.g., Windows OS and 
 .Net libraries) and cannot be easily extracted or reimplemented. 
-For example, some bugs are related to GUI widgets, which are too complicated to 
-re-implement. Some bugs' inefficient 
-loops traverse big graphs, whose bug-triggering inputs
-(i.e., the graphs) are difficult to figure out 
-without reproducing the original bugs.
+For example, some bugs are related to GUI widgets and some 
+require big complicated graphs to trigger.
+%, which are too complicated to 
+%re-implement. Some bugs' inefficient 
+%loops traverse big graphs, whose bug-triggering inputs
+%(i.e., the graphs) are difficult to figure out 
+%without reproducing the original bugs.
 
@@
 tool \cite{SongOOPSLA2014} to process a performance problem and identify 
-one or a few suspicious loops for \Tool to analyze.
+a few suspicious loops for \Tool to analyze.
 For all but four benchmarks, statistical debugging identifies the
-real root-cause loop as the most suspicious loop. For the remaining four
-benchmarks, which all come from Table \ref{tab:root},
+real root-cause loop as the most suspicious loop. For the remaining four,
+which all come from Table \ref{tab:root},
 the real root-cause loops are ranked number 2, 2, 4, and 10.
@@
 %XXX (what can we say about Toddler benchmark set here?)
-
 %\input section/tab_cover
-
 We use 0.001 as the default \textit{resultful rate} threshold for identifying

### 2017-02-13 section/evaltax.tex
shrink to 10 pages

@@
 (2) Chromium Google Chrome browser in C/C++;
-(3) GCC compiler suite in C/C++;
-(4) Mozilla suite, including Firefox web browser and Thunderbird
+(3) GCC compiler in C/C++;
+(4) Mozilla web browser and
 Email client in C/C++ and JavaScript; 
@@
 found 65 performance problems that are perceived and reported by users. 
-Among these 65 problems, 45 problems are related to inefficient loops and 
+Among these 65 problems, 45 are related to inefficient loops and 
 hence are the target of the study 

### 2017-02-13 section/3_redundancy.tex
remove red

@@
 
-{\color{red}
 We calculate the redundancy for an input instruction $I$ based on the
@@
 sequences are completely different.
-}
 The exact formula is the following:

### 2017-02-13 section/5_exper.tex
remove red

@@
 
-{\color{red}
 \noindent\textbf{Research questions to answer}
@@
 What is the run-time overhead of \Tool? (Sec.\ref{sec:result_perf})
-}
 
@@
 \label{sec:coverage}
-{\color{red}
 To answer \textbf{RQ1}, we apply \Tool to real root-cause loops to see if 
@@
 \Tool does provide good diagnosis coverage.
-}
 \Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
@@
 %\input section/tab_top5
-{\color{red}
 To answer \textbf{RQ2}, we apply
@@
 have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}.
-}
-{\color{red}
 Table \ref{tab:benchmarks} shows that \Tool is accurate, having five real
@@
 Consequently, they will not cause extra diagnosis effort for \Tool users.
-}
 
@@
 
-{\color{red}
 To answer \textbf{RQ3}, we evaluate the run-time performance of
 applying \Tool to the real root-cause loop. 
-}
 As shown in Table \ref{tab:performance}, 

### 2017-02-13 section/evaltax.tex
remove red

@@
 (5) MySQL database server in C/C++.
-{\color{red} By manually inspecting a set of randomly sampled bug reports,
+By manually inspecting a set of randomly sampled bug reports,
 previous work identified 
-65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.}  
+65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.
 Among these 65 problems, 45 problems are related to inefficient loops and 

### 2017-02-13 section/0_intro.tex
forgot to check in

@@
 
-Performance bugs\footnote{We also refer performance bugs as performance problems
-following previous works in this area~\cite{PerfBug,Alabama,SongOOPSLA2014}.} 
+Performance bugs 
 are software implementation mistakes that cause unnecessary performance
@@
 complexity of modern software
-~\cite{PerfBug,perf.fse10,rily.perftest,perfantipattern,xiao13:context}. 
+~\cite{PerfBug,perf.fse10,rily.perftest,Alabama,perfantipattern,SongOOPSLA2014,xiao13:context}. 
 They annoy end users and waste energy during production runs, and 
@@
 \centering
-\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
+\lstset{basicstyle=\ttfamily\fontsize{7}{8}\selectfont,
      morekeywords={+},keepspaces=true}
